jane lucy mcguire


Ten days of cleaning; of walking sentry; of guarding the sick. The camp is not only vulnerable to attack but holds a medical encampment of thousands who were left sick from venom after the reds left. They are heavily addicted and suffered horribly. Many have given up hope and died by their own hand so that they need not suffer anymore. A majority are afflicted with some manner of madness often mocking the nurses saying the reds are the masters and will return soon to exact vengeance great will it be to serve at their feet great will it be to die by their hand. There is no cure, they have faint hope of living long before the withdrawl kills them, a month on average or so I've seen.

One night I was on patrol after sunset in the camp. As I wandered by I heard loud angry voices. 

``We can save them dammit, general I just need more venom to complete my research my test subjects have shown improvement'', said the woman.

``Are you telling me you experimented on multiple patients? You know I only authorized you to work on one patient'', said the general.

``How am I supposed to make progress with a cure with a single test subject? When I seen it help one of them how could I bear to keep it from the others? Look at the suffering of these souls, surely we will be held to judgement on what we do here while they live'', said the woman.

The woman waved her hand over the multitude of victims in this tent. Most are restrained, most show self-mutilation like gouging out their own eyes or peeling the skin from their own face and body. A man in the distance is being worked on after the stress caused him to have a heart attack. He looked like he was in his mid 20s.

``You're right Jane, we will be judged. Surely we will also be judged if our pride leads us to harm these people in spite of such suffering. I won't cause it and I won't allow you to cause it. you have the one man and only one man and I won't jeopardize a mission to obtain more venom from old fellowship camps. it is only good to ease some people back. Very few. This work of yours is fruitless. Expect me to pull you from this self-glorifying project soon and put you into another project.''

``No you will not do that, I won't let you. This will work I just need more venom, I can synthesize more if I can isolate it's makeup. I am so close to creating a powerful anti-toxin that reverses the craving and lets the body heal. it works. The recipient isn't showing the signs like the others if I complete my work I will have created a praise Jesus cure for these people. You need to understand this is the only hope for these people. This needs to happen. Get me the goddamned venom'', said Jane.

``Tell you what. If you pack up your belongings and report to Colonel Bennett by Friday I won't demote you to sentry duty. Spit in a beaker you're sure to have quite enough venom that way.'', said the general.

``Fuck you Joe. You're damned right I have venom for you, this is fucking bullshit. You're betraying me, you gave me you're word I could research and test until I fing a cure. What's changed?'', said Jane.

``Venom. You need venom for this work and very little was kept by the fellowship over the years. Even if you only need it until you are able to fabricate the necessary components how do you know we are going to find any more out there at all? This is likely a dead end and without venom it is most assurredly a dead end. The Colonel has a good chance and could use the help. Most importantly the Colonel doesn't need any goddamned venom for his proposed cure. It's realistic.'', said Joe.

At that Joe walked away, and Jane took an old pipe and smashed a nearby table into pieces. Her face still red she walks back to her desk to read a research report but drops it. She violently sweeps everything off her desk and combs her fingers into her hair.

Curious I stealthily enter the tent. she isn't moving. Looking around I see some relevant material on her research. I can't understand medical research myself but Laura might. I'll get her to look at it.

As I'm leaving Jane turns around, ``Who the hell are you?''

Dammit, foiled again, ``