I received a request for audience from the emperor of the jade court. I’ve only ever heard of the jade court once before in my life but never encountered any. I wasn’t alone in considering the possibility that the jade court didn’t really exist. Here with an official document in hand I asked if this was real and the messenger said, ``very much so my queen, it was a respected member of our own people of obtained this request directly from the emperor himself.’’

I said, ``Why haven’t I ever seen anyone from the jade empire having spent so many years in battle against a vampire court?’’

He said, ``As we have understood them they found greater value in wisdom and obtaining power through self perfection. The other courts are thought of by them to be spoiled children in pursuit of worthless goals. I guess they are rather monkish and generally unseen by us in the new world.’’

I said, ``They would be searching for enlightenment? Seems rather unlike a vampire.’’

He said, ``Not quite that, they build themselves up to deify themselves. That way they can obtain power greater than they could obtain any other way.’’

I said, ``Sounds like the late red king.’’

He said, ``Yes, quite. Except that most are quiet and intense, perfectly focused on the building of personal power.’’

I travelled back down to the land of fire and brimstone, lightning and lava. I made my way back to my seat of power to prepare for the arrival. I wonder how much contact there has been between the three known courts and the jade court. There can’t have been much considering I didn’t even know if they were real or not. The only thing I know for sure is that they are the vampires that have roamed the far east, China, Japan, other locations at the far end of the globe. I returned the letter with my approval and started preparations immediately. Through messengers we confirmed a day two weeks hence, which should allow plenty of time to finalize the preparation and made sure they had what was needed for there stay here in my realm.

