Watching Jane I see with my own eyes something that perhaps has never been seen in the history of vampirism. This is my daughter and in her I am proud.

A recurring dream is plaguing me. It feels so real. Reverent whispers are coming from outside the alter; the smell of incense; the sound of chanting. I feel the athame cut my throat then pain;  tongues of lightning pulling me high into the sky; all around me the whole world seems to be aflame. Terrible power flowing into me; a terrible hunger being satiated within me. It's only in flashes, every dream shows me more. Is it memory or fantasy? Maybe time will tell.


The humans are our life and our hope. The vampire cannot hope to live without our food and they are more than just our food. If humans prosper then vampires prosper. We are the shepherds and our place is to lay down our lives for our flock. 

I am quite aware of myself and my own humanity that has passed safely to my new nature. Other vampires are also becoming aware if it is in their nature that their souls once fractured has been made whole. The black court followers and now my own daughter have shown me what has come to pass in the events of chichen itza if only in part. I have died and I have risen in deathlessness. Although not extraordinary for a vampire the circumstances are unequalled. Vampires who were once corrupted and without hope save for very few now have hope. According to their own choice they may follow into damnation or they may rise above. Every single vampire now has that choice of salvation if they wish to follow it. I am not the christ of vampires and I am not the way, the truth and the life. What I am is the queen, the one chosen to tear down the walls and lead all my species to  
