\lettrine[lines=2,lraise=0]{S}o I called father Gomez, It's in an industrial area noone is going through at night anymore, even by car. Nobody seems to be infected by these creatures (lucky bastards) but the unfortunate souls that meet them are torn to shreds. Like need dental records for ID kind of torn up. The police are investigating but the department is small and overwhelmed, the case is just not moving anywhere and the supernatural overtones makes it even worse for priority. It's been going on a year and the community has nowhere to turn. Well we pack up and head out. Jose needs to stay back for a family matter this time so it's me and Carlos to the rescue.

My ass is tenderized. Hell of a ride. We arrive at father Gomez's parish. He is going to keep us with him in the rectory as he is a bit worried someone might lay a hand on us in this fairly rough neighbourhood. I'm worried I might lay my own hand too heavily on some poor thug so I too see the wisdom in being in a safe place. Father asked if we are under hire by rome. I said no but a dear priest said I'm under the unexpected employ of God's grace. He laughs.

``That was father Forthill I assume?''

``Of course.''

``He accepts such strange characters to his company I suspect he sees grace where none other can.''

``I suspect you're right. Myself considered I know he can.''

``You want to know more about the zombie trouble.''

``Read my mind I certainly do.''

So from what was said they seem to be concentrated in particular around a warehouse marked as being owned by ACME inc. Well hell I thought that was only from looney tunes I didn't think it was an actual company. Anyway whether that was the actual owner anymore is yet to be known. He showed me on the map that location and the locations of sightings and bodies. About a dozen all in all. I made light of the shameful fact this is a low priority for police and father made a sorrowful pose.

The next day Susan shapeshifted herself into some average clothes with a KA-BAR in a concealed sheath. If she has to it's much better to poke a hole than blow some poor bastard into chunks with a left hook.

First stop town records. Lets see who owns that warehouse. Now if anyone has ever been to San Jose it is one of the most backward national capitals I know of. No transit system in place and the streets have no names. I haven't spent a lot of time here so other than taking flight to see where I'm going I had to accept A.J. along with me, who was father Gomez's suggestion as a guide. A.J. lived here all his life and works as a taxi driver. We travelled when he was off shift.

So it looks like the warehouse was owned by a company called ACME boot. Checking the microfiche around the time of purchase in the late 1950's to early '60s the company was heavily promoting the first western boot store in central america. It never got any traction, was repurchased by a real estate company for lease or resale but fell to the bank in repossession. Nothing since. So dead end nobody has really owned that building since the 60's. I need to do some on site investigating. If I can find a safe spot a stakeout would be best.

I get A.J. to show me the route to that warehouse and drive me around it a little bit. It's got the crap beat out of it from years of not being used. The warehousing around it is not faring any better. It's the middle of the day so we decide to drive up. I walk around and pass through a 10 foot high barbed wire perimeter fence as mist. There are tire marks coming from the locked gate, looks like trucks. There is an old rusty chain and padlock on the ground cut off with bolt cutters. Somebody replaced the chain. The old padlock didn't seem in too bad shape so it seems to me someone either lost the key or just never had it to start with. I think we are dealing with trespassing unless the bank is doing something here. I seriously doubt it though this place looks like it's ownership documents went through a shredder. Inside looks like a Freddy Krueger film. There is blood everywhere, small body parts deep scratched in the floors and walls. Some really solid looking steel tanks have deep indents in the forms of fists and steel girders have chunks bitten off them like they were taffy. Jesus, what the hell is going on in here? I look up and see an opening in the roof near a platform, maybe once used to oversee plant operations. I see signs where there has been people climbing up to this outpost recently, and often. Someone dropped a pen here, Monsantus Genetic Engineering LLC. MGEL for short I guess. Fascinating. There is some paperwork left behind also, it definately looks like an engineers handiwork I can't make most of it out. What I can pick out are words like specimens, candidates, fit for deployment, unfit, weak. I just get the sense they are up to no good. I leap down the 50 feet and land quiet and graceful as a cat. I hear a crash outside and shapeshift into urban camo bdu, and hit the floor with the KA-BAR in my teeth. Moving silently from stair to tank to drum I get to the nearest exit to where I heard the crash. I peer quickly and nobody. Sticking to the wall like I was part of it I move around the corner to see a cat in a garbage pail. ``reowww'' and it was gone. Handpalm. Good enough then. I shift back to my normal clothes and scabbard the KA-BAR. After misting back through the fence A.J. takes me back to the rectory.

So it's really not much good yet staking out the location the research comes first. If I stake it out too soon they may spook and take off to some location I don't know about. Or it turns out like last time at the cemetary they pick a fight and I pull my own version of Harry Dresden and end up leveling everything. Then come the inquiries on what happened and rumour of God knows what. Besides I promised father Forthill I would stay safe so no lets follow the leads I've found so far. We have a company name, and some engineering documents. Let's start with the company first.

We relax with some supper, Carlos helped father Gomez today with the caretaking of the parish. I let father know what I've found so far and it didn't mean too much to him but he thanked me for my work. That evening I borrowed fathers computer and booted tails. Let's see who this MGEL company is.

I found it. A biological engineering company working in the medical research field. Again fascinating. Was the mess in the warehouse something about medical waste or, sweet mercy, failed human experiments? It's got to be something that needed to take place in some remote warehouse so they are definately trying to hide something. As if I didn't already know that. I also see that they have a research location downtown so that looks like a good place to hang out.

I tell Maggie stories about the big bad zombies and how I beat them all up and sent them home without dinner.

Just as I intended I go to the location and find the entrance has a guard and is using a biometric entry system. The employees are the usual nerds with pocket protectors. I have a camera in some clothes on the table to snap shots then bluetoothing them to the tablet. Usimg my superhukan ears I'm picking up names and information of employees as they enter and talk with the guard. I keep it up for a week and get quite a bit of intel, names, weekend activities, relationships, shift patterns, work area. Thank God for the outgoing and chatty guard he almost did the work for me.

Carlos headed home  later in the week to care for his daily activities and I continued on in the rectory. This one is gonna make me work. I organised the pictures and practised shapeshifting them. I also studied the available data of the employees. Now how to get in. I need to bring a laptop to gather network info but this first venture I think it best to map out the floorplan and other details. Yet again how to get in.

I have a good profile of the guard. The night guard is likely best. The one named Peter is scheduled off Monday and Thursday the poor bastard. I say I wait around until the guard goes for a piss then sneak behind someone as the guard saying I need to grab keys or something. Who is going to suspect the guard of a security breach. I can shapeshift to Peter then and I guess it's just fast talking from there.

The day came and I was nervous as all hell. The moment came and I lucked out, Margo arrived while I posed as guard.

``Evening Margo how's Sparky is he feeling better?'', sparky is her pomeranian.

``Much better yes, he must have been eating something he shouldn't have thanks for asking''

``Oh shit I left my keyring inside.'' I slip behind her.

``Jesus Larry, Jacob will have your ass for that.''

``Who's gonna take it Marg, like really?''

``Jacob, so he can shove them up your ass''

``point taken.''

I enter and quickly assess the area I entered. A long hallway ahead and a small alcove immediately to the right for a security desk. I dive for the alcove and switch to Peter under the desk. I see a camera at the door and I'm hoping the exact coming and going of employees isn't tracked with it because security will be confused as hell.

So now I'm Peter. Time to wander.

Familiar faces in the labs. I've seen them enter and exit many times before at the front entrance. six labs on the left and a cafeteria to the right. Otherwise just one big long hall. Making note of who is in the labs for my next incursion. An elevator at the end of the hall. The second floor is empty, 9 to 5 people work here presumably. Assigned cubicles, I make note of the names the best I can. Nothing extraordinary here except computer access in privacy in the evening so bonus. I check out a workstation. Bios is locked and wont boot from cd. I expected that but it's still annoying. I'll need the laptop to clone the mac of the nic and hook up directly for a network mapping and recon of the network. That said I wonder where the IT offices are anyway?

Up to the third floor. Executive suites. Offices and conference rooms, secretarial pools where there are a couple people still working. At last the IT room. If I can get access to this area I'm in the game. Hmm, let's see. I try transitioning to the vampiric mist since there is nobody around and I get through the door no issue. Oh my God, morons. System passwords written down on all the equipment. Multiple Vpn tunnels for different department, connection information on a corkboard. A complete network map also. Good enough for now, I write it all down and take pictures then smoke my way out the door. Still nobody around. As i head toward the elevator the door opens, and I dive behind a wall. Oops. They would see my mist form, too far away to do a spidey thing and hang from the ceiling. I don't know enough about Peter to know if he is supposed to be on this floor. The guard! Why wouldn't a guard wander a facility if they think something isn't right.

``Hi Larry what are you up here for?''

``Somebody said they seen someone up here but I don't remember letting anyone in with access to this floor.''

``Shit. Maybe I'll grab that paperwork another night.''

``Could have been someone slipped in while I made water''

``Yeah could be, Or it could be Samantha she is always forgetting something. Most of these guys come in at the corporate entrance opposite Mindy's cafe''

``Yeah but not at 11 oclock at night.''

``Agreed. Well good Larry stay safe.''

``Much as I can take care.''

I wait a few minutes and head for the elevator, switch back to Peter in the elevator and back out past Larry to the outside of the complex then to the public john. I shapeshift back to myself and head off an emergency while I'm there. It's been a while since I've done an infiltration I need to get my sealegs back. That went without a hitch though. I don't think I need another infiltration, I may be able to make an attack from outside to gather evidence. Then also onsite photographic evidence at the warehouse I want to see the horrors that are unleashed out there.

Then back to the rectory for some meditation, back up in the morning.

Hmm, how to do this. I don't have to be onsite but I need to check the different components of their network to make sure I don't get detected. I have all my notes and references from back during the black hat work. I think top priority as always is to avoid detection. Best course of action is likely to create a GRE tunnel from the internet gateway server and I can redirect traffic through a box I control. Kind of a man in the middle. I probably wont get all of the internal traffic but if I get traffic to and from their headquarters that is likely going to be the most likely slam dunk anyway. I'll need to figure out where to find a location that has enough bandwidth to handle their traffic in and out reasonably, if I can find out how big a pipe ie. how fast their connection is, I can judge what I need on this end to make thing more transparent. Thinking about it I may be able to configure one or more of their internal routers to push all traffic to the internet gateway, then I could actually capture the internal communications. Hell if their routers are sophisticated enough I might be able to redirect only the E-Mail from the internal routers to the internet gateway to save on traffic. That might make my head explode though I need to check through these books to see if I have enough step by steps to do what I want to do already.

I studied most of the day to see what I can accomplish. The GRE tunnel is doable. Might be able to do more like redirect only E-Mail traffic through the tunnel then there would likely be nearly negligible traffic which would make things easier from this end, I won't need much bandwidth for the redirection. Configuring internal routers? I haven't a frickin clue and no documentation on it so skip that.

Good then, I don't want to put father in a pickle so I'll do my snooping of the network at the little library on the next block assuming it has internet of some kind. My laptop is installed with Kali linux so I am about ready to go. I'll just put the laptop on the huge stack of books in the old rucksack and over I go. Nice thing is having a stack of books beside you in a library makes more sense than a hotel, coffee bar, or wherever else one may go.

My brain got a little fried so I sat down for coffee with father Gomez.

``So where did you meet father Forthill?''

``At seminary actually. We haven't kept in touch like I would like but we do try to help each other out''

``Sounds like me, Marcos and Jose.''

``Perhaps so. I never heard about your background, what brought you to central america?''

``The war with the red court vampires. I assume you've heard about it.''

``Yes, it was a little more low key here in the city but I heard it was horrible in the rural areas.''

``I suppose there was a lot of denial up here.''

``between the victims who were controlled and the actual fervent disbelievers nobody could openly say the war existed.''

``They were called lunatics I imagine.''

``You bet. Say what group were you with in the war?''

``The fellowship of Saint Giles. I wish I ...''
father Gomez quickly grabs a sharp knife from the table and slices Susan's arm open. A slime discharge erupts and the would closes almost instantly.
He leaps backwards knocking over his chair and stands back to the wall with the knife shaking like a leaf.

``The fellowship is dead! The reds are dead! They cannot be returning please Lord Jesus protect us!''

``Whoa, easy father. I'm sorry you had to see that. I'm not a vampire, I'm a human soul in possession of a vampire body. Please relax and ask your questions I have no plan to move from this chair. I have been and always will be with the fellowship, it's in my heart.''

``What? How? How are you still alive?''

``First of all did father Forthill say anything about a sacrifice? About how the reds met their end?''

``Yes, the youngest full red vampire and some magical bloodline curse. I didn't really understand''

``Well it is a magical ritual, it was designed to destroy a bloodline. Thing is though the reds made a rite of ascension. Noone new but the king and one other as far as I know.''

``destroy a bloodline?''

``kill everyone that shares a bloodline with the victim. In that case sacrifice the red and only the reds die.''

``Jesus mercy, what a terrible black magic is that, most everyone shares ancestors from somewhere.''

``Well I'm pretty sure it only kills up a bloodline not back down again. I'm no wizard though it just makes sense to me.''

``OK I got that much''

``So it was a rite of ascension, which means others are killed in order to ascend one person to godhood.''

``You mean a really powerful person, there is only one God''

``The one who was sacrificed was the one who was resurrected as a God, problem is they did not have the human soul consumed yet so they are vampire with a human spirit.''

``What a sorrowful state. How many are left that have ascended like that, is there a danger? You haven't explained yourself yet were there some fellowship members that escaped the 
cataclysm?''

``Just the sacrifice lives as far as I know. You will have to help me find another description of myself by the way. Calling myself a God makes me so self-conscious.''

``By Christ be mercy, oh Susan, Oh dear Susan. A full red?''

``Yes, but only physically. Everything. Except my soul. I still command my soul.

``What a sorrowful state though. My heart bleeds for you. The most blasphemous thing is the feeding, that is what makes you inhuman and I cannot accept you in that. You are still inhuman and by that I stand''

``Actually I don't feed. I'm given donations and I receive what is given and never take. My power is growing also and there is coming a time very soon when I will not need to feed any more. The reds honored those who were able to feed the least often as they were the most powerful. As a God it is only fitting I should not feed at all.''

``powerful enough to wander in the sun, survive easily in a parish or rectory, cross a threshold to no effect. Maybe more. Okay.''

``As it is I am more like spiderman, the superhero of journalists righting terrible wrongs by the pen, which has always been greater than the sword.''

``Which you are going to do here, like spiderman using superpowers to find the truth and report it for the world to see, and force change.''

``Same as all good journalists try to do.''

``OK I get it. does father Forthill know?''

``He knows all these things, well except for the magical stuff and sacrifice and being a God thing, and whatnot.''

``So he doesn't know a hell, pardon my french, of a lot?''

``He knows things like being a dedicated member of the parish, mass every Sunday, funding the rebuilding of the town basilica.''

``Well shoot, that's enough for me. I will not turn away one filled with God's grace. I'm assuming I can call your parish priest and you haven't put him under some mind control.''

``Gotta have some mercy father, I haven't put you under a spell or sucked you dry. I'm a real good hearted vampire if there ever was one.''

``God help us all.''

``Amen father.''

Phew, disaster averted. Oh opportunity, maybe he could be my confessor. I mean I'm not really catholic but I'm getting a lot of support from the church it could build a lot of trust with people if I can get good references from priests. Vampires need all the help they can get. In many more ways than one.
`` Father would you be my confessor? It's hard to go to father Antonio being part of my everyday life and all it would mean a lot.''
father makes the sign of the cross three times, ``Yes child, I will do that.''

The confession was hard. It was somewhat difficult for father but poor Susan fell to pieces. She had been trying to reconcile what she had done especially what she had done to Martin. That was by far the most vicious and horrible feeding she had done. She talked about her sense of loss for Harry and being torn away from her greatest love, being forced apart from her daughter that she loved so much. All of it. Father Gomez ended up holding her for a very long time. They agreed to meet every two weeks when possible to work through the guild and shame of what seems like only yesterday to her.

``You have been carrying such a burden Susan. You are an extremely strong woman to have bore so much for so long. On lighter note I've never been confessor for a vampire before so thank you for the opportunity.''

``Your welcome father.''

Father also told Susan if she is ready she should check with the diocese of Yucat\'{a} n. It would be good for her to find his resting place to help her find closure by visiting him.

Susan took the rest of the day and took her meditation overnight. 

OK continuing on. It was good to have the time with Father Gomez but now is the time to get to work and gather the goods on this company.

Now the first thing is to find a way in. The access is likely blocked from the outside via IP. I can't defeat that but looking at the map there is a VPN server on the same subnet as the main server farm. That is likely used for outside administration. That is likely the best entry point to gain access to the network. I can then setup the tunnel on the internet facing router and gather the data. That should complete the better part of my work I just need to run scripts on the packet data.

So time to head out to the library. I've been studying maps of the city so I'm getting more of a sense of where things are now so I'm starting to travel some on my own. It's damn near midnight and I'm stuck for any more research so I figured I would take a walk around, see where things are so I don't waste the time later trying to find things. I heard someone behind. I lean up on the wall james dean style, they are pretty far away and noone else is around so I just waited until they came by.

``Hey girl you working?''

``Yeah why?''

``shit, man I'm so sorry sweetheart I'm not cutting in on your business just meeting a client who wanted to meetup at a motel near.''
I wondered what the hell she was talking about before I realized I'm wearing my black leather pants and a high tied shirt, chillin' out on a streetcorner. Heh, oops.

``Please don't tell your daddy I don't mean no harm, just passing through. Hey if it's a deal I'll sell you some protection. Girl can't do without it, deal girl?''
What the hell she selling me a box of condoms? I really don't have a lot of use for that now I'm dealing with shit. Don't even know if the equipment still functions in this body for Christ sake.
Then she pulls out some serious protection. Goddamned Glock 19 with concealed holster. Damn girl I like your style.

``Got me something smaller this is hard to carry discretely. Sorry don't have something better girl but yours for \$150 if it's a deal.''

``]Oh fricking yeah sweetheart you got a deal. This will keep the bastards in line.''

``Yeah girl, pull a piece and they run like children every time. Be cool girl.''

She's absolutely right. In the right circumstances pulling out a glock stops a fight before it happens. That's my deal with this, deterrence. I got good experience with all manner of weapons through the fellowship I'll get some common items tomorrow so I can strip apart the piece and conceal it for when I'm travelling. I've been looking for this. Next I get my beloved AK-47 back. Sweet Kalashnikov. The war is over though, I don't see the point in obtaining much ordinance.

I slip into an alley, loosen off my shirt a little, and strap on my peacemaker. I check out the neighbourhood some more then head back to the rectory. Then meditate until the morning light.
