\lettrine[lines=2,lraise=0]{S}usan's heart stopped. Just completely stopped. Her newly chosen pseudonym is getting proposals from the New York Times, The Guardian, Globe and Mail, Washington Post and the Chicago Tribune. Yay for Justine Carpenter!

The Arcane couldn't refuse to publish my pseudonym and contact. I insisted and obtained a contract signed and sealed to that end. God help me I had to use me real name on the contract which I \textit {know} \space is going to come back and bite me in the ass yet needed to be done. Glad I did the legwork on that. The verifiable media probably sank a three pointer with the feds as well. Holy shit Susan this is the big league! Unfricking believable which bloody major award winning news organization do you want to work for next?

I spent the next few days staring at walls with spontaneous giggles from time to time. Carlos asked me why with such gifts do I not use them more to be a genuine real world super hero. I said to him, ``I am and always will be a journalist Carlos. Private investigators are responsible to their clients alone. Police are responsible to serve and protect the people of their jurisdiction. Journalists though Carlos are responsible to all humanity. We may bend the law but we always maintain our integrity. We don't seek out to conquer villains with violence. We go forth with cameras and journals. We go forth with tools and skills to uncover the truth and reveal it to the world. We force proportionate legal action. We force changes of national and corporate policies. We bring down corruption in corporations, and destroy organized crime syndicates. We see to the collapse of dictatorships. We are changing the world one story at a time righting the wrongs of those who are untouchable and making the world a better place for generations to come. We are heros of the greatest degree, and that's why I am a journalist Carlos.''

``I may join, let me rephrase, I will join one of these major news organizations but I will continue to report on the supernatural too. People everywhere ignore or disbelieve what they cannot explain and it is one day going to harm or destroy us. My former lover Harry I fear will always be fighting on the edge of destruction attempting not only to serve his clients but also forestalling a very real Armageddon, the end of the world. Poor bastard. Look at me too, I was lucky that I am still me despite being in the body of a vampire. We faced true destruction by the red court and it was only by the rite of ascension the scourge of the red court ended. This work in supernatural journalism is certainly uncelebrated but is competing as the most important field of journalism humanity has ever known. I'm going to fight to help the arcane get positive publicity even if my stories for them are only something I fight to do on the side.''

I have to admit I favoured the Chicago Tribune the most but if I'm going to put more than one iron in the fire I don't want to put them all in Chicago. There is a greater chance I would be found out if I do. As far as security goes the Globe and Mail and The Guardian are the best having a securedrop. The other papers may have one it's just that I know those two do. Problem is between Canada and the UK, I would rather be working with a paper in the good ol' US of A. I ended up choosing the New York Times but among the worst for secure systems I put my foot down so hard I cracked concrete on insisting on dealing only with someone using GPG. I like being safe thank you very much. As it turns out the editor chose to adopt GPG for his E-Mail address just for my sake. I'll be submitting stories using the same throwaway Justine Carpenter E-Mail account and I can tor to it so I can maintain good anonymity that way. So good start. They want me on a VPN to work and submit articles but I'm raising thunder about anonymity so they are going to look at putting in Portal so I can VPN through tor. I would be happy with that.

They also want me to fly up to New York City for a meet and greet as well as basic orientation. I agreed to that. Well shit who wouldn't agree to that, I get to see New York City  and tour the Times as a foreign correspondent. Wow, I can't believe this.

Then i hear Carlos screaming like a little girl. Light itself, even thought hadn't the speed as I did getting to where the sound came from. There is Carlos in a corner in the foetal position and very nicely mummified black court vampire standing unconcerned at my threshold. ``you may enter'' I state.

The creature enters and prostrates ``my queen'', and I bid him rise. 

Carlos said ``what the fuck.''

``You missed a lot while you were gone Carlos''

``no shit. You trucking with the vampires now Susan?''

``No they hit me like a mac truck though. I cant avoid this Carlos they cant take me any way but as their queen. I'll need to work from the inside to make things right, as much as I can do. Please I hope you can understand.''

``Susan i can't be your companion anymore. Not until i can understand this. Jose can decide for himself I suppose I just cant manage this''

``Carlos please don't''

``I'm not angry Susan, i just don't understand. Leave me alone and give me time.''

Jose came out from another room, ``I do understand Susan. I knew the day would come when you would join them you are one of them. You have fought alongside us as an infected with such courage I mourn your loss and i wish you didn't have to change but that's the way it is. Me and Carlos will always keep your confidence and your belongings will always be here until you retrieve them. You must leave Susan.''

I leapt for him and he hadn't the time to scream. Just a little squeak. He received the biggest hug he probably ever had. Must have been ten minutes. I'm pretty sure he was aware of the honesty of the embrace because he said, ``please write me. I'll try and talk to Carlos.''

Well after all that I asked our visitor his business.

``My business is the fulfilment of your will my queen. I am your assigned servant and will see your will done.''

``Well 3 things, protect this village always and here none shall feed. Next remain in the crypt where it is dark and care for the tombs. Hide from mortals, if you must feed another is to relieve you so you may do so. Again, not to feed in the village. Last will be to await orders in the crypt. I will come to you, not you to me.''

He prostrates again, ``by your will my queen''. Then he was gone.\\

Fuck!\\

Fuck!\\

I lost my boys. I should have said something before now I've lost my boys.  I'll suffer their loss dearly. I've lost the need for feeding in that sense i don't really need them but the most important part of me is human and i need companionship. Not prey, or servants, just someone. Everybody needs someone.

I go to the crypt and call my stinky servant. ''Yes my queen?''

``Is there a place I can live in New York City, with these vast belongings?''

``We have a loyal mortal servant in the Red Hook. He is in corporate real estate and owns a large manufacturing facility where a large clan lives. Do you wish me to notify of your coming and the transport of your belongings?''

``Do that. How soon can I leave?''

``If you don't mind staying in our servants quarters you may leave post haste my queen.''

``Then tonight I fly there in true form. Show me where I am to go and I'll be there.''

``I shall, but even by the speed of a turboprop it would take you 16 hours my queen, shall I arrange stops that you may escape the sun?''

``hmm. No. The sun has no power over me. It's morning. I'll leave now hugging the terrain and arrive by night I expect. I will take information on shelter in the case I need it though.''

``Yes my queen.''

I had to get out of of Costa Rica before I fell apart. Push it back I can fall apart when I get there. No time now. I climb the tower one last time and soar away, skimming the trees and confusing cattle.

The trip wasn't eventful. Most of the journey through the US was by night and I memorized that new york skyline in vivid detail for use later. The place was pretty rough looking but pretty large. The perfect place to complete my evil plans of world domination, muahahaha. I can joke now, I'm not as afraid anymore. I think my dominion will be one of the heart, and change of the spirit rather than real world conquest. When I get the chance I'll disappear into obscurity though so I can push into my journalism career which is the most important thing to me.

I'm not tired even after a trip like that. I guess my cruising speed is about the equivalent of that turboprop the stinky one was talking about. It's good to know these things. I slip into a 24hour Mickey Dee's and work on a couple pots of coffee one cup at a time. I can't explain it but it feels right to be back in the US of A again. Feels like home. I feel like me, as if nothing had ever happened. Like it was all a dream and I'm still in Chicago working for the arcane. I'm excited about the move to the Times though it's really huge. I'm scared to death but I'm excited to be working beside some of the best in the business and learning from them.
In maybe 30 minutes the NYPD comes into the restaurant and asks around to see if anyone seen anything out of the ordinary at all. No one seen anything thank God, not that the police report is going to read anything like angel come down from heaven.

I go on into the complex and go trueform to avoid any misunderstandings. I was met by patrol and led into guest quarters for the remainder of the night. The mortal is respected here and save I should demand it the vampires will not disturb his rest.

When morning came I went for a daylight walk in the yard to get a look around. It is going to take a while to get my directions around this place it is so huge. I'm sure I have the time though. Hopefully all the time in the world while my career takes off. It is New York City after all and I do work for a very coveted company.

Me and Maggie play then in her dreams. She has developed enough dream control now to sprout her angel wings! We fly up in the sky over the New York skyline and play together there in the wee hours of the night. She said to me, ``It is very beautiful mommy.''

Morning comes and the vampires are sleeping in their lairs. Feels weird that my heart considers them my children. So very creepy. Anyway as the vampires sleep I knock on the door to the humans chambers. I heard his name is Phil.

``Who is it?''

``Susan, the guest from Costa Rica.''

``You mean the great mother? The great mother's name is Susan. How quaint.''

``Yes well I would like entry please so that I may settle in.''

``Good timing, I'm off to work soon. Come in and I'll take you on a quick tour. Then after I'm gone if you wish you can settle in.''

The place is absolutely huge! He has reserved the top four stories of a multistory industrial building for his own home. Think about having a four story apartment building all for your own to live in. It's like that. Much of it is completely open also because it was for industrial purposes so wow.

So bright in most areas. Much of it is still open space. We decided that I will take the top floor he will take the one immediately below and the 2 floors below will be shared for a library, ritual area, alchemy lab and so on. I was so happy he is a wizard of some sort! Not likely a powerful wizard I don't think he said he isn't a part of the white council but it still seems cool he could be a resource for me in researching things of a magical nature. One of the reasons I picked the top floor is of course so I can fly when I want to. Hard to do around here with such a dense population but the option is there. I'm glad I took the time I did to practise hard at flying where it was safe for me to do so. I miss my boys thinking of Costa Rica.
 
So I decided to leave most of the area open and put in place a separate kitchen and dining room, master and guest bedroom with bath included. I also build a personal office and library in it's own enclosed space. The open space I chose to manage with various types of moveable room separators. Out in that large space I'm placing a ritual area with a smaller library nearby. an entertainment area and a playroom for Maggie as if she would ever see it. I will see fit that she will dream it as I can meditate on the toys to project them in meditation. Then me and Maggie can play with them. It's all I got right now. I haven't seen here face to face in so long.

More and more I seem to be drifting towards a grandmother like taste in things. The bedroom of mine now has floral print wallpaper, doilies and such. I continue to change but I would like to get out and have fun again as I'm really still a young woman after all with entirely too much burden on my shoulders in my opinion.

I told the kids (the stinky vampires) they are going to have to clean up their space so that I might visit and tour their part of the complex. They know the things that are important from my speech. Something I wasn't aware of though is that the vampires that attended my speech in the cemetery were actually the most influential elders from around the world not local vampires! Wow. I must have made waves in the vampire world somehow. This means fewer humans are going to be killed needlessly now and that makes my feel pretty good.

I also put a barbeque and gazebo on the roof. There's a tennis court (yes the roof is huge), astroturf and fountains. I need to give my humanity as much as I can otherwise the vampire body is very powerful and I could lose myself very easily in it.
A large number of my stinky children came and finished the work in only 2 weeks. Phil's floor was also done according to his own tastes. I haven't seen it but I've heard he set his area up without the open area I do so all the rooms are permanent. I'm looking forward to seeing it later. I told him we can share the roof as well people need to get out and enjoy the sun when we can.
I start my new job in less than a month and I just don't know if I am ready. I distracted myself in reading while I laid out in the sun on a beach towel. I don't need to use suntan lotion any more but I do anyway. It just seems wrong not to. Like personal hygiene I feel I need it and I'll be damned if I'm going to take the lazy way out. That would just be too disgusting.

I fired up the BBQ and cooked up some nice thick juicy steak. Oh thank God my tastebuds haven't changed that is so heavenly! Had some hotdogs and potato salad to boot. I had some seed sprouts as a salad too in order to have that extra nourishment to satiate the bloodlust, even though I don't feed I'm still part vampire. I also work out even though my strength and fitness doesn't change. It pleases my human soul to do so and so I do.

Around 6:30PM Phil gets back. After his evening routine he meets me in my library so we could get to know each other better as neighbours.

``Good evening empress, may I enter?''

``Call me Susan, we're neighbours, and yes come on in.''

``Was your day eventful?''

``Did nothing useful but it was a happy day nonetheless. How about you?''

``I work in realty. I had a good day but nothing is ever truly eventful. So I hear you are the most powerful vampire that ever was and a God in your own right?''

``Well I'm not sure about that. I have some juice yes but I don't feel like God material. I am definately full vampire but I have a human soul really.''

``That is kind of you to say. The vampires are unlikely to speak of the kindness of a leader save they should doom them to the actions of their enemies. I overheard you saying you are a journalist? It doesn't seem to mesh with a powerful vampire.''

``Like I said I have a human soul, that means I have a career, love BBQs especially steak. Look forward to a yankees game and hotdogs. I enjoy sunbathing reading and ancient magick. Some of this is different from when I was a full human but it all amounts to a very human lifestyle. I need to find that balance between my vampire existence and my human spirit and I very rarely am able to truly do so.''

``It sounds like you're serious, that you have a human soul. You realize that isn't possible don't you Susan.''

``I believe it only happened once. When the red court fell I was the sacrifice. The ritual was one of ascension but noone really knew it except the ones who developed it. They were suicidal and sacrificed the whole court and maybe more to raise up a vampire God to conquer all of existance. They made a mistake. My body and mind were transforming but my spirit was not yet touched and the human soul and vampire body was merged. So here I am adjusting to my new life and growing as I go.''

``Jesus Susan, that has got to be confusing.''

``I have to give my humanity the greater attention and you can see why.''

``So I am really in no danger then? Being that you have a human soul? How do you feed?''

``Same way you do. Because of the power I've gained and my red court heritage I have no need to feed anymore. The greater in the red court fed very little and I guess it just makes sense that I have no need to feed. Human food is sufficient.''

``Incredible, do you have innate magical power as well?''

``I knew a white counsel wizard once, I don't think I can do what he does. I think as time goes on I'll find I have more innate abilities than there are stars in the sky though.''

``What of the ritual space and arcane books?''

``All of it is for ancient magick, which is quite different the the life force based magic used today.''

``It was abandoned long long ago. It hasn't the power associated with modern magic so nobody cared anymore. I don't bother with it. Do you use it for health or something? Like some kind of transcendental meditation?''

``Well it is good for that but it is also the only thing that really works against ancient creatures like the ethereal revenant I encountered in Costa Rica. It is also the only arcane study I can undertake that still allows me to not worry about effecting electronics and electrical circuits.''

``True enough. I've never heard of an ethereal revenant before though. I don't know what to say about that entity.''

``So you are some sort of wizard also?''

``Not exactly. My magical journey started in world war one. My parents were part of a very strict protestant faith and it was hard on me. I wanted to blaze my own trail and was very rebellious. I didn't want faith I wanted magic where I could have control over my own destiny. Someone named Kemmler crossed my path and said to me I have great magical potential and that I could be a powerful apprentice to the true magic. I wanted to practice that true magic of which he spoke of even though I didn't know anything about it. All I knew is that it was supposedly the true way and that's what I wanted to follow was the true way to magic to fulfil my desires in the world.''

``Seems reasonable.''

``I found this true magic to be difficult to swallow. It just seemed so evil. I believed in it though and believed that once past the rituals and learning I undertook I would get past my moral difficulties and find the true way to achieve my destiny.''

``Did you find that true way?''

``I had to learn all the horror and eventually I turned it in on itself so in that sense yes. I have control over life and death. I'm likely more powerful than most if not all of those on the white counsel. The council wants to execute me for my knowledge and previous crimes but as long as I am a servant of the black court with impeccable integrity the council dare not touch me or suffer war with the black court. So far the black court had fought with the reds as a matter of allegiance. If the council had to fight another war it would fall quickly. I doubt in the condition the council is in now that it would risk yet another vampire war.''

``They want you dead? why?''

``I am an extremely powerful necromancer and neuromancer among other things. a black magician. That's what Kemmler was, the greatest of all black magicians. Now I guess that's me. The council killed him so it would stand to reason it would do the same to me if it had the chance.''

``That's awful.''

``It is. Even though power over life and death means I can raise the dead and do good it just doesn't matter to them. I'm still conflicted over the nature of my magical specialty there is so much evil. I have to distance myself from the horrors of the past save I should think myself to be evil as well. Kemmler taught us all how not to be overtaken by the dark energies which would drive us to madness but sadly of him and the other followers it seems I'm the only one to abide those teachings. Even he did not abide his own wisdom.''

``Seriously? You can raise the dead?''

``Yeah. In addition the powers I have would come from the same death current that your vampire body would use for it's own innate powers. So I think we can likely be good study buddies together.''

``I believe you're right. Would you be agreeable to being my new companion.''

``What's that?''

``In Costa Rica I had two fellows that were with me constantly to care for my unusual needs. They were human companionship and caretakers for me to make sure I kept sailing a straight path. They were counsel for me and they kept in confidence everything we shared.''

``I can try, no harm in that.''

``Well excellent then. Lets peruse the library a while and you can teach me things. I don't wish to practise these things mind you to allow me to use computers but I do want to learn. Also is there a dance club nearby? It would be nice to get out to a club after all this time I've missed that. I'm still a youngish woman after all.''

``Sure no problem. We need to wrap up the night early though I have work again tomorrow morning.''

``Understood.''

I did my meditation in the play room tonight, visualized the toys in Maggies dreamworld and we had a very good time.

Well it's a week away from when I start work. I was taking a jog near the complex when I was thrown against the fence with visions. 

``Mommy daddy help! Mommy daddy!'' I am seeing through Maggies eyes ``Sam I'm scared.'' the girl with her seems to be a teen. probably a babysitter. 

Sam is rifling through her purse and there is a young man with a pistol saying, ``Come on come on give me what you got before I pop a cap on you!'' She turns to run and the young man raises his pistol. 

I kinda snap, instinct takes over. When instinct takes over with me I learn more about myself because my vampire mind just does things without the conscious intervention of my human spirit. That is the same as what happened here, I tore open a portal to the nevernever with a clawed hand and lept through the icy black energy. I appeared right behind the young man and threw him 30 feet into an alley as I flew right behind him. I fed him dry then tossed the husk of a body into a dumpster behind one of the apartment buildings. I never spilled a single drop. The whole thing happened in a few seconds. if the feeding alone was more than five to ten seconds I would be shocked.

``Mommie what happened to the bad man?'' 
I had to think fast, ``Mommie made him take a nap.'' 

``Oh, ok mommie.'' 

So now that I am consciously aware of how to travel through the nevernever I said to Maggie ``We're going to go to church so be very quiet so bad guys don't find us.'' 

``Ok mommie.'' 

A rift then opened in front of us and we walked through it like a door. We crawled out the other side on our knees under a pew.

``Maggie do you see anybody?'' 

``No mommie.'' 

``Perfect thanks baby. Lets run for the back door, then we'll open it and see if there's anyone there.'' Fact is I'm in real hot water, Maggie needs to get back to the Carpenter's but I absolutely can't be seen. We get to the door. ``I'm going to open the door Maggie you look out to see if anyone's there.'' 

``Nobody mommie.'' 

``Ok quickly off to the rectory!'' We waste no time getting to the rectory door but it's locked. After lifting the doormat there was the key and we were in. I locked the door behind us and the two of us looked around but the rectory was completely empty. I remembered father Forthill's number so I called.

``Hello father it's Susan.''

``Well Susan how are you doing?''

``Shitty but more to the point Maggie and some young girl named Sam were attacked by a mugger. Sam ran away, the bad guys are gone and I'm in your rectory hoping nobody sees me.''

``I know Sam she does babysit Maggie, she is Molly's friend. Ok, sit tight nobody is scheduled at the church today so you're safe. make some tea and try to calm down there are some toys in the guest room near the woodstove you can play together. I'll get ahold of Sam and make sure everything is calm. I'm doing visitation at St. Joseph's hospital today I'll be back this evening.''

So me and Maggie were able to spend some real life time together. Father Forthill did call back and caught me up on the fact the carpenters were travelling this weekend but Maggie had a dentist appointment today so Sam was supposed to watch her and get her to and from the appointment. They were on there way back when they were attacked. father said Maggie is safe and he's going to watch her while Sam goes back to her parents to settle down after the incident.

Me and Maggie played together for the first time in a couple years I would say. We had a tea party, read some books and Maggie played teacher for a while to me and some stuffed teddies. She put on a puppet show and we coloured together. We played dressup and searched for silly doras on father Forthill's computer. Oh did the silly pictures ever make her laugh. We played dressup together and made stories using picture cards. We went to play catch in the back. I thought her doggy mouse was going to tear me apart limb from limb but Maggie stood in front of me and said ``mouse stop! This is my mommy.'' Mouse stopped, tilted his head at me and I offered my hand. He sniffed it backed up and growled. Again Maggie intervened, ``Mouse!'' He whined and sniffed my hand again. It got to where he made peace with me and we were rolling and laughing together all three of us. I gave mouse some belly rubs and scratches behind the ear and we got along great. We cooked hamburgers and hotdogs. We were all watching disney movies together when father got home. 

``I see you and mouse are getting along, I was quite worried about that when I was out. Sam was babysitting at her house and her parents don't allow dogs so mouse stayed here.'' 

``Well he didn't like me much at first father but we are getting along ok now.'' 

Just then the big old wooly mammoth of a dog jumped into my lap and I let out an ``oof.'' Maggie laughed. 

I said to Maggie, ``ok little one time for bath.'' 

``No way I want to stay and watch tv! I like snuggling up with mommie watching tv!'' 

``You have no idea what it means for me to hear that baby. We need to go upstairs for a bath though. Maybe father will let us all share some hot cocoa before you go sleepy? 

``Definately Susan.'' 

``Well ok.'' Maggie said. So then came bath, pajamas and hot cocoa. Off to bed then.

``Mommy are you coming back soon?''

``I hope so baby. Mommies just hiding right now from big bad guys so I don't want anyone to know I'm walking around.''

``Wouldn't daddy want to know you're here though.''

``Not yet baby. He wouldn't believe us, nobody would. The most that would happen is people you know and love would get scared and people would get hurt. You have a good family now baby with brothers and sisters and daddy lives close. I promise to try and play with you every night while you dream.''

``That makes me so happy mommie I love playing with you. Why do we only have wings in my dreams mommie?''

``You never know what life might bring you baby, some day you might have wings like an angel. As for me, well''
I bring forth a black fog and tear back my flesh mask. I come forth with the battle dress of a centurion, and flex ten feet of wings in front of Maggie then kneel down at her bed.

``Mommie! You really are an angel! My mommies an angel! My mommies an angel!''

``Noone would believe you if you told them baby, our time together needs to stay between us. You can talk to father though he protects me and I always watch over you while you are awake and while you sleep.''

``Are you a great soldier like saint michael? Fighting monsters?''

``I am a queen sweetheart and I lead a great kingdom. I have many soldiers under my command and I am their mommy leading them, teaching them, and punishing them when they do bad things.''

``So I have lots and lots of brothers and sisters, and if you're a queen that means I must be a princess!''

``Yes baby it would.''

``Oh that's so awesome! I'm a princess to! Can I get to see my brothers and sisters?''

``No baby not until you're older. Your brothers and sisters are incredible soldiers and look like monsters. You would be so scared you would never sleep until you went to high school.''

``Oh that's bad. ok then maybe when I'm older. Can they enter dreams like you?''

``They certainly can and even more than that. I will not allow them into yours though so don't be afraid.''

``I won't mommy I believe you. You came from nowhere and saved me today so I know I'll always be safe.''

``Always baby. Always.''

``Goodnight mommy.''

``Goodnight little one.''\\

Susan turned off the light and headed downstairs.\\

``Sweet mercy Susan what happened to you?''

``I changed to true form so Maggie could see I am really the mommie from her dreams.''

``So what I heard from the other pastors is true, you have the visage of an angel. The almighty has made of you a great force of his grace. A tremendous force. I will certainly protect you with all I am able. For all I know Maggie slept the whole time after the attack and by that I stand. it is no lie and by this I will stand.''

``Thank you father I know that is extraordinarily generous thank you.''

I lay the cloud about me again and return to the form of Susan.

``Truly incredible. Would you like some tea, more cocoa?''

``More cocoa father, it has been a long time since I've had hot cocoa.''

``Certainly. Let's talk then it has been quite some time you have been out there and I've never known of your life out there.''
I catch him up on everything from Bianca's ball to the present. I leave out the d\ae mons Eury and company though, and Phils particular specialties. Eury became a fairy and Phil a stereotypical wizard.

``Oh my. What a confusing mess. The lord works in mysterious ways, this I know, but I see where in leading these monsters as a human soul you can protect us from them in a powerful way.''

``It does hurt though to hear you say it in such a way. Somehow in interacting with them it has sparked a deep love for them like a mother to her children. The title of great mother of the vampires is quite real to me and although it causes conflict with my human soul I love both people and vampires and want the best for all.''

``I am convinced you will achieve it. What happened to the scoundrel that attacked poor Maggie?''

I stared at him blankly.

``Oh. That's not good.''

``I'm sorry father. I don't need to feed and I don't but I'm still a predator of humans. He attacked my baby and I acted by instinct. I'm growing in wisdom and don't feel that condemnation of vampires for feeding is sensible. It's like condemning people for eating meat it's in our nature. I am trying to find alternatives and to teach them honour so hopefully future vampires will be able to choose their diet. It will always be my hope that sustenance could be gained by all vampires with normal foods but I know it's like feeding a dog grains and fruit in a sense not all will be willing to live on such a diet and I won't demand it of them either. I will demand honor of them though father to treat people with dignity and not feed more than they need to.''

``It's an interesting approach. It does seem sensible looking at it in a broad sense. I would think of them as monsters but what would a mouse think of a cat. We don't want to admit it but looking at it that way we are just simply not at the top of the food chain. I will always think of them as monsters but I think I do acknowledge what you say that I would be expected to think that way.''

``I have to admit father I would have never expected to be accepted so readily by the black court they are the most inhuman of all but they just seemed to be ready for a messiah to come. The whites are out there and I don't know what they are thinking right now. They have me worried I don't want them to engage in a war there has been enough slaughter.''

``I agree with that, but you are not the red king Susan. You seem to be the noble ruler who cares about others. A philosopher and a queen I am confident you can avert a war and bring a lasting peace. Thank God it is you who rules these creatures and not another warmonger as you say the red king wished you would be.''

``Thanks for the encouragement father I often worry if I'm doing the right things.''

``I am no expert but I believe that worry is no vice, it will make of you a righteous queen.''

``Oh thank you so much father. So how is Harry and the others doing.''

``Nothing new really. Harry for a long time wasn't spending too much time with Maggie but he is trying to put that effort in now.''

``What an ass. He is going to miss her best years.''

``Yes but you do know the extreme life he lives and how much the world needs him too.''

``You're right father. It's hard to lay blame on him for that but maybe I might pity him in a sense he really deserves a happy life not Bruce Mclean meets dragonballz''

``Hah! Yes that's one way of putting it.''

``Maggie is happy with the Carpenters?''

``Happy as a clam. A stable home with lots of brothers and sisters. Life is well disciplined and orderly over there which iw exactly what a child needs.''

``I agree. I could only provide a disfunctional home all lonely with black court vampires for brothers and sisters. Some kids have it worse but that's pretty bad.''

``Amen to that some kids do have it worse she has both parents in her life who really love her very much.''

``What a miracle that that should be true. Question father has there been any trouble with vampires around here that is definately something I might be able to help in.''

``Not that I know of child, I'll see if I can get Harry to drop a clue. If something comes up I'll let you know.''

``Thanks father. I think matters like that are becoming my responsibility.''

``I believe that's true. Someone humans can petition.''

``Honor the prey for they give their lives that we may live. This is what I tell them.''

``I believe native americans teach that.''

``I don't doubt it father. I hope we can live up to that, speaking of my vampiric side.''

``Me too child, me too.''

We talked well into the night, then I opened a portal and tunnelled home. I went into my meditation and flew with Maggie for a while over New York in her dream world.













