\lettrine[lines=2,lraise=0]{S}o I was brought before the white counsel in shackles. I could break out quick and easy but in the long run, standing before the counsel in peace, is much better. Ebenezar stood up fast when I entered counsel chambers exclaiming, ``what the hell is this?'' yet I remain silent. Ebenezer McCoy knew me before the sacrifice and has had no reason to question what he had seen that day. His fellow council member Listens-To-Wind calms him down. Damien brings his testimony of what he seen and his wardens under his command did the same. It all came down to wizard sight. Susan looked ascended, the sight alone killed damien when he looked at her. A warden under his command declared his spirit incapable of life after he gazed at Susan, and that it was reasonable to presume Susan was suffering to endure for him. She commanded a mastery of psychomancy in fully healing a spirit and even more so through necromancy in bringing about a resurrection whether by will or instinct. Admittedly there were quite a few gasps in council during the course of presentation. The senior counsel made inquiries and odd events seemed to come from the area of costa rica including weather systems that were just plain wrong, unusual vampire activity, and reports of a dark angel flying in the skies at night in that area also. Her kills were tracked all the way back to Chichen Itza, presumably around the third day after her death. Ebenezer asks counsel if he could have private words with the person under inquiry. Senior counsel passes the request without much thought. He looks white as a sheet and is acting rather nauseous. I think in his wisdom he has connected the dots and knows exactly what happened. I still have remained silent. 

I'm taken to a side chamber with Ebenezar. ``who are you?''
``I am one who appears as your sons lost love, and granddaughters mother. I can see in your composure that you have already made your decision. I deflect your inquiry then, who do you say that I am?''

``you tread carefully around a powerful wizard in the grips of powerful emotions. I understand. Allow me to discern what I have observed so far then including my own experience. In the end you were led to give in to hunger, you were sacrificed before fully transformed, and a conservative estimate says you consumed a quarter of a million immortal vampire souls in an instant. How long do you think you were in death?''

``best guess would be 3 days''

``precisely what I would expect for a certain rite of ascension. We've been duped. You were meant to be sacrificed all along to conquer everything from here to the outer gates in the form of Harry's lost love. God that would kill him over and over again all his days to see you as a full court vampire brutally conquering all that is.''

``you arent angry, or saying im full of shit or wanting to kill me?''

``Oh my god no child, I'm a senior member of the white council and the blackstaff to boot. I think I looked at the signs of what was taking place but I didn't really see them for what they were until tonight. I'm not angry child I feel like a fool for being caught up in emotion and seeing with blinders. We all were, and I imagine it's what was expected of us. We were being manipulated.''

``If Harry stayed his hand just a moment longer...''

``We would have been doomed. Everything would have been doomed. He acted while you were still bearing a human soul though so I sit before a humble, confused little god. That's all I know for sure, and I will ask no more of you today I doubt my heart could stand it. We do not have jurisdiction over any god, stay here Susan I'll return to counsel for discussions. It shouldn't be too hard to make an order to close with you throwing around signs and wonders like you Christ risen. I'll have a warden sent if I am successful to take you for a meal and a chamber to wash and change. I'll give you an hour then come knockin'''

Sure as shit a young warden came and thanked me for my time, advising me I've been dismissed with apologies. He leads me to an evening buffet where I eat with other members of the senior council who are quite uncomfortable around me. I believe the word may be cowering. Ebenezer winks. The buffet is large enough to find some high etheric foods that works to help ease my tension. Afterwards a nice hot bath and a few minutes to rest and relax. There's no TV but after that I am thankful just to sit quietly in the safety of no longer being under inquiry.

An icy figure in cold mist appeared in my room, ``Next time you travel our ways you will request permission before you embark.''

``Huh what? Permission from whom?''

``Mab, queen of the sidhe winter court. You have trodden upon her lands without authority and she frowns on rival powers presuming she is not of significance enough to warrant the request of the right of passage. You will ask or face the real likelyhood of our court facing your empire. You are still young, it is unlikely you would survive a free woman in such a confrontation of that you can rely.'' The figure disappeared as soon as it came. Fascinating.

Ebenezar did arrive at what I assume was an hour later and said "It is maybe four oclock on the surface and I want to get the hell out of here. I hate the goddamned political maneuvering. Let's go to the surface and past the park there is a Starbucks, does that sound OK?"

It did. It sounded better than OK. I'm stressed out, and tired, and desperately need somewhere to unwind. I sure wasn't going to find that here in this headquarters, or maybe bunker is the better word.

We made it out to the coffee shop and I got something that looked like coffee and was very large. I figure how much difference could there be between all the strangely named brews? To his credit Ebenezer just asked for a big-ass coffee and they provided. Maybe I'll try that next time.

``So girl when are you getting around to tell Harry.''

``Well I really wasnt going to, I mean we live in different cities and dangerous lives, maggie has a good home with the carpenters and seeing me would upset Harry I couldn't stand to see him upset given that he has to live with killing me as well. We were apart for the better part of a decade, we don't even know each other anymore really and I can't stand to see him hurt I couldn't be close to him and risk that.''

I don't think I've seen Ebenezer turn so red in all my life, I pissed him off a hell of a lot, ``You listen to what I have to say missy, and you listen good. You ain't done right by the boy for all that time being infected. You presume too much, take away decisions from others and have caused much hurt. You rejected his engagement without discussion, left him so you can fight a war off in hell's half acre without returning or keeping in touch, bore his child and gave her for adoption when he didn't even know she existed. You are a malignant, callous, calculating, brazenly presumptious thoughtlessly cold human being. Don't make me have to link the woman I see in front of me with the woman who died at chichen itza. Susan Rodriguez is dead and so it should be. She was loved but certainly didn't return love properly to those who loved her for nearly half the years she existed upon this earth. No do not allow me to link you to her for you are a new woman by the same name. You have a chance to turn things around, to love and be loved, to be open and honest, and make decisions with other people not for them.''

``Susan Rodriguez is dead, long live Susan Rodriguez?''

Ebenezer is calming down, a little, and chuckled, ``I suppose you could say it that way. Harry done some of the same things, keeping things from others, we all have. Just not like what you've done.''

``Like what she done, may she rest in peace you mean.''

``Aye. Fresh slate then?''

``Fresh slate. As long as you tell me when I'm doing wrong. I didn't get a good teaching as a girl about right thinking''

``Oh I'm sorry lass, surely I will if ye ask me. It be no excuse for what, that woman, done but it does explain it some. Is tomorrow morning too soon''

``Umm, for what?''

``To go to Chicago and meet with Harry.''

``Erk,'' Phew. ``Should be fine.'' I breathe in, I breathe out.

``You're doing good lass, doing what's right this time around. I know you're nervous and it's ok, I'll go in first to smooth it over if he's not ready I'll come out to let you know.''

``Ok, sounds ok. Are we walking the ways?''

``Yes, thats right. We'll be starting out at 2pm tomorrow be there by 8pm.''

``Uh, Ebenezer, we need to kinda ask permission from Mab if we go through winter territory.''

``She tell you that? What the hell girl? She say why?''

``She dislikes a rival power who violates her borders without asking permission''

``Did she say that? Jesus I hardly think that you got that kinda mojo. She must be drunk on pixie dust.''

``Not so much what I am, as much as what I am to be, I should assume.''

``She wants to teach you now while you are young, so it's habitual, before you grow equal or greater than herself. She is expecting great things from you if she's thinking that. Well no problem I'll open a channel so you may ask.''

``Thanks ebenezer.''

I ask mab for permission of passage and she granted it without hesitation, and thanked me for showing her the courtesy. I think Ebenezer was right. So we do arrive in Chicago at 8pm just like he said, all about time difference. We head over to Harry's apartment by Ebenezer's awesome redneck truck and I'm so nervous I could scream. I could have flung myself out the door but I held it down. I guess it's soon after the events of Chichen Itza so at least there isn't the worry of why did I wait so long. Ebenezer knows what I went through and understands that it can take up to a couple years for someone ascended the way I was to get adjusted to life again. So there's also that. All told we arrived at about 9pm.

Ebenezer said to me, ``There's a 24 hour Mcdonalds three blocks down, and a movie theater 4 blocks away. Mcanally's isn't a heck of a long way that direction'', he wrote out directions on some paper. ``The thing is I want to take some time with Hoss, and have you meet back here in three hours. Kick the door when you get back and I'll kick it back. Then wait, and I'll open the door and usher you in or walk out depending on how I do with him''

``Sounds good, I'll go loiter in a professional capacity.''

God, 3 hours is long enough but with my anxiety over this it seemed like a month.

I come back 3 hours on the dot feeling like I'm having a heart attack. I kick the door once. Almost immediately Ebenezer came to the door, ``he's ready, but we need to talk out here first there are some things you need to know.''

I didn't know a heart could stop that long before starting back up again.

Ebenezer speaks, ``It is reminiscent of our conversation in Edenburg, he can't acknowledge that you are his Susan. He can't acknowledge anything but what he believes is true, that he killed Susan in a bloodline curse. He is willing to accept you as an aftereffect, a shadow, a ghost that sprung from the massive scale of the bloodline curse. Basically whether or not you carry any part of his Susan you are a different woman, a new Susan he is accepting into his life. It will do by my books, you will be spending most of your time exorcising his demons though the wounds are still fresh in his mind...''

``...to the point of madness, yet I don't blame him my being here is pretty fucked up even for me. Well I guess Susan is dead, long live Susan.''

``Rightly so then. Susan is dead, long live Susan.''

So one year later plus an additional a couple months. Just short of christmas actually. I walk into Harry's apartment for the first time since my sacrifice. Harry's eyes grow wider than baseballs. My fleshmask is age appropriate, I look like Susan as I would actually look if I was the age I am. I prefer to live a normal life and looking my age is part of that. Harry's eyes are absolutely filled with tears.

Harry could hardly cough out the words, ``Oh my god you look so much like my Susan. You could be her twin sister.''

``Well I did come from the sacrifice perhaps Ebenezer helped you understanding that?''

``Hells bells, yeah and I disagree with him on major points. Susan is dead, and she isn't coming back. I killed her and will have to bear that burden for the rest of my life. You are the result of the magnitude of life energy released when the curse was unleashed so you are the shadow of my Susan, a facsimile and no more. Yet I have born the shadow of a fallen angel in me and she was no less a person in her own right. This is what I believe you are. I accept you as a new woman, a different person, and you can build your own life anew separate from the wonderful lady you were born from."

I lean over to Ebenezer, ``On a symbolic level, I can't disagree with him on anything he has said.''

``I know eh? He really makes an excellent argument and I can't counter it.''

\parasep

The man has demons. Sweet mercy. I've been sitting with him while he talks about his Susan, and weeps, on and on about how he killed me and didn't want to, dear Lord. I think Harry was the pin that broke and brought me here. I mean I could be wrong but with this much hurt I think the red king made his bet that I would be sitting on the table and complete the change long before the knife came down. Or at least he would have hesitated long enough that my human soul would be dislodged so that the plan would succeed. I owe Harry for getting it right so that I could live on, I told him as much. He just isn't ready to get off his bandwagon yet.

After a while he gets used to my face, which is different that the face he is used to. Before I was sacrificed I had the same 20 something appearance for over a decade. I just didn't grow older due to the infection. I could have lived hundreds of years and look the same. I can still wear the leather pants I had in my twenties though goddammit so there. Yes I did need to have them restitched to fit but that's not the point.

Father Forthill told me to give him a month, his is not pleased with me telling Harry about what happened and needs some time to return to being fatherly to me. How sweet.

I met Molly again, she is as sweet as ever. She believes what Harry believes, I guess that's just what any good apprentice should.

Karren Murphy believes as me and Ebenezer do, and is damned and determined that I am the true blue Susan Rodriguez from before my sacrifice. That actually doesn't fare well for me because she has taken it personally that I didn't tell Harry about Maggie. She doesn't like me and is going to be watching me every chance she gets because Karrin and Harry are the best of best friends. I must tread carefully.

I didn't see the Carpenter family, yet. I'm just not ready for that. I'm a bit lacking in the holy department.

So for the next month or so I work on a fairly good, but not great, local story at the Times. Well actually I got two done, they didn't take much research and didn't involve any huge conspiracies. At night I desperately try to work on leads to where Steve ended up when I fled with my children for Phil. Really, I got nothing right now. I do have the world's only professional wizard within arms reach though so at least theres that.

Then on the weekends I take to the skies literally, after dark of course, to head to Chicago. Takes me overnight but because I don't need to sleep I arrive in the morning and as much as I'm able I spend the time with Harry. It's done me good, I was carrying my own demons over him. Me and Rose have been more tolerant as well, only beating the crap out of each other ten times this month, and only using our human strength capacities. That is rather than demigod tidal wave craters and earthquakes and such. I'm keeping some of my seed sprouts and other high in ethereal foods at Harry's which he find's fascinating in a kind of redneck way. I say to him don't bother me I'm looking after my health. Which is right, my other potential diet wouldn't be too good for my health if someone sees me take prey. Very bad. I would hate myself for it too. Unless they were going to hurt Maggie then it's no holds barred, I would eat their souls just because I can.

I got to see Will and Georgia as well. Harry gave the spiel about who I am but they can smell something different. They talk to me like the real Susan, with a bit of an awkward kind of politeness. I think I'm going to talk to them privately sometime soon, they know something and I want to make sure they know the truth rather than getting misguided by what they picked up on.

Afterwards I decided to iron things out with Will and Georgia since it seems that if there is any outright misunderstandings it's going to kill my chances of ironing things out with the people I knew. I remember those two when I was younger here. They were only kids now they're all grown up. I think it's awesome. I called the number Harry had for them.

``Hey, Will and Georgia's, Will speaking''

``Hey Will I was just wondering if I could come over for some coffee?''

``Uh,'' I hear him whispering in the background. I intentionally didn't tune in with vampire senses. I wanted to give them the dignity of a private conversation.

``Could we go Burger King together? It's just that you... well it's just been a long time.''

``You don't have to say it. I get it. It's the reason I'm calling in the first place.''

``Oh, yeah well sure that makes sense. See you there at 7?''

``Sounds good, the one near your place?''

``Yuppers, sorry, yes that's the one.''

Right there, that's what I'm talking about. What's wrong with Yuppers? I'm not their english teacher. I'll figure this out. So I head over to the Burger King and sit down at a table, with a whopper. Doesn't have any nutritional value for me at all, but it does taste good I'll give you that. The two come in, ask if they can get food and then ask if they can sit down when they get back.

``ok what the hell you two? We've known each other a long time, granted I wish I could have spent more time with you over the years. My younger years were mercilessly stolen from me. To get the conversation back on track though why am I getting all this politeness?''

``I'm sorry we didn't mean to offend you if there is something we can do to make it up...''

``Will stop stop! Enough! Talk to me, it's Susan ok please talk?''

``Um. Susan, it's just that you have some. Well. Spectacularly evil mojo happening. Off the charts awfulness. We can smell it both me and Georgia and prefer to not be around to cause you trouble or get ourselves hurt. That's all. I'm sorry we have bothered you.''

They get up to leave and I sit them back down, ``Oh no you don't. Harry's story notwithstanding the whole truth of it is different.'' So I go ahead and tell them the story of what really happened, at least as far as I know it.

``Wow, ok, that makes sense. That would definitely make for a hell of a lot of really bad mojo. You're definately you, not some vampire spin and who you were?''

``It's me. Really me.''

``So what was Harry going on about, it was like you weren't even there. Some kind of phantasm. Kept talking about how he killed you, but, ahem, you're here like hello?''

``Now you see my frustration. His friends are just letting it slide, my death was just too much I guess and his noodle slipped a little. Not a big deal I can't imagine anyone else thinking any different than me in that he will get better and I'll be there when he is able to see me with his understanding. If you know what I mean it's hard to explain.''

``So everybody is treating Harry like he is a very special person when it comes to you. When he says how he killed you and you are standing right there beside him his friends say nothing except, Kind of, 'That's ok Harry, it's all going to be ok',''

``Right now that's about it. I've spent a lot of time with him, I wonder how much I help really when he doesn't acknowledge me but I firmly believe I'm making a difference somehow listening to him and comforting him.''

``I know you do Susan, I know it. You've always loved him dearly.''

``I do have a new bo now though, I don't think it interferes with the fact I still care for Harry. One problem with that though is my bo Steve disappeared on me like a fart in the wind and for all the research I've been doing I can't find him anywhere.''

``We'll help Susan, were did you last see him?''

``Back in New York City, we ran into some really bad dude named Phil. Me and the people I was with ran like hell from the guy but when I turned around Steve was gone. I understand the wardens went to nail the SOB but Steve was nowhere to be found.''

``What was he really?''

``An ancient black magician, a lich if that means anything.''

``It doesn't really, but I know black magicians though. Well I don't actually know any black magicians but I'm aware of their existence and power at least.''

``Well me too in some extent. Where does it help me to know where to look though? Everything has to go somewhere.''

``Say you guys, you got really good sniffers. Probably better than mine. Do you think you could see if you could smell out where he went?''

``Sure, do you want to travel there with us this weekend coming? We have some time then.''

``Sounds great, are you taking your car?''

``Planning on it yeah. Don't know where we're going though which is why we need you.''

``Well sure it only makes sense. I'm going to get back to Harry, then we'll meet here next weekend.''

``Awesome.''

I've been good to Harry, even though he doesn't see me I've stood by him and that did get Karrin Murphy's attention. She come by Harry's apartment on Saturday night.

``Evening Susan, mind if I come in?''

``No, come on in.''

``I'm not good at apologies, I am sorry for treating you bad. You are making a big effort to be with Harry in spite of him not seeing you as anything but a ghost. I've never seen a ghost take that much care in anybody before. Listen, Harry had a little problem once. We had fought the Denarians and they captured a little girl called the Archive. We made our way back to the Carpenters but something wasn't right with Harry. We weren't sure of ourselves but Molly checked him and by luck we found something wrong. Michael confronted Harry and broke the spell with an act of faith. He was missing memory and refused to see things he should have. I'm not saying it's the same here but it might be. Maybe somebody doesn't want him to know you are still alive for some reason. Nobody is going to risk hurting him to remedy the problem. We just don't know what it is but if it comes to a head some day, and steps need to be taken for the sake of his life or others, he may actually see you as you are then. None of his friends will push him on this and I just thought you should know. I don't think you should push him either Susan, do what you will just don't push him so see you as real if he can't. Can you follow me?''

``Actually, I think I do. I was afraid he had just gone mad. You think it might me magical manipulation?''

``Maybe. Harry called it neuromancy once. Or maybe psychomancy I don't know if it's the same or different. Either way it happened before and could happen again. He was alright when Michael helped him the first time so don't be too afraid he has broken something, he may have been manipulated. If it is that, like I said, if all things hang in the balance and it is broken he will see you.''

``Karrin, one day when I cleaned up for him he thanked magical faeries for cleaning up his place. I didn't see faeries. Does that mean anything?''

``With him being a wizard? No it really doesn't mean much. He may have had honest-to-God faeries clean his apartment once it's hard to say.''

``True enough. So you're ok with me?''

``Look girl, as long as you do right by my friend you're in my good graces. Hurt him again and I hurt you. Promise.''

``Heh, I'll be good, scout's honor.''

So that actually makes sense to me. It would match what I'm seeing. He has some sort of block. Well if that's true it actually makes me feel better. Knowing that his friends won't push him regarding me for his own sake is going to help me. I'll know that they're not rejecting me just thinking about his health. So I'll keep an eye out for that. Thanks Karrin, for helping me understand.

\parasep

``Susan,''

``Hi Karrin, wassup?''

``I have a case I'm on, a normal case against Marcone. There's a witness and I'm on a team to provide protection. I could use more muscle but that's not Harry's bag really.''

``Is there a story in it Karrin? I'm a bit needy.''

``Oh fuck you, if you don't want to do it spit it out.''

``Sorry, sorry, old habit. No problem. I'm pushing hard for a deadline this week.''

``It's a transfer from witness protection to the courthouse, it's on Saturday. Of all days you should be able to swing it.''

``Oh yeah no problem, I'd be coming up to see Harry anyway that works out great.''

``Thanks Susan.''

``Karrin, who is this guy? What's it about really? It would help for me to know to do my job here.''

``







