\lettrine[lines=2,lraise=0]{F}{i}rst day of work! Woohoo! I'm dressed outstanding, a little pink android phone with top notch business attire and a gorgeous white trench coat. I feel like I'm absolutely glowing. It has always been a major dream of mine to work for a major news organization and as far as I'm concerned the Times is the best of the best. At least very prestigious. When I get there security takes me to a side room and snaps a photo. They have my ID ready right there in only a few minutes. It has my real name Susan Rodriguez rather than my pen name Justine Carpenter but I can only ask for so much anonymity this is my employer after all. They tell me at security how to get to my editors office, as he is going to be the one I report directly to.

``Oh my god, Justine Carpenter! How are you doing Susan my name is Joachim Jameson!'' Spoken in a heavy gay lisp. 

Oh boy. I say, ``really? like as in J. Jameson?''

``Yeah yeah I've heard that before sweetheart, I know you ain't no superhero and this ain't the Bugle''

``Well speak for yourself I'm definately the next superhero.''

``Hah! I like that! Maybe I'll be your gorgeous sidekick?''

I'm thinking yeah you might just fit the bill there Joe.

``I talked to IT and both of us have that GPG you talked about. You're on the VPN now but they haven't put that VPN over TOR like you mentioned. At least not yet. I think they want to talk to you I couldn't explain it worth a damn.''

``Well that's a start. We can communicate well and safe with E-Mail and GPG.''

``Well come on Susan lets do lunch. I'm starting you fast, let's see how you do with this one. Nobody in the office could get any story from this. Over at the Sing Sing penitentiary the inmates have been acting very amorous toward each other. Now I know things happen in prison but this is the majority of inmates and even out in the open. There has been environmental testing, the water has been tested, the entire prison has been under 24 hour surveillance but no one can identify the cause. Even on release the inmates continue with this behaviour but at least as of yet it hasn't spread through the normal population. No one knows what is causing it. Dig into this one for me Susan see what you can get.''

``Before I forget I wanted to get a concealed weapon permit.''

``I'll do it myself, I know people. It will be a state permit with New York City endorsement. Outside of the state you're on your own. Look for it within a week.''

I get the orientation tour and get introduced to my office. An actual office, I'm not starting in a cubicle. Ooo nice. I didn't set up too much stuff yet but I think a white noise generator might be in order my senses in an office are going to drive me crazy. Actually sitting in a cubicle next to people may not have been easy either, I may not be hungry but it still is hard sitting a small wall away from the vampire equivalent of frying bacon. It's just cruel.

When I get back to the scourge I begin building a power structure based on the organization I started earlier.  The first ranks gather intel and report, carrying orders down. The field marshall for reporting on the state of the empire, the generals for regions or continents as it were, and captains for the principalities or countries. direct authority is given to Lieutenants for the towns and cities, the clans. Also direct authority is given to the Sergeants for the governance of the houses, who is also invested with the power to cull the dishonorable and deal with other petty matters. I sent the order out and assigned Seth as my first marshal. I had his office and living area built permanent onto an area nearest the elevator. Close to me but unseen. He is an elder black court vampire and not pretty. At least he is too old to be too stinky. He'll let me know our strategic position when I get back from Sing Sing. That should take a load off my shoulders, my direct interaction with the vampires will be minimized and I can focus on being human again. I really need that.

Me and Phil get together to talk shop. Joachim said it will take at least a week to get the cover ready, and good news on the concieled carry permit is that it might be ready before I go on assignment. Awesome.

Phil teaches me about Psychomancy. He actually enters my spirit to help me find anything in me that is a natural ability that replicates Psychomancy magic. I appreciate that. Phil says that although my human spirit and vampiric body are perfectly fused my human spirit has no natural understanding of my native abilities so I need to learn them where a vampire with a vampire soul would know their abilities from their birth as vampires. It makes a lot of sense to me.

He teaches me, and learns a little himself about my ability to read auras. He advises me to be careful as auras can be manipulated. Working with him I know now I can read a soul, including vampire souls, quite well and I know it will get better ov3r time. Their emotions, the kind of person they are, whether they are sick, the amount of life energy they contain for selection of prey (not high on my priority list but nice to know). It's extraordinary but as Phil says can't be absolutely trusted. I can also identify vampires from humans with the sight.

Phil took a while to talk about using death magic to heal a souldead person. The resurrection then quickening with ethereal energy to invoke self healing in a manner used by vampires but not leaving the soul in a vampiric state if that is not the casters desire. Killing a human would almost instantly heal the soul otherwise following the above necromantic techniques some Psychomancy should be used to ease or to eliminate the psychic pain of the soul from the damage it suffers. I said to him his magic is bordering on the godlike. He agreed, the power of black magic is without measure, which is but one of the ways it can corrupt a soul.

I apprenticed to an ancient black court vampire named Guy also. I wont let him in my head for anything for fear of what he might see or do, but I'm learning. He taught me suggestion under cloak and cowl in manhattan at night. I call it my `Jedi' move. I pretended to be a hypnotist and sent suggestions to peoples friends as a prank getting guys to sing I'm so pretty to the amusement of the girls they're with and other such silly things. My Jedi move might ultimately save lives. It's the same black court power that enthralls and renfields people though so I have to be careful. Having this power makes me wonder if I might be some sort of hybrid vampire. It's confusing.

Seth approaches me near the end of the week. ``My queen your new protocols are established, the first reports from the field are coming in. There have been no signs of any red court activity globally. Our empire stands at about a quarter of the black court population and no know associations with the white court. No contacts have been made with white council wizards or any other entity. Our prey remains quite reduced in all locations especially in central and south america assumably due to the savage ways of the reds.''

I ponder for a while. ``OK, heavily culling of dishonorable in central and south america and remove the remaining scourge to more bountiful locations globally. leave only what is necessary in those areas for gathering intelligence. Release thralls and let the prey recover in peace and dignity.''

``By your command my queen it will be so.''

I think this was a good move to build heirarchy, I may have just saved those people terrible suffering and pain. They need to heal as much as my own soul.

I returned to work the following Monday, everything is in place. I have an apartment in town now too. I've been thinking about it and I think it will be good for me. found a nice place in hells kitchen for a song. I don't have a car right now but that should change within a month or two, I need to setup the apartment. I also need first and last months rent among other things. Yeah I could let the kids provide but I need to have my own life too. My own completely human life paid with my own earnings and friends I can then relate to. god help me for saying so but maybe even a playmate. I still think of Harry a lot though so maybe not. I don't want to think the red king has won afterall in making me the great mother, I don't want Harry to be hurt by what I am now. I don't know if he could ever understand the choices I have to make. Would he just reject me as a vampire and just say I'm not his Susan? That his Susan died and I could never be her again? I don't know if I could survive it. I still love him in a real way and what happened really wasn't either of our fault. Maybe I could blame myself for being too stubborn and going to Biancas ball but if I had to do it again I think I would. I've never backed down from anything even now. If I backed down then I wouldn't be working at the times now. I'm working at the damn New York Times now, many a reporter would sell their soul for a chance here. So much was set in motion at that ball that is just being realized years later, and likely there is more to be seen yet. I would assume so. It transformed my life first for the worst and then to the incredible, and difficult. I live on 44th, the west end. I walked over to Broadway, then up into central park. I listened to the smells and sounds, looked at everything. Seen places I'd only ever heard of  on tv or in written word. Times square, the theaters on broadway, Gershwin theater. It felt like I was in a dream, like I would wake up as an infected again tortured by the hunger. This can't be real. It isn't possible. I tried to push down the joy in fear of everything being a lie. I pushed it down in fear of being hurt. This is cruel it can't be real. The clouds were starting to gather soon after the sun set. I made it to central park and after a few minutes it started to rain. It was coming down hard and I felt it against my skin. It felt real. This cant be happening. I bit my arm and the pain was real. My fangs were real. I had no hunger anymore, somehow somewhere I had risen above it. It's gone. I took out my ID for the times and stared. The rain poured down and formed droplets on it immediately. There was my name. My picture. The new york times logo. I stared up at the sky to see the rain fall and felt like I was moving at lightspeed, like the droplets were stars and I was rocketing fast and far beyond the confines of this world. My dreams are coming true, I need to let go of what was the time of suffering is gone. I am vampire but I am also human, my life has just begun and these little droplets show the course of things to come. My human life is blossoming at the same time as my vampiric. At this moment, as the rain fell, I felt that release in my heart. I could feel the pain of the past slipping away. I found peace with Martin and that which I held onto for so long. It is done, they are at peace so must I find peace with it also. My heart was moved with hope fulfilled and I boiled over with a primal scream. A human one, born of happiness. My happy life ended at Bianca's and now has begun again. I lifted my arms to the sky and shouted like my team just sunk the winning goal and danced. I skipped and wept and hollered through central park as the rain poured down. I was soaked and I didn't care. I defied all the odds, I was in the exact right place at the exact right moment. I have my human life back again, I've dealt with the childrens needs let them take care of themselves it's time for me to be human once again. After so many years just to be human once again!
I sat in a small gazebo with the rain pouring down around me, my smile would not fade. Nor would the giggles that replaced my shouting. Nonstop giggling. I must have sat there an hour, just didn't want to move. I was still afraid it might all just disappear. Slowly my acceptance of my life settled into me but I don't think the giddiness will go away anytime soon. I headed home in the downpour not caring about being wet or not. I would still look up in the sky from time to time and laugh. I would just laugh. I couldn't stop. I didn't want to either. Oh my god Susan. Oh my god.

I changed when I got home to my apartment. I loved it. It was an old victorian style apartment with a functioning wood fireplace. It is small. Honestly it makes me think of sherlock holmes and 221b baker st. It feels exactly like that. It's also buggy as all fuck so I sealed it up and put out for a heat remediator unit to use regularily. Things like that are what make it cheap. As long as I keep ahead of things all should be fine. I heard the landlord is a lazy ass. I still have that incessant need to make the place look like grandmas living room. floral print wallpaper and doylies and such. The bedroom is a complete rejection of the living area with solid bright colours, quite a bit of pink, and a bunk office. The space is small so my desk and work area is under my bed, with a steel ladder to climb up to my bed. There are some shelves for books and such above the bed. entertainment is through the computer playing movies, podcasts and such plus overtheair tv and radio. internet is with an unlimited cell phone plan. slow, crappy, but pretty damn cheap. Oh and music and movie posters scattered around of course. Beanbag in front of the tube or to hack around with a phone or tablet. Anyway, the rooms are contradictory. I'm still not comfortable with the need for a grandma environment it's just weird. Rocking chair and knitting yarn. It's calming I'll give you that. I think I've made plenty enough scarves though.

Back in to work tomorrow, I've heard everything is prepared. Even my conceiled weapon permit went through. Joe must got some juice to make it happen that fast. I'll pick it up tomorrow.

I am really extremely close to work. less than 10 mins walking. I like that. When I got there Joe had some time scheduled for me to talk with a reporter who worked the story before without getting anywhere. There's a better chance I might land it if I can learn from him and get a foot up on this thing.

``Hi I'm Susan.''

``Patrick. So you're going to try to crack Sing Sing?''

``Seems that way.''

``Good luck with that. I was the last one to try to crack this but I ended up just spinning my wheels.''

``So why don't you get me up to speed.''

``Sure. Here's the deal. You know what prison can be like, but at the same time depending on what day you get there there might be none or there might be 2 or 3 guys getting busy with each other. Completely in the open. Like roaches what you see in the open is a thousand times worse where it's hidden.''

``eww, is that normal there?''

``hell no, sure as shit not in front of the guards. Those bastards gotta either have som3 re big hairy gonads or something is d4iving them to it.''

``I get the picture. Did you find anything out?''

``Well it s3emed clear to me that some drug compqny is testing their newest formula on these clowns but I could never find a clear link. Right now there are three generic companies supplying the prison with it's prescription meds. There are numerous other sources for it's other drugs of need.''

``Right, I hear ya. So no smoking gun.''

``meds tested in the lab were what they said, a search of the cells turned up nothing. some contraband but it didn't test out incorrectly.''

``Have you thought of drugs without any residual blood toxicology?''

``Definately. The prisoners receive regular blood testing and even running it through forensics got nothing. That's the only way but how is it getting to them?''

``Exactly. Anything environmental turn up?''

``Cells were tested, 2ater supply, food, halls and yard. Everything really nothing turned up. mold, virii, bacteria, chemical nothing.''

``Where were you left spinning your wheels?''

``Finding the source of the drugs, how was it being trafficked, I focused on the drug angle it was the only one I had.''

``Is that what the previous guy or guys focused on too or did they cover other bases?''

``I think everybody went the same route but Jason was looking at the coming and going of people and personel at the end before he was pulled off.''

``Was he on the story a long time?''

``Longer than the rest of us. He told me he figured if he can't track the drugs, and it is a problem with people, then he should track the people.''

``I like that, it makes entirely too much sense. I think I'm going to follow Jason's idea when I get there and just skip what seems like a dead end. I'll be talking with the warden tomorrow.''

``Sounds good hope I could help.''

``You definately helped thanks a lot man, I can hopefully skip past most of the dead ends.''

Interesting. That is definately some rather extreme behaviour. I would think drugs too like a newer and better viagra testing phase or something. No weird drugs were found anywhere. I like the people angle, I think I'm going to go for that. When I talk to the warden I think I'll see if I can truck as an inmate. I'll need to be careful not to get heavy handed though I need to blend in ans not look like some superhuman. Or worse some kind of rite 9f passage and end up fighting the whole yard. There's no way I could hide my nature then.

I get back to my place. It's late fall now and the building hasn't fired the boilers that feed the hot water registers yet. I pull down some wood from the lumber room and atart up a fire. I kick back in my lounge chair and toss out the old miswak from the ashtray and cut a fresh one from the package. I don't smoke but I kinda need something to chew on sometimes to think. After a ahort while the dire got going well. The snap and pop is rather nice as sure as the heat on a cool evening. The temperature dropped fast over the last day. It was quite warm until after the rain past.

What possible advantage could anyone have in this? The drug end of it was a dead end, and it nevee fails if there is trouble afoot it is either for the love of money, power or lust. Very little else motivates save maybe vengeance. Vengeance makes little sense unless it wqs against the 2arden and there certainly are more effextive ways to mews with him. I think in chasing the drug angle 2e have nearly exhausted the money angle. As for lust well that would be the issue in itself, as a motivation I have yet to see it. For vengeance though I should check to see if only one segment of the inmate population is effexted. It would definately be an embarrasment to a rival gang to have this brought on them. So there is that. The po2er factor, unless like I thought it 2as rival gangs and an attempt at shaming the other I would say there is no power grasp in the population. There could be blackmail against the 2arden maybe, or q higher political maneuvering to gain advantage over one or more people thqt govern corr3ctions. Holding back that key evidence that would allow us journalists to print a story. The warden has not been threatened to silence that much I can see as he is helping me get placed inside. hmm. Also I need to examine administration at the prison to see if there are any inconsistencies. Jason was focused on people that would be the best place to start, to see if I can find any inconsistencies. I should take a look at the movements of 8nmates as well but I don't think I will spend a great time with that. All the work on tracking illicit srugs would have unearthed unusual activities of inmates I would think.

I got another chunk from the lumber room and fed the fire, then slipped off into meditation for the rest of the night, sitting in front of the fire in nightshirt and knitted shawl. lying restfully in my lounge chair. Having a tea party with Maggie in her little dream world.

Damned commute was over an hour and a half to Sing Sing. I'm going to need to bring work to do, or at least books to read, making this pilgrimage to and from every day. I might lock up a bicycle at the train station to turn a twenty minute walk into a five minute bike ride though. That would help. I presented my ID and weapon permit, leaving my glock at the guard station. Another guard escorted me to the wardens office. I introduced myself.

``Hello, I'm Susan from the times.''

``Ah good, I hope you can finally come to a conclusion to what in the hell is going on in my prison. Goddamned embarrassing. You wouldn't believe the wise cracks I get about the worlds biggest bathhouse and crap. Anyway that's my trouble not yours what would you like to do to start?''

``Well it's been made pretty clear what's been going on and where we've already looked, may I start just working in the qdministration office? If possible checking out the different roles and historical paperwork over the next couple weeks.''

``Um. Yeah. Nobodies done that yet. Try not to fall asleep.''

``I do not sleep that I am aware of, but thank you. I will assume you will show me fresh coffee?''

``Oh yes, we have a commercial coffeemaker. It's going all day long.''

``Heh, I'll bet.''

So he introduced me to the office staff as a new hire in need of job shadowing before moving to another local prison. The staff looked about as boring and plain as their job. Friendly enough though. I had a quick runthrough of the different positions  but the jumble of information just fell out of my head, I'll get to learning it over the next couple weeks. I couldn't use vampire vision to check their auras with them looking right at me, the change of my eyes would scare the hell out of them. Again plenty of time over the next couple of weeks.
Back home again, I'm taking a break from the evening work routine. Since I don't sleep I read at 24hour coffee pubs although I still need to eat a solid meal at night to stay firm and avoid needing to eat human prey. Talking about prey I've also been enjoying cruising bars and nightclubs. I haven't gotten more than a nice conversation yet. The odd one I've stayed with for the night but I can't go all the way. I'm afraid I might eat him. Eventually I'll lose it completely and either eat somebody, fuck somebody, or both. I hope I can recover some semblance of my original human sexuality, but I have little hope. I presume I may end up with a snuggle buddy like an asexual. If I was on a good old fashioned fuck-a-thon it really wouldn't matter but of the men I've met, at least the ones that approached me, they just aren't genuine or are really shallow. I think some of them are going to pull out a mirror just to look at themselves. So after kicking aside the players and aforementioned chaff, I did end up with some regular friends that may develop into something someday so at least there's that. I need something soon though, my pussy is starting to eat my leg.

Speaking of going out, after the first week of monumental boredom I went with the crew for the Friday night afterwork drinks. There's a little pub not too far away where we ordered some pitchers. I heard from them memories of times past and people they once worked with. Then came the frustrations of work. I really didn't get much from them but as they got more drunk I was able to use my vampire sight. I don't get drunk on alcohol by the way. It just comes out just as alcoholicn as it went in. Weird. Anyway what I found is that these people are scoundrels, the whole lot of them. They are shallow and petty, ready to take any bribe and kiss any ass. They are so crooked the couldn't lie in bed straight. Lying, cheating, stealing and all with a perfect friendly demeanor that hides a thousand crimes. These people are exactly where this shit is coming from. Now I need to find out who or how many of these snakes have made a deal and for what.

The night degenerated into petty arguments and rumours so I left team slimy and saddled up to the bar. A nice looking fellow named Chuck bought me a drink. He was a writer who authored some works in current affairs, so we chatted a long time essentially talking shop. It went well into the night and broke up at a coffee shop. The guy was still shallow but I enjoyed our time. We exchanged E-Mail addresses as he wanted to keep in touch. I'm not sure whether to be angry with him or just disappointed in general that my hope of a romantic encounter turned into an exercise in business networking.

That weekend I kicked it up with my phone rolling through about a million messages from players in an online dating site. Looked like every guy in manhattan loved me except the same generic message came up many times and the same guys came up multiple times. Blanket bombing. Nice guys are buried in ten tons of horseshit. With the Tinder literally every guy likes me. Blanket bombing players again. Nice guys mailboxes are probably so empty there is the sound of a single cricket and I'll be damned if I know how to get to them. Some of the players are idiots, made me laugh, the line was, ``I put the std in stud and all i need is u.'' Fuck.

So me, Eury and friends saddled up at my apartment for a game of french tarot. I used esoteric cards because they're so cool and it was a great afternoon. Except maybe when Eury said to me, ``Love the modern mother hubbard theme Susan'' when he got here. The only thing I could come back with at the time was, ``Oh shut up.'' In good humor though it worked out just fine. Later that night I went out again and the bars seemed to be filled with people that came together and left together. No singles. I really fucking hate that, I wish there were signs outside the establishment that literally said, ``singles bar.'' Sunday I did the church thing, where in the back of my mind even as poor a match as it would be I might find a good guy. Churches are the best place to find good guys I think if you can sift through the sea of grey hair and family men. I cruised through a library and a bookstore. More than one bookstore. Partly to get ideas to solve the mystery of my current assignment and partly to find men. I seem to have very quickly picked up another full time job in finding some man. I think I've heard it said a girl should establish herself first before looking for fresh meat, and I am solidly established so maybe that's why my interests are leaning this way. It my lifes next big challenge for personal success, not to sound shallow or anything just a psychological theory. On an emotional level I lost my hukan sexuality at Chich\'{e}n Itz\'{a} and it was imprisoned in an infected body around a decade earlier at Bianca's ball. I hope she's burning in hell for that. If not it seems to me Eury would know who to talk to in order to arrange it. Yes friends humour does help. It's still a horribly deep wound, and memories like Bianca especially burn deep. When I was in the fellowship I had a purpose and a mission. I was a hero of the people against the monsters who would devour them. Oh Harry I wish there was something I could have done, I would have taken your ring and married you in a second if I didn't pose a danger to you. It was the most painful thing I've ever had to do. To decline your ring and to leave for war. Even as much purpose as I had there I wanted so much for you to be with me, but I knew you couldn't, and I thought of you every single day. Every single day. Burn forever you fucking witch you ruined both our lives and I lost years of my humanity I will never get back. I'm only now catching up on building the happy life I could have had long ago. Thank God I consumed your species, and now the whole red court is gone. I pledge that I will never allow there to be another like you. I swear to it by my life.

All my infected life and since I was turned Bianca has been that representation to me of vampirism looking down in arrogance and patience. That voice that tells me it's only a matter of time and you will be exactly like us. 

Especially if my vampiric instinct comes out Bianca's voice echos as if through time telling me I am or have become just like them. She laughs and tells me, ``Child, how did you think it was not going to be so? You cannot resist, you are to be our sister, give up this futile struggle and let death come to your feeble human spirit. Savour the sweet taste of your spiritual death. Complete your journey and be the true full red court vampire I know you are to be.''

This hatred I have for vampires in my human soul I think, as horrible as it is for me, has made Bianca like a conscience to me. Oh I wish I could forget Bianca and what she did to me but perhaps that arrogant, ridiculing voice is something I desperately need when I am living with a mind and body of an immeasurably powerful vampire. Without it I might just risk the loss of my humanity in the psychological sense.

Back to work on Monday. I try to observe the employees in various ways but I'm not seeing much. A lot of ass kissing and trying to one up their coworkers is all. I think maybe that's all I'll get for now. The warden gives me leave to check out the prison proper and warns me I must be crazy. I go with two guards and when we enter the cell block as I expected the prisoners were yelling and whistling pretty good. When my fist brought down two feet of a 6 foot concrete wall there was quiet. I yell back, ``who wants some of this?'' All the inmates return to the rear of their cells saying ``Not worth it'' ``Not me'' ``No way'' ``The hell with you''. 

The guards said, ``How did you do that?'' 

I said to them, ``Someone I knew once, his dad was an illusionist. You know like stage magician?''

``He must have been real fucking good.''

``Damn straight.''

``Were you looking for anything in particular?''

``I don't think I'll know until I find it.''

``This big brute has been effected for quite a while. It might be a good place to start.''

Big brute is right. The guards had to yell at him to stand back, as soon as they came in he pushed right into them, one reached for his nightstick. I took that son of a bitch by the throat and had him high on the wall with just a touch of vampiric speed. I had him  there by one hand. Since this dude was being an ass I didn't give it a second thought and pulled over my third eyelid and started my sight. I did a red court thing for good measure all with the guards getting their senses behind me I ruffled my skin mask. See I don't really have skin as a vampire it is just a layer on top. A mask basically. I can't say for what the red court could or could not do but I can move it around like you could move around your tongue against your cheek. For me though it looks a little like a nest of flesh eating grubs squirming around under my skin. It is quite visually appealing, truly sexy. So what I found besides this guy being a scumbucket is that I seen residue of vampirism on him. This shit just got real interesting.

``Get her off me! Get her off me! She's a fucking alien man she'll eat my fucking brains get her off!''

I toss him on the bed, ``Buddy get off the cheap drugs and stay there. Don't fucking move.''

The guards recovered themselves, ``Where did you learn to do that miss?''

``I fought in a South American war for many years.''

``No shit? Maybe we'll hire you to protect us in here, I ain't never seen nothing like that from a girl.''

``Hey thanks. Well I think I may have found something. Let me search around I wont know what it is until I find it.''

I search around, using my sight when the guards weren't looking. I feel life energy signatures and sniff around. I haven't found anything strange though.

``Hey boys, this guy get it on with anybody in here? Do you know where it happened in here if he did?''

``Last week he was giving it to collins here over the sink.''

I sniff the area and I smell dispersed life force, quite a bit of it in fact, at that location.

``A month ago I seen him with O'Grady bent over the can here.''

I sniff, trying to set aside the other smell of the toilet. My vampiric senses picked up the life force signature not as strong as by the sink. To varying degrees I noted about a dozen points of abnormal static life force signatures. This dude was getting some business. I would like to shakedown this guy but I don't have the questions for him to answer yet.

``Ok who's next?''

``Well the lastest party animal is Jackson over there on the second level. He started a week ago and his latest shag was yesterday.''

``No kidding? So the just seem to take a pill or something and start racing? Do the ever quit?''

``We've had half a dozen quit. Dead of a heart attack.''

``Christ, were they older?''

``Most were young as spring kittens, which is why we've been trying to find what kind of drug they're bringing in here.''

``Man. Well ok you seen this latest one start a week ago. Do you remember anything else from a week ago, anything or any person coming to or from his cell?''

``No, same as when other cops and reporters came, nothing.''

``Well lets go, I'll try to gumshoe it.''

We arrive at the cell. This dude is more restrained. He's heard what went on outside and doesn't want any part of it. I sniff, same disturbances as before but only 3 distinctly rather than the shephards pie of disturbances from the guy below.

``He is this stuff like the kind enjoyed by both or not?''

``Don't say anyone I said it but I wish me and my wife had the joy these boneheads do when they're fucking in here.''

Wow, I'm assuming the guards relations are chilly. The way he said it indicates that it's rather over the top in pleasure. That's actually even more indication of something vampiric. It might be a phage, a fae entity that feeds on emotion. With only three disturbances I sniffed a little deeper. The oldest signature seems to have some other energy around it. I think Phil might be able to help me with that later. I found a little wooden talisman under the bed near to that original signature. I use my senses on it but I get nothing. I'll take that to examine later. Good search.

``Say has there been anything normal that started around the same time as these incidents?''

``Well thats quite the question. There has been a clinical trial for some vitamin supplements. We changed our medical supply contractor, food supplier has changed. Using different cleaning chemical supplier. Lady we are pretty much getting everything from somewhere else. Anything to try and resolve this problem.''

``Fascinating. Well good enough for now I better go finish some research on this.''

``Well have a good one.''

That was that. I'm going to put in extra time on research now that I got something to look into. I hate all this man chasing anyway I need a vacation from what is supposed to so much fun but isn't. I can't do too much without Phil but I can at least work through mine and Phils library to find this talisman. Then I'm going to meditate for a time to go play with Maggie.

what i found out was that the little talisman had symbols referring to the winter court and my knowledge of the ancient craft indicates it would be used as a spirit vessel. I'll have to verify with Phil on that but I do believe some is carrying faery spirits around and dollars to donuts it is some kind of phage due to the fluctuations of Life energies.

So, perhaps the motive lies in the change of contracts? There is a whole hell of a lot of money changing hands in this than could have been seen by the original investigators. I should be able to check documentation at the prison office to see whose hand is on what. Someone has to push this stuff through and it needs to go through that office. That administrative team are the Devil's own and if there is something foul going on in that prison I like them for it. There needs to be something supernatural or a practiced wizard involved to in order to know to capture and release phages with an intent.

I guess if for  nothing else having supernatural senses is a great advantage in journalism and I appreciate being able to scare the bejesus out of the bad guys too.

The next day I'm back at the prison. Staying in the office today now that I know what to look for. I found the cabinet where the contractor documents are kept. Shit it's gonna take a month of Sundays to get through that cabinet of papers. Well one day at a time. Issues started happening about 2 years ago so I grabbed records going back to around that time. One year at a time. Supply requests, bills and receipts, even the most ridiculous items were kept in the folders and I was staying up every night to pour through it all. A change in a generic drug distributor to a company named goodtime pharmaceuticals. I was inspired to find out more about that one. The company specializes in the distribution of sexual and mood drugs for pharmatherapy as well as aphrodesiacs mostly of the herbal variety, and pharmaceuticals related to transgender needs. Otherwise they are a general needs distributor and even so I don't understand why the happy hell the New York state correctional authority would choose a company named goodtime pharmaceuticals as it's medical use drugs contractor. That went off in my head like an air raid siren. The sanitary contracting supply company it Red Toad sanitary supply. Nothing jumped out as abnormal. I checked the website and looked at the promotional material. Based in San Francisco there were testimonials that offered a clue as to their client base at least. Three panties to the wind dance club, the Shiny Black Rubber garment manufacturing company, brothel house distribution of California, and you get the point. As a matter of fact the changes in contractors were pretty consistent in being linked to the sex industry which to me means the source of this phenomenon is originating with whoever has a common interest in these companies. Some kind of sex industry mogul seems to make the most sense and it links well to the nature of what is happening here.

I placed a hardware key-logger in-line with the wardens keyboard. I think the warden would have probably given up his password but I preferred to leave him with reasonable deniability since he has gone over and above in helping me with this story. I waited until after he punched out and grabbed some information on other institutions and printed it. This phenomenon is starting to branch out a little bit into other locations but as of yet the contractors in the other institutions haven't changed.

OK so it looks like the next stop is San Francisco. I gave Joe an update on the story so far and the Times got me the tickets to take a flight out there.

After a few hours of meditation and dreamworld play with Maggie. I have nothing to link these companies together yet so I need to do that. First thing is all of these locations have a physical address but not all are in the city proper so I found ownership and mortgage information on the locations some on-line and some I had to the actual land records office of the county they were in. No slam dunk here the ownerships were sometimes different. That doesn't mean the company or individuals listed are the actual companies in residence at the locations. Granted some are in personal names like Mandeep Patel but one stood out pretty clearly. A leasing company called Osreal Land Holdings LLC. So the easiest place to start seems to be to find that company and sweet talk them into spilling something useful. I found the headquarters in Los Angeles proper. Land records were to no avail, it owns it's own land. Evaluating the board of directors was interesting though, they all have links into the porn industry. Fairly heavy links. To three separate companies.

The porn companies seem to be distinct, I can't link them together to any common people yet. That's not a dead end though even without a smoking gun the story so far is enough to bring up questions about integrity in the correctional system or possibly questions of fraud within this particular company. I don't need to draw perfect lines as long as I can dismiss coincidence and make people think. Nonetheless I want to find the smoking gun and I'm feeling like I'm close.

I took a few days to track the comings and goings of the board of directors, see who they are meeting and where they do lunch. They all live in exclusive parts of town, and I used camerav on my phone to snap some pictures of some of these meetings for later. I relaxed some distance from them as they had casual lunches and off-site meetings just to listen, and get some names. I found most of these people fairly quickly, they are coordinating the supply, funding and operation of all these other organizations. At least one of the names on the land records was mentioned even though I couldn't find any record of the persons existence. I think the goods are all here.

As I was making notes I found the physical locations of many of the landowners listed in the land records, only the individuals in question seemed to have more than one name as I confronted them with their land records name on the street having allegedly met at a business function. Of course they responded as their alter ego and why shouldn't they? I asked them how their company was doing, intentionally forgetting the name, but they knew the name of their company everytime. This is getting more and more interesting all the time.

After about a week in a larger meeting at a local Starbucks there came an individual to the table that made the whole board rise and bow in a customary Japanese fashion. I think I just found the kingpin here! Everyone settled into their seats and I heard one name that made me turn away from the table save I should giggle right at them. Raith. They addressed him as mister Raith. This is a white court enterprise, oh most excellent!

OK, so what's left. Motive appears to be financial gain, the corrections contracts although I'm sure pale in comparison to the income through the porn industry are still decent enough and represent a very steady income. One thing that is nagging at me though is the fact that the money gain really doesn't fit, it isn't enough of a benefit to warrant all the time and effort to establish this enterprise. The means does not make sense either, I still don't know what is really going on at the prison. I do know a hell of a lot more than the other reporters found out so far though. I'll need to try to use what I know to find the true means and motive behind this mystery, the very fact that the Raith's are involved lends itself well to the talisman I found in that prisoners cell. The Raith family, being white court vampires, would have the connections and the knowledge to assemble a scheme involving the supernatural like that.

I picked myself up and settled my bill pretty much right away, again being vampires they are much more aware of their surroundings and to the fact that I am entirely too interested in their conversation. I can learn more later, I made a very big leap forward in this story. I fired up tails on my laptop and sent to Joe the update via GPG E-Mail including photos and identities, sometimes multiple identities per person, of those involved that I seen so far. Joe is liking what I am telling him so far the implications could be far reaching. Now I need to think about where to go next in this.

What do I need? The true motive. I need a solid link to implicate the Raith's in this, and I need to identify the nature of the phenomenon at the prison, hard facts as to what is really happening there. Maybe it's time to start preparing for an infiltration, I'll need to gather intel on the location in general and identify what I really need to obtain from this place. I need to check to see if there is a possibility for an electronic approach as well. I have some skill but if this location is setup too impressively my means of obtaining information electronically may be limited. I need to try though because such information is a journalistic bazooka.

I head to the building the next day for some preliminary recon. It isn't in a retail location like the last place, and is surrounded by small industry and a Wendy's. I love Frostys and I'm not ashamed to say it. So no sitting at a coffeeshop in a mall and observing the location. It isn't busy though, there is a security guard in the front who does little more than take mental note of who comes and goes. Like a scarecrow behind a desk to keep out the vagrants. I easily entered into the location and found the bottom floor to be composed of a small inhouse cafe and variety store and different departments setup as different suites. The hallway is huge and people are filtering back and forth constantly between departments. My quick passage in and out of the location went unnoticed although if I had to come back I'll need to get a stack of file folders to juggle with a bagel and a coffee as that is what I'm seeing the most of here. There is a small hallway leading to the back to supply the cafe and access to the garbage and recycling in the back. Note to self the back door there is one way only. The parking lot in the back is a pretty decent size. There are stairs and elevators to the second floor of this two story building. The hallways on the second floor are a little more of a labyrinth. The offices of all the senior staff are here as well as the secretarial pool. I think I can safely plan multiple incursions here, based on what I've heard from the employees nobody seems to know anybody very well and nobody cares. The impression is strong enough I really don't need the sight to know. I'll come in here first to identify some key people if I can but mostly to identify other weaknesses of electronic and social structure. I'll take a look at the inside of the different departments and see basically what I can accomplish on my next turn in. I'm going to avoid the second floor for now it is much less chaotic making it a lot more dangerous for me to infiltrate.

So the day near closing I head to the back of the building and flip over the garbage bins. They are those huge plate steel bins with the plastic flip doors on the top. They do weigh hundreds of pounds if not a ton or more but I'm a strong girl and eat my sprouts every day so easy peasy. I gathered what I needed from the ground of the trash and recycling and flipped the bins back to their proper place for the sanitation truck to deal with in the morning. So I got a pile of unclassified documents to read through and use during my incursion as well as company pens and swag. A nice real leather company foundation briefcase was disposed of due to a broken clasp, so I'll fix that. I got some names and itineraries, that little trick gained me quite a lot actually. Even the IT team through a bunch of old scratch notes to the recycling rather than the shredder. I'm sure not on purpose, not like I haven't seen security incompetence before or anything. So now I have an incomplete network map and some passwords as well as physical locations of network equipment. Not bad. It has the credentials for the company top level DNS server. I fall on the ground laughing, anyone ever met the man in the middle?

The next day I filter through the different departments, they are all laid out the same. A small departmental mail desk at the front passing paperwork and packages in and out, entering all the actions taken into a workstation, shooting the shit and drinking coffee. In behind are permanently assigned cubicles and a couple offices on one side for the assistant manager and manager of the department. Two meeting rooms are on the other side of the room currently unoccupied. There are half a dozen stand up workstations for brief use by the employees. There is a login but I have a few employee logins from the paperwork I snatched. There is an actual IT department that is just as busy as the rest of the office. From what I gather the existing IT staff has built the in house system with sufficient complexity and lack of automation as to assure their job security. I setup a postfix server at my own virtual hosted machine and took a moment at the stand up kiosk here to login and change the DNS MX record to point there. Now all company E-Mail is being sent to my own server, recorded, and relayed back to the company E-Mail server for normal delivery. That right there folks is called man in the middle. I'm going to go check what I got in a few days to see how badly I nailed these guys.

I made use of those good old social engineering skills while I was there and it worked out very well indeed. I obtained a clandestine recorded record of some of these conversations they were so sweet. The employees know very well the Raith family run this enterprise. Apparently it was actually spearheaded by Madeline Raith but later adopted by the family through her father. I got the names of some other companies involved and the hint that there has been a new project underway for the last couple years to increase the market penetration of this group of companies products. The employees on the floor do not know much more than it's a government initiative and uses the appropriation of exclusive contracts in New York State. I asked how are we getting those contracts or is it the old fashioned song and dance of effective sales technique. Apparently the director in charge of the logistics department is operating the project and the nuts and bolts of it are run offsite and noone knows anything else about it. I checked in the logistics department but the staff didn't know any more than the others and there wasn't much more to be found. I walked my useless papers back and forth between departments all day long and snapped some quick photos of the odd documents that I took into the can and then placed back into the various departments they came from. I headed out of what seemed like the New York stock exchange at closing time and went back to my hotel to process the material I had obtained. It took me the better part of the week to organize the documents and learn how everything fit together. There were still pieces missing but I knew the road I needed to take to finish the puzzle. After a quick trip back at the end of the week to correct the MX record on that companies DNS server I logged into my cloud server and pulled down the email I had saved from the company. There was a risk of getting my IP address traced but within the white court I would put a couple notches on my respect for executing an excellent intrigue. As far as the mortal world goes the cloud server belongs to a ghost, registered under the name of a dead woman named Susan Rodriguez and paid through a bank account of the same name via cash deposit. A dead end to any real world investigation, unless the investigators knew enough to dredge the Times employee records to find me.

As I expected, critically classified E-Mail was being exchanged without encryption the same as most companies do it. It was an absolute goldmine of incriminating correspondence. All roads lead to Rome of course and the E-Mail interchange showed headers that tracked back to the Chicago area. Somewhere I really really don't want to go. I'm going to have to though, to identify the location of the Raith office and finish the story by getting photographic records identifying them and linking them definitively to the operation.

First things first, I need to go to the lab. According to the E-Mails they are using magnetic manipulation of brain wave patterns to attempt to illicit a permanent increase in sexual desire that will lead to the Raith group of companies reaping increased profits upon success of the venture. I think it's a clever ruse, they are up to something that involves the nevernever and likely phage in some way.

I check out the location and find it is in a heavy industry location and is a sizeable property. Neighbouring buildings have the same design and are completely open warehouses sending and receiving shipments via big rig. Observing the outside I seen a touch pad security lock and loitering near the gate I observed the numerical combination that was used to lock up. Odds are the same combination is used to open up and the next morning proved the point. That evening I used the combination to disable the alarm and passed through the door in mist form. With my vampiric sight the pitch black warehouse looked like twilight, and within 20 minutes I located the lights and flipped them on. This was magical not scientific, I have no fucking clue what in the hell is going on here. I take some camerav snaps of the equipment in an equal share of the magical and the mundane, the first for Phil to look at and tell me what's going on and the second for use with the Times article to show evidence of experimentation and confirm the scientific aspect of the operation alleged in the E-Mails I obtained. In the wee hours having scoured the location and finding what I could I passed through the door again and set the alarm. Then escaped into the night to organize the documentation I found and got it sent to Joe who at this point is losing his shit with excitement.

I postponed the trip to Chicago so I could get back to New York and identify what the Raiths are doing in California.

``What is all this Phil? What's the real motive here I know they're up to something but I can't put my finger on exactly what.''

``Fucking genius that's what Susan. There's one dangerous motherfucker that has a serious mind to change the balance of power in the vampire world.''

``Phil. Spill it.''

``A lot of the magical theory is similar to the rite of ascension you underwent, it looks like whoever it was learned something, which means whoever it is knows what happened at Chich\'{e}n Itz\'{a}.''

``Great. A big nasty who knows I got the juju.''

``Or at least knows that you came out a human vampiric crossbreed. This work is an attempt to allow the white vampires to spawn themselves in a manner similar to the red and black courts. We were correct for the most part the talisman is a spirit cage, they are obtaining compatible phage from the nevernever and caging them in talismans. Once a human touches the talisman with their skin the phage is transferred to them and is awakened in them in their first sexual act. Similar to the coming of age of white court vampires. The talisman concept is similar to a group of fallen angels I know called the denarians. The difference being once the talisman has transferred the phage to the host it can be discarded or reused but is of no further use to the victim.''

``The white court is gaining an interest in conquest.''

``They're looking to grow their numbers fast, for purposes known only to them.''

``As far as I'm concerned it's conquest. Whether the Raith are intending to utterly conquer their own court or are looking at world domination it's still conquest. Why else would someone build an army?''

``Something else to be considered. It's generally accepted by you and me that the Red Court enlisted the aid of a very powerful wizard to write the spell that bid you to rise back in power and majesty, not to flatter you or anything. They did it to gain favor with the court, it would seem, and likely gain favor from you. I don't know why they haven't approached you about it yet. I think there were other hands in the pie that day in Chich\'{e}n Itz\'{a}, people this wizard would rather not cross. I think he is trying again with the white court to make them indebted to him in exchange for victory over their enemies.''

``It sounds probable. I can't know until I can confirm it though. I'll head over to the Times for a debriefing of the mundane side of this. Then I need to head to Chicago to visit the address for the Raith enterprise mentioned in the E-Mail to put a bow on the package and complete the story.''

``Godspeed Susan.''

Time goes fast and in a couple days I'm off to Chicago. I called Father Forthill ahead of time to see if I could stay with him and catch up for the few days I was going to be there. He said it was OK but be careful to keep it under wraps about being there. I told him if someone does see me I'll go mist form faster than he can say pop, they'll think I was nothing but a memory. That would be fine by him. So I arrived with a litigation briefcase, you know the kind, a briefcase with wheels. I pour over the documents I have to determine a plan of action. The location is downtown in one of those office towers, unit 508. Lorriatt Enterprises. All I really want to do is get some verifiable evidence that the office location exists, and then if I can get some camerav verifiable media snaps of the location, the name on the door, maybe some paperwork at the location. I thought about it and rather than that I think I will actually get a video recording of the place showing the people there and other nice things. I craft together a fake pocket protector and clip it near my shirt collar so my well endowed rack doesn't force the camera to take a video of the ceiling. I finally build a harness that works well with a powersuit I pick up downtown and keeps the cell phone camera pretty level. I practise with it to get a sense of it's frame rate and the optimal position to hold paperwork to get a reasonable facsimile in the recording. I sent a secure email to Joe to detail the plan I'm considering executing and so far he likes it. They might try to make the Chicago office vanish like the wind and this should nail them to the wall. Preparation takes a whole week and I think the carpenters were at the parish four score and ten by the time the week was up. That is while I hid in the guest bedroom in the manse of course. Well, to be honest I did peek outside the window to see Maggie. She was flying on angel wings most of the time  when I seen her in front of the church. It's the supernatural hearing thing I caught every word. She said she is an angel princess flying on angel wings with mommie over New York city and all it's twinkling lights. My face went red, aw shucks. I love you too Maggie.

The day came to go to the Lorriatt Enterprises office. I timed it so that I arrived at about noon. I entered under the guise of an FBI investigator. I had the fake ID with my stuff from the Arcane that was sent to me a year ago after I had risen. As for the warrant I knew a guy in town that rolls immigration papers for illegal immigrants from across the border. It wasn't much of a problem for him to roll me up a warrant. I got pretty much all the significant paperwork on video. It was just a matter of flip flip flip. I had my litigation briefcase with me so I filed a fair amount that was stamped or sealed. Through the resources of the Times I had documents, especially those signed or sealed, tested at a forensic facility and then returned to the  Lorriatt office. The office manager took a moment with me and I explained we are investigating reports of organized crime locating an office front in the building but advised him that his office is in the clear. He breathed a sigh of relief, and shook my hand as he left. Well, job done.

Back at the manse I get myself all packed up and give father Forthill a hug before I leave. Father opens the door and bang there's Harry! Aw shit! Poof! I'm mist, and I float away on a breeze.

Harry said, ``Hells bells father did you just see Susan? Was someone just there!''
``No son, no-ones here I'm afraid. Do come in.''
``Give me a minute father, I think I just dropped something. I'll be in shortly.''
``Take your time son, it's a beautiful day today.''

I looked as he put his head in his hands for a couple minutes. When he looked up his eyes were red and filled with tears. As I floated away I heard him say, ``Pull yourself together Harry, she's gone, let her go.''\\

If I had eyes at that moment, I would have wept too.\\

I considered the way things are now, again, so that I understood well why I haven't gone to him to explain that I've returned with my spirit still intact. First thing he probably wouldn't believe me, or if he did he would never believe I was anything but a full red court vampire. Second, I have my own life now and I'm very happy. I'm where I want to be in my career, and have a chance to make a difference in the world both as a journalist and as a leader of the vampire courts. I can't re-enter a relationship with him all the way out here and he has his own place in the world right here and I don't think he would ever move. Third Maggie has an excellent home, more than I could ever give her, close to her daddy and her mommie plays with her every night in her dreams. She has both her parents in her life insomuch as it is possible. Lastly, although I know there are more reasons Harry lives his life on the edge, he walks on the edge of a sword and if he leans too far one way or the other he is sure to be killed. It would destroy me and Maggie both and I'm unwilling to go through that although I would be there for Maggie without hesitation. As father Forthill told me stay safe Susan, if the worst happens and Harry is gone at least Maggie will have one parent left in this world.

I fly back to New York city and played with Maggie in her dream world. Well I'm halfway there, just need to write up the story so I'm going to be commuting to the office for a while to get the story written up. It took me a week and a half working full days to get it all right. I passed it to Joe who worked it over and it was in the paper the next day.

You could hear the shit rolling all the way to the governors office. FBI investigations dug up even more than I did writing the story. Mass corruption in the Sing Sing administrative pool triggered a mass firing and replacement of the existing staff, as well as placing New York state department of corrections under investigation for fraud in general. The negative publicity destroyed Lorriatt Enterprises and a significant part of the Raith power base with it. Executives went on trial for crimes against humanity, although there still didn't exist any causal link in the smoking gun sense there was massive evidence in documentation and email transactions that destroyed them.

I just executed an earth shaking power move that crippled house Raith and cemented a high degree of respect for me from the entire white court. The white king himself along with his daughter Lara declared their intention to parley and we met at Kenworth's pub to negotiate a private allegiance to the empire. So the matter won't be public, and the white king will remain the white king because he has access to the resources of the empire to protect the position of his house.

A small note, in the white court members of the empire are called imperialists and I plan on using that for colloquial reference to members of the empire internally just because I think it's rather cool, and a good definitive way for us to identify ourselves and each other.

Although the white court wasn't present when I returned to my house, at the news a scourge returned with a small gathering of prey picked from the murderers, rapists, predatory pedophiles and other wonderful fellows who were present in the city. There was a great feast in celebration of the great victory and acquisition of a white court house into our glorious empire. I abstained from the blood-letting and joined Phil on the balcony that sits off the 2nd floor (due to a floor collapse) and observed the celebrations sharing a glass of wine with each other.





