\lettrine[lines=2,lraise=0]{W}e rose the next morning having fallen asleep on each other in a lump. We were exhausted just from the emotional toll of Unsere's visit. There was so much I didn't know and the truth was a mixed bag of hope and terror. There is a lot me and Steve will need to talk about once everything settles in properly. Steve's mom woke us up but didn't say much, either thinking I'm repentant living on God's mercy or considered that it looked like the two of us were hit with a strong dose of ether and just dropped hard where we were. Which was about as close to the truth as it gets.

Steve's dad is taking me out to the neighbours today, and Steve is going to try and shim up the longwire antenna for the shortwave radio. Televangelism will never die on the shortwave dial. After breakfast me and Steve's dad checked out the field. There are some footprints I do see. Human footprints, not heavy at all though they must be from a very frail person. They are coming from the wooded area, and seem to be migrating in a straight line.

``Peter whats out there?''

``It would be that huge farm where the migrant workers are.''

``Hmm. You said there were some gone missing?''

``Half a dozen maybe, just up and vanished.''

``How many reside out there?''

``It's a tent city, about 10 men there altogether.''

``How long has it been since the men went missing?''

``About a month. Everyone is assuming they took off to get illegal papers, not thinking anything 9f it really.''

``Ok well these prints go to and from that direction. When did the last man go missing?''

``Three weeks.''

``Whats happened in three weeks, and rain, wind, anything that would remove these prints.''

``We had a downpour a week back, these prints should in no way be here now if it was one of those men Susan assuming he really did take off.''

``What kind of footwear do they have?''

``Construction boots, the family that owns the farm just wears sneakers.''

``They don't do the same kind of work?''

``Well leave the heavy stuff for the paid help I guess, it's what their paid for.''

``Reasonable enough I guess, they get a decent wage?''

He raises an eyebrow at me.

``Right, migrant workers in a tent. Needing more coffee.''

``I'll put some on when we get back.''

``OK so these tracks are consistent with work boots so may be a migrant worker. the workers may not be forthcoming if their own are helping them forge papers to get out. This would be the logical solution. Nonetheless until I see with my own eyes I won't presume. What is there in that tree lot?''

``Well it's about a mile or two in circumference but more of a rectangle. Just young growth in there, from maybe the past hundred years or so. It used to be a farm before the owner vanished.''

``Fascinating, just like these migrant workers?''

``In a sense yes, but there hadn't been any such disappearances in those hundred years.''

``Tell me about that farm, anything left of it?''

``Well the buildings still stand in there. Theres a small woodframe house standing attached to a horse shed. the barn is gone but the silo is there. There's an old mine that's been boarded up since before the farm even stood.''

``A mine? Good place to hide, and a house even better.''

``Not that house, it stands but with little of the roof left and most of the second floor collapsed.''

``Walls intact?''

``Well, yeah, it's ok otherwise.''

``Could provide shelter from wind and downpours, put up a tarp inside and it would be cozy enough.''

``anywhere in the wood should prove sufficient.''

``Not if all you have is a colorful tarp, you would stick out like a sore thumb. inside an abandoned house noone would see you unless they were on top of you.''

``Actually I didn't think of that.''

``It's a nice bright day, I say we check out the woods before we knock on doors.''

``We're going home for some coffee and breakfast first, we're going to need some nourishment. You like canadian bacon?''

``Do I ever! Anything that can be described as `bacon' is going to ring my bell.''

It's so nice to be able to still eat and enjoy normal food. Not everything has the etheric value I need but it still tastes so good. I'm glad for my life really, everything is like a dream. Whatever isn't does not seem to be effecting me terribly. I may be the great mother but I love my children so I don't really mind it much. Oddly it helps me express a nurturing side and reinforces a sense of my leadership competency that is important to my worldly success. Things are really coming together well for me. I just wish the kids didn't smell so bad. They need embombing when they are young it would help so much. Working on it.

``Well, we should head out soon.''

``Let's head out now while the light is good. If we time it right it is going to be high noon while we are exploring out there so lots of light to see what we are doing. Susan, I just feel like it may be some ungodly creature we find and it is best to be found in the light of day.''

``I agree. Let's go.''

So we head out, it doesn't take us long to get to where we are going, and first stop is the old homestead. Peter was right, although it looked in good shape from a distance once you got to it the other side had collapsed making it look like a barbie house I played with when I was a little girl. Most of the second floor was gone the remaining sagged precariously. The third floor was completely bowed with rotting floorboard. Graffiti covered the structure since time long forgotten. The wagon shelter was cool, open on two sides horse drawn wagons could enter on one side to be tied up then exit on the other side just going right through. I guess horses don't like backing up and the drivers don't like backing them up any less. Checking the ground were the same boot tracks we seen earlier, plus drag marks as if someone was knocked out cold and whoever it was couldn't be bothered to carry them any longer. After we past the dusty dirt, or possibly concrete with dirt on top, floor the prints disappear into the brush of the wood.

I say,  ``Let me guess, that is the direction of the cave.''

``That would be accurate. About half a mile in that direction.''

``That's a pretty sizeable wood Peter, The owners must have had quite a chunk of property here.''

``Hundreds of acres at least. The thing is though the further you go back the cheaper and more plentiful land was. It wasn't that hard to own quite a piece of land back then.''

``I can understand that. It wasn't until land became more scarce the plots became smaller and more costly. People had to do more with less. I learned a little about it as a reporter. When I was in central and south America there were some huge plots of land, though many had to make do with less.''

``What were you doing in in that area Susan?''

``Looking for a story I guess you could say. There was a war happening and it was hellish down there.''

``There's always a war happening in these foreign places. I don't know what people have to fight about.''

``In this case people were fighting for their lives against monsters that liked nothing better than to kill.''

``Granted, but why would these monstrous people want to kill in the first place?'''

``I agree with that. If only I had and answer for why they came to be Peter.''

``The influence of the devil is why. The destroyer aways seeks to have us kill each other.''

``That's as good an answer as any I say Peter. I don't always agree to the devil's influence but in this case it's likely the best answer I'm going to find. So amen brother, well spoken.''

We chat as we carry on towards the cave. We quiet down as we approach. The opening is placed into a small hill in midst of the wood.

``You said they mined here Peter?''

``That's right Susan, coal. I expect there is likely quite a bit more in there but as it was part of the farm, and it's owned by the kids, it's been unworked since the days the farm has fallen out of use. Sadly the kids have been in a legal dispute for years which is why the land has been sitting in such disuse for such a long time.''

``Sounds like so many other inheritances Peter, all locked up in greed.''

``We are such the fools to be caught up in such godlessness, if only people had the wisdom to know what they are doing.''



