\lettrine[lines=2,lraise=0]{S}teve wanted to go down for me to meet his folks. I think it might be a little soon but he says no they'll love me. He warns me that they're very devout Southern Baptists so I have to be on my best behaviour. I say, ``Christ Steve how's this gonna work? Tell them I only eat catholics?''

``Probably best to keep the vampire identity under your hat. Remember it's not like I'm innocent either.''

``Well...''

``Trust me, it wouldn't matter to them who we eat even if it's just that we eat each other when we fuck. Think about it Susan.''

``Point taken, but the teeth?''

``Uncle Remy had grossly enlarged canines. He was born that way. I've been chatting with them ahead of time just in case. They think you're completely normal. If I didn't know better I would think you were completely normal.''

``Well shit thanks. I'll see if I can trade off the story the Times has me on for something in the south and maybe we can work it in.''

``Sounds great!''

``Steve do they have ten thousand crosses, I'm allergic.''

``One or two in each room.''

``That I think I can handle.''

``Good start then. Lets see what we can do.''

``Your uncle had fangs?''

``Yup, the congregation wanted to put him out for being in league with the devil but my family worked hard to keep him in the church. There's still rumors that goes around twenty years later though.''

``Jesus, nice place.''

``nothing perfect, and don't forget to watch the language there.''

``Oh right. Gee, nice place.''

``Better.''

So I trade off a story for one about southern states and the modern day satanic-panic phenomenon. Actually sparks my interest anyway I'm glad to make the trade. Steve's family would be a good source too by the sounds of it. I'll bring my Daemonic paraphenalia along with my knitting and such one for a good impression and the other to find the paranoid southerners. Well, and to be closer to Eury that helps.

Eury comes over the night before the trip. We are driving down in Steve's Caddy. We both make really good money and have some nice things but we also live simply and save most of it. Me and Phil try and support our own house, the black court scourge, which puts some use to it. Steve just puts it in the bank and invests in things he uses for travelling which has been his life. He wants to settle down into private practice in New York though so we can be together. I love him for that.

``Let me pass on some rites to protect you down there Susan, first off is the rite for the blessing of water. It's unholy water you can use for healing and protection.''

``Well fucking eh, unholy water? Seriously?''

``yes quite. created by the blessing of the d\ae mon of water.''

``Who is this d\ae mon of water?''

``Don't be upset, his name is in the bible but it gets slandered a bit. Well, a lot. Used as one of many as a representation of worldly evil. Leviathan.''

``Jesus fucking christ on a stick the d\ae mon of water is the fucking chaos dragon? Jesus, Mary and Joseph that's troubling Eury.''

``Don't be troubled, you've known me for a little while now and he's my brother and yours too. He looks a little goth if you ever meet him and he's ambiguous by nature so you may meet and work with his feminine aspect instead it's all according to how your soul resonates with him.''

``Weird, but I trust you Eury. You, Balberith and Babeal have been good to me and we fought together.''

``That's true, there are other names you know as well who you haven't met. Lucifer is the d\ae mon governing air, he is not satan like the bible has referred to him. He has been an ancient light god and that is what the name translates to. The bringer of light. He brings wisdom too.''

``What about Satan?''

``Whose name translates to adversary. There is quite the history there. There is a satan that is our emperor, the ruler of all that is, but he channels energy from ``The All'' to sustain creation. depending on how your spirituality developed The All could be an unintelligent energy, an intelligent spirit like the spirit everywhere of the native peoples or just simply the Christian God. A basic understanding of him is that he is representative of the left hand path and so the lawful adversary of the right hand path. The right often uses him as a scapegoat because his ways lead followers of the right hand path astray of their path to salvation. the opposite is true as well.''

``I don't think the concept of Satan serving God is a sane one.''

``Look at the dialogue of Job which is fairly accurate compared to the the figurative representation of the new testament.  There's a startling difference.''

``It still sounds like I'm allied with hell, satan, and all his minions.''

``Some of our followers don't even have satan in their hierarchy at all, and just work with us d\ae mons. Everyone follows their own path in life each of which is very different from the other. There is only one road to a happy afterlife, you either walk on the left or the right.''

``What are the core things about the left?''

``Well let's compare, know that left hand path exists in all religions really just often in obsure more hidden traditions, Buddhism, hindu, muslem, and so on. release attachment to the things of this world by indulging and making them boring rather than on the right which uses avoidance. Break every social norm and taboo possible for the same reason. Know that you are a God from birth and perfect yourself through faith and sorcery versus we are made in Gods image and acting accordingly, both different views of the same road. It is a path of the self which means self worship, we love ourselves for who we are. The great work in life is to come to union with our higher self sometimes called the holy guardian angel and that is to be made perfect and whole and fully developed in our Godhood versus seeking union with God, the path to finding the holy guardian angel is to seek and gain personal power. Everyone seeks to find enlightenment and prepare for the life to come those are some of the ways it's done on the left hand path.''

``I think I kind of get the idea, I've never been big on religion and philosophy stuff so I can go with that.''

``The faith is no different than you've been doing except to you we demonstrate theophany which kind of negates the faith aspect. Anyone can believe in something they see and know by their senses, like a kitchen table, it's existence is obvious.''

``Eury who are you guys really, I've known you long enough to accept you for who you are and I want to know my brothers and sisters better.''

``Well your earthly d\ae monolaters are scattered and few. Those few that have the numbers form covens like witches otherwise most our followers follow down through family lines.''

``You guys then?''

``We are the first ones. The first Gods to come to be after the passing of the old ones. D\ae mon means replete with wisdom. My sister, the old ones were the darkness and we were born in the coming of the light. The Gods who are ancient only represent us, such as the Gods of life and death, or sea, or sky.''

He continues, ``Among the D\ae mons there are many. We are the death and life, light and darkness and wisdom and life of the world. We are healing, harm, hate, lust and love. These are not things we hold influence over. Please understand that we do not represent these but that we are these things. Do you understand?''

``So the D\ae mon of the sea, since he in truth is the sea, without him there would be no sea?''

``Exactly. Then for me, Balberith and Babeal we are death, dying and the grave respectively. Balberith has been popularized as the grim reaper as of late but his place is to guide souls in their journey not to reap them.''

I felt, and probably looked, like I just seen someone punch a baby.

``Yes Susan you fought along side of us. You fought as a champion of death but you did not know it.''

``I don't get it, you guys have been nothing but sweet and caring to me.''

``Right, that's who we really are, the way death is. We are all very kind and look to embrace and comfort those who suffer loss, and bring loving guidance to those who have passed and are confused and frightened in the face of something they don't know. Death is not an evil Susan, it is part of the natural life cycle. It exists alongside birth and parenthood. As death incarnate our influence is often corrupted in the world by those who wish to control the life cycle. The vampires take but do not return as they are immortal and disrupt the natural flow of the life cycle. It hurts us Susan when the natural balance is broken. For the three of us we hope you will continue to fight with us to keep your immortal children from harming the natural world. If they are born, and they eat, they also must die to release the energy back to the mortal world's lifecycle. If they wish to live forever may they live upon the nevernever there is no place for permanence here. You are our hope to preserve the cycle of life Susan.''

``Good Lord Eury, I can't say I follow exactly what you said but it sounds like you are asking me to preserve a balance in the human vampire dichotomy.''

``That's exactly it. Don't let there be many millenia of feedings of one vampire death should visit them also so the life cycle isn't harmed.''

``So basically do what I'm doing, cull our numbers, manage our spawning, protect the prey and don't overfeed.''

``Bang on Susan, you're keeping the balance like we knew you would.''

I picked up a little reading on psychology to learn more about what Steve was referring to the other day, his INTJ personality type. I got a lot of Jung which I always thought was some chinese guy but actually he was European. I kinda feel like a ditz.

\parasep

On the road trip down I started wondering about myself again. about the likelihood of having experienced the fusion of my soul to a vampiric body. I just don't think it was an unintentional event. I love Eury to pieces but I think all in all I may misunderstand him or he may may just simply not be entirely correct. Like some part of what he says is not within his competence. What does death have to do with fertility? Oh sure it's part of the mortal life cycle I know that and maybe there is a little crossover but really I wouldn't expect Eury to know much about that field of expertise he isn't God with a capital `G'.

I'm thinking too about the first ones, Eury and his ilk, the first of all ancient gods. Would they have more power than earth and the nevernever combined? I mean really earth and the nevernever both have air, water, earth and fire. The nevernever has all the things that might be expected on earth so the authority of the first ones would naturally extend throughout the whole of the nevernever right? I mean of course God himself is king and all that shit but I think Eury and all his brothers and sisters sure must have a lot of juju. I'm glad they are in my life to guide me in the power that has been given to me, I need their experience and wisdom. For that matter while we're on the subject who are the great old ones? Eury has mentioned them and they seem to be epic bad news. It's just that me being what I am I will likely come to face them in some way and it would be nice some day soon to learn about them so I'm ready when that day does come.

Not that I'm looking to pick a fight, there is wisdom in the words that say no matter how strong you are there is always someone stronger out there. I think that little piece of advice is what I consider when I'm looking at doing superhero stuff. Like I said to, I think it was Jose, I bring big change in the world just by being a journalist. I don't need superpowers to topple corruption and end atrocities.

We took one break on the drive down for gas, food, and to switch from him to me driving. Another 4 hours or so we're going to pull into a motel for the night. We're probably going to be to tired to party though road trips can be exhausting. I still enjoy the time with him though we chat it up a bit on the way and I had time to read. Eury told me a good book o grow spiritually is called the hermetica. So I got a copy but personally I find it a hard read.

So we pull into Roanoake for the night and we are pretty beat. Neither one of us feels relaxed and our muscles are pulled tight as a fiddle. I mean like there are always some reservations in meeting the family-in-law for the first time but bringing home a vampire is a little difficult. Presuming a person is going to believe the fact that you're a vampire there is a certain stigma associated with meeting someone higher up on the food chain than you are. Of meeting a creature that really should not be. Something that for all your worldly wisdom is beyond comprehension.

So that night I didn't sleep at all, I just meditated. For the first time I seen Steve not able to sleep at all either. Well maybe two or three hours but that's all. He read, watched TV, hacked away at his laptop, basically just burning time until morning in frustration.

The next day I offered to drive the rest of the way but Steve absolutely refused to. He was determined that we will share the driving. I don't really need sleep and I said to him, ``Come on Steve I can run on no rest at all. I'm fine to drive you're not.''

``Susan we need to be partners, it would be easy for me just to let you do everything you have been greatly gifted in many ways but that doesn't make for a good partnership. Yes I'm tired but let me be tired. I'll drive this leg of the journey if you keep me occupied or just keep talking to keep me alert that's all I would ask of you.''

``Ok, deal. If you drive off on the shoulder of the road though I'm taking over no argument.''

``Ok, I can agree to that too. So let's get going it's another days journey to get to my parents place.''

So that was the end of it. He had a satellite radio so we switched off the music to go to talk radio and we just talked and, God help us, argued for quite a bit of the trip. At some point during his leg of the trip I brought up the personality type reading I've been doing.

``So you said you were INTJ Steve?''

``Yeah, why do you ask?''

``Oh I've just been reading up on the psychology of the thing. I mean, I'm not the brightest bulb on the subject but I also went to forums and it looks fascinating, and very painful.''

``Uh, painful? How?''

``Well, the social difficulties, inability to navigate or engage in smalltalk, that stuff.''

``Ungh, agreed. I spent years blaming myself for inadequacies in that area. The impact on my social life in general not the least of which finding a romantic partner has been horrific.''

``I know, you've been pretty open about your struggles. You've been spitting distance from having ass burgers.''

``Uh, Susan, that's not exactly the pronunciation.''

``You'll have to give me a break there Steve, I don't know psych well and that's the only way I can remember the condition.''

Steve chuckles, ``I can see you're point there.''

``So then, I've been thinking about how I can help you heal over that rocky past because I've seen how much you hurt when you're reminded of other peoples normal social and romantic experiences. Especially in the casual encounter area. Not a big deal I can understand that I've just been lucky is all my social capacity has been good.''

Steve is starting to turn red, ``Look Susan enough, I don't need to know about anybodies awesome experiences or skills in `the game'. I'm not ever going to have the life that includes romantic partners outside of what few decide to pick me up and take me home. As far as I'm concerned that's you and maybe a couple of batshit crazy psychos. I've just been lucky I didn't get stuck with some plain jane broad that borders on asexuality. I've just got to accept my life as it is and thank God almighty I have you in my life and I'm finally out of the single life permanently. I hated being single even from high school, I never met anyone or had any enjoyment of it but rather incessant loneliness and misery. I just wish you were around when I was leaving high school I could have done much better in my studies without the constant romantic preoccupation.''

``Steve if I was there with you going into college I don't think you would have done better in your studies. I remember how I was at that age.''

``Goddammit Susan that's what I'm talking about. I was sitting alone while you were enjoying your life meeting guys and getting laid. The fact that it's generally assumed all young guys want to do is fuck would seem to deliver you with every opportunity in the world as it would for any young girl who wants to get laid.''

``Well if I went down that road I'd have some kind of reputation Steve, there would be little chance of having a decent relationship in college if I'm the campus cum bucket.''

Steve is rather angry right now, not at me, but just at the way his life turned out romantically. I know why now and like I mentioned I feel bad but as awful as he is socially that particular personality type is also called the 'mastermind'. Steve is a borderline genius, his mind works in powerfully logical ways and anything related to learning he picks up like a computer. He self-taught himself college material that in theory might have given him a bachelors degree in whatever given subject by default. He took final exams he obtained once and scored better than the average college student from self study alone. Like Christ Steve smart much?

``So anyway Steve this is how I'm going to work it out. I'm not going to let you quietly suffer and I would like to have you consider our relationship as a good match for it's own sake and not divine salvation from the horrors of the single life. Not when you're coming from where you are. So here's what I'm arranging. I found a sex club named `freedom manor' that we're going to go to. You can have a chance for free sexual expression there to heal old wounds and we can come at our relationship from a more balanced perspective. It's a really nice place, an actual edwardian mansion converted to a spa with a year round warm as bath water pool with toys like water noodles, beach balls and super soaker water guns. Seriously, they have water guns. They have a sauna, hot tub, showers and bar. There's large playrooms, it's safe and there are love gloves everywhere. It's got normal lighting, modern rock music playing at a sane volume, open all day and well into the night. I'm planning for us to go out on a Thursday night soon there's going to be an evening of spank and tickle school, as well as games for prizes like lick the melon and suck the banana. Oh and naked twister. You'll like naked twister.''

``Jesus fucking Christ Susan! I know you're trying to keep me awake but fuck me gently woman!''

``You bet I will sexy.''

``Ah hell, I'm not gonna win am I?''

``No you're not. I'm gonna get you laid so much you'll be walking like John Wayne, then we can look each other in the eye and build a solid relationship together without you feeling like I'm an escape from a life you hate. It just isn't a good foundation to build from.''

``Bloody hell Susan.''

``Same to you sweetie.''

``The problem is I'm never approached. I'm really not that good looking.''

``I read the material Steve, you've been approached, you just didn't pick up on the non-verbal cues. You don't have that instinct. I know that pretty clearly Steve you look like a god-damned movie star, like a sexier version of Matthew Mcconaughey. You got the looks Steve you need somewhere safe with the greatest opportunity. It will happen, trust me.''

``I seriously doubt that, you look like a sexier version of Rosario Dawson you could pull down serious booty if you wanted.''

``Don't want it. I've had that time in my life when I was younger I just want a good man and a good solid relationship now. It's your time for booty and if I have to drag you kicking and screaming I'm gonna get you some. Rosario Dawson huh? Well aren't we the rich and sexy match made for Hollywood.''

``You betcha.''

\parasep

Well Steve took over driving near Atlanta as his folks actually live in a rural area just outside of there. It was easier that way rather than him telling me to turn here or there or what did you go there for. You know the drill, relationships. It was like a rerun of the movie sweet home Alabama they were back country folk and there was definitely a cross in every room and bible verses on plaques mounted on the walls. They had brother Stair playing on the radio and I don't see a TV in any of the rooms in the house. There are the odd bookshelves which look like an evangelical theologians dream come true. I did find an awkward comfort in the floral print wallpaper, doilies, knitting basket and hand knitted items in the house. His dad was here, Peter. His mom, Mary, is due back tonight as she's picking raspberries on the fence-line behind the property. His dad said leave her be she has always needed alone time and picking berries is something he knows represents that alone time for her.

So I pick out my knitting supplies and sit down in a rocking chair. I'm working on an afghan for myself and I figured it was as good a time as any to get ahead on it. I'm wearing a vintage ankle length dress with floral print. Basically I have the spinster look. I wasn't sure what to expect so I decided to make a nod towards Amish fashion then turn it up a notch later. Steve's dad looked at me, then looked at him, and said in a very clear voice, ``This ones a heck of a lot better Steve, where'd you pick her up?''

I made a chuckle which his dad took as being coy but I was actually thinking of the conversation on the way in.

``You don't want to know dad''

``Oh, she doesn't look like the type. She looks rather wholesome in fact. I guess one can't really tell now a days but she still is a heck of a lot better than you're past entanglements.''

``There's no need bringing up the past dad it's all water under the bridge, I've moved on and found better.''

``I'm glad you learn from your mistakes son.''

``Enough dad, how are you and mom doing?''

``We all are fending ok here, nothing changes and that's the way we likes it.''

``I know, stable and God-fearing makes for a good home.''

``Darn right son. Darn right.''

``Fishing been good?''

``Haven't hardly caught a blessed thing this year boy, been a bad year for that.''

``That's too bad. What's going on around?''

``Been something out in them fields around here the last few weeks. I think it's the work of the devil out there but I can't prove it. It comes at night and smells like death out there. Ain't bothered nobody as of yet 'cept some mexican workers gone missing. No offence to you Ma'am.''

``None taken, I'm American born in New York city so I'm really not Mexican by any stretch of the imagination.''

``Ah, a yank born and raised. I won't hold it against you. Pay no mind to the colors of the south in 'ere.''

I notice that indeed there is a very prominent confederate flag mounted on one wall in the room.

``We all are proud southerners miss, and God-fearing folk to boot. We all are good people so don't you worry your pretty little head about nothing here. I promise you a safe stay on my word.''

``Thank you sir, it does ease my mind.''

``Steve your girl surely does have some fine canines. We all miss your uncle Remy he was a good and faithful servant to the Lord. I have no doubt the Lord Jesus took him on into his glory, no I have no doubt at all he was a good man.''

Steve's people are definitely all about Jesus, but the house isn't adorned with crosses like wallpaper so really, I do feel safe here. People of faith can be good people if they live true to what they believe, sadly so often they lead themselves into hypocrisy and persecutory beliefs.

I blurt, ``They're good with steak.''

Steve's dad lets out a hearty belly laugh, ``I'll bet they would be miss, makes me jealous 'cause I love steak. It's by far me favourite food.''

I let out a chuckle.

Mary walks in through the back porch, ``Have you seen our boy and his new girl yet Peter? I hope this one's better than the others he brought home. They all needed Jesus the whole lot of them.''

``They're here now Mary, You're gonna like this one she's a might Godly in her dress and deportment love.''

Mary came in and looked at me. She must like me because I rarely saw such a smile and glow come from a potential in-law before. I'm adored here.

``Knitting an afghan I see dear. Have you been practising for very long?''

``Only for the past year or so. Something drew me to taking it up.''

``Wisdom and maturity I imagine. It is a very calming and meditative thing for me, helps me ponder Godly wonders it does.''

``It certainly is something to help one clear the mind, I agree on that.''

Mary sits down in the lounge chair beside me. Her dress is strikingly similar to my own. The floral pattern is different but the style of the dress is indistinguishable. She's knitting a sweater and she picks up her work and starts in on it.

Steve's dad pipes up, ``Look at that son, I never could have imagined. The good Lord Jesus guided your eye to find this one. His mercy is endless, perhaps you have found your way out of your ungodly fornication and will settle down. You've been too long on the prowl son and the Lord seeks to share his mercy with you.''

I couldn't stop the laughter that threatened to erupt in me so I clasped my hands to my mouth, bent over, and fought with every part of me to smother the howling laughter that threatened to explode into the room. Once I got myself under control I came back up, wiped the tears from my eyes and resumed my knitting.

``Oh my God dear, Peter you pig you offended this young lady terribly. She doesn't need to hear such things about her suitor.''

``Oh I do apologize miss I forget myself. You needn't hear such vulgar things said of our boy. I am deeply ashamed of my behaviour.''

``Thank you, you're right I, uh, reacted to your words. I am of a timid sort. You said something about a foul thing in the fields earlier?''

``Yes, oh I did hear you were a journalist of course you would be interested in the mysterious. It's been every two or three days the animals howl and make a terrible racket and I for one can see some thing that looks like a person in the field out there. It's there one minute the gone the next. It's always the same, the animals get upset and most of the time if I watch long enough it appears. Sometimes it takes hours but it will be there. I do go tend to the animals as I really don't know what may be happening and I surely cannot afford to lose livestock.''

``Have you ever gone out into the field to investigate.''

``I have reason to go out to meet the devil himself, well enough I should be sure my family and possessions are safe and I return to the safety of the house to let it pass. We have a good home and Christ in our hearts no evil would dare pass our threshold the Lord protects us here.''

``What about your neighbours, you suggested they have similar troubles?''

``Yes, the neighbours to either side plus pretty well everyone one the sideroad over there beyond our land. People on the other side of the woodlot tell of trouble as well.''

``I'm going to go talk to these people over the next couple days then to find out what they know.''

``I had better take some time to tell you about them. A lot of the ones around me I am on good terms with and as a matter of fact play cards with on the weekend. Perhaps I may ask if I can bring you in on the next game you may learn more about what's happening. Also there are certain neighbours you want to be careful of or avoid. Be careful of the hermit there, he greets visitors with a shotgun and has been known to make use of it. There are 2 spinsters one is known to be a witch it may be one to avoid and the other one is mad, she is known to have kidnapped a man and the sherriff only found his remains years after his death laying on her couch. Even so she is still living there. The other ones to be careful of are extremists in the faith, they think we all are devils especially due to poor old Remy. They see you and you might come back with buckshot up you skirt.''

``Thanks for the warning. I'll let you map these places out for me tomorrow.''

``That's no trouble at all Susan, I keep a topographical map here of the area that should work perfectly.''

\parasep

Well me and Steve are settling in for the night. We are both exhausted, all the lost sleep and nerves are catching up with us. I do my meditation with a handful of fallen leaves for the balancing circle. I don't want to leave something odd on the carpet and have to explain what's happening. Steve just got out of the shower and I went in first. So as I'm meditating he got dressed in his room and shuffles in with a book. Yes, his parents insisted that we have our own rooms to avoid the temptation to Godless behaviour. It's ok I expected that from religious people in their own home. As he settles in with the book I feel the steam from his shower on my skin. He is out of the shower sitting here though and the shower is down the other end of the hall. I open my eyes and there is mist all around me.

``Steve do you see that mist?''

``Uh, sorry I was reading, yeah what is that Susan is it smoke?''

``No it is mist, I can feel the wet warmth of it, there's no smell.''

The mist coalesces into the form of a person, and she walks out. She looks kind of irish, with pale skin and long silky brown hair with streaks of silver. Her eyes are as deep and green as the plains of Ireland. She is giving off an energy I can't see, but feels gentle and nurturing. She is wearing a brilliant white cloak with a cowl like what you might think a druid might wear.

She speaks, ``I an Unsere, the d\ae mon of fertility and sorcery. I am that very life force that brings forth new life and powers the modern magic of all known realms. You were asking for greater knowledge and understanding of yourself?''

``Ah, Eury sent you. Thanks for coming.''

``Eury?''

``Oh, er, Euronymous.''

``I see you two are close, perhaps someday he may be your counterpart d\ae mon.''

``When I know what that is I'll consider it.''

``Yes granted you are young to our ways be patient sister, you have all the time in the world.''

``Your were saying then?''

``Thank you, yes it is rather complicated and your Eury knows only part and I too know only some. The first thing is you are a fusion of the human and vampiric though I think you probably know that.''

``Right yes, know that.''

``OK, so the vampire soul and your human soul together form a whole and your vampiric counterpart expresses itself through your subconscious unless it chooses to manifest.''

My blood, figuratively or otherwise, just turned to ice, ``Whoa, you mean my vampiric mind is influencing my human soul right? Please say I'm right?''

``Uh oh. Eury seems to have missed something. No dear you are whole body mind and spirit human and vampire coexistent.''

I literally felt something roll over in the depths of me. Swear to fuck just get up and roll over right inside my psyche.

``Oh God, it's alive, sweet Jesus say it ain't so that thing has life in me. Oh God please get it out, don't let me be like this...''

Unsere grabbed me quickly and held me for quite a while. Steve came in beside me to lend support. I started settling down after a while and Unsere continued still remaining close to me in case I needed her.

She continued, ``I think I had better bring this together with an example so you can understand me better. I feel it in both of you that you are mates and have mated often yes?''

``I only answer as it may help you help me. Yes we mate quite often.''

``Ok and I can see that fertile energy in your counterpart vampire soul as well, which means she has taken part in mating with Steve.''

``How in the fuck do you figure that? With none of my senses was I aware of any vampire with us and Steve didn't get eaten alive I would have noticed that.''

``Aw but he must have, you pulled something from him. He doesn't show any loss of life energy but it was still drawn from him, and giving back. Exchanged.''

``Right, but no vampire would give it back, and the vampire was red court. I remember the exchange of energies but it was precisely that energy. I was red court infected the red court drinks blood.''

``I think you may be making excuses at the moment. I understand your point but a jersey cow is no less a cow than  a holstein. You are the great mother of the vampires and have been sought out by the black court despite there being no red court left. It isn't about the court, by now you should see that.''

I felt a little defeated. I always hoped that eith the death of the red court none would follow me and I could return to my normal life wihen all this great mother controversy went away with the remaining courts. I guess I was in denial, but who can blame me? I've always wanted this to be over. Yes I've done something important in my life in fighting with the fellowship I wont deny that and I'll always be proud. It's just that every soldier at some point is going to get tired of war and wants to return to the peace. I do. I feel like Churchill if at some point in the war the nazi's suddenly declared him Furor and waited on his command. How does this all make any sense? Not that I don't understand the theory as much as I don't understand why me. I mutter, ``It's just hard Unsere, that's all.''

``Well snap out of it Susan, you are a very courageous woman and you have more than enough grit to handle this. Just get over yourself and do what needs to be done. You have your life back, you also have other responsibilities. ''

``You're right, I've been doing a  lot of whining. I want to get back to a life before I was infected and now I have that plus a lot more in every way. I can lead, I don't know how to lead this many but I am doing ok so far and I'm learning.''

``Exactly, I shudder to think if someone who wanted to lead such a dark and terrible force were to take power.''

``I get it, you're right. I remember what Eury said too that I keep the natural balance. I understand, I've had enough time.''

``Good, I'll continue then fussy britches. So you normally present yourself, unintentionally, with a human spirit and a vampire body. That's your normal state of being. If you desire something that is within the competance of the vampiric soul or human body then part or all of it is brought forth to execute it's function. It is not coersion. In your sexual act the human body emerged in response to you desire to mate with the human. It is the most pleasing way to submit to the act. In addition you desired to express your whole self as a person including the vampiric so your counterpart soul came out to execute the steps to make it possible, as well as to engage in the sexual act with you giving the feedback you needed to feel complete in your sexual expression. That was the sense of it having been pleasing to all of you and the extent of the release you experienced.

She continues, ``Look, it's going to result in your having greater strength than you have ever known. you just have to make peace with yourself and with her. You have the capacity to reproduce pure human offspring or hybrid, pure being human sexual act or hybrid the sexual act you and steve have explored, or any court vamp9re or fae you choose such as white which require sexual acts or the blacks where a successful feeding will do. I'll let you learn about these things.''

``What do you mean hybrid?''

``Think born infected with manageable hunger, like a hunger for junk food, feeding wont harm them they stay the same. powers are the same as an infected. steve would nurse it with his own blood until it could eat solid food.''

``Lovely. Want to make babies steve?''

``I'll have to think about that one.''

``So I'm heavy one whole full court vampire.''

``quite.''

``Wait, did you say fae?''

``I see in you a strong sidhe ancestry.''

``From where? Did tinkerbell fly up my ass on the alter of \chichenitza*?''

``Susan there are more mysteries yet to unfold in your life from the moment of your sacrifice at \chichenitza*. There were many hands in the pie that made you who you are today.''

``Amen sister.''


















