\chapter*{Prologue}
{Not everyone is a Dresden Files fan so not everyone is going to know who Susan is or what she's been through. This series is going to be an independent endeavour from the Dresden Files proper so once her background is explained here it will be easier to get into the following story. She was very much a main character in the first three books, then disappeared until death masks skipping a book. There were six books before she had a major role in changes only to die at the end by Harry's own hand. Her hopes ended.\\

So here goes:\\

Susan and Harry met when she arranged an interview on the opening of his business as a professional wizard in Chicago. It was a couple years before the Storm Front novel. She was a reporter for the Midwest Arcane at the time which was a supernatural version of today's tabloid with stories like ``JFK’s Mutant Ghost Abducts Shapeshifting Girl Scout.'' Little did people know from time to time the stories were real! Susan even went into syndication.

She had a tendancy to hound Harry for a good story although she had an ulterior romantic motive, and made no attempt to hide it. Of course her romantic expression served her well in getting information as well.

She is attractive, intelligent, funny and appealing. Her motivations are clear and simple, and she is honest in pursuing them. She is absolutely relentless. She has used her sexuality in pursuit of information. She is very aggressive and was the one to ask Harry to dinner not him. Susan took Harry out for their first date and treated him. She has a smile all her own, a patent smirk with her lips quirking up at the corners. Her hair is midnight black. She has dark eyes and a deeply tan complexion.

The first three books were completely Susan. She could easily have been the other primary protagonist as far as I was concerned.

In Storm Front she asked Harry out for dinner. Well, kinda tricked him into dinner in a playful way. She wants what and who she wants and works hard to get it. She and Harry ran into a demon they needed to combat. A toad creature. They did it but barely, Harry called down lightning on it and Susan was vomiting most of the time from potions Harry had her drink. The date turned out to be the worst night of Susan's life. As well as the best story she had written so far.

In Fool Moon, the second book in the series, her appearances gained speed until about half way through the book she took the drivers seat. Literally. Getting Harry out of the mess he got himself in as well as being the driver for him and those he needed her to drive for. Including some young werewolves. Susan saved the day in this novel and Harry was along for the ride.

In Grave Peril Harry was about to marry Susan though it wasn't apparent until near the end. They are still dating heavily and very serious. She had her first sight of vampires in this book, but not her last. Harry got an invitation to a ball by a local vampire that just got promoted to the nobility. Susan forged an invitation to get in with Harry. Harry had protection under the accords but she didn't because she was never really invited. This particular vampire held him accountable for the deaths of two people she loved. Vampires being what they are in the Dresden series she swore to dedicate her life to exacting vengeance against Harry in one way or another. She found a perfect way. She knew about him and Susan so she stole Susan away and ``turned'' her. Basically this ended their relationship because Susan was walking a tight rope from that point on, she hungered but if she ever fed she would complete her change and become something else. No more Susan. For now, denying her hunger, she could survive and live as a human but arousal, exhaustion, or the smell of blood, or a number of other things might cause her to lose it and make a kill then game over.

That was the last we seen Susan, she did not have a part in the next novel but in the following one she did reappear briefly. She had been fighting the vampires in South America and doing humanitarian aid to the residents there. South America was the heart of the Red Court Vampire territory, the world pretty much ignores what happens there and it had gotten really bad down there. They followed a high ranking vampire back to Chicago (where the novels take place). She gathered her belongings from the city to take back home and intervened against the plans of the vampires while there. Harry and Susan got to fight again and went to a ball together. They even had a dance together. Then she left to rejoin the fight in Central and South America.

It was seven novels of wondering what happened to Susan and when she was going to find the cure for her vampirism. In that final novel ``Changes'' she fights with Harry to save the daughter they had together (that he didn't even know existed). In the end of the novel Susan makes that first kill and begins to change. Their daughter was saved from being killed in a sacrifice and Susan was killed in her place.

That is where the Dresden files story ends and the Susan's Requiem story begins. Her life will never be the same.
}