\lettrine[lines=2,lraise=0]{I}\space made my way back in the morning to the tent I was sharing with my thralls. I didn't see any sign of Jane, nor did I seek her out. Things seemed ok. The general was waiting for me.

He said, ``The time has come for you to head north. We have a huey on the helipad and our teams patrolling north are in place now. Things are clear for the trip now but it has to happen now. You have a radio to call extraction among the gear that we placed in the chopper. You're going in alone, move your ass.''

I didn't have much more time than to say be safe to my thralls. I hope I'm not going to be too long I don't want them to get sick again.

Once I climbed into my chopper I had a vision of a small tent. A persons quarters, dresser, clothes, cooking area. It was so clear it was like I was there. Things were tossed about the tent. In my hand was a tissue. I am aware of where I am but also aware of this other location and it feels I'm here too. My eyes are full of tears. I'm not controlling my body in this other location, or it doesn't seem so, but I rise from sitting on a bed and see my reflection in the mirror. It's Jane. She is suffering a lot from her change. I tried to will her positive juju as they say, project the love I have for her as my firstborn. I see her looking around as if startled by something then the vision fades. I wonder what that was?

There is a sargeant flying with me that gives me a brief on the situation north. It's a report of a zombie outbreak. It's in an industrial area noone is going through at night anymore, even by car. Nobody seems to be infected by these creatures (lucky bastards) but the unfortunate souls that meet them are torn to shreds. Like need dental records for ID kind of torn up. The police are investigating but the department is small and overwhelmed, the case is just not moving anywhere and the supernatural overtones makes it even worse for priority. It's been going on a year and the community has nowhere to turn.

\parasep

We touch down and I'm sent to a Catholic parish, whose pastor has agreed to house me. His name is father Gomez. He is going to keep me with him in the rectory as he is a bit worried someone might lay a hand on me in this fairly rough neighbourhood. I'm worried I might lay my own hand too heavily on some poor thug so I too see the wisdom in being in a safe place. Father asked if we are under hire by Rome. 

He asked, ``You want to know more about the zombie trouble.''

I said, ``Read my mind I certainly do.''

So from what was said they seem to be concentrated in particular around a warehouse marked as being owned by ACME inc. Well hell I thought that was only from looney tunes I didn't think it was an actual company. Anyway whether that was the actual owner anymore is yet to be known. He showed me on the map that location and the locations of sightings and bodies. About a dozen all in all. I made light of the shameful fact this is a low priority for police and father made a sorrowful pose.

First stop town records. Lets see who owns that warehouse. Now if anyone has ever been to San Jose it is one of the most backward national capitals I know of. No transit system in place and the streets have no names. I haven't spent a lot of time here so other than taking flight to see where I'm going I had to accept A.J. along with me, who was father Gomez's suggestion as a guide. A.J. lived here all his life and works as a taxi driver. We travelled when he was off shift.

So it looks like the warehouse was owned by a company called ACME boot. Checking the microfiche around the time of purchase in the late 1950's to early '60s the company was heavily promoting the first western boot store in central America. It never got any traction, was repurchased by a real estate company for lease or resale but fell to the bank in repossession. Nothing since. So dead end nobody has really owned that building since the 60's. I need to do some on site investigating. If I can find a safe spot a stakeout would be best.

I see Jane again. I am her standing over her research desk with an empty mickey of whiskey in front of her. I hear her say, ``I can't even get drunk.'' she sits in her chair at her desk staring at the empty bottle. Then the vision fades.

I get A.J. to show me the route to that warehouse and drive me around it a little bit. It's got the crap beat out of it from years of not being used. The warehousing around it is not faring any better. It's the middle of the day so we decide to drive up. There are tire marks coming from the locked gate, looks like trucks. There is an old rusty chain and padlock on the ground cut off with bolt cutters. Somebody replaced the chain. The old padlock didn't seem in too bad shape so it seems to me someone either lost the key or just never had it to start with. I think we are dealing with trespassing unless the bank is doing something here. I seriously doubt it though this place looks like it's ownership documents went through a shredder. Inside looks like a Freddy Krueger film. There is blood everywhere, small body parts, deep scratches in the floors and walls. Some really solid looking steel tanks have deep indents in the forms of fists and steel girders have chunks bitten off them like they were taffy. Jesus, what the hell is going on in here? I look up and see an opening in the roof near a platform, maybe once used to oversee plant operations. I see signs where there has been people climbing up to this outpost recently, and often. Someone dropped a pen here, Monsantus Genetic Engineering LLC. MGEL for short I guess. Fascinating. There is some paperwork left behind also, it definitely looks like an engineers handiwork I can't make most of it out. What I can pick out are words like specimens, candidates, fit for deployment, unfit, weak. I just get the sense they are up to no good. I leap down the 50 feet and land quiet and graceful as a cat. I hear a crash outside. I find some urban camo bdu and through it on, and hit the floor with a KA-BAR in my teeth. Moving silently from stair to tank to drum I get to the nearest exit to where I heard the crash. I peer quickly and nobody. Sticking to the wall like I was part of it I move around the corner to see a cat in a garbage pail. ``reowww'' and it was gone. Handpalm. Good enough then. A.J. takes me back to the rectory.

So it's really not much good yet staking out the location the research comes first. If I stake it out too soon they may spook and take off to some location I don't know about. We have a company name, and some engineering documents. Let's start with the company first.

That night I relaxed for supper and tune in my radio. I updated my handler at the encampment and he thanked me for my work. That evening I borrowed fathers computer and booted tails. Let's see who this MGEL company is.

I found it. A biological engineering company working in the medical research field. Again fascinating. Was the mess in the warehouse something about medical waste or, sweet mercy, failed human experiments? It's got to be something that needed to take place in some remote warehouse so they are definitely trying to hide something. As if I didn't already know that. I also see that they have a research location downtown so that looks like a good place to hang out.

Just as I intended I go to the location and find the entrance has a guard and is using a biometric entry system. The employees are the usual nerds with pocket protectors. I have a camera in some clothes on the table to snap shots then bluetoothing them to the tablet. Using my superhuman ears I'm picking up names and information of employees as they enter and talk with the guard. I keep it up for a week and get quite a bit of intel, names, weekend activities, relationships, shift patterns, work area. Thank God for the outgoing and chatty guard he almost did the work for me.

I studied the available data of the employees. Now how to get in. I need to bring a laptop to gather network info but this first venture I think it best to map out the floorplan and other details. Yet again how to get in.

I have a good profile of the guard. The night guard is likely best. The one named Peter is scheduled off Monday and Thursday the poor bastard. I say I wait around until the guard goes for a piss then sneak behind someone as the guard saying I need to grab keys or something. Who is going to suspect the guard of a security breach. 

I remembered from when I was working in the research area with Spook there was some work with shapeshifting that resonated with me. I radioed back for him to see if I could manage to work the spell. I have innate magical abilities but that doesn't mean I suddenly have years of study behind me. After a couple days of frustration we found that I have an innate ability for shapeshifting. In the process I find a mistform which harkens back to my not so cherished days as an infected. God I'm so sorry Jane. After some practising I believed it's now or never.

I had a vision of Jane. She is working with one of the patients. She is trying to insert an IV. Despite the patient being strapped down the needle lacerated the patients neck. I feel intense hunger and see her moving to take the man, then I see she is running as fast as she can out of the tent. Then the vision fades.

I can shapeshift to Peter then and I guess it's just fast talking from there.

The day came and I was nervous as all hell. The moment came and I lucked out, Margo arrived while I posed as guard.

``Evening Margo how's Sparky is he feeling better?'', sparky is her pomeranian.

``Much better yes, he must have been eating something he shouldn't have thanks for asking''

``Oh shit I left my keyring inside.'' I slip behind her.

``Jesus Larry, Jacob will have your ass for that.''

``Who's gonna take it Marg, like really?''

``Jacob, so he can shove them up your ass''

``point taken.''

I enter and quickly assess the area I entered. A long hallway ahead and a small alcove immediately to the right for a security desk. I dive for the alcove and switch to Peter under the desk. I see a camera at the door and I'm hoping the exact coming and going of employees isn't tracked with it because security will be confused as hell.

So now I'm Peter. Time to wander.

Familiar faces in the labs. I've seen them enter and exit many times before at the front entrance. six labs on the left and a cafeteria to the right. Otherwise just one big long hall. Making note of who is in the labs for my next incursion. An elevator at the end of the hall. The second floor is empty, 9 to 5 people work here presumably. Assigned cubicles, I make note of the names the best I can. Nothing extraordinary here except computer access in privacy in the evening so bonus. I check out a workstation. Bios is locked and wont boot from cd. I expected that but it's still annoying. I'll need the laptop to clone the mac of the nic and hook up directly for a network mapping and recon of the network. That said I wonder where the IT offices are anyway?

Up to the third floor. Executive suites. Offices and conference rooms, secretarial pools where there are a couple people still working. At last the IT room. If I can get access to this area I'm in the game. Hmm, let's see. I try transitioning to the vampiric mist since there is nobody around and I get through the door no issue. Oh my God, morons. System passwords written down on all the equipment. Multiple Vpn tunnels for different department, connection information on a corkboard. A complete network map also. Good enough for now, I write it all down and take pictures then smoke my way out the door. Still nobody around. As i head toward the elevator the door opens, and I dive behind a wall. Oops. They would see my mist form, too far away to do a spidey thing and hang from the ceiling. I don't know enough about Peter to know if he is supposed to be on this floor. The guard! Why wouldn't a guard wander a facility if they think something isn't right.

``Hi Larry what are you up here for?''

``Somebody said they seen someone up here but I don't remember letting anyone in with access to this floor.''

``Shit. Maybe I'll grab that paperwork another night.''

``Could have been someone slipped in while I made water''

``Yeah could be, Or it could be Samantha she is always forgetting something. Most of these guys come in at the corporate entrance opposite Mindy's cafe''

``Yeah but not at 11 oclock at night.''

``Agreed. Well good Larry stay safe.''

``Much as I can take care.''

I wait a few minutes and head for the elevator, switch back to Peter in the elevator and back out past Larry to the outside of the complex then to the public john. I shapeshift back to myself and head off an emergency while I'm there. It's been a while since I've done an infiltration I need to get my sealegs back. That went without a hitch though. I don't think I need another infiltration, I may be able to make an attack from outside to gather evidence. Then also onsite photographic evidence at the warehouse I want to see the horrors that are unleashed out there.

Hmm, how to do this. I don't have to be onsite but I need to check the different components of their network to make sure I don't get detected. I have all my notes and references from back during the black hat work. I think top priority as always is to avoid detection. Best course of action is likely to create a GRE tunnel from the internet gateway server and I can redirect traffic through a box I control. Kind of a man in the middle. I probably wont get all of the internal traffic but if I get traffic to and from their headquarters that is likely going to be the most likely slam dunk anyway. I'll need to figure out where to find a location that has enough bandwidth to handle their traffic in and out reasonably, if I can find out how big a pipe ie. how fast their connection is, I can judge what I need on this end to make thing more transparent. Thinking about it I may be able to configure one or more of their internal routers to push all traffic to the internet gateway, then I could actually capture the internal communications. Hell if their routers are sophisticated enough I might be able to redirect only the E-Mail from the internal routers to the internet gateway to save on traffic. That might make my head explode though I need to check through these books to see if I have enough step by steps to do what I want to do already.

I studied most of the day to see what I can accomplish. The GRE tunnel is doable. Might be able to do more like redirect only E-Mail traffic through the tunnel then there would likely be nearly negligible traffic which would make things easier from this end, I won't need much bandwidth for the redirection. Configuring internal routers? I haven't a frickin clue and no documentation on it so skip that.

Good then, I don't want to put father in a pickle so I'll do my snooping of the network at the little library on the next block assuming it has internet of some kind. My laptop is installed with Kali linux so I am about ready to go. I'll just put the laptop on the huge stack of books in the old rucksack and over I go. Nice thing is having a stack of books beside you in a library makes more sense than a hotel, coffee bar, or wherever else one may go.

Now the first thing is to find a way in. The access is likely blocked from the outside via IP. I can't defeat that but looking at the map there is a VPN server on the same subnet as the main server farm. That is likely used for outside administration. That is likely the best entry point to gain access to the network. I can then setup the tunnel on the internet facing router and gather the data. That should complete the better part of my work I just need to run scripts on the packet data.

So time to head out to the library. I've been studying maps of the city so I'm getting more of a sense of where things are now so I'm starting to travel some on my own. 

Time to Rock. Get some items for pistol smuggling. Swing by the sporting goods store for firearms cleaning supplies, ammo and the like, then off to the library with a stack of hacking manuals. It seems so wrong. Maybe a hoodie and gangsta pants would make it right. Need a pocket protector for the hoodie to make the look complete.

OK laptop on lets go for a spin with wireless.

Checking the network map I scribbled down, admin.mgel.us good, now lets skip a risky port scan and just go with what we got here. a VPN tunnel is setup for remote administration on this box. Logged in perfectly. Debian linux system they are connecting using SSH, which is expected nowadays. Lets run some traces to check latency on the network.\\
\bigskip

First to check the path from here to that office.

\begin{verbatim}
#traceroute admin.mgel.us
traceroute: admin.mgel.us has multiple
traceroute to admin.mgel.us (173.194.2
1  vl160-d2.acc.sea2.hopone.net (192.9
2  ge4-2.core1.sea2.hopone.net (209.16
3  xe5-0.core1.sea1.hopone.net (209.16
4  * * *
5  66.249.94.212 (66.249.94.212)  62.7
6  74.125.37.211 (74.125.37.211)  22.7
209.85.248.93 (209.85.248.93)  15.559 
7  72.14.233.110 (72.14.233.110)  42.0
72.14.239.208 (72.14.239.208)  42.665 
72.14.233.110 (72.14.233.110)  43.943 
8  209.85.248.116 (209.85.248.116)  78
72.14.239.90 (72.14.239.90)  77.351 ms
9  209.85.143.193 (209.85.143.193)  76
209.85.254.105 (209.85.254.105)  88.90
10  admin.mgel.us (64.233.174.133)  80	
\end{verbatim}
\medskip

All appears quite normal Latency is a good judge of health and the connection speed should be good too. At least until we know otherwise. Lets try the VPN and hope to hell the passwords I have actually work. Add a system connection name. Call it ruffles. Now please realize I did my research and I'm following steps from a couple books and more than a couple websites. I ain't no hacker but I know enough by experience to find what I need and run like hell if I fuck up. Which happens more often than I dare to admit.

\begin{verbatim}
password-flags=0
[vpn-secrets]
password=booyukker
\end{verbatim}
\medskip

Moment of truth let's connect this thing.

\begin{verbatim}
sudo nmcli con up "ruffles"
Connection successfully activated (D-B
\end{verbatim}
\medskip

Oh sweeeet! The password information works! I'm right where I want to be now. Let's try root access. Got that password too. The thing with being able to log into a server with root is you have absolute control over that server. I mean absolute control. I'll have to use this guy mandeville's account. direct connection to root remotely is pretty much always blocked.

\begin{verbatim}
$ ssh mandeville@admin.mgel.us
mandeville@admin.mgel.us's password: 
NetBSD 7.0.1_PATCH (GENERIC.2016072205

% su root
Password:
# 
\end{verbatim}
\medskip

Not like in the movies really boring actually. Until you get done what you got to do. That ``su'' command escalated me to root from the mandeville account. Mission accomplished. Now I need to check if I can access the internet firewall. The redirection will need to happen there. Secureshell otherwise known as SSH is the one and only way to connect for most administrative work on servers today. So lets give it the old college try. I only have a password listed so it seems like they got some dumbass consumer router on point. These guys are awful

\begin{verbatim}
ssh root@gateway.mgel.us
root@gateway.mgel.us's password: 
Permission denied, please try again.
root@gateway.mgel.us's password: 
Permission denied, please try again.
root@gateway.mgel.us's password: 
Permission denied (publickey,password,
\end{verbatim}

Well that was strike one. I don't know what the hell that box is, it's not on the network map. OK think Susan think, what did we use back in the day. Port scanner, sticky note here, nmap! right, It can read digital signatures for an idea of what this thing is. OK let's give it a whirl.

\begin{verbatim}
# nmap -O -v gateway.mgel.us

Starting Nmap ( http://nmap.org )
Nmap scan report for gateway.mgel.us 
Not shown: 994 closed ports
PORT      STATE    SERVICE
22/tcp    open     ssh
80/tcp    open     http
646/tcp   filtered ldp
1720/tcp  filtered H.323/Q.931
9929/tcp  open     nping-echo
Device type: general purpose
Running: FreeBSD 10.2
OS CPE: unknown
OS details: unknown
Uptime guess: 1.674 days (since Fri Sep
Network Distance: 10 hops
TCP Sequence Prediction: Difficulty=205
IP ID Sequence Generation: All zeros

Read data files from: /usr/local/bin/..
Nmap done: 1 IP address (1 host up) sca
Raw packets sent: 1063 (47.432KB) | Rcv
\end{verbatim}

I don't like port scanning tools, too easy to trigger a red alarm. I was actually very lucky the administrative machine had it installed. Normally there aren't any ``offensive'' tools resident on network servers. I wonder what the deal is here? I need to tread carefully.

What do we got? a FreeBSD box. This place is a BSD shop for sure. I have a password but it isn't working. Not a root password. The www port is open so there's a web page there. Let's see if we can surf the gateway.

Ohhh. The browser opened a pfsense administration page. Sticky note time. Default username is admin. Perhaps they only changed the password?

Yup, logged right in. OK now I know what I'm dealing with. Time to break away from this before I fuck something up and get caught. I need to create a rule to use in order to redirect traffic now that I know what I'm dealing with. So I grab the Kali CD out and tuck in a hidden pocket. Let the laptop boot windows and flip it closed. I say the laptop runs kali linux because for all intents and purposes it does but windows is still on the computer with ditzy apps and official looking business documents. Basically to cover up any shady work I've been up to and stay out of trouble.

Bloody hell, just like from the US Marines that just burst through the door. What the hell are US Marines doing in the ghetto?

``Everyone will submit to search, any who do not submit will be taken into marine custody for questioning. We will start with you.''

The master sergeant proceeded to deploy his men in tactical positions when shortly two more men entered. The salutes were immediate and powerful.

``General Lancaster! Sir! Area is secure to proceed with investigation Sir!''

Oh my God, what the hell is a marine general doing in a ghetto! Christ Susan if you don't have a story here! Something is up, and unless angels fly out of Obama's ass this is hitting the front page of any paper! So the search proceeded specifically for electronic equipment. The general had with him an officer who seemed to be well trained in electronic warfare. Looks like perhaps black hat shit. One of the soldiers snatched my laptop rather forcefully and the black hat examined it fully. I was sweating bullets. Not literally thank God given the company I'm keeping at the moment but nonetheless I hoped I had enough training to not leave enough of a trace.

``This thing is clear general, this couldn't have generated the connections. Nothing in the logs, hardware MAC is incorrect and it looks like it was setup by a homemaker all cheesy games and recipe lists.''

The general responded, ``Goddamned MGEL admins, fricking off for a coffee and refuse to register out. We go out chasing some Goddamned shade midafternoon just to find he was doing his shit on a Goddamned park bench outside the motherfucking target address. Jesus fucking Christ pack it in boys we're going back to assignment.''

The military has their way with words. Anyway it's time to get a hold of my teacher and see if he can draw up some rules for me. I could probably do it but I'm getting a headache just thinking about it. Mercy.

I head back to the rectory and lay down for a bit. Fascinating how things change. The next course of action I'm thinking of may be a bit dangerous. There are marines here and I need to find out more about that. Maybe the first thing is to find them physically. What is their assignment? I feel like I should do a real stakeout of the warehouse now, dollars to doughnuts that's where the marines are going to be when things go down out there. I'll send out the E-Mail request to my buddy first. If I don't do a stakeout now I don't see where it would be easy for me to sort the captured data, I wouldn't have a point of reference to look for. Text queries makes things quick folks, either by the grep command or a more sophisticated keyword search if you have the right words it's easier to pull better stuff out of the muck. I think I will have that bath. I can't stop thinking about it.

I start getting ready. I shape shift into marine fatigues with full webbing and ruck and strap on a glock. I shape shift a KA-BAR under the other arm. Various little supplies I put in the webbing and make it real and ready for an infiltration. I include among other things my phone for photographic media and recording and a really boring brown colour trench coat to conceal the warrior underneath.

I see a vision of Jane, she is milking her venom into a beaker. She turns around quickly and the general is entering the tent. He is very joyous speaks for a bit then leaves. Jane leaves the tent and enters the nearest patient tent. It housed a few hundred sick. a quarter were healthy already the rest were very much improved. She said, ``If you're listening Susan, and I hope you are, you were right. It had to be me. As soon as my work started producing results without venom the general had me quarantined in the presumption I was in league with some remaining red court contingent.  The killing would have started all over again.''

So I start to walk over to the warehouse. Nobody really pays me much attention even though I look like I must be hot. Really though I soak the heat right in. I seem to be a cold blooded creature I really enjoy hot and humid weather. It's approaching evening now when I get there. I look and listen and there is nobody here. Unless they're dead. In which case they won't notice me anyway. I would assume. I climb to the roof, using the ladder outside the building this time. I put away the cloak, finish my dress with things like putting on the boonie and finishing face paint as well as tying back my hair. I go over to the front edge of the roof and take out my scope to remain hidden and be able to see the truck assuming it's coming tonight. My ears can hear a pin drop from 50 paces as if it was a crash of thunder so it's not likely anyone is going to sneak up on me.

Sometime after midnight I see the lights of a military truck roll in. A fair size canvas top likely a couple long rows of benches inside. It stops snug to the buildings main door. I hear the sound of men exiting, a couple dozen I would say. I pick up pieces of conversation inside as I sit on the edge of the roof. Test subjects, ensuring their protective devices are functional. They are taking their ``places'' and the subjects are released. I hear hissing from below. Oh God tell me it isn't what I think. I hear commands going down to the creatures line up, spread out, take position, fight, relent, and so on. They are taking orders like soldiers and being commanded to fight. I get to the trapdoor and use my scope to look down. I am just over the top catwalk and see some men including the general stationed in the control booth closest to the top of the structure. There are actually white coated scientists making notes up there with MGEL insignia on their coats. I look below and see the ugliest test subjects I have ever seen, black court vampires! What in the fricking hell are these people doing? Are they completely mad!

Extraordinarily enough the vampires are obedient. They are taking orders and fighting. There were 2 who broke free but the soldiers present took them down with conventional weapons, as well as holy water, garlic, holy symbols and such. The little bloodsuckers didn't have a chance. Maybe that's why they obey like they do. If they all united together though they could be able to break free. Why haven't the munched the other soldiers. There's what I see, what I hear, smells like putrification but also of garlic. Taking a closer look there is something hanging from the soldiers necks, and I see the item exposed on one soldier. They wear garlic. Probably other items as well so they are protected.


``How many of the subjects have been able to independently carry out orders?''

``We have released 6 subjects in the last 2 weeks general, 4 have returned and we have confirmed have met their objective. The two remaining have not returned.''

``We need to carry back at least a 95 percent conformance ratio so we need to keep working. The DNA injections progressing well?''

``Satisfactorily sir. Ever since we started with the cream based application and applied the solar radiation the changes seem to be taking place. Some of the expected human characteristics in personality seem apparent allowing more control and more self discipline.''

``How much longer?''

``Months, on the outside, assuming progress continues at the current rate.''

``That's excellent. The perfect super soldier. Scary as hell, tough, fast and strong. Able to raise dying enemies to fight alongside them. Incredible.''

My stomach turned. I've heard of monstrous experiments to create new and terrible weapons and even supersoldiers, but someone really didn't think this one through. Vampires are organized you fools! Flooded with intrigue and backstabbing yes but united, their word being their bond like any of the supernatural beings. They could bring a war. Humans have no chance in such a war vampires are higher up the food chain.

As I pondered the ways of idiocy below I seen the creatures stop what they were doing. The were sniffing the air. Like dogs. Some of them climbed the walls ten feet sniffing. They all started orienting their eyes, and eye sockets as it were, directly at this hatch and let out a hiss. Oh hell I'm in some trouble, mmhmm some trouble yep. They lit a straight line directly for me. Soldiers opened fire the general and all the softie scientists hit the floor. The general opened fire with a pistol right through the window of the control booth. The creatures couldn't have cared less they smelled me without the lovely aroma of garlic. Time to practise the art of pulling punches I guess.

I did a tuck and roll out of the way of the hatch and at least a dozen black court vampires sprang out of it with a united hungry hiss. I heard below the call for all soldiers to hit the roof and make the attack. The test subjects are not to escape. The first three i avoid with a leap to the left and barrel roll. Two more come to the left i pull up hard on my hands and use the momentum from the roll to land a solid boot to the two knocking them down. I follow through punching through one of the next two. Grabbing my KA-BAR i come behind another and remove a head. One down. Four are advancing i holster the KA-BAR, then cartwheel back onto one knee and open fire with my glock those four go down. I leap high and force both steel toed combat boots down hard on two of the four destroying skulls. Three down.

The general and soldiers arrive as a trickle through the hatch on the roof, and the general has his holy shit face on. The soldiers are going to fire but he yells, ``hold fire you morons, there's a soldier on the roof. You goddamned ballerinas take notes because that's how it's fricking done right there!''

The two remaining each grab an arm i leap my body behind them and crack their skulls together and they let go. I unsheathe my ka-bar and make a vicious swing. Off goes a head. Now 4 down. They rush in I tuck and roll knocking over one and plant the ka-bar through it's skull. 5 down and 7 left. They pile on me and I become a chew toy. Shit.

The general shouts, ``fuck, she's gone. Hell of a soldier. Ready weapons to fire!''

I burst straight up through the pile and blast three rounds straight down. 2 exploding skulls, 2 more down.

The general shouts, ``hold fire! Jesus Christ what is this Die Hard? Who is this soldier?''

The soldiers shout in unison, ``Hoo Rah!''

The third I crush under my boot 1 down 4 to go. Tuck and roll knock one down, grab my KA-BAR then plant my feet and reverse momentum. Launch at one and remove it's head. I land and turn ready to roll to the side but one decides to rush in and meet my KA-BAR, so off goes another head and 2 to go. Both rush in i leap forward and clothesline both to the ground. I tuck and roll come up with the glock and shatter a skull. The remainder made it to the 3dge of the roof in time and jumped. Somehow it landed in one piece. The soldier open fire on it but it leaped the fence and was gone.

The general walked up, ``That was some bit of fighting soldier. I don't remember seeing you before you got ID?'' 

I check my pockets in a fake attempt to find ID, then I point to the pile of dead vampires, ``on it's way to hell?''. 

The general responds, ``well shit so it is, fuck it I seem to suddenly be getting my memory back I remember you just fine. Come on down have some whiskey on me. Men stand down lets get back to it.'' 

I descend and notice a shit ton of juicy paperwork waiting for a pocket or a photo. Checking down below there seems not to be any more `subjects' to work with. I seem to have destroyed them all. Aw shucks. 

The general states, ``I'm going to go down and help the boys clean up this mess. Well frick I wish I knew what the hell might have caused this shit.'' He gives me a devilish smile.

So I'm left with a couple drunk scientists who tried to use liquid courage to bolster themselves earlier. Easy as pie my phone works so i snap some verifiable media with the camerav app, and other papers i just pocket. The scientists are too drunk to know. Then i go down and help clean up. The whole time snapping photos where i can. When it's time to go everyone boards the truck except me who holds on to the undercarriage. Down the road i tuck and roll out of the carriage and into an alley. I move into the rear area of a shop with spare garbage cans and a huge propane tank and take a breather. I meditate a couple hours then get up and make my way towards the parking lot to try and make sure the troop truck doesn't double back to find me.

I had another vision of Jane, I seen Jill and my thralls with her.

Jane said, ``Thank you all so much, it's getting out of control. I can't get the warlock tattoo to control my hunger. If I asked I would get killed off as the only red left. I needed help.''

Jill said, ``Susan is beloved of us Jane, we will help you any way we can. We will just have to chain you up at night so you can feel safe to rest. I don't know what else we can do.

Jane said, ``Jill, tell me more about Susan---''

As I walk out I find myself ambushed by the black court. They probably seen me while i was meditating. Should have waited until i was back to the rectory shit.

There's about 2 dozen maybe more. Although no people around now so i can let rip so not so bad. They spread out directly in front of me and about 3 walk out to face me closer than the rest. One speaks.

``The three of us are the elders of this district. You have killed a dozen of our brethren. You, a mere mortal, have embarrassed us in front of our court and all vampires. You have invited destruction to us and have dishonored us, you who are no more than food. You foolish pathetic creature did you think we would let you live after such insolence? You are going to wish you died on the roof for now your death will be slow and quite painful I assure you.''

I spread my stance to get ready for what's coming, ``OK, come give me a little. Don't be shy.''

One of the other elders shouts, ``more insolence! Take her down! dont kill her I want her alive to play with later!''

Holy shit did they ever send in the troops! Not a couple dozen, many dozen. If I do manage to clear out all these vamps would it set me up for more? I want to get my life back not get into the superhero market battling super-villains the rest of my days. He wants me captured so i'll get captured and break away. Easiest thing. What happens next time though? They arent going to forget and thats what i want most.

So without a better plan i decided to just go with just chilling at the bottom of a football style pileup and getting driven back to the day spa they offered me.

Trouble was i didnt like how they were trying to feast on me anyway. It hurt real bad and i was getting really pissed. I noticed for lack of a better word i was smoking. Light black smoke was drifting off my body and i was getting real hungry. One of the vampires broke through my flesh mask and stood up quick, ``My lord, we have a big problem here!'' 

The elder that he addressed said, ``what the hell kind of problem could you have?'' 

Another vampire broke through and screamed, ``She's red court!''

``What! Impossible! The red court is dead! Kill her! Kill her! Do not let the red court return!''

Oh i lost it. I snapped. These guys are a liability now i need to wipe them out before I'm revealed! There were a dozen on me i burst straight up and some kind of speed do i have. I threw a fist before they moved and 4 slammed into a wall. Now the strangest thing happened. The smoke edged toward the 4 and a thick oily smoke rose from them. It flowed into me and they had what looked like a grand maul seizures, then they were still. Then they turned to dust. I turned to face the remaining vampires and my fangs were dripping what was in appearance hot tar, that same colour and consistency.

The elders hit the dirt in prostration so fast i thought they might have eaten gravel. ``Spare us oh great mother, queen and empress we did not know have mercy on us!'' The other vampires looked at each other then prostrated the same. Oh shit, what did i just do. Can i get out of this? I cant kill them now, as much as i hate vampires i cant hurt any being if it is begging mercy. I don't think they will take it back because i have no idea what tipped them off. Oh this is not good, not good at all. I'll play dumb.

``excuse me?''

``you are the long awaited great mother, the one prophesied to lead the vampire courts to world domination! You are her the devourer of souls! We are your servants great one, we are your children oh great mother lead us and guide us!''

Sounds like I'm Jesus Christ with boobs, should i speak parables? Cant bring them back to the rectory i wouldn't think. Their skin is falling off i'll call them lepers. Hah, no. I don't really want to go to their lair it would be horrible, bodies piled around people mind controlled and chained to be used for food i cant handle it. I need time to figure out what to do.

``meet me at the church cemetery 3 blocks west, in two days. Once it's dark. We will talk then. I have important tasks to perform.''

``yes my queen it will be so''

I had another vision of Jane, I see her on top of a man a second away from making a kill. Her venom is dripping on him and he is writhing in ecstacy. A loud blast from a shotgun and another man drags him away. Jane is thrown 10 feet away with a hole in her chest. She regenerates in a few seconds and I feel the overwhelming hunger. She runs into a patient tent and grabs a fresh test vial. The nurse said, ``Hey where you going with that?'' and Jane flew out the other door into the forest cracking open the vial, drinking the contents, still running.

Well, tomorrow I start the network redirect to check for useful E-Mail and gather the papers and photos. I'll also start my report. What I have now is damning enough alone but there is no such thing as too much evidence.

I start the redirect of network traffic in the morning. I'll leave it going for at least a week and grab Wireshark and that book i got for it and run the data capture through a sieve to find juicy E-Mails.

I talk to father about the event and he recommends considering we both hate vampires but if a group of them look up to you in such a way then godless or not you could influence them in ways combat cant. He says try, the worst thing I could do is fail then I'm just back to not being an influence having lost nothing for trying. Hell that seems ok to me.

I strip cleaned my glock and did that laying down thing again. I like it. Its very comfy.

I feel like this might be an important story for me, so I created an E-Mail address and a pen name. I also drew up a binding agreement so that the arcane has to publish my pen name and contact in the article so I can get feedback on this one. I have material of a high calibre in it and I can learn a lot about writing this kind of story in the future. I mean this is like the pelican brief of paranormal articles. The best i've done to date i think and the electronic surveillance is just started.

I see a vision of Jane again, walking back into the encampment. Her hunger is still barely manageable. People are talking about the assault, the victims symptoms and lack of the body of the attacker. People are thinking the red court might not be as dead as they thought. She enters her research tent and begins work.

Time does fly. I head over to the cemetery a bit early and sit on a tree stump. Best seat in the house. Over the course of an hour after sunset they begin to arrive. Five, then ten, fucking fifty then fuck me gently i think it was a hundred vampire souls came.  It was like that loaves and fishes story in the bible they just kept coming.verily verily i say to thee the cemetery was alive with undead.

``tell us what we must do most glorious queen.''

\begin{quotation}
	``take only the prey you need to live and no more. To be ruled by hunger is to be enslaved, to lose honour even to the point of being fit only for destruction. Have honour in all things, any to be shown gravely lacking are to be destroyed. Strength and honour are the greatest virtues of our kind let no one tell you otherwise. By strength we will take to battle. Only by honour though can an empire truly conquer and subject it's foes. The only way to have honor is to give it away, show honour and it will be increased in you. Honour is not a rule of law to be obeyed in rote, it burns in the heart of the vampire. The vampire is honour and from there it comes forth to illuminate others in it's righteousness. Honour your prey, they give their lives so that you may live. Remember this always. Do not offend the dignity of the prey, they are free we are not to bind them this is an offence to dignity. Protect the prey, just as the Sheppard would lay down his life for his sheep we must also for our own flock they are our food and our life. This is also how we honour our prey and one way how each coven's honour will be judged.''
	Continuing, ``You duty now is that all will cleanse their house of the dishonourable. Every house will be judged  by the honour of those who belong, a dishonourable house is destroyed, the honourable within banished upon their honour let them never forfeit the honour they have on pain of death. we will be houses, the bloodline families or adopted kin. Clans, organised for each town or municipality of human law. principalities for the country and kingdom for the continent. I am great mother, empress or queen. There will be no other queen but me. The white court as is their will shall unite with us under their own houses and clans. We are one empire, one blood unites us. So speaks the last and greatest of her kind. I leave you now to speak among yourselves. Leave when you wish and no feeding in the cemetery please.''
\end{quotation}

a mass wave of prostration followed, visually appearing like a domino effect, ``hail to our great mother, our philosopher queen!'' 

Followed by a thundering ``hail! Hail! Hail!'' 

Then they disappeared into a non-corporeal state. They will hopefully come to understanding because with a single short speech i saved innumerable human lives and hopefully put an end to all the people in chains or tortured currently by these monsters. As I was walking away I missed Maggie. The talking of the great mother thing just made my heart bleed, I want to be with my baby. I turned back to the cemetery for no particular reason and my vampire vision went up. I could see all the vampires talking in their non-corporeal forms that humans cant see. I could hear the quiet telepathic chatter they were making. I just stood there a few minutes in awe of what i hope to be accomplishing from within this vampire society to help people. Help them from within the ranks of the oppressor. My mind started wandering through my fight and struggles against the red court for all that time, the hopeless frustration of what seemed so often to be a hopeless battle against hopeless odds. Like trying to bail out the ocean with a spoon. Now having been made a vampire if i could call it that I am looking at the best chance to finally make things right. Something i could never do before. Maybe even use my work to release them of this accursed hunger.\\
\bigskip

Then I felt something unexpected. Horribly shocking.\\
\bigskip

I felt love.\\
\bigskip

Not pity, not sympathy or empathy. No, a burning love ignited in me like a mother to her children. I'm falling in love with these wretched creatures very quickly and very powerfully after interacting with them as their great mother. Almost like they had tempted me to do something only to have triggered the catalyst to my own transformation without my warning. The second bite of the heart. I remember all the horrors i've seen these creatures do but all i can think now is to embrace them and heal the twisted nature that commands them to do such horrible acts. I see them and they have become beautiful to me. Oh fuck me gently that is just so wrong on so many levels.

As I was about to turn away three figures appeared from out of the cemetary. A thick mist came and one by one they emerged. The first was a gentleman with translucent hair and pure white eyes. Nothing else special about him just an ordinary bloke. He spoke and said that his name is Eurynomous. He introduced his two friends the first had a robe and cowl that made him look like the grim reaper minus the scythe. The robe covered every part of him. Eurynomous stated this gentleman's name is Balberith. The last gentleman to emerge, if you could call him a gentleman by appearance was named Babeal. He was semi-corporeal, with long flowing robes.

Eurynomous said, ``This seemed to be a good opportunity to introduce ourselves. I believe you have already met our brother Leviathan. He is d\ae mon of water, as I am d\ae mon of death. My brother Balberith is the d\ae mon of dying and Babeal is d\ae mon of graves. Our being has intimacy with yours so I found it imperative that we meet.''

I said, ``So I met death today. Literally. A person just can't make that stuff up without having their sanity questioned.''

He said, ``Ha! Agreed. We owe you a lot Susan, you ended so much pain and bloodshed.''

I said, ``So says the d\ae mon of death? I thought you desired as much death as you could.''

He said, ``No. I desire a good death at the appointed time. I comfort both the living and the death upon the death of a being. I help with the transition. Balberith is a companion of the dying and counsel to those who love them. He and I take them gently into the final journey. Babeal watches over the resting place of those who have taken that road. As he says watching over the vehicle of earthly gods from when the roamed this earth. It means a lot to him, the greatest honour one could have. I certainly am humbled over his reverent dedication.''

I said, ``Interesting. I never really looked at it that way.''

He said, ``It's the cycle of life, as they say to all things there is a season. We are going to part from you now. I just want to tell you that we are staying close to you as you learn and grow in your new powers. We will help keep you from danger, for as you will soon find out there is not normally any right of a d\ae mon to be manifest in the physical world. It's far too dangerous. Remember it's your destiny to be manifest here Susan, it is prophesy fulfilled, try not to be afraid.''

They turned and reentered the mist at the cemetary gate. I think although I don't entirely understand what they said that it will become important to know I have d\ae monic brothers looking out for me, and that I'm doing what I'm destined to in being here. How is it dangerous to be in the physical world? I was born here and have not known any other.

I arrive back at the rectory to see a complete skeleton standing beside the door. ``Hello, I am He Who Dances With Wind.'' He prostrates. I bid him rise again. 

That shit is so embarrassing. ``Are you a skeleton?''

``I am a black court vampire''

``but you are no more than a skeleton''

``I am the most elder of the court. I have walked this earth from before the reckoning of time. Before civilization came upon the earth. Even upon all these years spoken record heralded your coming. I never thought I would see the day I would stand before you.''

``So you are what would be called an ancient vampire then.''

I look at the door, then back to him, what the hell. Father has heard worse from me I'm sure he wont mind seeing worse also.

``Are you able to enter a holy place? Would you be hurt?''

``Susan I'll be fine.''

``How did you know my name? Never mind, ancient vampire, needn't ask more. Please come in.''

We sit at the kitchen table to parley.

Father Gomez came in and fell flat on his ass.

He Who Dances With Wind stood and bowed low to father, ``I am sorry to have startled you most honourable shaman, i am He Who Dances With Wind. I am the most ancient of vampires at your service oh king.''

father rose, and coughed, ``you presume i am a priest king like Melchizedek high priest and king. I am no shaman but the humble priest of the most high god. Um, my dear?'', he raises an eyebrow.

``he is very polite i didn't think you would mind.''

Father makes a face-palm. Taking the seat across from us at the table he looks to He Who Dances With Wind and rubs his chin.
We talked until morning and father agreed to allow he who dances with wind to stay if he can do penance by staying in the crypt to clean and maintain the tombs. He agreed.
It continued that way and he would come up and father was fascinated with his experience and understanding. He stopped feeding millennia ago, he was tired of it. He left to become a hermit. And a legend of the vampires in the north east of the US. Only the elders would dare approach him and never did except on rare occasions.

I gathered the email transactions at the end of the week and found some rather juicy stuff. In particular the messages to and from the main office. If they actually used gpg for their confidential email I wouldn't have been able to have snatched what I did. The story is done and sent. 

My wise man who came from afar, He Who Dances With Wind, is going home. This time he is being granted permission by Rome to remain as a hermit on land governed by Rome. 
The native americans of new york state, the highest elders specifically, also became aware of him and he spends much more time sharing lodge on reservations sharing knowledge lost long ago of the history of his people which now is the history of all native people. Last i heard him say he is happier than he has been in a long time. Which to me means a very very long time.

I see a vision of Jane. The man from before that fired a shotgun into her is threatening her saying he knows what she is. I feel the hunger she has, and at that moment the fear that assaults her from being discovered caused her to lose control. She moved on the man and took him down hard and fast. Blood was everywhere. The body was badly torn. I felt the familiar ecstatic pain of final transformation begin in her. She runs as fast as she can into the forest and she is torn apart from the inside by the final change. Fear has changed into sheer terror because like any of us she has seen this before in other people. They were not them anymore. They were, something, else.

I need to get to her now before it's too late.

