\lettrine[lines=2,lraise=0]{S}teve is with us now, and time is running short. The adversary is going to tend to the details, we are gathered in Saint Mary of the Angels for when the event takes place. The entire Carpenter family sits in eucharistic adoration and father is watching over the rest of us. Karrin, Will and Georgia. Maggie is playing with mouse and me. It was explained that Maggie will return to my being, and then be reborn at the appointed time. We will meet mouse at the appointed time as well. Apparently Rose was born at my turning, though she was in an incubation stage. I'm told because of the complexities involved she will manifest human at chichen itza. I can just hear the cursing now. I hope she finds Steve, everyone deserves to be happy.

I've done what I was meant to do, I've taken the mantle of godhood and no matter where I go even across realities it cannot be taken away from me. I am and ever will be the God of all vampires, the great mother. There can be no other but me.

We are returning to a turning point in Harry's life, a critical moment in my life also. The thread of reality we are creating is splitting from Bianca's Ball. The adversary explained I am returning human, with all the memories and skills I have learned up until this moment. I may unleash minor effects from time to time during emotional moments so be careful, stay hidden. Red forces will continue to gather one reality at a time at the outer walls of the nevernever as other realities reach the time of chichen itza. I will be quickened over and over by the immortal life forces of one reality after another. I'll feel the heaviness a day or two ahead. At the moment it comes down hard, I have time to sit, and a flurry of lightning will hammer me for up to 5 minutes. Noone else will see it though, only that I'm sitting disoriented wherever I am. Me and Karrin maintain the master/spawn link and she retains the increased speed and strength. That's all, we start fresh together, and help each other. Karrin couldn't help but let her lip curl into a smile realizing she is going to be Lieutenant again, and me and her grasped hands like soldiers swearing we will work together with our link to keep her from losing rank again.

The time ticked away so slowly. Michael went out to get us some Burger King. None of us ate that much. I hugged Maggie a lot because I knew I wouldn't see her for quite a while after I get there. Mouse too for that matter. We're scared, all of us. Something bad is happening and one world after another is collapsing into emptiness around us but we have no awareness of it. As we look at each other we realize that I'm going to be filling up with the power of millions, perhaps billions, of immortal souls over the course of years. That makes it worse not better, what manner of horror is coming that any being needs to have that much strength to stand against it, and be one of many generals to do so. I imagine the staggering power of the elite vampire army that is amassing. One hundred and twenty thousand more every time I'm quickened, only six thousand of which were needed to bring Mab to her knees in one shot. The adversary isn't pulling any punches, he is going to fight with everything he's got to save his earthly empire. \\

\textit{Do not go gentle into that good night. Rage, rage against the dying of the light.}\\


\parasep

I remember this beach. I'm wearing a white bikini this day, I'm trying to ease the suffering of my hunger by time out in this sun. One of the last warm days of the year. I was still officially working for the Arcane but I've already got my apartment cleaned out. Everything dumped in long term storage. I was like the million dollar man all stronger, faster and whatever. Took no time at all. I hated it. I was losing Harry. I sent him flowers and called him desperate not to allow myself to get close enough to eat him because the hunger can't sort through my passions properly.

This was that very moment when he gave me the ring, he proposed, he loved me that much that he was willing to get eaten rather than lose me. This is another moment where I didn't consider him. I made my own decision in spite of his feelings. This is something I'm going to change right fucking now. I hurt myself and other people when I don't pay attention to them.

I looked at my hand. It looks like he got the ring at a carnival. Neither of us had a lot of money back then though. It might as well have been worth a million dollars to me. He knew it too. Heh. He \textit{knows} it too.

I leaned over and give him a slow kiss. A long sensual endless kiss. We broke away slowly and he has a big shit eating grin on him. Right now I feel like I'm with my knight in shining armour. I really love my Harry.

``Yes Harry! Oh my God yes! Thank you for taking the risk of being with me still.''

``Oh thank God Susan, I was sure you were getting ready to leave and never come back.''

``I was.''

``Oh.''

``I grew wise. If you love me so much you're willing to do everything possible to make it work, make me better, hell just live as happy as we can fuck it. I respect that you're willing to take the risk and I'll do my part to mitigate it.''

``I love you Susan, Oh God I love you.''

We flew into one of the most passionate kisses of our lives right there. Completely unbridled passion that made the passers by look out and take notice. Some cameras flashed. We didn't give a flying fuck. Especially me. I'm finally getting a chance to live my life the way it should have been. Yeah Bianca. Fuck. You. Bianca.

We broke it slowly a couple of times, only to throw ourselves at each other again. We both cut it short when our clothes were starting to come off.

``Harry could I stay at your place a little while? All my stuff is in long term storage. Besides I need to know if I'll be OK. Do you have restraints suitable for an up and coming vampire?''

``Pfft, hard to believe you're getting your humor back in spite of all this. God you're a strong woman. I definately have some good restraints, good enough for trolls and ogres.''

``Hmm. You'll have to tell me about trolls and ogres sometime.'' 

This place makes me think of the hunger I once fought so hard. That same restraint worked when I went to visit Harry years afterward though, working together I think we could have had a happy life even if a rather unusual one.

``Let's get going Harry, I've had enough sun for today. Gotta get home and make sure you can find those restraints.''

I'm quite human enough but I'm not going to confuse things. I came into this reality at the point I held the ring. Just before that I remember I was moaning about how terrible my hunger was. It was awful but I know now if I just gave myself time my will would grow and things would be better. Of course then I was gone to fight with the fellowship where I found purpose in my life but fucked up again later with Maggie. Sigh.

``It's heading toward evening Harry, do you have those restraints? It would be a good time to hook them up.''

``Hells bells. You're right. Better no than sorry. I'm going to find that cure Susan don't worry ok?''

``Not worried Harry. At least being restrained I'm no danger to you or anybody else for that matter. It's good to tie up your girlfriend.''

Harry let out a snort of laughter, hung his head and shook it. I'm kinda liking this actually. Glad the powers that be allowed me to come back. Me and Harry can get kinky.

That night I woke up to hear Harry scream, I yell back into his bedroom, ``Harry! Are you OK?''

``Susan, Oh my God Susan you're OK! They were everywhere! Thank God you stayed with me I was so afraid you would move away.''

Fuck Susan you cruel heartless bitch. You never even thought that Harry really needed you, you were just thinking of yourself. You heartless bitch. Poor Harry is screaming with nightmares and you could have been there for him, even tied up you could have been there for him. I'm really starting to hate myself.

``Harry get some cards, we can play some crazy eights until you can settle down again. Just remember you're half vampire girlfriend can kick their ass with speed, strength, wit and charm and of course a good nose for a story all monsters flee at the sight of the press.''

``I don't know how you're doing it, but glad you're back Susan. I'm taking you up on that, cards it is.''

``Then try to sleep when you feel ready. Better keep me on the end of my leash so I don't bite.''

I'm not sure if he was about to laugh or cry because all I heard was a cough. We sat down to play cards.

I heard Karrin communicate, ``How is going Susan?''

``Karrin. I'm such an incredible inexcusable monstrous bitch.''

``I already knew that.''

``I suppose you seen a lot of the train wreck I left behind?''

``Duh. But you were gone so I had no more fucks left to give. Harry got better.''

``Jesus I'm a bitch. Shit is gonna change right now.''

``Back to my original question, how is it going?''

``Oh well Harry had a screaming nightmare assumably about vampires, I'm played cards with him until he can sleep. I'm all bound up in troll restraints.''

``Kinky.''

``That's what I said. At least I got Harry to laugh.''

``Yeah you're good for him. Just don't fuck up this time because I swear to God I will kill you.''

``Sokath, his eyes uncovered. I know what I have done.''

``Who what now?''

``Tamarian language, star trek. I used to be a trekkie.''

``Well shit. Goodnight Uhura''

``Goodnight Bones.''

``How the fuck, ah whatever goodnight.''

I think we stayed up pretty well all night playing cards. He just needs me around. I think but I wont ask Karrin, that Harry may not have slept, worked, showered or even eaten after I left. That, would damn well have been my fault. I would have done that to the one I loved.

So I lived at Harry's, for now. As bad a shape as I'm supposed to be in he's worse. I should have realized that back in the day, but I was too selfish to understand. I'm considering letting my apartment go. I'll keep my things in storage and stay at Harry's. I think he'll feel better to have me near the same as anyone would want a sick loved one close so they know they're ok. If that means I dutifully submit to my nightly restraints so be it. I'm going to need some nice shiny black rubber accessories to wear at night though to complete the ensemble. The sad thing is I'm rocking a completely human body, I'm just not sure how to say to him that I'm actually quite fine. Well, health wise anyway.

Michael and Karrin came over with a care package. Soup and canned goods, charcoal and kerosene for winter. Also got some groceries and fruit for us. Harry volunteered to stay with me if Harry needed him too because of his fairly vampire proof self. Karrin tossed over a care item especially for me. A glock 18 machine pistol with varied accessories. I squealed, leapt up, and hugged her tight. I let her go when she gasped out the words, 

``Get... Off... Me...'' 

I bellowed, ``Thank you so much Karrin! I wish I had something to give you...''

``You didn't run away this time. That's enough.''

Harry said, ``What do you mean run away?''

Karrin replied, ``I came over before she left the apartment. That's all.''

``Oh,'' Harry is lost so just drops it.

I'm flipping and clicking the machine pistol over like a navy seal, with Harry staring in disbelief the whole time.

They stay for a game of Euchre and then are off, I start the fireplace and Harry makes a meal. Afterwards he readies the restraints for another nights rest. The couch is rolled close to the bedroom door so I can see into the bedroom by my request. I want to be able to talk or yell at him if he has another one of those horrible nightmares. We're going to try to find a more permanent arrangement to I can have a normal bed to sleep in, or something more closely approximating it. I felt something heavy on me after the game and communicated Karrin about it. The next day at work it hit, I was sitting at my desk and after it was done seen that about 3 mins had past since the quickening began. I communicated back to Karrin it had past and everything was OK.

The vampires declared war on the council at this point. If Harry has to go out at night I've been going with him. It took me a while to convince him. He enchanted an army surplus ACU-UCP uniform as a shield and gave it to me to wear. It gave him peace of mind. He almost lost me before and he is determined not to lose me again. I've been taking down vampires like it's going out of style. He doesn't know about the decade of combat I endured in a previous life. He just keeps asking me when I got my SEAL training. Michael is gathering tactical gear for me, MOLLE, IOTV armor, and ordinance. Harry in turn is blessing gear with spells, mostly protection. Charity made me a cloak-tent that I can wrap around to obscure myself if I'm going out armed. I'm told I should have a nice Christmas present. I can't wait. I spar with Karrin regularly. She is being kind since she was left with enhanced reflexes not me. She does let loose from time to time though because, after all, I will be engaging in combat with vampires. 

I'm training hard. Really fucking hard. Rocky would tip his hat and bow. I've fought for over a decade with the fellowship. I'm proud of it and I won't lose what it has given me. Michael Carpenter is a carpenter by trade. Karrin is a part of Chicago PD's `whitewash and spin' department, Thomas and the Raiths are sex industry moguls. Harry is a tough determined gumshoe and I'm a reporter. Michael is also a knight of the cross, Karrin is a tough and clued in cop. Thomas is a white court vampire. Harry is a wizard and I am a soldier. That's our team.

\parasep

Halloween came and I was beside myself. In another life I was far from here and sent a blank postcard to Harry saying, `I love you'. I didn't write or call. I cut him off. Just like that. Harry didn't understand why I was so miserable but Karrin did, she came to visit. We played some spontaneous Halloween games and some cards. Karrin brought beer and pizza which might as well have been valium it helped me relax so much. Harry may be getting near to letting me out of my restraints at night, I asked him if he thought it was wise. He said at some point what we do to protect our lives starts to prevent us from living our life, He said he needs to make that choice at some point and that it's going to be soon. He said he is still looking for a cure, all I could say is, ``Thank you.''

That evening Harry said, ``Susan, there's things you aren't telling me. I haven't seen signs of infection in you since I proposed. It doesn't just go away, and I know for a fact you were infected at Bianca's Ball there was no hiding it.''

I sat there for what seemed like forever, staring at my jeans. I wasn't sure what to say and I couldn't lie. Eventually all I could say was, ``I made a deal with the Devil Harry. If I tried to explain more you wouldn't understand. I'm gonna be called up to defend the world in the end-times my love, In exchange I live my human life as it was meant to be lived until my days are done. I am at peace with this, you should be too.''

He nods at me, ``We get to live our lives out together, and you will be a hero in the end of days. Those times when you seem despondent, that's part of this too?''

I nod back. Then he smiles. 'nough said. No more restraints tonight, I slept with Harry.

\parasep

A message came by courier, sealed by white counsel. Harry opened it and said it specifically mentions I am to read it with him. It said, ``Wizard Dresden, this is written at the behest of the Merlin. The border of the nevernever is too turbulent and the Ways too dangerous for travel to hold a meeting in your area. Please investigate and resolve, the council will pay for successful service rendered. Please advise Susan also that I and Ebenezar have travelled the same road as she.''

``Susan, do you know anything about that last part or is it worth asking.''

``I can't explain what I can't understand Harry, what they have said, they have said.''

Harry smiled, shook his head, and shrugged.

We decided I'll come along






