\lettrine[lines=2,lraise=0]{T}\space he darkness slowly began to burn away and I seen that Spook and I were high in the air above a precipice. I could make out a small group of people below.

As we continued in a soon to be fatal plunge I noticed I have returned to human form and Spook noticed the same wide eyed. I can't hear, the sound of wind rushing around me is too intense. I can't reach Spook. We hurtle closer and I see it is our group down there. Time has passed we are somewhere else. Over the precipasse I see a huge encampment. Vast expanses of medical tents are surrounded by armed forces. Fellowship forces. We found the encampment we've been looking for.

Directly below us there is a pire. The bodies of me and spook lie on it.

Sarg lights a torch, me and spook are waving our arms and yelling as the pire is lit. What is this? We can't be in two places at once? I notice we are hurtling straight for our bodies. I wave to Spook, it took him a minute before he cleared his thoughts and realized we need to go faster not slower. We aren't falling to our doom we are racing to save our lives. We need to reunite to our bodies before it's too late.

We tucked ourselves into olympic divers pose and slipped through the air like a knife through butter. We pulled ourselves in tight hoping for once two people might attain to break the law of terminal velocity.

We get closer, and closer. The fire is spreading up the pire. We can see the flames strike only feet away from our bodies. I have an idea. I pull Spook closer, aiming our dive at the fire. He waves his arms in confusion and I make a swooping gesture to explain. He smiles. If we are rejoining our bodies it might cause a physical jolt. If we aim for the fire we might be snapped laterally into our bodies and the jolt might roll us away from the fire. Maybe.

Everything went black.

%sequel - emotion
The next thing we see is our people standing over us, Bones is kneeling down checking us over.

``What happened?'' I said.

``You tell us'' Bones said.

``That was unexpected. Jesus what the hell happened?'' said Spook.

``I think it's clear noone knows what happened. Do you two know what happened in the last couple days? We assumed you were braindead and decided to light you up. There are no words to describe how shitty I feel right now. I almost killed someone I love. I don't think I can ever forgive myself---'' Jill said.

``You didn't know hun. How could you have? If I was braindead to bring my body to peace would be an act of mercy. An act of love even. It will be ok.'' I said.

``well, at least I can say we aeem to have made it. Just below that bluff is the Fellowship encampment we were looking for. I know from Sarg this is definately it.'' Jill said.

``How long were we gone?'' I said.

``A few days, doc seen to it you were provided sustenance intraveneously. You and Spook too of course. We would never have put you on a funeral pire otherwise please understand Susan.'' Jill said.

``Its ok Jill I understand. No worries.'' I said.

I looked down and seen a huge encampment. We stood at the top of a towering embankment and seen the entirety of the camp. There was a long road leading down to it but from here I seen a vast tent city. There was a long series of huge tents marked with a red cross indicating a medical encampment that could hold what looked like twenty thousand souls. Surrounding the medical facility was a well provisioned military presence, and a fully intact airport which was our greatest hope. I can get out and bring help to our cause thank God. Things are finally looking up. What horrors lie in those medical tents though, is it for the care of earthly wounds or the horrors of the supernatural unleashed on defenseless people? In tgis part of the world it's hard to know. I'm hopeful it's not the latter.

``Well, I feel like an asshole so let's move on and start marching towards our salvation down there. I think that's what matter the most right now. Every one of us has a place in cleaning uo this mess whether we admit it or not and you all know it. All of us start makinf things right down there by God'' said Sarg.

It wasn't terribly eventful on that journey but me and Spook had time to talk over the past events. I was so far from underatanding what happened.

% sequel - thought
``There is something very dangerous in you Susan, nothing like I've ever seen or heard by word of mouth. I don't know what to make of it .'' said Spook.

``How do you figure Spook?'' I said.

``Well, really it's what happened in the incantation. I don't see any reason why there should be such a reaction to you entering upon it. The only reason it should create such havoc is as if you were the sourcw from whixh all dark energy flowed. It just doesn't make sense Susan no matter what form you may take. There has been a change in the fabric of the plane as a result. It indicates you are more than you appear and yet still you are just Susan there has to be another explanation.'' Spook said.

I said, ``What are you talking about Spook? A change in the fabric of the planes? What planes?''

Spook said, `` The part of the ethereal plane that we are aware of. Since we left I had a chance to scry upon it to aee what has taken place. It is without form. The evil of the darkness has somehow been dispelled. it is without order if it makes anu sense to you. The best way I can discribe it is that that part of the astral has been unmade since our passing. The evil has been expelled but to where I don't know. It would take an intelligence of extreme power to do what I perceive has been done. I need to maintain humility in the matter though Susan I may be an experienced warlock but I can only say be damned careful there is a primeval and terrifying power about you.''

I said, ``Understood Spook. I honestly don't know what is going on with me. Not since \chichenitza* have I had any idea what is going on with me. Pray God if you know anything please tell me Spook I don't know what is going on.''

\begin{quote}
	Spook said, ``I don't either Susan honestly. I've seen power, earthly and demonic; I've seen power heavenly and otherworldly; I've seen the power of fae and of the outer chaos; I've seen the power afforded to demi-gods; I've seen the darkest powers of the greater gods, the destroyers of worlds. Few powers have the potential to reshape a plane the way you did. I can't know how vast your transformation was but I've seen that if it wasn't all encompassing it certainly was vast.

	``Let me put it this way Susan, whatever has touched you is epic, primeval even, I would not work with a power that great the consequences of failure are too dire. When I encounter such a power I give it a wide berth until it's presence passes from my perception. I don't even make my presence known to such a power; I would suggest to you even the fae would do the same; I suggest even the gods would do no less.

	``Be careful Susan, if you can safely escape this power do it. Whatever this is it was not meant to be made manifest; it was not meant to dwell upon this earth. Let this power be known to the greatest of gods alone for I trust only the wisest and most powerful among them to be fit to have contact with a dark power such as this.''
\end{quote}

I said, ``Jesus.''

He said, ``It's well and good you might be a vampire as your heart is the heart of a hero in spite of your nature. There are few benevolent vampires in existence and certainly you are one of the good ones. Be a vampire with the power expected of a vampire Susan. Get away from this power you currently have safely, but expeditiously. This situation you are in is very dangerous for everyone and everything.

``The curse is broken. You deserve to know that. The bane of the warlock is no more. We aren't chained to the fate of madness anymore. Madness will only come if we are found wanting in our psychology. Since time immemorial we have been afflicted and even the gods who seen fit to break the curse could not. Respect this power Susan, if you can set it aside do it the good you can do isn't worth the risk.''

I'm shaking. I'm terrified and cold to the bone. I trust Spook and he expressed well the danger of the power I'm holding in my hands. I want to walk away but what if it falls into the wrong hands? Spook is thinking of me too in what he says, but unless I knew this terrible power were placed in the right hands how could I risk setting it aside? How would I even know the god I should entrust it with would be a wise caretaker of such a thing? I have so much to think about.

The journey to the camp was fairly uneventful. the descent was slow as we travelled on a trail that was cut into the side of a sheer cliff. A couple times I had a sense of something cool and wet on my shoulder but when I touched my shoulder there was nothing there. The way things are here in central america I figure if it isn't trying to kill me then it's alright. Presumably it was real that is Spook had me very, well, spooked earlier.

We set camp for the night. One more days march should get us there. We did get down the cliff though. We are settling into an overgrown area for the night to stay hidden, having hacked into a small clearing with machetes.

Jill was entering into the tent I shared with my companions. I caught her arm gently before she went in.

I said, ``Jill, I'm going to sleep alone tonight. I'm not really hungry.''

She said, ``Oh Susan we didn't know, please don't turn away from us you know we need you. It's been a long time and our troubles are starting to return to us.''

I said, ``Oh no no it's not that Jill, I'm just shaken over my experience. Everything is ok with us. I just need some time alone to think that's all. It was difficult and terrible unlike you could imagine and I need to digest it all.''

Jill said, ``I'm not sure I believe you but I trust you. Just remember I love you and if there's anything you need come get me.''

I said, ``Absolutely. I definately will. Thanks hun.''

We hugged long and hard.

I grabbed a sleep system pack and let Sarg know where I was crashing out, some distance from camp. He paused, yet didn't take long to realize why. Not a word more needed to be said. He gave a nod to me and turned back to the sentry for the night leaving me and Spook out of rotation.

In the wee hours of the night I heard a rustle. I woke up and seen something that looked like a goth. Ambiguous looking with straight and long flowing black hair, and whose eyes looked like the depths of the ocean. In a moment my kabar was in my hands and I leapt clear of my sleeping bag to slowly circle the stranger. I need to drop this fool before someone gets hurt.

I said, ``Who are you? What is your purpose here?''

He said, ``You are my purpose Susan. You are lost.''

I said, ``I know exactly where I am, I think you should consider yourself lost if you think you can overtake our group. How many of you are there?''

He said, ``I am one but we are many, I have not come to fight but it would please me to meet your blade in battle. Prepare yourself then.''

I said, ``You haven't answered my questions. Answer me one then, who are you?''

He said, ``Of course, pardon my failure of etiquette. My name is Leviathan, and I am d\ae mon. We meet again Susan''

Oh shit.
