\lettrine[lines=2,lraise=0]{I}\space leapt onto the chopper when it arrived.

I said, ``Hey bud, change of mission, I need you to get me somewhere.''

He said, ``Yeah, back to base, that's my orders. We need all teams home a red court vamp just made a kill on our base.''

I said, ``Well goddamn it, ain't that the shit. You're still getting me where I'm asking.''

He said, ``Look soldier, I have my orders and I ain't got radioed no changes. Everyone back to base no exceptions. You're going back to base.''

I said, ``What if I said I was holding you by gunpoint, would that change your orders?''

He said, ``You're not holding no weapon at me.''

I said, ``Do you want me to?''

He said, ``Jesus, what's the deal miss?''

I said, ``There's a soldier out there and she's in real bad trouble. I gotta find her and help her get herself home.''

He said, ``Well that is my orders, to get everyone back to base no exceptions. I say that would include her. Where's our comrade?''

I said, ``Thanks man.''

He said, ``Stay on mission.''


I seen a vision of Jane, she is by a stream and she has changed. Her body anyway. Her skin is black, she is muscular and big. Something different from me in that. She is as terrified as ever. I hear her whisper to me. She wants help. I do what I can to send her feelings of comfort and of my impending arrival. She seems to pick up on it and calms down a little.

\parasep

I'm trying hard to use my psychic connection to Jane to find her location. I'm not good yet on how it works but I did find the stream and got chopper boy to follow it until I had some really strong sensations.

I said, ``This is the spot man, I'm gonna get off here.''

He said, ``Lady there isn't anywhere to land and we got no chutes. What are you gonna do tuck and roll?''

I said, ``Not your problem I got this.''

I did some shapeshifting on the last mission, I'm feeling rather confident on changing to and from trueform now. If not well I'm saving someones life so if I die trying there is honor in it.

I leapt from the chopper right into true form. Even as I passed doors of the huey. Chopper boy was praising God but getting the words mixed up.

My senses got stronger as I was able to fly on my own. I could feel her close. I heard her in my thoughts.

Jane said, ``Susan, is that you up there?''

I said, ``I can feel you I think. I hope. I want to say yes.''

I heard a disturbance in the forest below, and through the leaves I seen what looked like an honest to hell demon fly out. The fire and brimstone type. It had leathery bat wings, barbed tail, ungulate legs. It was definitely Jane but the changes were significant. Looks like she is about 10 feet tall like me, with a vulgar display of muscle. Her skin is black like a red court but her whole body is rippling with fire. Her talons were hand and foot as well as at the four points at the rear of her wings. She had a rear facing talon behind her foot, representing her thumb. She demonstrated she also can present feet or hooves by curling her talons. She had heavy horns that curled from her temples back then down and away from her head in a clockwise curl. As much as I may be somewhat light in mass my daughter here was like a massive sherman tank. How in Christ's name she can fly and fly well with wings I am without knowing save that it be by supernatural means which is to be assumed given that I find nothing natural about her current form.

We flew hard toward each other, and embraced in mid air. I was unaffected by her fire. Then together we flew hugging the treetops a mile and descended to the stream again. We're fellowship, it's all about staying hidden. Chopper boy could bring the cavalry after us if he knew where we actually were. We both reverted back to a human form.

I said, ``You seem different. I take it you couldn't stick to your diet?''

She said, ``It seemed sometimes you were there with me, I'm not sure how. A couple times I felt your presence, reassurance, in a real way. Were you really there?''

I said, ``I would get visions of you, like I was you. So maybe, but not intentionally you didn't want me around.''

She said, ``I was angry. I'm a bit of a hot head even when I try not to be. I got over it. Especially when I seen I healed a good quarter of the thousands of sick people under my care. I'm sorry, you were right.''

I said, ``I seen them, you showed me. I heard your apology, you were successful in getting it to me. There's a lot of healing that has to be done for people. We may not bear the burden of guilt but we do bear a certain burden of making it right. Even after this I think you will find there is a need for you as you are in this world. You're a healer, be a healer.''

She said, ``Then of course eternal life. I was actually looking forward to a good death and living within the frame of my generation. I'll lose over and over endlessly.''

I said, ``Eternal life on earth is a lie. Vampires were supposed to be immmortal but we seen in our own time the death of an entire court of vampires, all killed in an instant. Everything changed.''

She said, ``I hate changes.''

I said, ``Who doesn't.''

She said, ``So how do we eat then?''

I looked her up and down, then I said, ``I think you already know girl.''

She said, ``No no I mean, the reds had thralls to feed from. I hate the practise with a passion they left such horror behind.''

I said, ``Remember it took a vampire to heal the harm done by other vampires. I'll help you understand your dietary concerns in the mean time just be careful who you eat you don't know where they've been.''

She said, ``Christ.''

She started chuckling, then I said, ``See? I finally broke through. Have a laugh, and feel a little better. I'll help you get back on your feet doc.''

She looked at her hand as talons split open through her fingertips. I said, ``Whoa careful Jane, that looked like a flesh mask. You might have a red court inheritance like me. You don't want that true form in daylight, don't shed any more it's going to hurt.''

Of course she didn't listen, or didn't hear me, the flesh mask tore open to reveal a red court true form. The sizzling and smoke in that bright sun was horrific. She shrieked and the flesh mask went back on so fast I thought I might have heard a shmuck.

She said, ``Oh my God was that what I think it was?''

I said, ``Yeah. That form is readily accessible to me like an alternate true form. It's a red court true form.''

She said, ``Oh God, this can't be happening, I'm changing, I'm going to lose my soul to corruption''

I said, ``No you won't. We came from a red court heritage Jane. It's in our genes so to speak. That's all it means.''

She said, ``What kind of fool are you? It's red court. We are bringing them back into this world to cause even greater suffering to people.''

I said, ``First thing, you seen your other true form. It is absolutely not red court you know that. Second if you have true form you have completed your turning. Finally listen to yourself, you have compassion, and true empathy for people. The reds did not have that. No virtue. If there was even a single one who did I never met them in all my years of fighting down here. When I came here the fellowship counselled me on my infection. They related it to a child of a murderous and terrible parent. They said to me your genes do not make you, they do not ensure your fate. You are your own person and you choose who you are going to be freely. You need to understand that it stays true for us, I can swear to you I have lived by that motto both before and after I completed my turning. The same goes to you, don't deceive yourself, you are still and always will be your own person.''

She looked at me, nodded and smiled. She laughed then and I was a little confused until she said, ``Those red court bastards must be rolling over in whatever manner of grave they have.'' I snorted and smiled.

She said, ``Well I guess we should start heading back, I'm getting hungry. I guess we'll make some kills and have some laughs then retire for the night.'' Then put a hand to her head and clenched her teeth.

It felt like blood ran from my face, I said, ``Jesus Christ no, not that. Bloody hell. I think it's time for you to meet my friends.''

I must say caring for me and Jane's needs over the next few weeks gave my friends great joy. We arranged for them to have the healthiest food we could find and they got enough venom to keep them healthy as olympians.

\parasep

We sat there by a stream for some time. Skipped some rocks and I laid my arm across her shoulders while she wept for a while. Eventually we decided to head back. We flew low to the trees and landed in a desolate forested area close to the encampment. We wandered out and were immediately met by a search party that was looking for Jane and me. It wasn't too hard to dismiss Jane's transformation as she was very fast to get out of the encampment when she was completing her change. We went with the story that she suffered a mental breakdown and I took some time to help her work through her troubles. They told us of the brutal red court vampire attack in the camp. Of course we expressed shock and horror. It was a couple weeks of sentry and personnel testing. It consisted of taking blood from the population as red court vampires don't bleed. Together me and Jane passed fine as our shapeshifting allowed us to take to a perfect human form. We are turning out to be rather bad-ass in my humble opinion. We fed together with my thralls, now our thralls. We flew together many times at night and talked at length about our place in the world and our future. Jill was jealous as fuck. I explained that Jane is my spawn, effectively my daughter, and I need time with her too especially with her being a newborn vampire. Jill was still troubled but she understood what I meant.

We received reports of the incursion of a species known as fomor. Most of us just called them frogs since they were in fact a striking resemblance to a frog. Supposedly they were pouring out of the sea in great numbers into central and south America, taking up the vacuum left by the red court where the other supernatural species were so far unable to. Say goodbye to the old master and hello to the new master, just like the old master. Jane swore to protect the encampment with her life and serve her general with honour. I'm proud of her, that's exactly what I hoped she would do. As a side-note she needed the thralls a great deal to keep her fed as she found if she was working with the sick while she was hungry they seemed to know it. The screaming and horror became almost silent. They attempted to tempt her into a feeding with submissive bodily language or even bearing their neck in a blatantly obvious suggestion. It rouses a hell of a lot of suspicion. She blamed it on pheromones from a bad batch of the cure. She did catch herself a few times when she foolishly left herself hungry succumbing to the temptations of a patient and taking a bloodmeal from them. She cried with shame afterwards but picked herself up and kept going. Those she cured showed no signs of bad health afterwards which gave her a whole new joyful outlook on our world, a hope for happiness and peace among people and beasts.

After a month had passed I received many invitations to work for or consult for the most prestigious newspapers in existence. I received a nomination for a Pulitzer from the story I wrote on the San Jose zombie abominations. I knew then it was time for me to go north and drum up the support we need down here. I got myself scheduled on a craft bound for New York City and made a deal for a consulting job with the New York Times. Geoffrey was leaving with me to share \chichenitza* research with the local New York City white council office. He was then of course returning to the queen to present the knowledge he uncovered from \chichenitza* and received from other authorities there such as the white counsel.

On the day we were to leave there were reports of fomor troops in the area. The generals intelligence contingent determined it didn't pose any risk as it was shown not to be moving near us and will pass the encampment by a few miles. All is good so far, and I'm ready for the next leg of my quest. That morning I stopped by the tent to see how my thralls are with the preparations for our departure.

I had some time to talk with Jane before I left, and found the news fascinating.

 Things are changing in the fellowship, and it all can be blamed on the destruction that had taken place at \chichenitza*. Those who were infected by the red court were half vampire, as long as they resisted the urge to feed they could remain half-turned. If they fed they would kill, there is no controlling feeding for a half-vampire. Once they killed their human body and spirit were consumed with their prey and the vampire inside, corrupt and evil, took over. Oh there was the one in a million exception like the brother of my ex-boyfriend Harry but it would not be wrong to assume the evil of a vampire and never trust any of them ever.

 The day the vampires died at \chichenitza* so did the symbiotic vampire halves of those fellowship members. Most of us died as most of us had already lived far beyond our natural human lifespans. The natural law had finally served justice on us. We had the aid of local people as we fought for them, although most of the local people did not officially belong to the fellowship. This also changed that day at \chichenitza*. The locals poured into our ranks and also vulnerable supernatural beings are pouring in as well. Our terrorist aspect is diminishing and we are showing ourselves as we really are, a much more obviously organized military force. Up until \chichenitza* we presented ourselves as a loose band of terrorists acting against the red court. We were more organized than we appeared to be from the outside, and that was by intention. The less the reds thought of us the better. We needed to be organized to be one step ahead and I don't think they ever realized how tight a military structure we actually had. As a matter of fact nobody outside our ranks knew it and nobody outside would believe it by our tactics. The official Fellowship, the infected, all stood to fight at \chichenitza* but our uninfected contingent wasn't there. We wouldn't under any circumstances show our hand. The human contingent and membership, and the few other supernaturals within or aligned with our ranks weren't there. So now we're gathering together again, our human allies are joining the fellowship and our supernatural contingent is also joining in great numbers in other areas due to the tremendous unrest and few remaining from the original fellowship. The fomor seems to have the potential to completely overwhelm us as they appear to be pouring out of the sea and there may be more down there than there are stars in the sky. Luckily enough our numbers are swelling. So far the continued existence of the fellowship is unknown outside of the central and south American areas and we are representing ourselves as guerrillas in the tradition of those of the central American past. In other words we are back to our old tricks, just as the history of the organizational structure of the fellowship is revealed we are presenting evidence of the death of the fellowship at \chichenitza* in order to regroup and use a new deception to allow ourselves to fight on for a new cause. I am going to be drumming up support for central American guerrillas fighting for democracy, since that is what the northerners would be able to believe. It's like a return to the Reagan years.
 
 The morning we were to leave was quiet. I looked around and seen the soldier talking and patrolling with little to concern themselves about. The dust was kicked up with every step as the camp grounds were long since turned to 'naught but dust. It had been quite dry as of late not that the forest surrounding us had noticed. The sun was blazing down, the sky was blue and there was not a cloud in the sky. The cries of the medical tents were not as they were, Jane has given her own venom as if it were life itself, procuring the cure that indeed gave the patients life back. George, Vinny, Jack and Craig were assisting Jane, especially Craig. Having been assisted with venom by Jane he was once again a  capable surgeon and was quite indispensable in the care of the patients self inflicted injuries. Everything in the world seemed to be perfect. It’s the new normal. It makes me think that the time is ripe for something terrible to happen. Such is life as I know it.
 
 Nonetheless, me and Geoffrey walked casually toward the airstrip. The weekly flight for supplies was due, heading to NYC which is convenient for me. That is where my destination is. That is where I'm going to set myself up, and gather support for my fight down here. It is also where I'm going to fulfill my contract with the NYTimes as a reporter. I'm really goddamned excited.

The last of the fuel was being pumped into the cargo jet and the cargo bay was cleaned out, passenger seats erected along the fuselage walls for the handful of people, including us, that will be travelling north where this craft is expected to pick up needed supplies.

The general wandered up to wish me godspeed.

He said, ``Any ideas on how you are going to go about the business up there?’’

I said, ``I have my contract settled with the Times, I can at least start there. I can get some ideas in my day to day research.’’

He said, ``That’s something. I recommend not spilling the beans in any article of course.’’

I said, ``Of course. I need to live. When I spill beans I’ll try to not do so on my own doorstep.’’

He said, ``Good plan.''

\parasep{}

As I walk to the plane with Geoffrey I feel the ground shake slightly. No one else seems to notice and when I look on the horizon I don't see any other aircraft. I asked the general if anyone checked out radar for clear skies and he said the skies were empty.

Something isn't right. I don't know what it is but something is wrong. I told the general my gut is telling me trouble is coming. He stared into my eyes a moment and said he remembered what sarg told him about my being an elite.

The general told the officer nearest to him, ``call a code yellow, and get this bird in the air now. Somethings afoot outside our border.''

Me and Geoffrey were rushed to the aircraft and the plane was started and starting to move as we hurled ourselves up the boarding ladder and into the entry door. A crewman pushed the door closed and spun the flywheel to seal it. Me and Geoffrey were strapped to the personnel benches on the sides of the cargo bay. We heard a whistling sound close to the left wall and a crewman said, ``Oh\dots my\dots God''

Me and Geoffrey looked at each other, I could see his eyes widen. We both unbuckled our straps and went to the left windows of the aircraft. An army group was advancing on the camp. They were fomor. Hundreds of thousands of them. They were moving carefully I could tell but there is no doubt that was what caused the mild tremors I felt before we left the ground.

They won't miss the camp after all. They are aware of it and circled around to do as they will with it. I cant imagine why they would attack a location whose greatest purpose was to tend to the sick. I also have no idea how or why a ground movement of that colossal size would be assembled and moved overland. What the hell are these creatures attempting to accomplish? 

The red king must have struck a deal in his time to keep them at bay. I wonder what it could have been.

I said to Geoffrey, ``we need to keep that clusterfuck away from the camp. Somehow get them to turn about and travel to what they think is a more important target.''

Geoffrey said, ``Quick, find some radio equipment, maybe we can find a way to inject communications.''

``Jesus, I wish we had Laura here'' I said.

We asked the crewman and he ran towards the front of the craft, and we quickly followed. He said, ``we used this plane as an airborne repeater station on its last deployment. We took out most of the equipment but this beast was integrated too well into the fuselage so we left it.''

Geoffrey and I worked together to see how it worked. I moved to the nearest window and seen that the troops were moving somewhat to one side of the encampment. Maybe the didn't intend to assault it? Still it could provide a target of opportunity. Maybe they did wish to make an assault but cant locate precisely where the camp is. We need to hear their communications to figure out what their plan is. I know I have the power to communicate in any language if the fomor used one none else here spoke I'm sure to know.

The crewman radioed down an encrypted communication about what we see and a couple minutes later the camp looked like a disturbed ant nest as soldiers moved quickly to appropriate battle positions. The whistle earlier must have been a round passing within a couple feet of the fuselage. Just because they seem us they may not know exactly where we took off from. We always keep close to the ground and we were circled around to the same side they are now heading when I heard the round. That's why they aren't heading straight for the camp I bet.

Just then the crewman said, ``I have a call, from someone named Laura on a secure channel. She said she is attempting to turn the group around. She is asking for you.''

I take the mic, and Laura said, ``We are going to open fire on you from a field unit. Slowly rise and perform a flyby. I'm going to get the coordinates sent to you. We are trying to make it look like you were coming in from a distance to make an attack indicating you are an adversary and the camp is a few miles out at that location. There's no way they would know where you took off from only the place in which they seen you. I hope this works.''

We receive the teletype of the orders and bring it to the pilot who looked like he was going to shut himself hearing about the situation. He lowered himself back to the treeline and pulled the plane around. A couple minutes later he began a slow ascent. The location began unleashing smoke rounds from what seemed like a 40mm anti-aircraft vehicle. The fire sang well away from us but at a trajectory that would not be so obvious to the army group. When we got close enough we banked hard. Returning to a tree skimming altitude we again continued north.

The army group halted. I imagine they were trying to interpret the meaning of what they just observed. Everything was quiet for a few minutes but it felt like a few hours. Then the single shot heard around the world. One of the fellowship soldiers accidentally fired a chambered round and the sound echoed like a single kernel of popcorn popping. I hoped the Fomor might not be able to interpret the direction it came from but unfortunately they formed the troops and moved in on the encampment

We are doomed. The size of that force has hardly ever been seen marching across any land. As they wrapped around the came the whoomph of artillery hitting the ground echoed to my ears. The fellowship soldiers were in panic and shooting each other in confusion. The general called for the chainguns to open fire on the treeline and a buzz starting with the sound of a power transformer and escalating into a hive of angry bees started to come from the camp. Much of the treeline fell and a thousand Fomor likely fell in the counterattack. This was far from enough though and the lines of troops continued to move in. Soon the fellowship troops began to turn on each other as the Fomor were close enough to unleash their psychic abilities and possess the fellowship soldiers. I tried to counter the psychic attack from where i was but I don't know enough about my abilities yet and couldn't do it.

Just then an artillery sheel struck at the medical tent. I didn't know but could only assume that many of the sick were killed in the strike. There was one other that I feel was killed though, as I heard a scream in my mind and intense pain. Then nothing. Jane was also hit. I fear she was killed, I don't know, but for the first time since I turned her I felt a sickness in my heart; an emptiness has settled on me.

More artillery strikes came down. Rifles fired and grenades dropped. The fellowship heavy weapons may have taken down a thousand Fomor but I would be surprised if even half the camp was left alive. The Fomor are only just now coming out of the treeline yet so much damage has been done we have no chance against them, we never really had a chance at all though. As soon as that rifle fired we were all but beyond hope. Indeed our only hope was to hide, to let them pass.

Now only a single hospital tent stands, Janes formula and cure for the suffering is likely destroyed, in fact her research tent is quite destroyed. Most of the tents are gone. I have no idea how many have survived this far much less who.

Pouring like water out of the trees the Fomor came, washing away all that they touched.\\

Then came a roaring thunder from within the camp.\\

From the hospital tent area, now all but swept away in the assault, in fact from where the research tent of Jane's once stood, an eruption of lava came.

I don't understand what the purpose is for the Fomor to cause such a demonstration over and above the shock and awe they are already demonstrating in our destruction. Bastards.

The ground there started to spray lava all the more, and for some reason the Fomor assault slowed. Oddly they seemed concerned by this development. If it is as it seems this occurance is hardly of their making.

The fellowship were just as wary, now already backed to the rear of the camp as the Fomor were moving in on three sides. This gave them a chance to run for cover as the fire stopped while the Fomor observed and calculated a response.

%thunder and lightning
Just then there was an explosion from the ground identical to, but not as intense, as a volcanic eruption. Jane emerged in true form, looking like a demon risen from the bowels of hell. hovering in the air on her wings and flames pouring out from her every side. She roared and the ground shook hard, knocking the whole of the Fomor army off it's feet and cracking the ground from which lava began to flow. The remainder of the fellowship was able to huddle close together but the Fomor weren't so lucky. There was just too many of them. Thousands were instantly turned to ash with a single roar. She held a fist out and said \enochianxx with a growl. The possessed fellowship soldiers were instantly pulled back to their normal selves. She held the other hand out flat and said \encohianxx in another growl and the cracked earth sealed enough for the once controlled soldiers to flee back to their comrades. A few hundred Fomor pulled them back under control but Jane said \enochianxx in another angry growl then clapped her hands in front of her temple. A couple thousand Fomor collapsed with a crushed cranium. Jane rose higher with her wings and her voice echoed across a great expanse of forest and hill, echoing out much farther than the army ranks that stood before her.

She said, ``Be it known now that this people are under my protection for I am demon and sworn servant of my emperor, so has it been decreed by the one almighty Satan of both the earthly domain and of hell. Leave this place now for you shall make no fool of the the emperor Satan or the empire over which he rules. You shall not be forgiven this day, leave now and by his good humor perhaps you may yet live another.''

The troops began their march, unaffected by the speech. They haven't tried any deathstone so either they are idiots or they are geniuses. Or they just don't have any.

Jane begins a strafe of their ranks She seems to be able to devour souls with a successful attack of her claws where I just do it by an act of will. My God I wish I was better with my talents I could have done at least something even if I'm all the way up here. I feel like a heel.

She took some heavy hits but after maybe half a dozen kills she began healing faster until she seemed almost semi-corporial. She was no longer getting hurt by anything they could hit her with. She rose into the air and growled out ore words \enochianxx and a ball of lava struck the earth hard and slaughtered hundreds. The troops began moving faster to the camp. As it is she can't defeat the Fomor fast enough there are too many. Under heavy fire she barreled backward in the air and made a circular gesture in the air in front of her forehead growling \enochianxx then clasped her hands in front of her and released them pointing her open palms at the army. Five thousand became possessed and the army became confused. She flexed her to her side, puffed out her chest and roared into the sky. Slowly she became a brilliant as the sun and everyone on every side of the conflict shielded their eyes. An incomprehensible ball of brilliant light burst from her and bowled through the mass of the incoming force. Tens of thousands were as best I could determine disintegrated. The earth melted into glass and the ball hit a mountain in the distance and collapsed at least half of it by the impact resulting in a mushroom cloud. She once again dove directly into the incoming troops and devoured them in a strafe then pulled back up to observe. Some of the Fomor were in fact fleeing, half the remaining force at least. The other remaining half were fighting each other as most of them were possessed by Jane.

Our plane was maintaining position some distance away from the action. For the longest time I think I was the only one that could see what was happening although Geoffrey certainly heard the disaster on the radio.

After the last of the Fomor were defeated and the remained routed the possessed Fomor soldiers dutifully walked into the remaining lava streams. Jane's flames died down and she slowly became fully corporial again. She landed amidst the slowly coalescing flows of lava and walked forward towards the remaining Fellowship. Dear God she looked like some kind of superhero, ghost rider or something. She was breathing smoke, truly massive musculature all rippling, the ground shook with every step. Her breathe remained quick and took a long time to slow. As she approached the Fellowship soldiers stared at her, in complete silence. Everyone was absolutely, and perfectly still. Her steps started becoming lighter until they made no more noise than any soldier. her stoic expression became a smile, and the only thing to break the silence was a single soldier dropping a rifle. Still, no one either moved or broke the silence.

Our aircraft continued it's course north, knowing at least for the time being the aircraft has something to come back to. As a matter of fact that is likely why the pilot decided to stick around was to have some idea whether it was coming back. Given the destruction and the fact the camp location is known by a hostile force the reality is the aircraft will likely stay north, until the situation changes for the fellowship here and another airstrip is attained for supplies to come in. This was a very bad day for the fellowship. I'm not sure if we can survive this, and if we can't survive this whatever wicked plans the Fomor has may very well happen uncontested. We must find another way to contend with this new threat even if it means returning to our origins of being a terrorist cell against them. Jane is a formidable advantage to the Fellowship but this day the Fomor did not have any deathstone. The next encounter they will most certainly have deathstone ordinance with them. They will be focused on ending Jane then, as the biggest threat, and I will surely lose my baby girl.

As a matter of fact as she was approaching


 
