% scene- conflict continued.
\lettrine[lines=2,lraise=0]{I} move Spook up towards me, and pull down even closer to the water. As I see the smoke from the lead birds eyes I touch down of the river and begin hydroplaning. I lay myself as close to the river as possible with my wings raised slightly ready for action. As I skim over the river I bump the occasional bird as I move at incredible speed. The action of touching the river stirred the fish to launch into the air behind me consuming the birds I move past. Before I lose all my speed or push my wings out and use the last momentum to flap and move myself 5 feet into the air and move of as the fish consume the last of the surprised birds behind me.

The flocks are decimated now, only a few remain. Most of them are attacking each other and one by one fall to be consumed by the fish. One of the few remaining creatures, which is heavily injured, flies toward me to make a final attack. I move Spook down to my foot talons and grab the creature by the neck. I break the bones of it's limbs to completely hobble it. I look into it's eyes to try to find a spirit, a spirit that exists in all creatures. I must have a spirit, even if it is deathless it is still a creature.

Nothing. There is no aura. There is no spirit. Only evil is left.

I see in it every dark and terrible nature of man. First and foremost I see madness. Within the madness I see: anger, arrogance, bitterness, coldness, paranoia, rage, resentment, envy, cruelty, selfishness, hatred, viciousness and of course violence.

It is sad that a person can be consumed by darkness but I never thought I would ever see someone consumed to the point where the spirit is utterly destroyed. I never thought I would see such horror.\\

I break it's neck, and throw it to the fishes.\\

Time to move on.\\

%sequel - emotion
We fly off resuming the course we had started in. The remaining creatures fight each other, flee, or get consumed. They no longer pay any attention to us. Now I know why. They prey on the weak, and heed the strong resentfully waiting for their chance for treachery. We have proven ourselves strong, and we are going to leave this evil game to these creatures in their wretchedness.

There is no redemption for these creatures; there is no redemption for this place; there is no spirit to be found in this place, only abominations of life that once was diabolically animated to mock the life that once was.

Why did this happen? What has created this horror, this place?

I said, ``Dear God Spook what happened here? Why did this happen?''

He said, ``I wish I knew Susan. To some warlocks this is justice but to many this fate is a crime. No one has the answer, even though many warlocks have searched for a cure for this fate none have yet found it.''

I said, ``Is there no way to evoke the magic to do the same things without descending into the accursed place?''

He said, ``No. Anyone who uses the black magic, who bends magic too far will come here. Even using black magic a single time will create a draw on a warlock to use it again. Every time a warlock uses dark magic the draw gets stronger and the damage to their ethereal body becomes worse and worse.''

%sequel - thought
I said, ``Yet the half vampires could use the black magic with impunity.''

He said, ``Yeah. We were impregnated with undeath, we had the dark nature within us by being infected by the red court. Now we don't.''

I said, ``So what happens now? Can we destroy this place?''

He said, ``No. This place is part of the curse that we don't know how to undo.''

I said, ``So what happens then? If there aren't any more half vampires to work dark magic for good purposes? In the fellowship it was part of our burden, there was a lot of dark warlocks among us to do healing that no others could.''

He said, ``Susan I don't know what happens. I guess dark warlocks just have to make a choice to follow the dark path, and accept the destiny that will come to them. I don't even know if there are enough people with magical talent sufficient to replace those that are lost. Maybe in the end more people will die from magical and ethereal disease and that's just the way it will be.''

I said, ``Spook that's horrible. No way, I've seen the horrors in these creatures but I've seen worse horror in the ethereally ill. Left as a vegetable, with an ethereal body torn to shreds in horrifying ways. Destined to live all eternity suffering in pain from wounds that never heal and a body that can't release them to the afterlife. I could never imagine how terrible a fate that is anymore than I could imagine the destruction of a spirit like these once mad warlocks had undergone. I only hope that most of these were truly evil in life.''

He said, ``They were. The majority of dark warlocks seek wealth and power through magic. They were evil before they even took up magic. It's the minority, the well intentioned dark healers that share the same fate. It's unimaginable that there is no way to stop the carnage.''

%sequel - decision
We just need to get to Spook's tower, find a way out of here. I don't want to spend another minute here to consider the injustice that surrounds me. I don't want to even think about it anymore. It's wrong in every imaginable way.

I said, ``Spook, when we get to your tower what do we do, to get out I mean?''

He said, ``My ethereal tower has all the magical material I own. It is not only duplicated but books and equiment that are long lost to time remain in my tower safe from anything that would ruin them. My tower here has been here since I was an apprentice and will be here until my dying day. Probably even after I pass. It's the nature of the Astral, even though time passes quickly here nothing that has come into being here ever will cease to be.''

I said, ``Time passes quickly here?''

He said, ``Yes, quite quickly. I can work and study a long time here and time in the real world has not passed as far. I never measured the difference but there is definitely a difference. I have an exit spell that I used once, it worked well, it is an emergency spell but unfortunately it does take some time to cast properly. I've been here a millenia already I'm pretty sure so what's a little more time?''

I said, ``You and me both, or so it would seem anyway. This God awful place is an abomination unto itself.''

There was a magic circle set into the ground inscribed with strange sigils. Spook said they were the sigils of the four elemental d\ae mons each considered to be of the d\ae monic divine, the most powerful d\ae mons in existence.

All still remains quiet. we climb up into the tower. I was startled by an unearthly growl to see an animated corpse. I spring back and prepare to destroy the monstrosity when Spook calmly places his hand on my shoulder.

``It's my own creation Susan, it wont attack any friend of it's master. The soul has long since departed and it is no use leaving their shell to waste. The former owner certainly has no use for it now.'' said Spook.

I said, ``How many of these are here?''

He said, ``About half a dozen, and in the crypt below the tower roam the oldest servants skeletons and mummified corpses. I don't let any creation go to waste.''

I shudder, yet he smiles. He is without a doubt a true warlock to find this necromancy acceptable. I'm glad he's on our side. Dear God the smell, the unholy smell of rotting flesh. I can't help but gag yet manage to get it under control.

``My library is on the third floor.'' said Spook.

We climb up and see endless shelves of books. As far as the eye could see. This library is far larger than should fit into the tower we entered which was quite small in circumference.

I said, ``I take it the usual laws of physics don't apply here?''

He said, ``Precisely. I define the laws of existence in this realm of mine in the astral. My library is infinite, although sadly more often than not mostly redundant. What you see is vanity.''

I said, ``Good. I couldn't figure out how you acquired all this in your short lifetime.''

He said, ``A magical exercise in recursion. Over here, third shelf down. Let me see---''

%sequel - action
Just then we heard the most horrible scream coming from outside the tower, still some distance away. We looked at each other and his zombie minions grabbed polearms. With a growl they shuffled down the stairs.

I said, ``What was that?''

He said, ``Inspiration. Lets get what we need and get the hell out of here.''

He described the book he needed. Bound in human flesh I found the grimoire and he let out his breath in relief. He disappeared on the next level up with some ingredients. He had stones, herbs, oils and other items. We continued down and checking the grimoire he gathered items of flesh. I dare not ask what exactly they were or where they came from. Once on the ground floor he began setting up candles at four points. chanting he dusted around the circle holding the grimoire, reciting words of power as he went. A purple light began to eminate from the circle and black oily smoke arose smelling like burning flesh. I could hear distant sounds of crying and screaming coming from the general direction of the circle. Spook gently touched my shoulder and led me with him into the circle.

The door smashed open.

%scene
The spell shattered as I entered the circle, the landscape around us filled with deafening screams as the tower broke to pieces. We are sent hurling into darkness as the world around us seemed to consume itself into a break in reality, consumed by a black hole that left behind complete nothingness. Where once was a land and sea that nearly consumed us now we are witness to the horrible plane having consumed itself.

Are we next to be pulled into this darkness, to meet our doom?

