\lettrine[lines=2,lraise=0]{S}o what the hell do they want to hear? I just decide to start with a realistic description of what we are. I said, ``We're refugees for God's sake! Mercy, leave us be!''

``Well don't you have brass balls. I would believe it from these quivering wretches but you are something else. You a merc? I think so. I have no use for rogue red court assassins. Your masters are gone, now you die murderer.''

%scene disaster
Veronica leaps up to defend me, ``No! Don't hurt her!'' Crack! Literally the shot heard around the world she took an AK round through the temple. She was dead before she hit the ground. My friends all screamed and jumped to her.

One of the gunmen said, ``Cease fire, these poor wretches have been through enough. This woman is a problem, she could kill a hundred before she falls.''

The gunman raised his rifle and said, ``Stay on mission.'' The others repeated, ``Stay on mission.'' The motto of the fellowship. I found them.

I said, 

\begin{quote}
	    I am a Fellowship Soldier.
	    
	    I am a Warrior and a member of a team.
	    
	    I serve good, and live the Fellowship Values.
	    
	    I will always place the mission first.
	    
	    I will never accept defeat.
	    
	    I will never quit.
	    
	    I will never leave a fallen comrade.
	    
	    I am disciplined, physically and mentally tough, trained and proficient in my warrior tasks and drills.
	    
	    I always maintain my arms, my equipment and myself.
	    
	    I am an expert and I am a professional.
	    
	    I stand ready to deploy, engage, and destroy the enemies of humanity, in close combat.
	    
	    I am a guardian of freedom and the right way of life.
	    
	    I am a Fellowship Soldier.
\end{quote}

%transition
The gunmen immediately click on the safeties of their rifles, and lower weapons. The one gunman said, ``Now that is something that never got far from any base camp. Sorry ma'am it's hell out here. What's your name?''

I said, ``Susan\dots{} Corporal Susan Rodriguez.''

He said, ``Well good to see a sister out here Susan, I feel like shit about that woman I'm so sorry people. We don't know who are friends from who are enemies out here.''
%Sequel emotion

Jill said, ``You fucking monster, does she look like a threat? What the hell could she have done?''

The gunman said, ``Quite a lot. If she had a pistol, or worse explosive ordinance she could have taken one or all of us down quick.''

I said, ``Doesn't make it right bud. You know my name what is yours?''

He said, ``Sargeant Miller, Dwight Miller. Everyone calls me Sarg.''

``Well Sarg, just so you know, we're all tight here and would be quick to lay down our lives for each other. We don't know you yet, I would like some private time with my friends here so we can decide what to do next.''

``Granted. You take what time you need. We are going to make camp here for the night. We've been in cover for hours here observing you all and we are tired. Especially tired given we killed an innocent today.''

``I hear you. We'll debrief in the morning then as to where we go from here.''

``You are welcome to travel with us if you decide so. We are heading south to find base camp, if it is still there. Most of the fireteams I've met up with are doing the same. We need to regroup and figure out our place in this new world.''

``Who are your people then?''

``I'm Sargeant Dwight Miller; some say I look like the punisher, the comic book anti-hero. We also have Edgar the spook Chalmers our warlock; he's a dishevelled millennial. Our heavy hitter is Jamar aka Jobu, like in the old `Major League' movie; He looks like Michael Clarke Duncan. Then there's Strength our scout; We sometimes just call him injun. The finally there's Doc Seth our medic, sometimes just called bones; he looks a little like Jeremy Renner I guess.''

``Well, you don't have that superhero physique Sarg. Otherwise I guess sort of. Spook looks like some kind of evil hacker, are you sure he's a warlock and not working cyber warfare? Jamar is chiselled and not nearly as friendly looking. Doc definately looks like Hawkeye, hands down. You didn't mention Injun, I guess he's just a wiry, sure footed, long haired native american. A small man but he is the quickest and quietest soldier I've ever seen. Sarg how'd you get infected?''

``I didn't. My wife was infected and one of her children was her first kill. Our other children were killed immediately after. Then she fled without a trace. I left my life to come here as a human to fight in my families memory.''

I gasp, and rest a hand over my heart. ``You wouldn't be the first. I'm so glad the red court is gone.''

``Perhaps, as long as I live though I will never set aside my vigilance.''

``I understand. Even if I wanted to I don't think I ever will either. I'm shocked you have a warlock? He's precious as gold. You must have anti-vampire ordinance then?''

``Or as we call it now supernatural ordinance. We have more than vampires to worry about out here.''

``Yeah, I know. Lord do I know. Thanks Sarg, I'll let you know what we decide.''

\parasep

%sequel thought
``I am not going to go anywhere with those assholes. We'll roll on our own, I would rather fall on my sword than travel with them.'', Jill said.

Vinnie said, ``I will believe to get us to be loved in a jerk or will be lived love during when they are far. For spectacles believe they fear. A jerk or by far. Lots by far. Lots spectacular. I will by want us in. Want us to get ass cheeks.''

I smirk, and roll my eyes.

We were gathered around in an area not too far from our campsite, far enough away from the soldiers we hopefully won't be heard easily. Without the vampire part of the fellowship, the infection, it's much easier to say we are out of earshot. The infected or half vampires like I was had supernatural hearing nearly as good as full red court vampires.

%sequel - thought
George wiped his eyes and said, ``The more of us the more chance some manner of contagion might invade the group. That's what Veronica would have said. I vote nay, we go it alone.''

I said, ``It would be safer, we would have a better chance of getting somewhere safe. It only makes sense.''

Jill said, ``Oh yeah, so we should believe the one who lethally fed off our friend Daniel? Sucked him dry, I seen you. I know. We all know. Here we are and you wont damn well touch us.''

I sat there feeling surreal. This is what I worst feared. They knew.

Craig said, ``Great. Thanks Jill that helped. Now we're going to lose our vampire and along with her all hope of getting better.''

I said, ``Hello, I'm right here. I have a name you know. I didn't think you knew about Daniel, I'm so sorry. I know saying I was hungry doesn't help much. I guess I wish I could have munched a bad guy there just weren't any around right then. That didn't come out right sorry.''

Jill said, ``No there is no good way to say it. I know you didn't mean anything by it Susan it's just the way you are. You need to feed soon though or you are going to kill again. I've lived with reds long enough to know, you need to accept us or you will kill again. It's your nature. I love that nature, please be the vampire you are it is a noble and beautiful thing.'' She grabs her fang necklace and holds it tenderly.

I sat there thinking. She's right. The soldiers killed today to defend themselves but my hunger is worsening and it will eventually make me kill to feed. The soldiers had no choice but I do. I can't keep on starving myself. I have to have enough wisdom to realize if I'm stubborn and blind to the reality of my new nature I will kill again and again. I need to eat a regular diet so I don't gorge myself. Just like anyone.

I sat there a moment. Then I looked at them and I said, ``OK, I'll try. I only know to kill though. I refuse to feed in the hope I wouldn't need to and then I just end up killing from hunger. I've never fed normally. I don't even know if I have venom, at least not the kind you need. I'm sorry guys I don't know for sure what I am, I'm scared. I'm scared that I am a monster more horrific than any of the reds could be.''

Jack said, ``You're a vamp. I don't know how you could be a daywalker after only having risen a few days. Maybe you have amnesia, you're old but can't remember. You're just a red though, you drink blood. I don't care what Jill said, wings and talons and such. She tells long tales.''

I look at Jack and raise my arms. I give him a little smirk in the hope he is not going to attack me and then I extend my talons. Everyone except Jill jumps back. Jack pulls up his fists then backs down. Everyone looks at Jill. Jill said, ``I told you. It's all true she took on that thing, changed to some kind of vengeful angel and drove it off. There's her talons like I said. It was all true.''

I said, ``If you want me to try feeding I will. You can see now I'm not any red that any of us have ever seen. I'm not the same. So you know feeding is a risk. I still say we need to join the soldiers. It's not about whether they are worthy or not, it is not about what happened to Veronica. She would not like us putting ourselves in danger just in stubborn defiance especially for the sake of her memory. You know that. I'm starting to realize my abstinence has been putting your lives in danger too. So if I'm taking the risk with feeding, please take the risk in joining with the soldiers. These are fellowship soldiers, not mercs. It's not for sure we are safe with them, they may have forsaken their oath but at least the fellowship \textit{has} an oath.''

%decision
Laura finally piped in and said, ``I agree. These soldiers give us an excellent strategic advantage in our plans. I will follow them. The odds are well placed. It is less likely they will betray us than other men of war and that possibility weighs well against the tactical defensibility they would provide.''

Jill said, ``Agreed then. We follow them. Let's camp for the night. Laura it's your turn to tantalize the vampire.''

Vinnie chuckled, then said, ``Provide for the lift of the need to cause food. If takes for Life and heinous food, in the chef nutty nutty nutty impact. Heals needs thy Food, nutritious for lift of thrones ornate food, nutty Food. To top the need for methyl of their cough, if youth for continuous.''

Laura said, ``Understood.''

I snorted and laughed.

Then I let out a kind of maniacal giggle, thinking of willingly taking thralls. I'm not entirely able to accept the reality quite yet. I have thralls. Whether or not I choose to feed from them they will follow me. Jesus. I have thralls.\\

That night Laura snuggled up to me. I nuzzled her for a while, slobbering on her like a dog. She started giggling and moaning, when she started falling limp I was aroused to feed big time. Then I just let go and bit and fed from Laura. She let out a deep gasp and moaned intensely in pleasure. I heard Jill from the other side of the tent, ``Thank God. It's about time.''

Vinnie said, ``Thunder cheese.''

\parasep

%action
I let the Sarg know we decided to accompany them. He made the order to make ready to escort the refugees south with them to freedom. Or hopefully so.

He said, ``Strength take point.''

A quick and silent native warrior said, ``Aye.'' and slithered into the forest silently and quickly. So silent I couldn't hear him myself with my vampiric hearing. Amazing.

Sarg said, ``Jamar take rear.''

A huge african-american bear with ma deuce broke his way to the back.

Sarg said, ``Seth stay with the people, make sure they aren't wounded.''

A man that looked like Dr. Strange from the comic books, grey at the temples, moved amongst my friends to check them. He's a medic, he carried medical gear.

Sarg said, ``Edgar stay with me, corporal Susan same stay here. Spook we need more jars, we deployed too many on those blacks a few weeks ago and haven't got any back yet.''

Spook looked like the epitomy of the lanky greasy haired computer hacker.

Spook said, ``Aye. Susan do your people have any jars? Like literally empty jars of any kind?''

I asked, we had a dozen in the unlikely case we found a warlock. Freaky, we actually did.

We started out. Laura had no interest in world domination today. She looked like a teenage girl in love. She would steal glances at me from time to time and was just generally in her own happy place. I'm not one to talk though, I felt the same. When we made camp for lunch that day we sat together. I noticed the venom caused a vampiric reaction on her skin searing it. I cooled it with a rag and some water. She is going to make sure to cover her neck and upper torso from the sun to protect herself.

``I should have known better. The venom always kinda turns skin vampiric. It's just been so long since I've provided to my master.'' she giggled, ``you were wonderful Susan thank you.''

She snuggled in with me as the lunch was being cooked at the fire and I felt a rush of joy go through me from her touch. Like that being young and in love feeling. It was great. It made no sense. I just don't care, it feels so innocent and wonderful. I held her close and kissed her tenderly on the cheek. I love this.

Everyone seen us, and we made no attempt to hide anything. My friends, or, thralls, were looking very confused. I heard one soldier say to Sarg, ``Uh, Sarg. I think our new corporal is. Uh. You know. Like playing for the other te---''

``They look happy. I'm glad. How much longer for lunch, how are our rations\dots{}''

Jill came up to us and asked Laura, ``Girl, does it feel the same? Is the venom as it should be?''

Laura said, ``Perfect, feels exactly the same. Exactly what we need Jill, Susan's a keeper for sure.''

Jill said, ``Uh Susan, you're acting a little bit different from what you should. What are you feeling right now?''

I told her what I could about how I felt.

Jill said, ``Susan have you ever been fed on, ever?''

I said, ``No, I just got turned as far as I remember.''

Jill said, ``It's just that what you're feeling mirror the effects of the venom with only a few differences. What happened at the turning?''

I said, ``Dear God. Well if you want to know grab something to vomit in.''

So I proceeded to recollect my experience of the turning, and my thoughts about it.

\begin{quote}
		``The turning. I could probably turn someone too, it's an instinct, I just never tried or had the interest yet. 
	
	``My experience was very intimate. My clothes were torn and my body exposed, then Bianca in true form took me into her arms and caressed me, sliming me with her bodies excretions. That is, that slime they excrete like sweat in their true form. She continued massaging the fluid into me, and started cuddling me intimately. She drank from me, until I was delirious and near death. She savoured the taste of my blood for an eternity while my delirium worsened. I was nearly passing out probably from blood loss. I seen something change in her face, a kind of ecstatic release I guess. She rose up from me and her body started heaving. She leaned toward me like she was going to give me a kiss. Her claws sunk deep into my back immobilizing me. When our lips connected she started vomiting directly into me. It felt like worms inside me and I seen writhing beneath my skin. The feeling passed as she cuddled me. As the wormy sensation dissipated my senses seemed to just awaken as if all my life they were merely sleeping for lack of a better word. The dark room became like twilight. I was still confused and semi conscious from the lack of blood which I guess was returned to me when she regurgitated in me but I couldn't snap out of it. The bloodlust was there right away too but I didn't know what it was. I was thrown into a room, my love Harry was thrown in after. I nearly killed him but he snapped me out of it, the rest is history.''

\end{quote}	

Jill held a hand to her mouth and looked a little green. She said, ``Oh Jesus. I didn't know it happened like that. My God that's disgusting. They threw your beau in the room for you to eat? Who pissed off the red you or him?''

I said, ``Him. He is good at pissing people off.''

She said, ``God, were they ever vindictive. I'm so glad they're gone. I want them back again but not like that. If only they could be the noble creatures I know they are deep down. Like you. You're definitely a keeper Susan you're a sweetheart.'' She smiled and rubbed her fang necklace, snuggling it to her cheek.

I said, ``I already killed two people Jill, your friend and some random dude driving down a road. I don't think sweetheart applies.''

She said, ``All things are relative. The reds were really awful, you aren't. You are still a vampire Susan. A predator of humans. Apparently the definition of thrall with you has become a human who dedicates themselves to the proper feeding, care and protection of a vampire. What a brave new world it is. The slaves are the keepers of their master.''

We talked for a while, and came to the conclusion that I've established a telepathic link to Laura and am sharing her pleasure. Nonetheless at the time of feeding I still had to contend with the mania, until it settled into this sense of connectedness. We noticed a difference, my connection to Laura showed a dominant aspect. I want to protect her. She wants to please me. There is a bond of love between us. George said it was the natural thrall relationship of love restored. He said that it is based on the trust of a big strong wonderful vampire. He said me and Laura are going to have a beautiful and eternally loving relationship. That's George, he sure has a flair for the dramatic.

\parasep

After a few days had gone by, I have had a feed from all the thralls. We all feel interconnected and on top of the world. We have a telepathic bond of some sort. The soldiers are suspicious but can't seem to put their finger on it, or at least we haven't been confronted. 

%scene
We heard a hell of a racket close to camp, everybody leapt up.

A person raising a war cry, roaring of great beasts. Trees are crashing down and yells of pain. Someone outside, one of our team, is in a life and death battle with a great monster. Or perhaps many such monsters. They need help urgently.

Me and Craig were in the middle of the joy of feeding me. Needless to stay we stopped cold and were working furiously cleaning ourselves up. Jill and Laura helped. He was intoxicated and fell back to the sleep roll. We explained to the soldiers he hasn't felt well tonight. Sarg is worried we might need to stay camped an extra day, or drag a stretcher tomorrow.

Sarg said, ``Who's on sentry?''

I said, ``Jack. Oh God Jack.''

I heard gasps from my thralls behind me.

Craig said, ``He'll be fine. He is getting his senses back now.''

Everybody looked straight at Craig, then the thralls looked at me, and all the thralls raised eyebrows and smiled.

Jill said, ``It's working.''

Sarg said, ``What? What's working?''

Jill said, ``The increased fibre in my diet, I'm more regular now.''

Sarg said, ``Jesus fu--- Nevermind, you clowns stay here. Grab your gear men and get ready to engage.''

%sequel
It was getting quiet as soon as the soldier left. Soon we heard the call, ``OK people, it's safe to exit the tent. Conan the barbarian butchered some Jaguars.''

I said, ``Pardon?''

Me and the thralls left and headed to where the soldiers are. Jaguars? Plural? The hell? We seen quite the sight. It definately looked like a Frank Frazetta sketch. Jack took down six fricking jaguars with fist and kabar. His shirt and pants were torn and his massive bodybuilder physique shined with sweat. Blood trickled from his breast with what precious few injuries he had taken. I turned my eyes away from him, between the trickling blood and that outrageous body I was getting two or three different kinds of hungry.

Jack said, ``I was cool in the fight. I'm not berserking anymore. I was hungry for the battle, and fought with strength and skill, but my wits were about me. I'm me again. Thank God, and thank you Susan. Thank you so much.''

Sarg said, ``For what? What is he thanking you f---''

I said, ``---Sarg, all things considered do you \textit{really} want to know?''

Sarg said, ``No. Actually no, that'll do just fine.''

I said, ``Sarg, I'm moving up with you and your boys. Jaguars aside our own personal X-man Wolverine can take care of the thr--- er, civilians.''

Sarg said, ``Granted. It will be good working with you.''

%scene
We need to keep moving south quietly. The last thing we need is to have some hostile force come down on us due to some territorial bullshit. Soon after that thought a bullet hit a tree and we hit the dirt. We need to take care of this quickly. I found my telepathic link to the thralls was strong now, strong enough for open communication.

I said telepathically, \textit{``Hit the dirt people, we have inbound fire here.''}

Jack said, \textit{``Damn. Hear you loud and clear. Bloody amazing. Everybody Down!''}

Everybody answered in their minds tongue. I listen for activity; there is something on the road. The road is 500 yards out; I hear a vehicle. I said, ``Stay down Sarg, I'm gonna look.''

Sarg said, ``Aye.''

It's an APC, about a dozen soldiers around it. It looks like militia but they are probably raiders.

I said, ``Sarg, looks like a dozen. Irregular troops, trained civies. An APC also. If you don't have anything I have a 20mm rifle with incendiary rounds for the APC.''

Jack transmitted by thought, and said \textit{``I have movement due south of us Susan. Sounds like a rabbit but if there is something up there it could very well be hostiles down here also.''}

\textit{``I hear you Jack, I'll listen to see what it is.''}, I said to Jack.

``There is something in the bushes around our people Sarg, I might be able to find out what it is.''

Sarg said, ``How the hell do you know that? Never mind. Do your shit.''
%scene (continues)

I listen 150 yards away, where the thralls are, and I hear something like a housecat, moving silently. Or almost so. I squint my eyes in concentration and hear the breathing. A large animal. I hear a whisper, ``Alpha tango, target appears to be refugees. I see nothing of value except supplies.'' I don't hear the reply but in the bush the voice of the hostile soldier returns, ``Aye, order understood.''

I said to Sarg, ``They're checking us out, it sounds like raiders. They may not realize our people are distant from us. I believe they may think our people are the whole of our contingent when the troops on the road fired at us thinking we were the same group. This may work to our advantage if they don't know there are organized fellowship soldiers within reach. I say we start to move back slowly Sarg, I will try and gather more intel on the way.''

Sarg said, ``What the fuck are you using for intel woman? You got some cybernetic implants I don't know about? We are going to have a real come to Jesus conversation soon if you don't come clean. Agreed, we stealth south to our people.''

Another shot hit an inch from the soldier Jamar's head. 

I said, ``The force on the road is trying to keep us down. Likely it's in order to allow the team south of our people to make their strike.''

Sarg said, ``How can you you deduce that? Were you working intelligence?''

I said, ``Yeah actually. I was a journalist before infection so that became part of my duty. Intelligence, counter-intelligence, infiltration, special ops.''

He said, ``Ok. I'll run with it then. Wait, you're special ops? Do you mean you're a `Snake Eater?'''

I said, ``Um, yeah. I was on some international assignments.  I'm from the special forces personnel.''

He said, ``Fuck. Can you ease Joe Boo's troubles back there?''

I said, ``Aye Sarg, I'll get it done.''

I moved over that 150 yards in five seconds slithering through the underbrush, like a wild stallion on a straight stretch. I reached Joeboo snapping off his pistol to keep the enemy down, only to draw return fire. He is hit in his left shoulder so likely won't be able to wield the ma deuce but it's hard to say.

I said, ``What's out there?''

He jumped back and got a radio call. Over the radio Sarg said, ``Joeboo I'm sending Susan your way. Found out she's a snake eater give her a wide berth to work her craft out there.''

Joeboo said, ``Yeah. She's here now.''
%scene (continues)

Sarg said, ``What the f---, Jesus!''

It sounded like a hive of bees the bullets were flying so close. As I was there Joe Boo took two in the chest and went flat. I took one in the shoulder as I went down beside him, casting an oath as I went.

``Jobu how bad is it?'' his eyes were wide and glassy. I opened his fatigues and he was bleeding badly. Deadly badly. Damn me to hell it looked yummy. I had to look away. I was drooling like a dog again.

``I'll get you help Jamar, somehow I'll get Bones here.''

``Too weak\dots{} need to get that bullet out\dots{}, Susan please try. My medkit has surgical supplies\dots{}'' He nearly passed out, I shook him, ``Jamar stay with me, come on man stay with me!''

He said, ``\dots{}supplies. Dig and stitch. You remember training? Just try.''

I got his medkit. Why he had a field surgeons kit I may never know but his was complete. I got sanitizing wipes, scalpel, tweezers, and more. I tried, I didn't know how to stop the bleeding. Without stopping the bleeding I didn't know how to see to remove the bullet. I can't stitch him without removing the bullet. I still remember enough from my training to know Jamar is a dead man with this much bleeding even if I did get a patch to suck the chest wound. I can't stand the hunger anymore, I set aside the tools. I said, ``I'm sorry Jamar. I thought I could do this, I don't know how.''

Jamar looked at me with empty eyes as I leaned in to finish him off. I'm drawing his blood through his wound. I inadvertantly drew the bullet out from feeding. Scalpel be damned I extended a talon and removed the bullet with exacting precision. More precision than even the best surgeon could ever do. I had the steady reflexes of a vampire using an extension of her own body to do her work. I grabbed some stitching and pulled it through quick as a sewing machine using talons.

I noticed the areas I touched with my venom during feeding were not as inflamed as they were so I used the venom like an antiseptic as I closed up the wound. I used the shirt from his fatigues to wrap him and keep the venom soaked skin out of the sun and out of the danger of burning. It also worked as a anesthetic as well as soothing him and bringing him pleasure. I tried not to use too much in fear of addicting him.

I said, ``Jamar, I need to take down these motherfuckers so you lie like the dead until I get back. Don't forget to stay alive because if you don't I'll kill you OK?''
%scene (continues)

Jamar laughed, ``No promises I'll try.''

I said, ``There is no try---''

He said, ``only do or not do. OK I will.''

He looked at me as I left. Confusion maybe, no emotion at all; he just stared. As if he was trying to look inside me; as if he was trying to figure out what I truly am.

Then I listened. Facing to our groups rear I'm looking north. 150 yards out, a rustle in a bush 10 degrees left, then a short burst coming from 45 degrees right, and the sound of a mag being changed 30 degrees left. I hear a small group 300 yards distant, rustling, rattling and some but not much incoming fire. OK what's around here, pretty open to the north, and to the east the treeline opens to a field leading to the road. West there's a depression. I walk over to the depression and find it's a stream bed, not much stream though. I slip into the depression and listen north, a slight rustle, no inbound fire. One soldier it sounds like. I look and they're 300 yards out and hidden well. I caught the sight of their earring. I make my way quickly and quietly and take the soldier down quickly. using a talon in the lung they couldn't scream and fangs to the neck made it a deadly feeding. I hid the body well. Looking to the east I see the four behind a very large fallen tree. These people are well armed! If they move forward Sarg will never get back in time to save my thralls.

Using telepathy I said, \textit{``You guys have got to move out now! Grab what you can and get to the Sargeant! These people back here are formidable. They will plow through our rear guard and all of you right quick.''}

My thralls replied, \textit{``We're moving now Susan, we'll get forward to the Sergeant as fast as we can.''}

If I fire off my M16, with the tiny little 5.56 rounds I won't penetrate the tree. The 20mm would punch through the tree and take one down, at this range it would surgically punch through the tree, one soldier, and a hundred yards of trees down the line fire would have perfect little holes until the last one has a fiery explosion. That's no good. Besides I could drive them forward rather than back if I open fire from here. They know Jamar is the only one between them and their target and if taken on multiple fronts they will go for Jamar or flee. With him injured I doubt they will flee. I need to make them run or dig in. Scaring the bejesus out of them should do the trick. Facing a vicious unseen predator should do it if I can be terrifying enough. I've decided then, I must eat.

At the thought my vision changed. It darkened and became clearer, like a good pair of sunglasses. I was also seeing beyond normal vision, the colours and aspects of true vampire vision. I shook my head and closed my eyes for a moment and it was still the same. I had a small mirror I used for camouflage face paint. I looked at my eyes and they weren't human. They weren't the pure black of a red court vampire either they were a terrifying pure white. They seemed to glow in the light of the sun. I forced my eyes closed and did what I could to calm my hunger a little. I looked again and something swooshed towards the bridge of my nose and my human eyes returned. Well shit, I seem to have nictitating membranes. They pulled out to protect my vampiric eyes for a daylight hunt. I've never seen that in any red or any supernatural species I know of. I wonder if that's why Jamar looked at me funny. Things are going to get weird if we all get through this alive.
%scene (continues)

I  crouch down moving in silently, not even so much as a leaf or a twig moves. I hear them plainly but the words are drowned out by the thrill of the hunt. 

A movement in the leaves behind the log they're hiding behind and one peeks up. Like a shot I darted out of the bush I was hiding behind and without even touching the ground I hit him broadside and hurled ourselves silently into the brush east of them. The force of the impact had broken nearly every bone in his body. I immediately went for the kill while I listened intently to the remaining raiders behind that log.

``Where did Jim go? I was just talking to him. I swear by Christ I was looking right at him and he up and vanished like a fart in the wind..''

A second man said, ``The hell? What manner of sorcery is this? We have to get in and get the slaughter finished.''

The first man said, ``Don't forget to save two or three for the slavers we should be able to herd that many with us. The black court of vampires were looking for human components and hides for their own rituals we should check to see if there are any of these humans that could be harvested. It fetches a high price Tom, you know it's worth it even if it is disgusting.''

Holy Jesus fucking Christ they would do that to their own species? Oh my God these humans are all food, I'm taking them all down. First I need to keep them away from the camp. I stealthily drag the corpse south of where they are entrenched and separate the parts with surgical cuts from my talons and some tearing.

one of the men entrenched north of me said, ``What is that sound? It sounds like someone's eating chicken, tearing off the legs and stuff.''

Another one said, ``Dude, that ain't no chicken.''

At that I hurled the head still attached to the spine right behind that log. They were screaming like little girls. As they ran north to escape I took to the trees and easily caught up to them. I reached the lead man and with my talons truncated his torso from his legs and hurled his legs into the raider immediately behind. I had a pretty good idea what was coming next. I took the torso to the trees, an old thick tree that looked like it would stand up to an rpg easily. 

The raider shreaked, shouts of terror came from below and they opened fire in every direction. Clip after clip, m249, m16, ak47 handguns rpgs everything was getting emptied into empty air. When it stopped it looked like a forest fire had torn through. Smoke was everywhere and the trees were little more than jagged torn trunks to both sides of them. Only the oldest still stood, which included mine. They never shot into the trees, they never thought of it. They were too terrified to think of it.

In the meantime I fed. There wasn't much blood left in this cadaver and no life left in the blood that was left. It was disgusting I stopped drinking. I just don't seem to get anything from humans that arent still alive. I tried sucking the marrow from his bones and never was there a sweeter food. It was like the icing on the cake. I will need to remember that. The rest of the cadaver is like the rind of an orange or the shell of a peanut I don't like the taste of broken flesh.

One said, ``We got him. We had to have gotten him. Nothing could survive that.''

Another said, ``Ok, moving south. Let's get what we came here for and get the hell out of this place.''

I move in to the south sliding down a large tree, purring like a great cat. Just loud enough to hear.

One said, ``Dude what's that sound?''

Another said, ``Just a monkey or something, forget it, keep moving.''

``You're a fool, if a monkey survived the onslaught we just laid out for it pray mercy I never have occasion to see that monkey. Especially not one that purrs like a great cat.''

I lash some vines to the torso and suspending him upside down I skin the cadaver and strip it's organs. I weave together a jute like bag from the undergrowth to create a kind of fetish and lay the organs inside. After I move into the trees some distance away.

I hear a scream, a cry, and vomiting. I peer in their direction to see them circling around themselves back to back. each of them were checking their weapons one by one, reloading as necessary.

``Tom, what do we do? My God man what do we do? The devil himself has come to harvest our soul. I swear it's true. What else can survive the destruction we've dished out? He's come for payment he has, come to take us back to hell with him.''

``Shutup idiot. There ain't no devil this is just some earthbound creature. If we can catch it we can kill it.''

I see them moving together tightly packed. If I determined some earthly creature was the enemy I would do the same. They are getting too close to Jobu I need to get back to him to figure out a way to get him out and in a safe place.

One of the raiders said, ``Tom, you and I both know it ain't no monkey. No earthbound creature. It ain't the devil neither man. What sits in between these two ideas hmm? What is the most sensible idea?''

Tom said, ``A goddamn supernatural, of course. a vamp or demon. No a vamp don't sound like that, can't survive what we dished out. Willy you're the warlock what is this?''

OOOOoooo shit!  There's a warlock with them! That is the one thing that could be a worry to me. Jars and other supernatural ordinance can do me in. Move you're ass Susan get to Jobu if you take on a warlock you might not live to help him.

I stop bothering to listen to them and focus on getting to Jobu. He's in bad shape.

``Are you able to move Jamar?''

``Not a chance Susan, I'm sorry. The shock is wearing off and I can't move even so much as a finger without crumpling up with pain. I'm done. You're hurt Susan, you're covered in blood.''

``Not my blood.''

``All the screaming out there, they were utterly terrified. You're covered in their blood\dots{}''

Does he know? I hope not. If he thinks I'm a vamp then I'm an instant enemy.

``\dots{}You're one of our elite aren't you? How are you so good without infection? Man, you're the real thing. A real elite soldier. Special forces material.''

Just then the enemy soldiers yell, ``Whatever you are, what manner of supernatural creature know now that we have supernatural ordinance and we're rearmed. You won't win. You are going to suffer for what you did to our people.''

Fear washed over me. I'm in real danger of death or banishment now. They don't even know what I am yet they are breaking out the crafts of their warlock. It's their only hope if they come across a supernatural adversary. When I was fellowship we would wait to see the whites of their eyes before we rearmed with supernatural ammo, or antivamp, whatever you want to call it. I have them really scared.

``Susan their coming this way. Leave me, get to safety.''

``I do not leave a fellow soldier.''

``I saw the fear in your eye just then, you aren't exactly human are you?''

``\dots{} Well\dots{} not exactly no.''

``Then what\dots{} are you?''

``I don't know Jamar, I'm learning more everyday. I have red court characteristics but---''

I extend my talons

``There are other things about me that aren't the same.''

``So you weren't in any real danger before, are you now?''

``I've been jarred before Jamar.''

``You are in danger, grave danger. Why are you fighting for us, what are we to you and you're species?''

``I am a fellowship soldier Jamar, same as before. I won't leave a man down. I won't turn my back on my mission. Sarge sent me to do a job and I'll see it done or die trying. It is a point of honour and by honour I abide.''

I felt a pressure in my back for a moment. I felt like I grew a foot taller. I think I'm learning what it may take to transform to that dark angel true form. It's not a matter of trying but of being. I have to be the person that it represents. First piece of the puzzle is honour.

A bullet hit me in the side and I screeched. Deathstone ammunition. Mordite. A stream of disintegration follow the trajectory. It's outsider technology harnessed by warlock spells. It is, anti-matter. The bullet missed anything vital but that wound is not going to heal any way but naturally and slowly.

Jamar said, ``Get out now Susan! Run!''

I run toward them moving to the west side. Jamar said, ``No! Susan get out it's suicide!'' I make a rustle here and there as I go to draw fire away from Jamar. Disintegration followed me as the deathstone bullets flew. I dove and rolled through the ditch I was in some time ago. I overtook one who laid wait in the ditch and pierced his ribcage with my talons hard enough to exit the other side. He couldn't scream I was on him and drank him dry. Screw the games I left him to lie. I grabbed his deathstone grenade launcher and moved north. Leaping out of the ditch they opened fire. They must have expended some personal enhancement technologies. Technomage, not a warlock. They have a frickin technomage! They are able to bind mystical spells and items to modern technology. Weapons especially. They have the covetted ability to merge outsider materials to modern weapons. I thought they just had one shot and jars. I was wrong. The forest behind me disintegrated and became the landscape of mars.

I fired my launcher back at the raiders and saw a purple flash. A wave of cold lashed back at me freezing the trees and vegitation around me. Looking there appeared a lifeless pocket of twenty by twenty martian landscape. Two of the raiders didn't have much left and three were left there with a muddy appearance. Counter mordite technology. Their budies didn't have it and weren't so lucky. I feel bad for the devil the mordite probably disintegrated their souls as well. It is the most dangerous substance in our universe, in all creation, because it comes from the chaos beyond our universe. The ``outside,'' the outer chaos.

I throw a rock to hit one and it disintegrates. It must be attuned to them somehow, it is acting like mordite in protecting them. I need a warlock to counter this. I'm grabbing Jamar and running, I hope I don't hurt him too bad doing that.

Jamar had some bouncing betties, I'm not sure if it will help but I plant them then run. I'm trying hard not to hurt him so it is going to take a few minutes to get south. We heard a mine blow but I was pretty sure that wouldn't do much against mordite technology. Sure enough a few minutes later I heard another blast as they hit another mine. We are getting fairly distant now and my friends should now be up with the sargeant. 

When we got up to the Sargeant to find his battle was successful. He blew the APC with a recoilless rifle and it looks like he took down a dozen soldiers as they came in from the open area around the road. Nobody was injured and here we come limping in like we were at Io Jima.

``Sarg shit is coming from the south, got them outsider tech down there,'' I said.

``Jesus christ Susan these people didn't, why would they?''

Bones said, ``Yeah they did Sarg, this one has a ton in his ruck.''

Jamar said, ``Same here Sarg. They just would waste deployment on a conventional enemy. Mostly jars here it wouldn't work on humans anyway.''

Sarg said, ``bloody hell, we gotta get outtqa here fast..''

I said, ``I can hold them off Sarg, I might not be able to finish them but I can at least slow them down---''

Sarg said, ``Absolutely not. We're a team, we all live or we all die.''

Laura said, ``Get me to that APC. I'll get it running and we'll be gone.''

Sarg said, ``Nobody could get that thing going I plugged it with a Carl G.''

Laura said, ``I ain't just nobody, trust me, it will run. I'll make it run.''

``Are you willing to bet your life on it; to bet our lives on it?''

``I would Sargeant, damn right I would.''

``Well we don't have a hell of a lot of choice here. I haven't known you long Laura but either we go or we die. How are we getting there  without getting killed in the open?''

Edgar the warlock said, ``I'll lay down a spread of decoys Sarg, it will redirect them away from us as we run.''

Sarg said, ``Do it now. Everyone grab what you need quickly. We can go encumbered, grab only what you need and we run fast. Spook do your work I'll pack shit for you to grab as you're running.''

All of us are scampering doing what needs to be done as if we were mice being chased by cats. Spook was chanting burning and dancing, quickly burning embers scattering into the forest. A terrible cold surrounded him, black magic, what is he doing?

Sarg said, ``Spook, do we need to go? I don't want to leave you it's suicidal for any of us to stay.''

Spook told Sarg to hold five, then he said, ``right, all is set Sarg let's move.''

Sarg said, ``You heard the spook, everyone move full speed to the APC, gather to the far side 20 meters north where there is a drainage ditch. We stay there, if there is inbound fire we'll take it away from the APC if we can. Laura we will try to draw fire from you but God help you.''

Laura said, ``God be damned, I'll get it done.''


