%scene continues
\lettrine[lines=2,lraise=0]{W}e heard screams from the wood. Spook is acting really odd, he seems, narcissistic somehow. I looked into the wood and saw a horror show. They are laughing; they are laughing and tearing into each other; they are disintegrating each other; they are laughing and eating each other; they are enjoyed the taste of each others flesh; they relished the sensation of being consumed by each other; they tore each other apart piece by piece, organ by organ, flesh for flesh, disembowelling, consuming blood and drowning in absolute ecstacy from it all. Death came slow to them and yet they embraced death like a long lost love. That's what the cold was, Spook wasn't casting a distraction he cast some kind of very dark spell.

It took about an hour, far longer than Laura thought but the raiders were cannibalizing each other. They paid no interest in us. The forest became more and more quiet as they died. Spook's eyes became more and more empty as the effect of the black magic he cast took hold. The fellowship warlocks that were infected could cast black magic with impunity but now that they are human every use of black magic causes ever greater corruption and insanity. Human spellcasters have been this way and the white court of wizards have known this. They have wardens whose duty it is to decapitate anyone who even so much as makes a single act of black magic. We  were overlooked simply because we were their allies in the war against red court vampires.  What about now though?

I make my way to Spook. He doesn't make any sense, he is maniacal and quite psychotic. It isn't him who is speaking now, he is trapped inside himself.

%sequel. emotion

%%%


%sequel, review
I said to Sarg, ``Have you noticed Spook isn't quite right?''

Sarg said, ``I've noticed. I don't know what to think except he needs some sleep. It's been a hell of a haul for all of us.'' Then he spoke out to everyone to board the APC. I took spook aside for a brief feeding in order to try to make a psychic bond with him.

I said telepathically to me people, \textit{``Is everyone OK? We haven't had long to talk.''}

Jill said, \textit{I'm OK. Tired as hell. I'll be glad to get south to safety and rest.''}

The others, in turn, said essentially the same. They hadn't felt any connections to the kills I made. I guess it takes consistency. Maybe it takes willingness. 

I'm scared for spook. He might get lost inside himself and never come back. I'm his only hope. If I can't come through for him whether it's the wardens or not we are going to need to take off his head. There is no other way for his own safety and those of others who might be harmed or killed by him in his insanity.

%sequel-thought
I moved in towards Jill to talk a while. I said, ``I'm sorry Jill I failed you guys. I tried so hard. I had them scared it should have been so easy to take them down. Jamar got hurt and I don't know if Spook will ever be the same. He is falling to the corruption of black magic and I don't know if I can save him''

``Susan you didn't know they had paranormal ordinance. How could you? There's nothing you could have done. What happened to Spook would have happened eventually. But it happened now. And you're here. Guess what? I didn't feel the connection to the other enemies but Susan I felt spook. Just a little. I think what you believe is a failure may be hope for Spook. Maybe you can heal him, maybe even galvanize him from the corruption like he was during infection. You're here now. What if he fell sick from his magic later when you weren't here? I believe in you Susan, you can save him.''

``It doesn't make it right Jill there must have been something more I could have done, you guys took down a dozen of the bastards I couldn't take down half a dozen, and I'm easily ten times the strength and speed of any man.''

``Yeah but you're not counting the women.''

I laughed and said, ``OK. OK girl. I hear ya.''

``It's not about the speed, or the strength Susan. Gotta outsmart them.''

``They brought out paranormal ordinance, if I tried to drive them off rather than kill them it might not have happened. Spook might have been OK. He's falling into dark magic corruption trying to save us. It's my fault. I caused it.''

``Bullshit. Get a hold of yourself Susan. Sarg send Jamar south to guard us and he was wounded all the same. Jamar didn't know enemies were coming from the south. He didn't want to get injured anymore than you wanted them to pull out the mordite and come at us. I've lost people in my life too Susan, I could blame myself and get stuck in woulda, coulda, shoulda but that doesn't help anybody. You faced mordite for us Susan, you faced death for our sake. You didn't run away or avoid the danger. To show such courage what more could anyone ask of you? Hindsight is twenty twenty and we learn by our mistakes. You didn't fail us you stood and fought through it all.''

Something took a hold on me. It was like I saw Jill as who she really was for the first time. It wasnt about telepathy, it was deeper than that. She is just such a beautiful soul. She accepts me for who I am; she accepts me for what I am. She's there for me in everything, feeding me, consoling me. I raised my hands to her cheeks and smiled. Then I kissed her; it was a real kiss, a passionate kiss. I took her into my arms and held her tight; held her like there was no tomorrow. I kissed her again and released her, then held her hands intimately. I released no venom, the feelings I was developing displaced my hunger. She was becoming to me something far different than a thrall, and it left me confused.

She said, ``Um, Susan I really don't swing that way. You're my vampire and all and I show you great love but I can't be your mate. At the moment I wish I could but I don't see how.''

I laughed and said, ``Where have I heard that before? I guess the tables have turned hmm?''

She was confused a moment then laughed. Then she said, ``of course, when we first met I tried to draw you close and tempt you by spooning you. You told me then you don't swing that way. If that's right why make a move on me?''

``It's about the feelings I've come to have for you. Maybe it's not love; maybe it's not a crush. Maybe it's a squish. Whatever it is I want to follow how I feel.''

``Well let me think about it. We'll talk at a later time about it. I'm just not ready yet, I'm confused. Let me be your thrall at least for now. I need the healing properties of your venom Susan and if changing our relationship takes that away then we can't. When you made you're move, God help me, you didn't release venom. Need I say that scares the hell out of me.''

I felt so embarrased. I said to Jill, ``I understand. I don't think my feelings will change but I'll let you have as much time as you need.''

She said, ``Thanks. For what it's worth I love you too. Don't feel embarrased. I just need to search my feelings to know what it means to me; I need to understand the consequences of any decision I make.''

She was absolutely right. I made mistakes but I acted with a lionheart. I didn't hide or run away I moved in and did what I felt was right. We had to flee, but facing mordite weapons there was nothing else anyone could have done. The gods themselves would flee mordite.

%review
We did OK. Jamar is injured but alive. We are all alive. Spook isn't well, his spirit is corrupted. I need to bring him healing somehow. We had to leave behind a lot of our gear when we fled. We now have an APC though.

%analysis
We aren't going to be able to stay out here very long without our rations. We have some on our person but we need to find somewhere to reprovision very soon. This APC has got to keep running, to get us south before we starve. What if our main camp has fallen? What if our people had to relocate? Oh God I hope not, I don't know what we would do.

%planning
Right now I think the most important thing for me to do would be to help Jamar, I can talk to Bones to see what I can do. Spook needs me, Bones can't help him. Noone but me can help him and even then I can't be sure I will be able to rescue him from the darkness that is consuming him. I will try and convince Sarg to let Spook stay with me and my thralls so I can feed my way to a deeper connection with him.

%decision
I'll talk to Sarg tonight to take Spook in with my people. The fellowship soldiers have enough to worry about tactically without worrying about spook so it shouldn't be a problem. I think he is in the most need right now Bones can work with Jamar but it is far beyond his ability to treat Spook in any way.

It's up to me, I'm the only one with supernatural ability and the only one then that can cure a supernatural ailment. I know my venom and bite can heal, I need to heal him. I need to find a way to spin this to prevent the soldiers from suspecting me of being anything but human for my own safety and maybe even the safety of my thralls. They wouldn't know if they are infected and with their loyalty to me the odds are they will be executed along with me as traitors to the human species.

%action
I go to Sarg, ``I want to take spook into camp with us Sarg, with our people. We have always camped alone together with out own gear and we still need that privacy at night. You have enough tactically to deal with and Spook is a burden to your people in his current state. We can take care of him.''

``Granted. You all can take him but we are going to have to take his head soon, he is going to be a danger to himself and us too. I have a lot greater tolerance than the white council regarding the corruption of black magic but then again warlocks can be life and death for us out here.''

``I think the fellowship as a whole feels that way. Personally I am even more tolerant than before since most of our warlocks don't have the protection offered by the infection.''

``Yeah. I don't know what we are going to do. Assuming the fellowship is going to continue even accepting the warlock refugees from other places in the world may just invite greater danger for the fellowship and others.''

``There are a lot of decisions to be made in the near future. I guess we just continue one day at a time.''

``Yeah. One day at a time. Damn right.''

So I talked to Bones about Jobu.

I said, ``Do you need any help Bones? I'm mostly involved with my own people and we don't have the same military responsibility as you and the other fellowship people.''

``I'm good looking after him at night. We all need sleep though so if you want to have one of your people watch over him so everyone can get better sleep. As it is having the one sentry rotation at night works out well and I would like us all to stick with that.''

``OK, one of us will rotate at night to watch him. How is he anyway?''

``One of his wounds has become infected. Badly infected. He isn't in immediate danger right now but he could get a lot worse very soon. I have him on antibiotics and I'm hoping it will work to cure the infection soon.''

``A personal question, do you have any experience in psychology at all?''

``I was in doctors without borders when I got infected, took remedial training to support the people out here. So yeah. You got issues? Need to seek help?''

``Yeah doc a labotomy and a straightjacket oughtta do me. It's like a. Err\dots{} Kaffkaff, sex thing\dots{}''

``OooOOOoo, having female issues?''

``Not exactly no.''

I go on to explain what is happening with me and my feelings for Jill and how I like guys and not girls so I'm confused.

``Jill you're just bi-romantic that's all.''

``I am not gay doc I already told you---''

``No no not bi-sexual, bi-romantic.''

``That's a thing?''

``Yes that's a thing. Maybe it's the changes in your life since your infection was cured or maybe the current war or the possibility of resuming your pre-infected life. I think something triggered it to surface. It may be fluidity and your romantic orientation changed. Regardless romantic orientation is who you get feelings for, seek companionship and intimacy with and maybe even fall in love with. Just not necessarily having sexual attraction for. It's just how we're wired.''

``Oh I get it. It doesn't make things any easier, it might even make things harder, but it helps knowing.''

``Anytime Susan.''

%action
That night I took a feeding from Spook to try to heal him like I heal my thralls. Then we all went to sleep for the night. As I slept I had a vision of Spook. I seen a creature like an octopus attacking him in the darkness. I could see his psyche batting off tentacles. Every once in a while one would pierce his body and he would scream and pull it out. Sometimes another would pierce him while he struggled with the first. Then sometimes he couldn't get to one in time and it sank it's barbed tentacle deep inside him and he was powerless to pull it out. Slowly one after another pierced him deeply and the octopus drew in closer slithering the tentacles in deeper and deeper. Parts of his psyche were killed little by little by the tentacles invading his mind. The tentacles then slowly took over his mind creating anger, jealousy, mania and senseless behaviour. He can't control the parts of him that are dead or dying, under the control of the monster. I drew myself closer and the octopus creature, being somewhat humanoid in appearance, bowed and began to back away and leave him. It meant the creature was tearing out the barbed tentacles. Spook was shrieking at the top of his lungs as his psyche was being ripped apart. At that moment I awoke shaking. Jill and the other thralls were also shaking as well as vomiting from the vision we shared telepathically. We ran to look at Spook and his eyes were glassy; his mouth was foaming. His hands were clawing at his chest and tore open the skin. We heard him moan in an empty zombie like way. He bit a piece of flesh off his arm and we leapt at him and restrained him with a rope. He was chewing peacefully on the chunk of flesh he tore off himself. We held a piece of gauze to his arm to stop the bleeding and Craig ran to wake Bones to patch him up.

``Susan we can't leave him to suffer any more. He has gotten far worse tonight and it's clear he is a danger to himself now. I'm going to talk to Sarg in the morning and recommend to him that the time has come to take his head. It was commendable of you to try helping him but there is no cure for the madness that comes from the practise of black magic.''

``I just need more time Bones, we can help him. I only just started to reach him tonight, please don't do this.''

``I'm sorry Susan but my medical opinion stands. He's gone, we need to execute him before he causes harm.''

I need to do something to save him, Bones isn't going to give Spook a chance to recover, no chance for me to heal him. I need to do something to stop this. I know Sarg won't have a choice but to order the execution now that Spook is harming himself.

I nibbled on Spook for those last few hours before sunrise, trying with faint hope to bring him back before we break camp. The soldiers are camped outside under one man tents we found in the APC. Me, Spook, and the thralls are inside. Once we are underway there is no way I can nibble on Spook without getting caught. Oh please Spook get better. Please get better before it's too late.

\parasep



That night at the campfire the fellowship team carried along a solar radio. ``Who wants to live forever'' started playing and Injun took out a harmonica and played along to the tune. It really effected me. I will live forever. I will see people be born; I will see people die; I will see the cycle then start anew. I will see empires rise; then I will see them fall, rulers will rise and then they will be thrown down again and again throughout my existence. I will not know a friend who I will not lose; I will not know a lover who will not be torn from my arms. Even the very earth itself will change before my eyes, seas will rise and mountains will fall. Yet still will I be here; yet still will I walk this accursed realm. Long will I long for a good death, to see my parents who bore me and the friends and family long passed before but such mercy will never come. Never will I know peace; never will I find real belonging in the world again; there will only be that damnable cycle of feeding; there will be that damnable curse, neverending. Is this all for having killed Martin? So many men have killed other men and yet death comes to the good and the evil why not me? Oh why not me.

Who wants to live forever. Not me. My head hung low and tears started to run down my cheeks. I press my eyes closed and shake my head. I can feel the familiar ecstasy, the manic release as the flesh mask falls from my fingers and my talons begin to emerge appearing retracted and like the claws of a red court vampire. I look down to them as my tears flowed, flexed them and looked on the physical proof of my nightmare; the physical proof of my deathless state.

%scene secondary goal
A revelation of this proportion is difficult but I need to keep this from becoming a deadly revelation. I need to control myself, the last thing I need is for a greater change to come over me now.

I started to come back to reality and realized I just revealed myself. Everyone knows I'm a vampire now. I should be afraid; I should run but I don't care. I just don't care anymore. Let them take my head. The fellowship would kill it's own when they turned and only jar them as a final resort. It is the only mercy we would allow for our fellow soldiers who fully turned. The mercy of being destroyed.

I slowly looked up. My thralls were looking at the fellowship soldiers with eyes wide enough they risked falling out. Jill began stroking her fang necklace and wringing her hands. Jamar looked over at Sarg quickly and spoke in a soft voice, ``Sarg, no worries ok, she's been righteous. She ain't got no claws on her but talons she ain't no red Sarg. She ain't no red---'' Sarg said, ``The hell she isn't. I know a red when I see one and she's been decieving us this whole time. The reds ain't dead this has been their plan all along. They went somewhere and this one got left out to die, and die she will. We need to find their strategy in this Jamar, she obviously took out out warlock because he is the only one who is any threat to her. Bones, check the supernatural ordinance. Are our jars accounted for?'' 

Bones checked and said, ``Aye Sarg, everything is fully accounted for.'' 

Jamar grabbed Sarg with both hands and lightly shook him, then said, ``Don't you see Sarg? She ain't the enemy here. Something happened to her but she didn't turn red. She's something else and she ain't corrupted. She saved my life man and risked her own against the raiders despite supernatural ordinance. She's righteous man don't ask it!''

Sarg said, ``Injun, get the katana. Jamar you son of a bitch you're gonna do her else I'll take you as enthralled and cut you down as well.'' 

I remained still while they argued, then assumed a kneeling position slowly in front of Sarg. I intended to show him the obedience he deserves as a sargeant of the fellowship and place myself willingly before the blade. Besides I do still wish this to be over. I don't wish to be incarcerated on this earth indefinately, I want to go to the sleep of death and rise to my heavenly destination where I could meet the family I never knew and the soldiers that had fought and fallen by my side. I grieve for them all so much; their death has caused wounds on me that have never healed, nor will they ever fully heal.

``Sarg, look. She kneels before the blade. Still she's righteous to her vows, she's one of us Sarg she's\dots uncorrupted.'' said Jamar. 

``It's a trick! Injun check the perimeter, Jamar back up and cover her with your rifle; ready a jar in case you need it. Bones cover Injun when we find the bastards you and me are gonna open up on them. Ready the jars.'' 

Bones put a hand on his forehead and dipped his head slightly. Bones said, ``Jesus Christ, Sarg this is ludicrous, think about what you are doing. The way of our life is one of paranoia but we both know fellowship divided will fall. She hasn't in any way shown herself to be corrupted. This is madness, there is no contingent in this bush.'' 

Sarg said, ``You're the one that is mad, the only good red is a dead red.''

``Perimeter is clear Sarg.'' said Injun. 

%scene disaster
``Bullshit, fine there is some other scheme. Well I won't be swindled by this bitch whatever is up she has a purpose here and that purpose ends here and now. Proceed with the execution Jamar, time to end this.'' said Sarg.










