\lettrine[lines=2,lraise=0]{Q}\space uietly in the still of the night we circle each other again, this time in human form.

%scene
I said, ``Why do you stalk me? What am I to you?''

He said, ``You are my sister though you do not know me.''

I said, ``I have no family. I have no brother. A fine brother you would be to do battle with your supposed sister anyway.''

He said, ``Hah, a d\ae mon is always ready for battle my sister. As above so below, existance is a struggle, the clash of swords, the victory and the defeat. The way of war is the way of life and of our existence for we are existence.''

He stood at ease and raised his hands palm up.

He said, ``Will you stand down my sister and hear my wisdom?''

I stood easy and slowly opened my palms, my kabar resting easily in my open palm. Slowly I returned my blade to my sheath and we stood facing each other. I'm still very much on edge.

I said, ``Speak.''

He said, ``I am Leviathan. I am d\ae mon. I am not the Leviathan of evil legend, I am not that same creature. Me and my kind bear accursed names but we are spirits replete with wisdom. I am the d\ae mon of water. In this I am no god of water I am water. I am the very element made manifest. As long as creation has been and as long as it will be so also will there be the d\ae monic for we are creation. 

You are the reason men fear the dark;you are the reason they fear the night. The events of \chichenitza* were a quickening. A catalyst as it were, to bring you forth in power. Ever since you have been you were the same, only now you are blooming into your true self. Fear not yourself.

I needed to speak to your learned elder aspect, now accessible to me since \chichenitza*, to do so I needed to weaken you enough to cause her to come forth so I battled with you. You are beloved to me Susan, and I am at peace with you now.''

I said, ``You're long winded dude. So basically you say I'll be fine, and I got some juice. So what if I fuck up and like blow the world up?''

He said, ``Just don't.''

I said, ``That inspires confidence.''

%microsequel
I decided to nickname him Levi. It helps me differentiate him from the biblical reference and it's just easier all around. I guess I got more juice than an east German female powerlifter. Not that I know what I'm doing yet. Give a kid some nitro glycerin and tell them not to blow themselves up. Good idea. Fucking \chichenitza*.

\parasep
%scene
In the afternoon of the next day we arrive at camp. It became apparent that the tents were full of victims addicted to venom. The bad ones. Just like any bad drug some people are more susceptable to addictions than others. Some life-threatening in fact if the drug were removed too quickly. These are the bad cases. Many are restrained. Many show signs of blown voice boxes from screaming. Most are cadaverous from not eating and limited intravenous because they thrash too much to keep the iv in. Most are restrained, most show self-mutilation like gouging out their own eyes or peeling the skin from their own face and body. A man in the distance is being worked on after the stress caused him to have a heart attack. He looked like he was in his mid 20s. They are heavily addicted and suffered horribly. Many have given up hope and died by their own hand so that they need not suffer anymore. A majority are afflicted with some manner of madness often mocking the nurses saying the reds are the masters and will return soon to exact vengeance great will it be to serve at their feet great will it be to die by their hand. There is no cure, they have faint hope of living long before the withdrawl kills them, a month on average or so I've seen before. 

It's like hell on earth. Fucking red court vampires.

It took no time at all for the sentries to intercept us. we identified ourselves with an old sign countersign. So we were just detained rather than stripped of belongings and thrown in the clink. I give thanks for small wonders. We met the general who said, ``either you're a useful asset and you stay or youre useless and you go. We dont have the resources to keep any nonessential personnel here. So choose.'' Needless to say we found ourselves being useful. Me and Spook took the first assignment as working with the warlocks in their research tent because we told the general about our recent adventure. I mostly organized tomes and scrolls while Spook worked doing actual research.

\parasep

A familiar face came running up to me while I was on sentry. Geoffrey, from the house of Windsor in the UK. Anotherwards a member of the royal family.

When the reds were still around some British representatives were present here. In one of the fellowship raids I freed them when they were held hostage. It was in our best interest to clue in the monarchy and get their support in our resistance. So we took the risk to free them and send them back with some fangs procured from dying reds. Needless to say they clued in and we had support that was desperately needed.

He said, ``Lady Rodriguez, it has been a long time. I see things are changed but not better here. It is a travesty the people of central and south America are so relentlessly afflicted. Pray God should have mercy on these suffering souls.''

Oh yeah. I was knighted for my courage by the queen in a fairly secret manner. It doesn't change anything in my day to day life so I often forget the fact.

I said, ``Wassup Geoffrey?''

He said, ``I'm acting as an attache to the queen. She wants to know what is happening down here. Her wizards reported a massive release of black magic some time ago. I'm told the reds were consumed in the release and the fellowship here reported a truly historic event at \chichenitza*. Needless to say it was assumed you were burnt to dust. I'm glad you are well but what happened to you?''

I said, ``I woke up with the world's worst hangover.''

He said, ``ok. You could just say you don't know. There's no reason to always drip sarcasm you know.''

I grunted.

He said, ``Well, anyway. I'm looking to take the first flight out to report back are you leaving north I assume? Your journalistic ways are less useful down here than educating the northerners on this tragedy.''

I said, ``Exactly my thought. I'll need to figure out how to get noticed but I need to drum up support from up north somehow.''

We met the base commander, a general Kraghstrom. He advised me my journalistic background makes me first pick for a mission north. An outbreak of zombies seems to be underway and it carries the risk of apocalypse if it is viral based. When I return he will see that I am on the next flight north to undertake whatever means necessary to get support to us down here.

%sequel - review
That night I walked among the tents and considered these latest events. I laid plans to achieve my goals.

This could move me closer to having enough clout to be heard up north if I can report something credible. Nobody north of Mexico will believe raw stories of demons and zombies. Something believable is what I need. That will carry my message to the eyes of those whose support we need most.

I can get closer to my daughter. I am always her mom in my heart and I need to be close to her but am I still her mom in body? I've undergone a tremendous physical change that goes far beyond what I could ever understand. Oh little Maggie, your mother is dead, long live your mother.

\parasep

Ten days of cleaning; of walking sentry; of guarding the sick.

One night I was on patrol after sunset in the camp. As I wandered by an area dedicated to research many researchers are on edge, and competing with each other to find a cure. Only one of these researchers was having undeniable success yet her continued research was threatened.

I heard loud angry voices coming from her research tent. 

``We can save them dammit, general I just need more venom to complete my research my test subjects have shown improvement'', said the woman.

``Are you telling me you experimented on multiple patients? You know I only authorized you to work on one patient'', said the general.

``How am I supposed to make progress with a cure with a single test subject? When I seen it help one of them how could I bear to keep it from the others? Look at the suffering of these souls, surely we will be held to judgement on what we do here while they live'', said the woman.

The woman waved her hand over the multitude of patient tents. 

``You're right Jane, we will be judged. Surely we will also be judged if our pride leads us to harm these people in spite of such suffering. I won't cause it and I won't allow you to cause it. you have the one man and only one man and I won't jeopardize a mission to obtain more venom from old fellowship camps. it is only good to ease some people back. Very few. This work of yours is fruitless. Expect me to pull you from this self-glorifying project soon and put you into another project.''

``No you will not do that, I won't let you. This will work I just need more venom, I can synthesize more if I can isolate it's makeup. I am so close to creating a powerful anti-toxin that reverses the craving and lets the body heal. it works. The recipient isn't showing the signs like the others if I complete my work I will have created a praise Jesus cure for these people. You need to understand this is the only hope for these people. This needs to happen. Get me the goddamned venom'', said Jane.

``Tell you what. If you pack up your belongings and report to Colonel Bennett by Friday I won't demote you to sentry duty. Besides if you spit in a beaker you will find you have quite enough venom already.'', said the general.

``Fuck you Joe. You're damned right I have venom for you, this is fucking bullshit. You're betraying me, you gave me your word I could research and test until I found a cure. What's changed?'', said Jane.

``Venom. You need venom for this work and very little was kept by the fellowship over the years. Even if you only need it until you are able to fabricate the necessary components how do you know we are going to find any more out there at all? This is likely a dead end and without venom it is most assurredly a dead end. The Colonel has a good chance and could use the help. Most importantly the Colonel doesn't need any goddamned venom for his proposed cure. It's realistic.'', said Joe.

At that Joe walked away, and Jane took an old pipe and smashed a nearby table into pieces. Her face still red she walks back to her desk to read a research report but drops it. She violently sweeps everything off her desk and combs her fingers through her hair.

Curious I stealthily enter the tent. she isn't moving. Looking around I see some relevant material on her research. I can't understand medical research myself but Laura might. I'll get her to look at it.

As I'm leaving Jane turns around, ``Who the hell are you?''

``Um. I'm Susan. I overheard that conversation you had with the general---'', I said.

``What business do you have eavesdropping on a private conversation?'', she said.

``Lady that conversation was anything but private. Is muffin getting a bit tired? Do you need to go down for your afternoon nap? Momma ever tell you to use your indoor voice asshat?'', I said.

She was so red with rage she was blind. I took the opportunity to snatch a handful of paperwork, ducking just in time to evade the fist that sailed quickly toward my jaw.

I backed away, and apologized. I slipped out of the tent and made my way back for Laura to examine the journals.

%sequel - analysis
``This is quite advanced Susan. She may in fact have done it but I don't think it's possible to synthesize venom. Her work in that area is quite far from a working solution. She is going to need venom.'' said Laura.

I said, ``Would any of this help you guys?'' I said.

``No. Maybe synthesized venom but that is the weak area in her research like I said. We don't need freedom from addiction as you well know we need the healing effects of venom.'' she said.

I said, ``I needed to ask. I just can't be comfortable with my friends being so dependant on me.''

She said, ``I agree Susan. We've been together long enough I don't feel I need to butter you up anymore. On another level though all of us love you dearly. You are the kindest and most caring vamp we've ever seen.''

I said, ``Then there's Jill---''

She said, ``She loves you more than the air she breathes. She adored her evil vampire masters as undeserving as they were. Now she finds a lover in a really good and decent vampire. Heaven would have nothing better to offer that woman. Please don't start to glitter.''

I said, ``If I do you have my permission to stake me.''

I shuddered.

She said, ``If you don't mind me asking, I never thought you played for the other team?''

I said, ``Subtle. No I never found I want any woman in any way like that I just don't want that. It's an intense romantic involvement. I'm not sure how else to explain it.''

She said, ``That'll do. Just wondering.''

So I knew as much as any other member of the fellowship we really didn't keep a stockpile of venom. There just wasn't any need to do so. Jane is fucked. So are those poor victims. Laura said flat out Jane is not near enough to be able to synthesize venom if she ever will.

%sequel - planning
What are her options then? I could risk providing my own venom somehow but I need to go north to get help and I need to ensure my thralls are provided for as well although they are no burden to me realistically. Providing like that puts me and my thralls in danger too, we don't really know these people. Raiding to obtain pre \chichenitza* venom stocks is unrealistic. She will need to produce venom somehow.

%sequel - decision
I shuddered. I better find out if she is truly sincere about her willingness to do anything to help those people because unless I can think of another answer there's no way back from the road I would have her travel.

%sequel - statement of action
Something new is about to come into this world with the power to either save it or to destroy it. May the world forgive me if I have made the wrong choice, but my choice is made and I am going to see it through.


























