
\begin{quote}
	``Martin,” I said, my voice low and very quiet. “Did you tell them about Maggie?”
	He closed his eyes, but his voice was steady. “Yes.”
\end{quote}

%using past tense
%scene goal
\lettrine[lines=2,lraise=0]{A}t that moment I was beyond saving. I've been on the edge ever since my daughter Maggie went missing, and now here we are at the altar of \chichenitza surrounded by vampires and their many minions determined to sacrifice my baby girl on the altar. I need to save her. 
%scene conflict
My emotions are on high, I've been far too close to losing it and now dumbass Martin tells me he led my only daughter to the slaughter. I couldn't see through my rage, I was so far beyond control I don't even think an immortal could have stopped me. My vampiric part foreseen it's victory over my will and poured it's power into me and drove me quickly and irreversibly to my kill. It shackled me to it's purpose and terror came from my soul to intermix with the rage. My humanity foreseen it's own death but was unable to pull back, the vampire in me had stolen control to ensure it takes the life it needs to fully emerge. Quick as lighting and lithe as a snake, I took Martin down hard and made the kill with complete abandon. 
%scene disaster
I knew what was going to happen to me but Martin was calling the shots, using the one thing that would be successful in causing me to lose it. To really really lose it. I just didn't care. I desperately wanted to care. I could do nothing but devour his life blood. I tore out his throat the feeding was so vicious. When he was dead I was changing. It was too late, I couldn't take it back. I had control of myself but only for a few moments. Oh my God the pain, horrible intimate euphoric pain. Searing with power and pleasure as I experience the wretched agony of my flesh tearing from the inside out. I started to feel the pain give way to a new mass, a new body not my own was devouring me and emerging in my place. The monster has been set loose in me, in my loss of control I sacrificed a life to the slumbering vampire and brought it forth to consume me. I think my hands came first as they were elongated and clawed, breaking through my skin. I seen the new being crawling beneath my skin like a snake or worm, a ghastly sight to behold.

She is coming, the vampire that I am to be, she is not me. I could feel the others coming, other vampires. I heard the memory of the Red Kings call to battle. I hear them, I feel them. My vampire half is becoming whole in me, while I live it now coexists with me but I will not be here long. My soul is soon to be consumed. Harry reminds me I am the youngest of the red court now, I can destroy them all by my sacrifice. I can take every last one of the red court. I scream to Harry to save our daughter Maggie. Maggie was all I could think about, I have to save Maggie.

Harry took Maggie from the altar as gently as he could, and laid me down. I am still being consumed, I haven't much longer for my humanity to live. Harry promised me Maggie will be safe, I felt confident in his words. That didn't completely absolve my worry, and it did nothing to absolve the sheer terror I felt over what is happening to me. Harry was going to sacrifice me. I've never been so scared in my life but I still knew it would preserve me from the completion of my transition, and destroy the monsters that have caused so much suffering. Oh I was so scared. He closed my eyes with his hand, and kissed me. It was a sharing of our blood and our tears. I cried out to Maggie, perhaps just to tell her everything will be ok, but I don't think it came out as more than a whisper.\\
%no, and furthermore

\textit{Then Harry cut my throat, and I was dying.}\\

All was black, but for less than a moment. Lighting came down from the heavens and struck me in the darkness, maybe it was a dream, but it kept frying me for what seems like forever. I felt the consumption of my body, well, come to completion. Bye bye human me. After a time I felt myself floating up and seen myself, my blood flowing out from all over the altar. My body glowing and sparking with energy repeatedly, like when lightning hits a large transformer in the street. The energy slowly being absorbed. The vampires were gone, my friends survived. I am dead. The whole red court is gone including myself the youngest of their kind. Thank God for that. Soon enough I know that sweet chariot is going to swing low and come to carry me home.

Harry was in such pain. I could see it. I rested my hand on his shoulder and tried to talk to him. He neither felt it nor heard it but I could do no less. Harry is standing there, in shock, not moving. The vampires all fell leaving nothing but black sludge. The infected were mostly killed except the younger ones, since the vampire part was killed and it was what was keeping many young, even alive. 

%scene continued with Erlking
Walking toward the altar is the Erlking and I take my place beside Harry.\\

	``Huntress, Sir knight, well met.''

I had to check but yes, I'm still a ghost. I turn to Harry with a tear. Yes ghosts have tears, apparently.

``To you as well.'' I said.
	
	``I hope thou wilt be pleased with the strength of thine new nature huntress. Nay, I played no small part in bringing it to you. I was most certainly pleased that thou wert the first to have been my guest. Thou art honorable and wise my dear, such cannot be hidden in you. Thou likely thinkest that thine visit to mine realm twas coincidence? Be not a fool I willed it so. I was needful that you could be near me, that I might know that thou wert pureborne.''

	The Erlking smashed Maggies shackles and placed her in Harry's hands. ``Thou art the greatest hunter of thine kind, I cleared thine path for you. I ensured that thou wert slain. Your life has been hideous child, thou wert pitted against thyself like thou wert thine own prey, to live thou wouldst needfully refrain from the kill and blaspheme thine own nature. It is now abolished in you. May you and yours now hunt in freedom and rejoice in the kill. Thou hast redeemed thine species in the shedding of thine own blood. Thou art now free to join your hunt without fear of destruction. Thou canst replace these dishonourable wretches with thine own children as thee see fit. A pity I could not get the chance to hunt the red king and his ilk myself.''
	
	I don't see where I can enjoy the hunt as a spook, or how me and Harry can make little spooks together. Bloody Markov chains I'm gonna have to wait out the answer.

``Perhaps you might elaborate more and explain what you mean?'', I said.
	
	``Thou art always welcome as mine guest o' queen, then shall we speak together by the fire enjoying our kill.'' The Erlking bows low to me. He looks at Harry with a sort of piteous eye, ``I promise that by my hand thine mate shall not be slain. I know thine mate twas torn from thee in a most hideous way.''\\

Then at that he swiftly left on his way. Harry seemed to come to his senses after what seemed like forever. Just as well he would have been confused as fuck. I know I am.  As a matter of fact a helicopter came in and landed taking in a couple people, then left. Harry still stood there with a thousand mile stare, holding Maggie. I stayed with him, I wouldn't leave him, even if he couldn't see me. I hear our friends conversations with my enhanced hearing. I sat there with Ebenezer and Harry while they chatted, they were none the wiser. It's amazing he is actually Harry's grandpa, I wonder what other wizards are in Harry's line. I wonder if my Maggie will be a wizard when she grows up? I'm not sure how to feel about that. I still sat there with Harry as Karrin came over to chat. Harry was determined he was going to give up Maggie for adoption. Oh my God I was scared, but then I realized what I did but giving her up to a familiar family was pretty close. I hope he decides against it but if he does let her go for a better life I would understand. The rest escaped into a portal and Harry's Faerie Godmother remained. I felt my purpose accomplished and as I heard the sound of a vehicle approaching I begun to feel light and being pulled somewhere. Well this is it then, I'm going home to the family I've never known. I get to see the hereafter and Godwilling enter into paradise. I was being pulled toward the altar. My body was melting into the same black sludge as all the reds had, mingling with my blood and seemingly seeping into the stone of the altar. As it did I was drawn into it rather than being released like I expected. I was terrified that my soul was meant to be trapped in \chichenitza forever.\\

Fuck.\\

Then I was sucked into the alter.\\

I guess that chariot isn't swinging low for me after all.\\

%scene disaster
As I lay there some words I heard earlier that day keep repeating in my mind.
\begin{quotation}
	``You son of a bitch,'' I said, ``You fucking traitor.''
	
	Martin’s expression flickered at my words. But his eyes never left the Red King.``I give you the Fellowship of St. Giles, my lord,'' he said. ``And I beg you to grant me my reward.''
	
	``Reward,'' I said, blind with rage,``What could they possibly give you, Martin, to make it worth what you’ve done\dots''

	``And what do you get?'' I said to Martin.
	The Red King states, ``Ascension.''
\end{quotation}

I hear him say ascension over and over again in my head. What is happening? 

%transition 4days
I did lie in the alter many days. My eyes could see the sun rise and set upon that altar, the surface of my solid tomb. I could feel the warm sun and hear the breeze and chattering tourists. I thought to myself that it's not so bad being stuck here. I have company, I'll get used to it.
%sequel emotion

I'm dead. The silence of this altar allowed reality to catch up with me. My life has been wasted. Ever since I was half turned life has been nothing but a struggle and getting killed has been my only release from it. I knew it would be that way though, deep in my heart I knew the only escape was death. The fellowship had been working on a cure for a vampires turning ever since the fellowship came to be hundreds of years ago. They never found it. Either I must die, or make a kill and allow the vampire part to consume me and take over. I think Harry is going to be ruined, the man is going to need full time therapy when he gets back. Sure he's tough but this is too much. On top of that if Maggie were aware of anything going on she will be scarred for life. I want to just hide in this altar indefinately, just hide away from the reality of what happened outside of here in that world outside. Hide from the hereafter and from what other transitioned souls might say in my afterlife. What am I really? Innocent or guilty of making a kill? Depends on who you ask I guess. I place no blame on Harry I climbed right up on the altar and waited on him. The question is am I culpable of something?

What an odd word to use when Martin would perhaps be promoted within the court, raised to an office of a position, ascension is like to a king ascending to a throne of Christ ascending to heaven or a lesser being ascending to Godhood. Would the Red King really want Martin, being of a traitorous nature, to take power to himself in a worldly way much less a supernatural way? Really, who is Martin to raise him up to any position when any given responsibility would be poorly invested in anyone who could have executed such a grievious betrayal as he had done. The red king is mad but I don't see how he could be that mad. So if it was intentional it may be something the king was going to inflict him with, ascended and enslaved. Given significant power. Or something Martin was to cause, his actions are to cause and ascension of something or someone else. Everything is speculation right now.
%decision
I need to find out, something big is going on I feel it. I need to understand it and what role I'm playing in this game. who is the mastermind and what are his intentions? I'm in danger even as a ghost. Since I got sucked into this altar it's pretty clear to me something is weird and why would the Erlking have said that weirdness that he did? I'm all questions and no answers, very fews clues either. I need clues. I need answers.

%action
It's midnight, on the fifth day. I feel my body rise, the next thing I know I'm lying on my back on top of the altar. My arms are crossed fists on shoulders, my head laying to the side. It made me think of a song, ``walk like an egyptian''.

\parasep
%switch now to present tense, flashback is concluded.
%scene goal

I look at myself and shudder.\\

Oh God, I'm not human. This is the true form of the red court vampire. I really did complete my change. I feel normal though. I seem to be physically a typical red court vampire except maybe the odd thing, like talons rather than claws that resemble razor sharp scythes. I'm hungry. I'm very hungry. Oh my God sweet Jesus mercy and pass me an artery hungry. I have control for now. I catch the scent of human on the breeze and crouched low in a tiger's purr. The sound catches me by surprise as the red court never made such cat sounds that I'm aware of. I'm a little different somehow. I concentrate a little while and manage to put on a flesh mask, a convincing one, but being naked I decide to forego the flesh mask and go with the xenomorph look. A xenomorph born of a man sized vampire bat host is the essence of what a red court vampire true form looks like. H. R. Giger never goes out of style. 

All around, throughout the countryside, it sounds like popcorn. Anarchy has descended in the land and armed conflict is everywhere. People and paranormals are struggling in the power vacuum and damage caused by the destruction of the red court. No good deed goes unpunished.
%scene goal

So here's what I need to do then, find the nearest town and investigate more of what happened. I would look around here but I'm hungry. I've held my hunger as an infected I should be fine now, but not for long. Maybe I could take a couple sips while I'm there, I'm not that bad off right? A little nibble, that's all.

%introduction conflict, hunger drives her into damian, who prevents her from getting further

I leapt to the edge of the temple, onto the stairs of the pyramid. I'm smelling the air, I can't help it, my vision goes from black of midnight to the shadows of twilight as my eyes see through the darkness. I smell life-blood and I see the glow of human life off in one direction, at line of sight. With a growl I'm off. A growl, like a great cat. Not a shriek, wail or hiss as would be expected of my kind. Heh, my kind. Shoot me now. I laid tracks fast for the source of the radiance and I see someone driving a truck down the road and I hit the windshield at a speed faster than the truck was moving and smashed the bloody carcass out through the back window onto the road. I utterly destroyed the man tearing flesh from limb with my claws, chewing, sucking, lapping and gulping every last bit of the poor victim. They wont even be able to identify him with dental records. I'm too hungry to have any control. I genuinely hope someone just shoots me.

A black court vampire appears. He seems to be quite unusual, like from the Sherlock Holmes era, except for the chainmail gambeson draped over him and the combat boots he wears a very upper class Edwardian suit. God he looks cold as ice even for a vampire. He throws down a child he just consumed, a little 4 year old boy, blonde hair and freckles. dead and gone. He pops his collapsible top hat, and bows to me with a flourish of his hat. Then fills a pipe and speaks.

``Has anyone ever told you of natural selection? Foolish morsel decided upon himself to go forth into the night and deep forest I know not why. Most certainly I can say of him that he quite simply is a feeble-minded child. It is well that I had found him that he might be most effectatiously culled from the local herd. Alas it nearly came to pass that the noble vampire society might have been deprived of this most delicious morsel should he have perished in and of himself. Do you not agree dear lady? Yet as you are a most grievous poacher, oh what shall I do?''

``You fucking monster!''

``Ah yes, this I have heard many a time. 'Tis rare though that I should hear it from a kindred species, 'twould seem like to the pot calling the kettle black as they say. Let it be agreed then that I am a monster. So what of you dear? I cannot accuse you of wasting a single drop of that kill all chopped up and wrung dry so don't you dare be hypocritical. At least my kill is in one piece. I'm proud of who and what I am. Are you? I don't think you are.''
% scene climaxing

At that he withdraws something from his gambeson, damn. He's got a jar. Like as in ``A Jar'' trademark pending, a weapon I'm sure was first devised by the fellowship against the red court. Although not really used for anything but vampires, they may work on other supernatural entities or powers. They have no effect on humans. On vampires we used them as grenades and mines, hard as hell to get them triggered but when they do it's a guaranteed capture and the vampire is trapped in the jar which acts as a spirit container. We would then bury it deep, if we could drop it down with a post-hole digger we would. That way, just as Damian said, the creature would sit and rot until the second coming.

Problem is, now the shoe is on the other foot. I have no idea how he could be so confident that he won't get trapped but being I'm of the vulnerable species now I'm in hot water. He must be either crazy or stupid. My money is on crazy.

He casually taps the pipe empty on his gambeson and replaces it in his pocket, then drops his walking stick aside. He holds up his right hand and with a few words a slow moving black and purple ball slowly forms in his palm, the size of a basketball. I understood the words though I shouldn't have. I've never known such a language.

He said, ``Livyatan niis d ol nobloh tzrvt ollor adin zerimah''

Instinctively I know it means, ``Leviathan come, into my hand forms a gentle flow.'' Although I have no idea of the implications of the words. I repeat the words in english out of curiosity and see black and purple mist, unfocused energy flowing around me.

He said, ``Most singular indeed you are. It was best that I should have the jar.''

Without much warning he said, ``Lhtchl'' and the ball hurtles at me, I throw myself and roll. The ball curves toward me, I vault behind a tree and the ball crashes into the tree. The tree makes a low moan like it was being subjected to an immense weight then is still. Even the leaves flutter far too slowly given the force of the wind today.

Then he said, ``Flereus niis lishloach mad setani prg lehashlich forth, pon in oyev'' and a ball of flame hurtled from his hand directly at me. Fire is not good, I'm particularily vulnerable to it.

To my surprise it burnt straight through that same tree and it fell to the earth. Of course it caught me off guard and I hurled myself just in time, it hit my left bicep burning it off straight to the bone and I wailed, the shoulder on my other side hit a rock hard on the ground where I fell and I wailed again. I leapt backwards with a shriek and came up to stand with two useless arms. I'm in big trouble now.

He decides it's a good time for a tackle, he leaps and I dodge, he lands where I was just a split second ago.

No he predicted it. His walking stick is special I see, he wielded it as a sword stick and sliced open my belly. I figured I was done for but the wound stuck and I managed to bear through the pain and land a hard kick on him. I break his neck, which heals itself before he falls to the ground. I really hate vampires. Myself included.

He grabs for the jar but I'm already on the road ready to speed away. he throws the swordcane hard and in crunches into my hip. I sorely miss my firearms. I had an automatic pistol once I really loved. Snap out of it Susan, don't drop now, fight.

I'm on the ground. I can't move. He is throwing the jar for the final attack. I'm at the rear quarter of the truck. My arms are working again. I throw a rebar off the truck which goes right through his side but it only redirects the jar slightly from my head to the steel quarter panel where it triggers.

It was right where it needed to be. Right in the sweet spot. Inky black smoke licked out of the jar and just as I was afraid of it enveloped me. It felt like being on the scariest rollercoaster ever. I shrieked. After that, I was a jar. It is surprisingly spacious for a vampire in a jar. I never knew that. Rather than infinitely small it's infinately spacious. Must have something to do with the magic used. A rebar sails into the truck and it starts to roll backward crushing the jar. I'm released seemingly with a pop to land on the road with a plop. My body feels like jello and I yank myself to my feet by grabbing the truck and hurling myself to the other side.

I hear a familiar word of power, damian says, ``Fuego'' and a laser beam of fire pierces the body of the truck and wings me on the way to the ground on the other side. I howl and wonder what can I possibly do to overcome someone proficient in magic. I tear off the back quarter panel and narrowly block a rebar yet it still shreds through and narrowly missed my right arm on the way down. Split in two I swung the one side of the quarter panel at him knocking him to the ground and head to the side of the road. An unfocused ball of fire burns toward me and I turn what's left of the quarter panel and deflect it skyward. the impact sears my hands as the metal turns molten and throws me into the treeline. I break into a run deeper into the treeline and hear an animal behind me. It closes on me as I run then it's jaws tear at my ankles. I fall. Damian appears ahead of me and I roll as he hits the earth with his fist and around me the earth begins to buckle and split. It splits deep and my hands grasp the other side of the fissure to catch myself from falling in but it is still spitting and soon I won't be able to reach the other side.

Damian says, ``Wonderful my lady, 'tis most suitable that you should perish for all the trouble you seem to cause me. I do forsake the chance of casting you into the jar you are hardly the willing maiden with such a spectacle you have displayed.''
% scene disaster

I fall into the crevase, grabbing into the rock face and landing on a small outcropping on the way down. Holding onto a couple awkward handholds my feet are hardly wide enough to span the size of the outcropping. Soon I'll be heading into the lava pool at the bottom with the shaking of the ground as the ground continues to split.

Damian says, ``Well adieu then dear lady, may I suggest that you should refrain from holding onto false hope and embrace the fires below. I assure you your destruction will be quick then there shall be no more pain nor suffering of this most noble vampire existance. I wish you could have embraced your nature and come to be my comrade and not mine enemy.''

At which point he heartlessly walks away. I expected such heartless behaviour of course from a creature who could make a kill of an innocent child. I have a rather perplexing situation now though, I can't reach the top I'm too far down. Another quake causes part of the face of the cliff to fall and I grab new handholds just in time as the old ones give way. I'm leaning farther and farther over though I'm going over. I pull hard on the handholds and manage to get myself back against the rock face. Oh God what the hell is going to get me out of this. I look around but only see sheer rock face with handholds I cannot reach. Another quake causes more erosion of the cliff face. I try using my talons but it just erodes the rock face faster rather than grabbing hold. Too much earth mixed into the rock. Another quake and the outcropping I'm standing on falls. I'm holding desperately onto the handholds and I scream this is freaking crazy I'm going to die right here. No matter how much I can regenerate a lava pool is permanent. A handhold crumbles then another quake causes the other to crumble and I'm in freefall. I slash my talons into the rock face and manage to slow my descent but there is no other outcropping to save me. The lava pool is getting closer then my talons hit something substantial, solid rock, the impact jars me and my feet don't seem to feel the rock face anymore. It seems to be some sort of tunnel. Oh thank you Odin. I rock my body like a pendulum and throw myself into the tunnel. This is something that looks untouched by man, stalactites and stalagmites, dust on the floor of the tunnel undisturbed by any creature.

I fall on my ass, shaking with adrenaline. OK I just need to figure out how to get back up the fissure. What's around here. Is there at least some vine? The ground rumbles again. I look out into the ravine and see the walls closing back together. Oh man I gotta find something. My heart is in my throat, I'm scrambling around in the pitch darkness with vampiric vision to find something to get me out of here and back to the surface. Nothing. Absolutely nothing. Another rumble. I grab a stalactite and place it between the two 
%disaster, and furthermore
walls. Another rumble, the stalactite shatters. The walls are sealed. My fate is sealed.

I can see in here with vampire vision. The tunnel is wide open. A room essentially. No way out.

%sequel, emotion
I sit down on the floor of the room. Now what. There must have been something I could have done to stop this. Harry would have found a way. He gets in this sort of thing all the time. This really isn't my bag. Clandestine strikes. In and out. Fellowship style. I can do that. I have no right to be in a battle with an entity like Damian. I was outclassed. I should have ran, found a way to hide. Just let him jar me maybe someone would find me. What if he buried me though? Noone would ever find me. What was I to do? Now I die here. Maybe this is going to be my jar. I'll just go crazy in bloodlust and fade away. Hidden beneath the earth, noone will find me and I can harm noone. He was right, I should have saved myself the pain and just thrown myself into the lava pool. I want to die anyway. I don't want to live as a monster. I don't want to be this creature. Why do I feel this way though? I've never known a vampire to display such self loathing. They are narcissistic, maybe even psychopathic. What am I? I am so terrified. I want to die but I don't. I want to live. Somehow. To find a cure, to refrain from the feeding somehow. To stop killing. To stop hunting. Should I even attempt to find a way out of this. It's futile. Why should I?

%sequel thought
To stop the vampires that's why. To find a way to defend people against the supernatural forces. I am the only one with the strength of a vampire, the speed, the invulnerability against their hunger. They can't feed on me, we're made of the same stuff. I represent a hope for mankind. Despite being a human predator. Is that what they call an anti-hero? I guess that's me.

%sequel decision
Right then, time to get the frick out of here. I need to feed and I need to get somewhere to find out what happened to me. I have a purpose. I'm like the only vampire with a human soul. I don't know how but I'm important, I don't know how but I came to be for a reason. Some mysterious reason. I need to learn my purpose and fulfil it. I need to get out and back to the road.

%sequel action
I look along the walls of the room to see if there is a break into a further tunnel or chamber. In the twilight sight of my vampiric eyes I look as deep as I can but see nothing. On the floor of the chamber is nothing. Some dust but no footprints. Every once in a while I trip on something I should know is there. I look and see nothing. I must be exhausted. I lay down for a few minutes. What am I missing? Please don't tell me I was meant to die in some cavern. I was never a big cave explorer, although I can see how beautiful it is in these deep places.

I feel bad for messing it up. Walking all around scuffing up the floor of the cave and leaving it disturbed somehow. Like it's unclean in a way, having been touched by a person it's like it lost it's virginity leaving footprints all around. Hey wait a minute, I didn't leave footprints? Such a fine dust on the floor I should have left footprints. Something isn't right in this place. I swipe the floor with my hand, I don't feel dust. I look at where the rock face was and I see there once was a tunnel. The spell closed it off though. OK there once was a way out. Now there isn't. To hell with it I'm laying down, this is making me tired.

As I lay down I see on the ceiling what looks like a switch. A silver switch embedded in a green jewel. I think I get it. Tripping on things not here. Not leaving footprints. Some kind a veil. It has to be. I feel around the walls and find many indescrepencies, and something in particular I was looking for. I find what looks like a ramp along the wall. The creator of the veil would have been able to see though it and climb to the switch to disable the veil so others could see. I blindly climb up the ramp and sure enough it takes me to the switch. I move it over and the veil disperses. I find myself in a ritual chamber. Skeletons are scattered on the floor, wearing ritual cloaks. Wizards, warlocks, something like that. Something killed them, a very long time ago. That was what I was tripping on were these bones. I jump down and look around. Magical ingredients many of which have long expired. A gold ritual circle embedded in the floor. An alcemy alcove and bookshelves along the walls. The floors and ceiling are perfectly flat and polished to a sheen. I check along the walls to see what's behind books and I find one bookshelf opens to reveal a tunnel, well hewn with carbide lamps along the length.
%quasi-scene goal

Time to move out of here, 
Travelling along the tunnel I find it slopes up. It continues on forever. I come to the end to find a door which opens up into a basement. Stairs lead to a cabin via a secret door in the floor, under a rug no less. Everywhere is long unused, but still functional. The cabin still holds some useful supplies, it seems it was enchanted against decay even if dust and spiderwebs still accumulated. I found some nice post-vietnam gear, olive drab combats and alice webbing. An M-16 rifle. An Anzio 20mm vulcan sniper rifle fitted to breakdown for 2 to 3 man carry, various loadouts mostly HEI. An M1911 semi-auto pistol. Jars and grenades, a mix of anti-paranormal and conventional loadout. Goldmine. Now I have a better chance against paranormals. I shrink into a skinmask and don the equipment. I feel a little more normal now, and a lot relieved. There were some notes in the basement though, it is a furnished basement and the way to the cabin was through a trap door. Somebody wanted to hide something.

It looks like the papers indicate wizards stayed here. Amongst a significant contingent of red court vampires. There were some quick kills here as I see the unusual skeletal remains of reds. Usually they dissolve. It was a covert mission to find out more about a legend within the higher escelon of the red court. The queen to come, the great mother. I copy down some notes of the material for use later. I think this is what I was looking for, I may not need to go to the town afterall. As I search through I see some personal letters of the team of wizards how were researchers here. Letters from wives, kids, mothers, the odd incomplete letter that was going home to sweethearts, sons and daughters.

%scene development
I need air, I need to get outta here. The wizards deserved better, they were husbands and fathers on a scientific quest, they were not of any threat to the reds. Why were they killed? The reds were monsters, that's all I can say, and the world is better off now that they're gone. I race up the ladder and can't open the door. I yank and beat the door I can't get out. I let out a shriek and the trap door glows. Now it's locked. My skin is burning, it tastes like cool mist but burns me. Holy water. I'm going to be burnt up by this mist. I triggered a defensive trap that the wizards set in the cabin in case any reds came into the door. I need out now.

I look up and see the mist is descending from the ceiling, I grab a table and hold it above me. It helps but the mist is still swirling up and under the table and I don't know how long it is going to be coming down. I look at the notes I scribbled down but I only wrote the information I needed, not any words of power that might be useful here. How was I to know this was going to happen? I scan around the room, displays of taxidermy, a fireplace, wooden floor and ceiling with mist pouring out between the boards. I try to get into the fireplace, no go. There's a window, but a wall of force holds it safe. I swipe at the ceiling and the force sparks off my talons. I'm showing the equivalent of 3rd degree burns and not regenerating. I shriek again, this time in pain, I'm at a loss, how can I stop this slow death?

How would the reds have got in? Of course, turn a wizard and they have his knowledge and skills. An age old trick. That only means there is a way to bypass this trap but it doesn't tell how. Only that it isn't something particular to reds that triggers this, I can get past it. Somehow. Words, if it isn't detecting reds it must be controlled by magical words. If I was a wizard would I have placed the words somewhere in this cabin? Where? I don't have much time I'm melting away.

Under the carpet, I check, nothing there. I lifted the table up there wasn't anything under it, no note. It would have to be accessible when triggered somehow. Either that or it just stops sometime after I'm melted away and there is no failsafe. No there would have to be the wizards may have taken red court samples in here if there wasn't a failsafe their efforts would melt away in their hands. There has to be a failsafe. Hey wait a minute, maybe I did write what I need down, but it isn't instructions it is a word sequence to deactivate this trap.

I'm reading my notes to see if I wrote something odd verbatim to check later. The letters are english, spanish, portegese, italian, latin, russian. When I was alive I could speak and write english and spanish. Now I can read, write and speak them all. I'm panlingual, I know all language even the magickal! Oh snap!

``We're not in the cabin anymore sweetheart, we're safe now they can't find us. If they do though we only need to refrain from cease the mist and all will be fine --''

Huh? Oh. As in if they do find us, double negative? No, refrain from then grammatical disaster. What if I'm looking for ``cease the mist''? the all will be fine is declared as a double negative so it seems to affirm the possibility. Of course pseudo-latin. Here goes, I say, ``cessare in caligine!'' And-- nothing. I don't know that cockney latin, at least not for spell work. Maybe I resonate with enochian. I heard Harry say once magic works not by rite but by self. If I believe something is powerful and works for me that's what really will work for me. This time I say, ``lehafsik oiad arafel!''. I hear a moan from above, then drops fall and I dive under the table. My bones are showing through now, I'm cadaverous. The dripping slows, then stops. As soon as it seems safe I dive for the trap door, it opens, and I close it behind me. I am in so much pain. I wrap myself up in some blankets that I find in the basement area and rest inside a closet to try to conserve heat. After a while I drift off to sleep. I'm not going to be leaving this little cabin. At least not today.
%scene disaster

%Sequel emotion
I remain sleeping on and off for a couple days, healing less quickly than I normally would but I healed nonetheless. My clothes are fine since the attack was just using water. I'm rather hungry now though. So here we go again. This is what pisses me off, if I would consider myself some sort of anti-hero considering whenever I put myself, or get caught in, the fray I get hurt. When I get hurt I get hungry. When I get hungry I hunt, and I kill. I don't want thralls to sip off of I could kill them if I get hungry enough whether I want to or not. I would addict them to my venom. There has to be an answer. There has to be a way out of this existence. I dare not call it a life. Is this equipment I have going to help keep me from getting injured? Is there a way I could just randomly sip, no killing, no addicting? At least until I can take full control of feeding.

%Sequel thought
All that aside I need out. I should kit up and get out of this basement. If I trigger the trap again I know how to get out. It probably just got triggered as a combination of my presence and pounding on the front door. So move around normally.

%Sequel action
I go upstairs without a trouble. I find a front door key under the mat believe it or not. I exited normally and the door is set to lock behind and the key works fine to open the door. It is a proximity key, a magical one, the mechanical lock on the outside is a ruse. I go back inside and kick my feet up on the couch and burn my ass. It's still wet from the holy water. I go back into the basement.

%Scene goal
So what now? I can get out, but then what? Where should I actually go? I can't stay here, I have a little information now there isn't a need to find a village except to feed. No matter which direction I go I'll find food. Eventually. Maybe I can link up with some former fellowship people, people I've fought with. I can find out news about what's going on and decide where to go and what to do. Again it doesn't tell me which direction to go. Maybe going outside there might be an easier way to figure out where best to go. The sniper rifle has extremely long range sights. The roof, a tree, I need to find a high vantage point to see far around and decide what to do. When I was outside I could see I am at the top of a cliff face, I'll take a reading off the compass I have in my kit. OK, let's check things out.

%Scene development
The road is to the west, a mile out. Not much but forest around. Cant see south im partway up a mountain. There is a path down from here so i think thats my next move. The discharge of weapons look like twinkling stars in the night. It looks like the black court are getting a foothold i see them moving amongst the trees in many places. I see slavers are active, many bodies hanging in trees. A nearby river is filled with bloated corpses. Its armageddon out here sweet mercy.

 






I'm keenly aware or what goes on outside though, and Damian is perfectly well healed from the rebar and is walking this way. All there is left for him to do is bury me. He walks off to the front of the truck and to the other side. A post hole digger. I'm getting good treatment. He grabs the jar, smiles at me, and as he starts to dig shouts go up in the distance. ``There! There's that monster and he has a shovel!''

Another shout goes up, ``What have you done with my baby boy?''

Damian drops the post hole digger and starts running just as 3 jars hit the earth beside me, two trip and are spent in a flash and the other didn't trigger. Thats the way they are. A good batch works well others are too sensitive or are just duds. Another reason I thought Damian a fool.

A man runs up first, then another, 

``Have you seen the child?''

``No I thought he might be here, just the vampire and he is probably long gone now.''

``Any of the jars still useable?''

The man uses a device we used that checks magical charge in the devices. We had to keep really good track because a charge could mean it's untriggered or\...

``I got 2 spent and 2 live, I thought you only loosed 3?''

``Must have been someone else down there, grab them.''

\... it already had an occupant. Sweet. I'm angry as hell though about that poor little boy.

``Jose, where do you think the little boy was taken?''

``Jorge I don't know. I think we have to start back at the village to pick up the trail again.''

Jorge said, ``What do you think are the chances now?''

Jose said, ``After this long? Most that come back are, they come back as something else Jorge.''

I was screaming inside myself, they have to find the child. They're right the boy will come back as a black court vampire. Jose seems to know at least some I hope it's enough. I'm yelling at Jose from in the jar, no vampire has ever penetrated their power through a jar but I'm feeling desperate.

``Jorge look here, tracks going toward the road. Gather the people we're going this way. Get the jars ready. Thank God for the fellowship in giving them to us.''

Your welcome Jose. Just hold onto me, I didn't get even close to what I wanted but I don't want to be left out here. Bring all the jars home.

They found the boy, Miguel, and burnt him on a pyre before the sun set that evening. Little Miguel is at peace now.

So I ended up with Jesus, pronounced hey zeus. So many jokes about that name. Anyway, he keeps his jars in his daughters room for protection. So I got to watch many hours of playtime. Time to think as well as I sat there on her shelf beside a raggity anne.

The rural areas are really dangerous, I really got screwed out there. So did that little boy. How many other people, even children, are becoming black court now? Are they going to be the menace that fills the vacuum left by the red court's demise? I cringe at the thought of an army of little Miguels marching through towns devouring people, maybe even their own parents. Like a classic zombie movie except the black court are very intelligent. Which is even worse. Did I do any long term good out here?

Well no, I can't think like that. There is a vacuum but there is a chance things are going to be a lot better than they were.



%scene development
I say, ``whoa buddy how am i supposed to know you had this one marked, you put a brand on him? Piss on his shoe? something?''

``How would we have had time to even cough hmm? You rode though here like you were on the back of a tomahawk missile. You are the most violent, loud and clumsy young bat I've seen in a long time. If you were my spawn I would kill you, so since you're not. We will all kill you. It seems fair.''

So they all surround me from the bushes, six in total. They would have had to have been smart and dangerous to have survived out here during the red courts reign so I have to act smart.

``I see you are likely thinking we must be good to survive out here so long. You're right. I know you aren't any ordinary red to come down from \chichenitza alive. You likely have known about jars like this yes?''

uh oh. The fellowship had been recruiting warlocks ever since i had known. The jar as they called it was one of the successful ventures that we undertook. Paranormal creatures like the reds and others could not always be defeated by any other way but capture. The jars could be used as grenades or mines to immediately trap the creature circumventing the need to traditional battle. The jar would then be buried safe many feet into the ground where the creature would spend eternity. Using jars would be dangerous for them too but with this many if one of them were trapped another could simply break the jar.

``Can we maybe just talk this out? Like you said I'm kinda new and now I know I should be a little less bold. So lesson learned. Live and let live right guys? Fellow vampires always support each other right?''

``Hah. Damnable reds with their insanity put all vampires in harms way. That court is gone and you alone are not part of any living court. I would be pleased to feast on your corpse to pay back all the misery your people caused.''

``That wasn't me. I'm the new guy in town. I finished my meal and meant no harm, why must I die?''

``That's just the way it's done. Even if I meant no ill will.''

``Is there something I can do?''

``Ok, sure we can make a deal. If you are here now you must have had birth through the altar, the central focus of the spell. Tell me names and locations of the team that assaulted the altar and we will let you go.''

I thought for a minute, what would it matter if I said who was there? Nobody at the top would be able to do much to my friends on their home turf. Then I thought it might lead them back to Maggie again and that's something I wouldn't allow. So after thqt moment of thought I said, ``No.''

``So be it then. See you in hell.''

All six started moving toward me and what was left of the truck, I couldn't be caught in restrictive cover when the jar is in play, somehow I need to keep that thing away from me. They wouldn't want to waste it, so triggering it when one of their own was near might waste it. Inevitably I need to get the hell out of here to be safe. Oh to be human again the jars would not be effective.






That town is the closest one to \chichenitza so should have the best clues as to what happened to me. I need to ask around and see what everyone knows. I'm still so  hungry. Jesus. I resume running for my destination. I enter into a village and spring for a tree. I smell quite a bit of food, between what I smell and the life energy I see I guess maybe two hundred? Hunting other humans is not a skill I want to get better at. So here I am up in a tree hissing and purring. This fact finding mission is not going so well, I need to calm down. I'm sensing something close, I leap to another tree and see some teens outside what looks like a drinking hole. It's a start, they might know something, I need to find clothes first though since first impressions count. Watching, I see one move around the corner to urinate and I land on him fangs first. I hold him fast with a powerful grip of my talons. He's done after a few minutes but the others have disappeared likely around a corner. This is not going so well so far. Still hungry. 

I prowl back to the area they were, I smell prey close. I also smell alcohol inside the building I'm leaning against. It looks like a four story building with a solid roof. I scale the walls like a cockroach to the roof and perch, waiting for more prey. I hear a shout come from the rear of the building, where my last victim lay. The call is going out for a vampire in the town and the people are scurrying about. I don't really feel like I should care. I think I would be better off dead anyway than to suffer through a life like this. I hate myself with a passion. 

I leap to an adjacent building to see options, how can I get into the village to ask the difficult questions? It's what all us reporters do, albeit no other reporter in the world would have this particular problem. At least I hope not.

A dry cleaners, most excellent. I need to move across the square though. The building next door has about a dozen townsmen vampire-hunting. They don't see me yet but as fast as I am I can't cross that distance without being seen whether in true form or as a naked Susan. either would stick out like a sore thumb.

Hey, wait a minute, that's it.

I put on the flesh mask and run like hell for the dry cleaners. I hear rounds of hooting and whistling from the men and jealous disapproval from the women. Heh. Nobody is thinking much about vampires now as I bust the front door lock and roll inside. There is a roar of voices and laughter outside giving me time enough to throw something ugly and flowery on and walk back out. I looked up to see what seemed like half the town looking at me with various reactions. I just looked down and walked toward the tavern like I hadn't a care in the world. Around me groups of people especially at the tavern whispering and giggling. Occasionally some fellow would grope. One fellow I think I knocked out some teeth, then none would grope me after that.

I walked into the tavern and sat down at the bar. I ordered an ale but advised I hadn't anything to pay.

The bartender said, ``That ain't no worry miss. After that spectacle everything is on the house for you tonight.''

``That's mighty sweet of you sir. My name is Susan, what do you go by?''

``Frank. Do you mind me asking how you got caught in that situation tonight?''

``Well, rather not say sir. It would make the embarrassment worse I'm afraid.''

``Fair enough. Well enjoy the beer, I hope it helps matters.''

I did. I appreciate the fact I can still enjoy a beer. I always wondered if vampires could actually enjoy human foods and not have it taste like styrofoam or excrement for that matter.

God, I'm still hungry. I need some way to deal with that but I'm not sure how.

I see Frank head to the side door to speak with someone then return.

``What's up Frank?''

``Reports of a vampire, poor kid was taken by one in back but noone has found it yet. Where did you come from miss, and I never caught your name?''

``It's Susan. I came down from \chichenitza only just tonight. Hell of a mess these last few days.''

``Yeah I've had the blue blues lately, I should go see the doctor.''

Uh, wow. Bartender is fellowship! Signs and countersigns were used with us to identify ourselves. Each cell held a secret key and each soldier held their own. We had numbers stations broadcasting our ever changing public key on shortwave trying to keep one step ahead of the reds. It decrypted to a word or phrase we could use to identify each other as well as codes to authenticate cells and individuals. On the day of the battle the sign was blue, countersign honeycomb.

``I've heard eating honeycomb helps cure the blues.''

``manere in missione?''

I whisper to him, ``authenticate bravo bravo alpha november foxtrot whiskey.''
he responds, ``I authenticate alpha whiskey november november quebec tango''

``Jesus, are we still operating?''

``yes, the authentications you have are 5 days old in fact. There is a vacuum and other species are moving in and the wilderness outside the towns are chaos.''

``Bloody hell.''

``Here, a portable shortwave. Our number stations are still broadcasting at least for now. Do you still have your certificates?''

``No, just memorized the authentications from the day of the battle.''

``How are you just coming down from \chichenitza now?''

``Got sucked into the altar. Weird shit. Must have been some effect caused by the execution of the ritual.''

``Likely, it was like the end of days up there. The power of that magick lit the sky with terrible lightning and eclipsed the sun.''

``Seriously? I don't remember anything it's all just black.''

``Anyway, let me radio out for some new certs for you. I'm an area coordinator so I have the authority for it. All that much so since my area includes the site of the battle. I've had to reissue quite a few certs that day.''

``That's great thanks Frank. Do we have an encampment nearby?''

``No. The closest one is that town in Costa Rica that we had our largest medical facilities. You remember it?''

``I think I'm going to head down there to regroup and see what I do from here. I'll leave you to your duties Frank. You have vodka?

``Heh. One of those days. I absolutely got the hard stuff. Straight up?''

``Straight up.''

Frank served some more then went into the kitchen. I could see he went into the office. I figured he went in there to radio me some new certs. I kicked it back and relaxed. I'm still hungry but I can hold it for a while. I wish I could get rid of the hunger I'm just not the evil corrupt vampire I was meant to be. I hate my life.

Wow Frank is taking forever. It should only take 20 minutes at the most for him to get new certs I've seen it done before. It's been over an hour already. I gotta see what's up. I can't just walk through the kitchen someone might stop me and if any of the kitchen staff sees him obtaining new certs it would compromise his cover. I need to go around through the side door, I remember a window on the office when I made the kill on the teen. God help me.





















As I sat brooding a little girl came around the corner.

``Are you the vampire girl?''

``Why yes, yes I am my dear.''

``You're not dead?''

``It would seem not. Whats your name?''

``Maria, what's your name?''

``Susan.''

``I didn't know vampires have names''

``We do. We were people once too.''

``I'm told vampires are bad monsters''

``We are. vampires turn people into other vampires and they become monsters.''

``You don't seem to be a monster, except you eat people that's very bad''

``Yes it is, and I'll need to eat more people soon I'm very hungry''

``Please don't eat me''

``I won't. I'll eat someone else.''

``There is a jail north of here. There's drug dealers and other very bad people. You could eat the bad people.''

I smiled at the little girl. ``Thank you! I'll eat the bad people for you.'' I give her a hug, and soak her with the blood on me.

``ew.''

``sorry. I'm going to go eat the bad guys now. You should go back to your mom I wouldn't want to see you hurt by bad people out here.''

``I will. Be careful Susan.''

So she ran off to her mom, and I double time it to the north of the village and there is one hell of a prison there. This must house baddies from far and wide. The walls are high and topped with razor wire. I pass the wall by going to noncorporeal form, I don't think anyone has created anything a vampire cannot pass. The yard is empty, it is still the middle of the night. I'll try and avoid the guards I don't want the people of the village hurt, they need to be protected from these bad guys. I return solid after passing the wall to conserve my energy. I duck and weave around the floodlights in the guard towers. I'm able to sense the cells, and it's nearly 3am. I don't have long. I pass walls into and through four cells devouring inmates claw and fang before the sun starts to peek out. I thought my skin was going to burst into flame! I seen the solitary cell in the back and fled into it right through the open door for speeds sake, closing the door behind me. I left a trail of smoke behind where my flesh was burning. I perched myself in the cell's ceiling for a rest. Yes I seem to be able to find rest in pretty much any position. I haven't been able to sleep though, not since I rose from death.

The shout went out and the alarm rang in the prison at about 9am would be my guess.

A guard entered the isolation cell, the sunlight leaking into the cell caused my skin to begin to burn. It was all I could do to keep from yelling out from the pain. The guard looked at the walls, then down at the floor. Fuck, some of the blood fell off me onto the floor. Just a couple drops but I think I just blew my cover. He looked up! Before he was able to yell out I had my hand around his neck. I dropped from the ceiling and shut the door from the pain of the light. He's mine now. I tease him a little, a nibble here and a tickle there, followed by a deep deep kiss. He took a truckload of venom and went under fast. I whispered my command to him and let him go. A command to forget. He left the room a little red around the collar and called out the all clear. I'm good for now.

The jail was rather busy that day while I hid. There was a significant amount of fear, fear that the reds were back. A fear that they never really left but only drew back to regroup. I'm causing chaos here and it isn't what I want at all, I'm just trying to get by long enough to overcome my present state. As night fell I peered out into the jail. There are guards and volunteers taking shifts on the floor, armed with goddamned incendiary shotguns and holy items. Looks like holy oil and water as well. I'm pretty much fucked. I look for the guard I enthralled but I don't see him anywhere. I need to get the hell out of here somehow.

I can go non-corporeal to pass walls and doors but I have no fucking clue how to stay in that state to do anything else. It's not like I have a full red court master or mentor to teach me the ropes. Not that I want that, I just want back to normal. So I look around, the cells of the inmates I fed on are empty now, off to my right. 4 stories of row upon row of cells are to both sides of the hall facing forward, continuing for 20 cells in series. Twenty people sitting or sleeping in the main hall here sweeping flashlight and naptha lanterns. It's well lit in here tonight.



