%scene development
\lettrine[lines=2,lraise=0]{J}iminy the cricket from hell only just turned slightly by the time I threw aside my firearms. I was in the air at full speed. I threw my arms apart and extended my scythe like talons. I kinda felt like the female wolverine Laura Kinney. My talons aren't adamantine and yet I had a shit eating smirk thinking about that as I pounced.

It was only a brief thought though I had some serious ass kicking to attend to. One of his raptorial arms came up toward me and I made like an olympic high jumper and bent over his swing slashing at his arm. The creature roared but my hit was quickly healed over. I need to keep it busy but the kabar is the tool that is going to get the job done here. He can't heal iron or steel. My talons are neither iron nor steel.

I land on it's thorax talons first, plunging both my arms into each side of it. Another roar and it thrashes around like a wild stallion. I'm holding strong to it's back as I'm thrown about, my legs thrown skyward and my hair twirling about me. Part of it's thorax tears loose and I sail into a tree as it roars in pain. I use my talons to spin around a strong branch and into the air, coming down gently using foot talons to grab and suspend myself inversely on the same branch. I shed my skin and go true form to allow me to fight better although my new clothes may never forgive me. My boots for one will be cool and breezy after today.

The creature skitters around on the ground peering up and making chirping noises. I think this is my chance. I grab my kabar in my right hand and ready talons in the left. The creature loses interest. As it starts cleaning itself I have a break in the action. I'm getting rather hot in this uniform. I haven't worn anything since my change so for now I take off the uniform keeping my weapons close. A get myself closer and grabbing my kabar I release from the branch and land the blow above the thorax but not quite to the brain as I wanted.

Suddenly the creature leaps to the treetops taking me with it, the thorax parts revealing wings and it flies straight up. I hold on rather than fall but after a few hundred feet have come between me and the ground I'm thinking maybe falling a hundred feet may have been the best option after all.

Only a fool fights in a burning house, I can't kill this thing if it means I'm going to fall hundreds of feet to the ground. Oh sure I might just heal up from it but I'll still feel it and at this height the force of the fall might sent me straight to hell whole and in person. It is still bucking against my presence so I stash the kabar and strike talons hand and foot into the creature. I'm rolling side to side and upside down this creature can't get enough G forces on me to throw me off.

It dives hard and cruises through treetops. I'm getting hit by leaves and branches. One solid hit knocks my grip loose and makes the creature scream as my talons tear into it more. Then another branch knocks all but one arm free of the creature and it pulls up hard loosening my grip again.

I plunge in more talons and it dives again throwing them loose, it plunges back into the treetops and up again, my grip on the creature is slipping. It climbs very high up in the air again and it dives. My grip fails, and the creature is flying away.
%scene disaster

I'm falling full speed to the ground, and there's not a damned thing I can do to stop it. What happens when I hit? I would presume I spatter and start regenerating but the question is for how long? A very long time indeed. The sun would likely end me when it rises unless a footsoldier ended me with paranormal munitions like a jar. There isn't anything absolute about being immortal, just because I can heal anything doesn't mean I can't be doomed. I'm learning that quickly enough.

%sequel emotion
The dawn is starting to erupt on the horizon, I can feel myself burning. I hate what I am. I want this existence to end I tried to save my world but I only led it to disaster. I gave my life for nothing. I shouldn't be here. As the ground became closer I could picture it as paradise. A final escape to a senseless existence. What am I even doing here? I could convince myself I was some kind of hero but everywhere I go is death and who's to say I might not cause just as much death as lives I save? I think I likely will if my every encounter is like this. It never ends.

%sequel thought
Yet I've always made it out somehow. I think it might in fact be futile to believe that I can just let go and die and be done with it. I did that once to kill myself and destroy an evil empire just to become like them. I think dying is a bad idea here. I don't know what I might become.

%sequel decision
OK, so try to live we shall. How to not go schmuck, that is the question. I have only a few seconds here. There is some dense foliage off to my left I just need to get over there somehow. I've never done freefalling, I have no idea how to navigate. I'm kicking my legs and swinging my arms and the only thing I'm heading towards is a clearing.

%sequel action
Bloody hell, I'm thrashing trying to figure out how to move.

I'm thrashing and swinging my arms.

I'm kicking. I'm feeling numb. I'm feeling funny.

I'm flying. What the fuck. The pressure I was in forced a new change on me. I got within seconds of the treetops and felt myself pull up like I grew a second set of legs. Not legs, wings. I can feel the rhythm of wings now, working involuntarily like any person might breath. Controllable but automatic.

I flutter in to land at my belongings. Screw the insectoid, I wouldn't get anything out of that fight anyway. If others got in the way they would get hurt. I'll splatter the bug later if I can. I use a mirror from my pack to look at myself. I must be damn near ten feet tall this way. I'm me, literally. I look older than my previous form which is a snapshot of the way I looked a decade ago. My skin has a slick sheen to it. I have wings, feathered and black. With my normal complexion I'm dark anyway so it all matches well. All in all I look like some kind of fallen angel, beautiful and muscular and naked as the day I was born.

I grabbed the cloak-tent the insectoid was wearing and used it as a kind of olive drab tunica.

%sequel review
Ok then I came into this actually not to beat up a random insect demon but rather to save some people who were under attack by them. I need to see if they got away OK.
%sequel analysis
I need to change back human again so I don't freak anybody out. I'm not hungry so I won't need to worry about that.
%sequel planning
So I change back to human, and throw the cloak over myself to protect me from the morning sun. Oh God I'm so hungry.
%sequel decision
I need to feed right now, then I'll save the rest.
%sequel action
My nose is in the air, smelling out prey. I see in the area immediately ahead where I first seen the demon there are two live humans.
%scene development
I dash in and make the kill. Being satisfied enough I shake off the need and go to save the other one. She is smiling and stroking a necklace with a set of red court fangs on it, whispering something profound. I say, ``Are you all right?''

``Is Daniel OK? My friend over there? He's going to make it I know it. He's so strong.''

%scene disaster
I shake my head sadly.

``Oh no! Oh Daniel. You've been so brave.''

She proceeded to describe how she was being stupid in her curiosity and made the creature take notice. Daniel was the one who tried to fight off the creature and save her. I feel like a real asshole. I change the subject.

%sequel emotion
``Are there any more of you?''

``There are six of us left altogether. My name is Jill.''

``Who are the others?''

``Jack, he is a big guy with a flat top haircut. Don't go to him, let him come to you. Vinny, the italian guy. He was with the fellowship once, but became lost. George, he's a gay stereotype. Craig, he is tall, lanky and unkept. He's also very awkward and clumsy with a stutter. Veronica, who is a real princess, terrified of everything. She would wash her hands all day long to keep germs off. Finally there is Laura, she has no hair. She is always in pain, it's so sad. I hope she finds someone it would make it so much better for her.''

I say ``Oh. Cool.'' Then begin a little smirk that ended in a smile. I've found some company on my quest. I say, ``Do you think they will accept me?''

She said, ``absolutely! You are a very strong and good soldier, and we could use a soldier. The closest we have is Jack and he is more of a suicidal berserker.''

``Well done deal then, are we able to catch up and find them?''

``We have an emergency rendezvous. We are travelling south to a large fellowship encampment. It moves around a lot but I hope it is still hidden away there, some fellowship soldiers we moving that way a couple days ago and said where it was. The rendezvous point is due north, about a kilometer. Are you OK to travel?''

``I think the question is are you OK to travel. You are a fright girl, with your clothes torn up.''

``Sadly that's the way it is for me. It wasn't the encounter but rather that I'm a hobo like the rest of us. We work long enough for food but then need to move on. All of us are disabled or ill in some way and can't hold down a job much less be accepted by any town.''

Now I really feel like an evil bastard. I ate one of these poor people. I say, ``Well off we go then I guess.''

``For sure lets get going. They will probably be heading this way in a day anyway so we will probably meet up. That tent cloak, can we use it?''

``Yeah, it's a glorified tarp, blocks light and likely will hold up to wind and rain quite well. I figure it's a two man size.''

``Great! Let's rest the day out of the sun and start tonight. We can just throw it over us so you can stay out of the sun. Er, I mean, get some rest you must be exhausted after that fight.''

``Umm, yeah. Tired. Ok.'' How does she know about the sun? Does she know something about me? She doesn't seem afraid so I guess not.

I say, ``Jill, what is that odd necklace you wear?''

``Oh, please don't be offended, I used to be a red court thrall. My last master was slaughtered by the fellowship by fire, and I harvested his fangs and wore them under my clothes. After the cataclysm when the reds were destroyed I wore them exposed to remember. I have had two masters, the first beat and tortured me, many of my fellow thralls died needlessly in his service. He traded me to my second master in exchange for some service. My second master was cruel but did no more than beat us, and only for reasons he seen fit to do so. I suffered under him but not like the first and he provided me the venom I needed to stay well even as I provided him my own lifeblood that kept him nourished. It is a symbiotic relationship really.''

My stomach turned at her words, but I tried not to show it. ``You are addicted though, that's why you revere him right?''

``I've been through my withdrawal, I revere him because he was my medicine. I have a mental illness and no medicine helped me. His essence kept me in balance. You cannot possibly comprehend the suffering I endured before I was enthralled, everything I've endured with the reds pales in comparison to the suffering of my sickness. I am indebted to them, and since the cataclysm long for their return that I may find wellness again. I hope it doesn't offend you. All of us were enthralled, all of us survived the withdrawal, and all of us are becoming sick again. Do you understand?''

``Honestly I can't understand. I can accept what you say though in the deepest sadness.''

``Let's rest then until sunset.''

So we did. She was out in the sunrise without burning so I believe her. I'm worried about the fact she wants to keep me from the sun. Did she see me kill Daniel? As we rested she spooned me. It was a little uncomfortable that she wanted to get so close. I was worried that she was some manner of phobophage that I didn't know so I looked at her with vampire sight. This is something I had even as an infected. I learned to gain control of it back then and it turns darkness to a kind of twilight. The sight has a number of additional features since my change, uncountable features that I don't understand. I know what a human looks like with this new sight though and she is definitely human. I can feel the warmth of human lifeforce from a distance as well and that lifeforce is definitely in her. I get the feeling she may be trying to tempt me. Either she is lesbian or she wants me to drink. I won't make assumptions.

``A little close there Jill, I appreciate the comfort you are giving me and I sure don't want to put you off but I really would only like to be friends. Out here though a person could use deep friendships to deal with this post-apocalyptic nightmare. Are you OK with that?''

``Uh, sorry I didn't mean to-- oooOOOOooo right gotcha sorry, my mistake. Of course I'll be a friend.''

``What did you do before coming here, I mean, like before getting enthralled.''

``I was a lifecoach. I worked with some of the greatest people in hollywood. I inspired them, listened to their woes and gave sage advice. When I started getting sick I started falling into psychosis and my sage advice started getting more and more profound. The trust my clients had in me leant them to believe me when I spoke of aliens, pending invasions, hidden knowledge in physics research being held from the world by corrupt governments. They were wearing talismans I made for them, drinking potions and burning odd incense. It was only after I was picked up wandering the streets spewing word salad that they took me to the hospital for treatment. No drug worked I was in there a couple years crying, screaming, sedated, in electroshock therapies. Yet what was going on inside was far worse than what could be seen, unless someone lived it they could never know. A kind hearted nurse was infected and made her first kill in there. She changed, she became the opposite of what she was, cruel, heartless, powerhungry. She took me as a thrall because I was convenient and travelled south to her new people. I guess everything else was history. I was well as a thrall as I said before and even with my addiction broken I would give my life for that medicine again.''

``My story is rather different. I was a journalist writing stories about the paranormal. I snuck into a vampire ball with the love of my life, a wizard. The ball was for the promotion of a female vampire to nobility. She had a grudge with my wizard and infected me to tear us apart. It did. I was afraid I might kill him so I joined the fellowship down here. My daughter was abducted by the reds and I came to set her free before she was sacrificed. I lost control and made my first kill. I started changing, my lover killed me as a sacrifice and since it was a bloodline curse the reds, all of them, died. It worked because I was the youngest full red court vampire yet my change did not complete.  The vampire part died so like other younger fellowship members I just got cured. Then I just came back to life. Sort of. I guess. I really don't know, so sue me.''

``Sort of?''

``I'm not quite the same. I'm still human by nature, I think like a human. I'm not corrupted I don't think. Honestly I'm still learning. I'm not a red, and I'm figuring out what I actually am.''

She seemed to deflate somehow. Not being a true red court vampire she figures I'm no cure for her ills and I just don't know about myself. I don't know if I could help her. I sure don't want to enthrall her out of chance, I abhor the practise.

She said, ``That's lucky for you. I hope you find your path in life and use your new nature to help people who most need it.'' I think that was a poke at me to give it a try just on the chance I might help her. I just won't do it.

She said, ``Well, if I ever do find my vampire despite all facts to the contrary I would be a loyal and caring thrall for them. They would not need for anything if I could provide it to them.'' She kissed me on the cheek, rolled over and went to sleep. She slept like a baby and I just laid there. I'm conflicted.

%sequel thought - review
I guess I could try. It's just for me, it's almost like euthanasia. It's horrible. I've seen so much down here, I've seen the horrors of enthrallment and the treatment of thralls. 
%sequel analysis
Based on what I've encountered so far though I really need help. I could mislead myself in believing I'm a one woman panzer and ready to plow through all enemies to get to my destination, but if fate hadn't intervened I would be dead now. I'm not an island. If there were others with me they could have distracted that thing and I could have had a chance to sink in my kabar where it mattered.
%sequel planning
So I need to move north with Jill and meet these new comrades, assuming they will take me on.
%review
Jill to her credit is really snuggling up to me. Literally. She thinks I may be her salvation and the others may think the same. I would say I'm a shoein.
%analysis
The trouble is they may do exactly as Jill and snuggle in to entice me. Jill will undoubtedly reveal to them I may have the old red court juice they feel the need so much.
%planning
So I would need to make kills. I would have to avoid enthralling them by staying fed some other way. If there were enough encounters I might not even need to make a kill just sip as I go along. I would not addict anyone.
%review
Jill told of her suffering though, I'm not sure if that's fair.
%analysis
I guess the only thing is to try. Honestly try to avoid feeding at all. It could work, just push my boundaries, maybe I can break the cycle of feeding somehow.
%planning
I need to try refraining from feeding as much as I can, the need to feed covertly will help.
%decision
So feed only if I have to then.
%action
Night comes, I make sure my bag is packed and fold the cloak tent to wear. I give Jill a hug and she purrs. The two of us head north to meet her people.

Death is everywhere now. We seem not to hardly travel a half mile without seeing one corpse if not more. I hope they aren't black court victims but even if they aren't these people are still dead. Some are suicides, others killings, some have been eaten by things natural and unnatural. Things unearthly show the signs of their passing raising the hair on our heads. There are things in this part of the world now that can only be said to be wrong. Just wrong in the sense that there are things that simply should not be walking these fields of slaughter. 

%goal
I may not feel that I can morally provide them the venom they feel they need but that doesn't mean I can't be part of their group. Why would they even know about the vampiric part of me anyway, not unless they see me feed. 

%scene introduction
Jill said, ``We always pick a place to meet every mile or so. We found this old abandoned hunting cabin as a waypoint so we could flee back to it and meetup.'' We passed out of the underbrush and found the cabin some twenty to thirty feet away. Jill went first and her crew turned around to greet her and I came right behind her.

There was a low powerful roar from what looked like a real life rambo, ``mugger!'' Then I heard Jill yell back, ``No Jack! She's OK it's our new friend Susan!'' Too late. Just to illustrate how goddamned powerful Jack is he had a tree up by it's roots and thrown towards me before Jill's words registered. I leaped backwards as the tree flew within inches of my nose. I felt like I was in the movie matrix, the adrenaline slowed everything down to the point it felt like an hour for me to hit the ground on my back. I rolled over to face Jill's people, most of whom with their eyes wide as saucers were asking me, ``My God are you OK?'' I walked toward them carefully, and said, ``Jesus Christ!'' without meeting Jack's gaze. I was thinking about wolves and how meeting the alpha male gaze is considered a challenge. I don't want to challenge Jack, it might hurt.

Another one walked toward me and said, ``Fucking ass, Oi, Fuck.'' He extended his hand smiling in order to shake mine but somehow seemed to be genuinely greeting me. As if something was shortcircuited in his greeting mechanism.

Another guy came towards me skipping like a little girl and clapping his hands, ``Oh you have such a wonderful complexion! Your outfit is sooo embarrassing but that hair is to die for! Where do you get it done girl? My name is George'' He came right up bypassing the handshake and hugged me tight, kicking up one leg.

One girl wouldn't look at me but rather asked Jill, ``Oh my God Jill, did you wash her before you decided to take her home? You don't know where she came from!'' to which I responded back, ``I flew out her ass.'' The girl turned back to me and said, ``You bitch, who invited you here?'' Jill looked at me and said, ``Here is Veronica. I realize she is difficult but she is a tad paranoid.'' I said, ``I can tell.''

One girl was bent over wearing welders equipment, modifying a rocket launcher. She said, ``Quiet, my plans are nearly complete. With correctly enhanced ordinance we will finally conquer and rule this land!'' She would seem to be some sort of evil mastermind. Always helps to have a pet super-villain on duty. 

Then finally a tall lanky fellow walks clumsily toward me. He trips, his rifle goes off, the bullet hits a tree limb above his head which then falls. Then it hits him on the head knocking him flat to the ground. The rest of us dive for the ground not realizing at first where the gunshot came from. Once we perceived what happened Jill said to him, ``Oh Craig, always the same with you isn't it dear.'' All I could say was, ``Oh Christ.'' What a motley crew Jill's people are.

Introductions done, Jill said, ``Well it's getting towards sunrise so why don't we go into the cabin and rest today. We can head out tonight where are you going Susan we'll tag along and keep each other safe?''

``Well the best I can figure I'm going to head south, I want to get the hell out of here to somewhere that's safer. I or we can do a lot more to help here from outside, if we stay the only thing we can do is die. If not today, eventually, and soon.''

``Agreed then. Veronica I want you to put sheets up on the windows to keep the sun out so we can rest. Make sure not a ray of sun enters in on us.''

Veronica said, ``Why would you bother to block the windows none of us have ever cared one way or the other\dots'' Jill looked unwaveringly at Veronica and her eyes lit up. She said, ``OOOooo, really? Well damn you're right we never sleep right in sunlight do we. Excellent idea.''

%scene disaster
The rest of the people looked at each other unsure of what that exchange was about and then I could then see the slow realization in their faces like a man having walked through a desert discovering a babbling brook. Nobody let me in on the wonderful news though. Maybe it's better I just didn't know. Way down I feel like I already know the creepy truth.

%sequel emotion
%sequel thought
That first day everyone talked to me like I was the cool kid in school, wanting me to like them and working hard at it. It gave me a chance for us to get to know each other and I considered it a good thing.

The next day I was walking with Laura as we were heading south. The first thing she did of course is curse having such a simple-minded companion, and then said at least Jack might prove useful. Between her and George it's going to be a very affectionate journey.

``So then \dots , you like the clean look? I mean clean shaved head. It's cool.'' I said.

``Well actually, it wasn't that long ago, well actually it was quite a long time ago, I fought my way through cancer. There is quite a bit of pain even now and my hair never grew back. Being, Er, of use to the reds relieved the trouble. No pain, regained my hair. They were evil, that I know, yet I miss them. Part of me wants them back.'' said Laura.

She seemed unexpectedly forward, like she is actually trying to connect with me unlike how she treats the others. I say, ``Man that sucks. What's everyone hoping to find south of here?''

Laura said, ``Well, I can't speak for everyone but for me I hope either the fellowship encampment south has found a way to replace the need for the red court people have, or I will attempt to find the answer. That way I can fulfill my manifest destiny to rule. Unless of course I can find someone who can help me in a more old fashioned way.''

``Like a different diet you mean?'' I said.

``No I make sure to eat well, I'm clean, no diseases and I take good care of myself. I'm good and healthy and \dots'' Laura said.

It creeped me out a bit when she turned to me with an overly warm smile. I shrank away, and slipped over to chat with Craig. He turned his head toward me and smiled as I approached. The side of his head hit a branch as he walked. He arched his torso back like a high jumper and flailed his arms one of which grabbed hold of the trunk of the tree. He wrapped himself around the trunk then spun off it like a dancer who just executed a dip. Finally having pulled himself back up he straightened his collar and continued on loose legged like he just put on a show for my entertainment. Admittedly I was entertained, curling up a little smirk due to the little spectacle. Amazing. Like a real life Kramer in a way.

``Hey Craig wassup?'' I said.

``Nuttin' much. Hows you?'' He said.

``So what's your story? What did you do for a living before stuff happened?'' I said.

Craig hung his head in sorrow. ``Once, a lifetime ago, I was a doctor. I was a neurosurgeon in fact, sought after by every cancer patient in Los Angeles. Celebrities and tech tycoons from all over the country, hell all over the world were knocking at my door. When I was enthralled my master sought to teach me the evil of too much sugar in his coffee and beat me about the head with the leg of a coffee table. Something was damaged, I have no balance, spasms, falling all over myself. I was better when I was fed from, and I needed it regularily in order to have some semblance of a normal life. I wonder if he knew what he was doing would make me all that much more dependant on him? Probably not. He wouldn't care either way, I was just a dog for him to beat.''

Craig kicked the dirt, grabbed a large tree branch and threw it far into the darkness of the night.

I felt like shit. I tried not to think of the fact that I inherited much of the red court legacy. It would be such a glorious thing to be rid of it all. I timidly put my hand on his shoulder and patted him in an awkward attempt to comfort his anger.

``I really can't say I can understand, that would be insulting. They have hurt me too Craig. I had a wonderful guy and my infection tore us apart. I fought down here for a decade and by the time we met again we were almost strangers. At the last day at \chichenitza* I was left for dead. I hope to meet him again, find my little girl and start my life again. That's my story, so far. God it sucks down here.''

Craig said, ``No shit. I thought it was bad before the fall of the reds but we hadn't seen nothing like the hell that we see now. The worst atrocities in history are happening here and nobody outside of these jungles have any idea.''

I sigh, and shake my head, and say, ``It's always been that way. Nobody cares what happens down here. The middle east is having a melt down in terrorism, and the whole world is watching. Is it about the oil? So stupid. Like what has to happen down here before the world is willing to see?'' I punched a tree hard and it tore open. A twenty inch diameter tree.

Craig said, ``Damn girl, that's quite the left hook you got there. Remind me not to piss you off. What are you carrying with you? They touched you somehow didn't they? Everybody here thinks so.''

I looked at him wide eyed, ``I guess I do, what are the others saying about me? I'm getting bad vibes man.''

Craig sighed, and said, ``Well, we think you might have the venom. That maybe you could heal us. We know the reds fell, the sky was like Armageddon. The sun eclipsed and filled with fire and lightning. We seen them all drop, those who didn't found out by word of mouth and the abandonment of their strongholds. Everyone knows. If you have what we think we will stick to you like glue and protect you to our death. You can be sure of that.''

My heart sank. I hung my head low and said, ``I don't know what all I am Craig, or what I can do. I'm not entirely like them, I have talons. Well I guess maybe, well OK I am carrying their legacy in me to some degree. I just don't want to hurt you guys. I think it would, if I do have the venom and I don't know. I hope I don't really, I could kill you if something isn't right with me. Maybe I might kill myself with some kind of feedback from the attempt. I don't know what I am Craig.''

Craig pursed his lips, and said, ``You're right, we are willing to die but there is a remote possibility we could kill you. That isn't what we want. I'll leave you alone sure enough Susan if it is as you wish but the others are going to try to tempt you to feed, the only thing they care about is being healthy again. I understand how they feel. I think you might too, deep down.''

I nodded, ``Yeah I do. I am conflicted over this, honestly. I don't know what is right here. I know the evils of the venom but I really didn't consider where it might heal others as well. It just doesn't make sense to me.''

We continued through the bush heading south, bodies in various stages of decomposition were scattered in our path. We raided the corpses for ammo and supplies along the way. Every so often we heard a noise and dove for cover, only to find out it was some local fauna, and we sighed a breath of relief.

When it was coming to morning we camped. They had a ten man canvas tent, army issue, no light dared to either enter or leave the old monstrosity and yet they took my canvas cloak tent and gathered it around me all the same. I felt like a unicorn discovered by a team of zoologists, overprotected.

Inside a small coleman lantern burned, and Jack was shoring up the tent from the inside. As he was circling around to where I was he accidentally got a sliver from one of the wooden spikes. More than a sliver. He used his ka-bar to slice open his palm to remove it. Blood splashed onto the ground. I had to cover my eyes. I whipped my head around but the arousal of my body and animal like sniffing of the air was apparent. I desperately tried not to but I released a vampiric hiss. A quiet one. Jack clearly heard it though. He said, ``How much longer can you hold it lady? We'll break you, we need what you got.'' Damn. This doesn't sound good.

Renewed whispers rippled through the camp, and Laura snuggled up to me. She said, ``We could rule the world you know, you and I. I have the knowledge, and the willingness to help you reconquer this land. We could be invincible.'' After she bit her lip hard. A stream of blood accumulated. I covered my eyes and convulsed, rolled over and bit down on an iron spike. They have a kind of blood like taste, being iron and all. It helped only a little bit. It was like hard taffy to me, which helped a little more being something to chew on. I was sweating profusely for a few minutes, breathing deeply to calm down, hissing gently. I'm not going to be able to stand much more of this, it will twist my mind up. The hunger cannot be perpetually ignored.

I just laid there, no sleep for me. I'm starting to smell them. I can smell their humanity. I can smell their blood. Only mildly now but it will get worse.

Later I checked my watch and it showed 12:00. Oh crap! I got everyone up, we are way late getting going. It's already halfway through the night and we wasted hours with me just sitting there and them sleeping. All of them groggy, Jill said, ``What's up Susan? We have hours before we need to leave.

I said, ``No we don't it's midnight already we have to go!''

She said, ``What? My clock says high noon? So does Jack's Susan. Wait! No don't go out!''

Sure enough it was a bright and sunny when I leapt from the tent. I covered myself and rolled into a ball, crouched, and was close to leaping back for the tent. Then I realized I'm not burning now. Ever since my transformation fighting the cricket demon I tried to enter into that angelic form again but couldn't. I don't know how I did that. Yet I believed I might be changing, growing somehow, into something unique. Growing into a beast not before seen. It seems some part of what I predicted is true. The fact that I'm growing and changing. As of this moment I'm unaffected by the sun, whether or not it stays that way it's hard to tell.

I relaxed my crouch and stood up. I looked skyward to see my long lost love. I was a sun worshipper in the m modern sense when I was human and infected. I would lie out in the sun and tan endlessly. The warmth on my skin was wonderful, it made me feel normal again. The sun eased my hunger slightly too, but only slightly. The other members of the crew leapt out of the tent expecting to see a smoking puddle and seen me standing there staring up at the sun. They all hit the ground on their knees and planted their face in the dirt. A spontaneous reaction for thralls I expect, only the most elder and powerful of the reds were daywalkers.

I stared at the sky and said, ``This is new. I wonder when I became a daywalker? It's OK guys I'm not old. Seems like millenia but really it's only been days since the wierd shit happened at \chichenitza*.''

One by one they looked up, and sat there staring. I said, ``I'm gonna hang out here a while guys go back and sleep. I wanna learn more about this if I can.''

Jack said, ``Look lady this ain't safe. If everyone's OK I'm gonna take over sentry, I got the beef to handle shit.''

The rest looked at each other and nodded in agreement.

Jack said, ``Right then, here's the deal lady if there's a problem I'm putting you back in here by force if I have to. I don't think anyone here would disagree we would all die trying to help you if you even so much as stubbed a toe on a rock.''

I said, ``OK I hear you Jack. No prob.''

So I rolled things up and did some sunbathing. It felt so good, it seems like it's been a lifetime.

