\lettrine[lines=2,lraise=0]{C}lang! I look up and Bones had swung his rifle in the path of the katana as it came down, tears flowing in Jamar's eyes.

%scene 2 disaster continued
Bones said, ``Goddammit Sarg, I hearby relieve you of duty Sargeant Dwight Miller on cause of madness. Jamar you will take leadership of this team until I deem Sargeant Miller to be fit for duty again.''

Sarg said, ``You have got to be kidding, don't fucking joke Bones I ain't in the mood and there's an enemy among us. Jamar get it done.''

Jamar said, ``No Sarg, he is our medic and he has the authority. You are acting mad right now and you need to get your squirrels out.''

Sarg said, ``What a goddamn clusterfuck, you people have a goddamned screw loose she must have poisoned the rations, or you all got enthralled! Bloody hell that's it you all are going down.'' He pulled forward his rifle and clicked off the safety, ``for the fellowship, for justice!''

I didn't know if I could do it but I know the reds could hypnotize by looking into a humans eyes, control them from afar. I quickly raised my eyes to meet Sarg. Instinctively reacting to my intent the black vampire eyes unveiled themselves as my third eyelid covered over my eyes and I could see the world again as no human could. The vitality of my human companions was evident, the health of their bodies and the vision of their blood flowing through them. Their psychic aura presented itself revealing more about them than they knew about themselves if I chose to observe them intently but there was no time and no reason for doing it. My eyes drilled into Sarg's and I pierced his psyche; I pierced that burning red aura that revealed without doubt the sheer anger he was feeling; I pierced the madness that had surrounded him and consumed him. His thoughts lay before me at my mercy, to be twisted by my will but this I refuse to do. I raised my hand and blew a cool breeze from my lips as if I was blowing a kiss and moulded it into a psychic wind that washed over Sarg extinguishing the fire and madness that was consuming him. I could see him fall limp but his fire once again began to grow. Bones grabbed his rifle and threw it while Jamar covered him with his own rifle. 

I'm trying to fall back into a fully human form but it's not happening. I never did anything like that before and I have no experience that would allow me to know how to return. I see the ice surrounding Sarg, the cone of ice formed on the ground from me to him like some kind of telltale sign that neuromantic power was just unleashed. It's inevitable, I'm trying to hold back the ocean as I continue my change into another form. I'm clenching my jaw, I'm holding on for now but not much longer.

Bones said, ``I swore to you that I would keep your confidence Sarg but I will not do so in the face of murder. You have never resolved your pain from the loss of your wife we both know that and I do believe we both knew it would someday cause you to make mistakes. I hoped that it would not cause too much trouble or put anyone in danger but this lunacy is far and above what I thought. I take the blame for that you should never have had a position of power in this fellowship. I pray to God above may he have mercy on my soul for making such a grievous error as this. Now you look at that woman and look real close, who do you see? Who do you see in her you fool?''

%scene 2 disaster continued
Sarg looked at me, wrung his hands and rolled his head. He held his hand to his chin and then I seen his eyes start to grow. His face grew white. He started to shake and turned to the side to vomit into a bush. Sarg said, ``My God, Jennifer! She looks exactly like Jennifer!''

Bones said, ``That's right fool. Your wife. You're trying to bring peace to your wife. Is this your wife Sarg? If it is I weep for you man but I do believe she said her name was Susan did she not?''

Sarg said, ``She isn't Jennifer. She looks like her but I knew Jennifer, her likes, her dislikes, the way she could make me laugh and inspire me every day. My love knew her and still knows her and no this is not Jennifer; this is not my beloved Jennifer.'' Sarg was on his knees now facing me, with his head hung low to the ground he wept.

Bones let out a long whistle and shook his head as he turned towards me. Jamar in his new command declared, ``I'll watch him doc, take a look at Susan she looks like shes trying to shit a brick.''

I was clenching my teeth and now I'm clenching my whole face. I'm feeling dizzy from the effort and sweat is pouring off me. I have tightly clenched fists; my body is trembling. Jamar gave a very fair description. I'm desperately holding off the change.

Bones looked at me and said, ``What is it about today, ain't no full moon that I know. Oh Sarg, goddamit man, what did you do to this poor woman in your mad display. Susan what is going on with you?''

I looked at Bones and said, ``The effort I put in helping Sarg, I triggered something. I'm undergoing some sort of change. I've been holding on the best I can; I can't do it forever. I'm scared Bones. I can't know what this change will be and it scares me.''

Bones looked to Jamar who was close enough to hear me out. Bones said to Jamar, ``OK call it boss.''

Jamar said, ``Right. Bones and Injun take position twenty feet equidistant from Susan. Sarg, we'll cover the civilians.''

Jack said, ``Damn straight. 'bout time you took notice of us over here. We'll grab rifles as well to support you guys.''

Bones said, ``Good. Cry 'Havoc,' and let slip the hounds of hell, Susan let yourself go.''

%scene disaster no-and-furthermore

\parasep

I let go. There was nothing for a moment then I felt a trembling from deep within me. Then like a distant explosion the fire and mania poured through me and seemingly out of every pore. It pulled me into the air; I hovered; my wings broke free from my back and my clothes tore and fell to the ground. I grew to a height of ten feet tall; my body flowed into supermodel proportions; my hair fell out in wild abandon and my legs transformed to a digitigrade stance, with my talons extended. My calves grew sleek, sexy and furry. My foot talons then folded to form hooves. My body was firm and gorgeous like the greek goddess Aphrodite. The men surrounding me left a lake of drool fit to fish in. I stretched my wings slightly. Flap-flap, flap\dots flap. I descended to the ground landing on my pseudo-hooves. The sheer power of my awareness was overwhelming. I lowered myself down to one knee and covered my head in my arms to try to block out stimuli. It was too much for me to process and it took a few moments for me to block it all out. I looked up again, now holding back the torrent of sensations; I am in fear of cracks appearing in that dam I erected; I rest precariously on nothing but my own strength to keep me sane.

Sarg was getting his senses back slowly, enough to say, ``That ain't no red. She be a greek god maybe or some fallen angel but she ain't be no red by God.''

I slowly looked myself over. I grabbed a mirror and seen myself dark with midnight hair flowing like in a breeze yet on this day when the air is still. I've never seen anything like this. I look out over my friends to behold a sea of thousand mile stares, their psyches overwhelmed. I see Spook, but not in this physical world. My eyes perceive an infinity of realities, all time, all places, all things and spirits are within my knowing and all these and more I block out but I see him in a place that is not of this physical plane. Oh yes his body is here but I see that he has been stolen from us and imprisoned in a dark horror of his own creation. Yet in my being, as I am, I know this place to be in my reach; and it is mine to travel; it is my duty to seek him and to find him; it is my duty to bring him home.

I am burdened by miraculous purpose and focus on Spook. I lift myself up on these wings of glory and follow a mysterious path. I flew not in any of the directions of a compass, nor up or down. Into a foreign and twisted reality I flew and the world faded like a thick cloud coming over the sun; it faded like those same clouds passing into twilight; it faded from twilight to night, then from night to the darkness of a cavern in the midst of the earth. Yet once consumed by this new reality I find it is vast, truly endless. My eyes adjust and all I can see here is shades of grey. It appears as if everything here was once alive but has long since become dead. Not even decay has survived as everything has become simply dust, time has had no power to consume that which has been and death has become immortal in all that I see. The burden on my heart is profound, the pain of the descent of oblivion has settled on me. I am raging against the psychological effect of this corrupt and dark environment assaulted by guilt, horror, terror, hopelessness. This place seems to attack me, it wishes to assimilate me into this horrible death that I see before me. I must reach Spook, and quickly, my new form and the burden of this place will soon be too much. I cannot let myself be consumed.

I began walking to where I knew Spook was. I don't know how it is that I knew, I just knew where he will be. Leafless trees and grass still in it's perfect shape but falling to dust as I walk on it with with my hooves. After about a mile I noticed the fur on my calves and some of my skin was turning black. The damned dust is necrotizing my flesh. I leap far into the air and thrust out my wings. I'm going to try to fly there. I'm going to exhaust myself before I get anywhere near Spook. I try extending my wings out as far as I can. I find I can lay out a wingspan of fifty feet and glide like an eagle. Perhaps I will get there ok after all. The landscape below passes quickly but not quickly enough Spook is far away indeed. Far beyond the horizon.

After a few hours I'm exhausted. Flapping or not I cant go on like this. even if I was driving a car I would have to stop from time to time but the ground is toxic I can't stop. yet neither can I keep going.

I must have fallen asleep, or passed out, either way I skimmed the top of a gnarly tree and tried to pull up. I hadn't the strength to. As I neared the ground I pushed up hard with my legs but it was no use. I tumbled to the deadly ground and lay in a pile thoroughly exhausted.

%sequel emotion

I can't afford to lose track of what I'm doing. I need to stay focused and I can't make any more mistakes. I shouldn't have changed, in part or in whole. I drove Sarg to madness and I don't know if he's OK. If he isn't I don't know if anyone can bring him back. I don't know if I can bring spook back. I don't know anything about what I am or what I can do. It seems rather evident to me I'm not going to get to Spook and it's not even likely that I'll live through the attempt to rescue him. I'm an idiot. Why did I plunge into this realm not knowing whether I could do this? All full of valour but without any common sense. So what now Susan? Lay down and die like a fool it seems I can't see any way this could come out any different.

Well, no, I don't need to be a coward either. I'll get my rest then at least I can walk for a while, flesh eating dust be damned. I know where Spook is, I kind of know where I came from. Kind of. At least that's something. What's my chances? ten out of ninety? five out of ninety five? Pretty much guaranteed death. Well I don't know where I'll die out here, so there isn't any reason for being late in getting there.

I pull myself up, and walk around slowly to get the circulation back in my limbs. The necrotization hasn't spread any farther, so I'm lucky for that. I start limping toward Spook.

Well OK, so I can't fly there but maybe I can travel a little by foor and then by wing. Maybe the necrotizing effect of this dust and soil isn't as bad as I presumed. Maybe. The trees are nothing but dust, touch one and it crumbles into nothingness. No help there. Flat dusty surface for as far as I can see in every direction and Spook is beyond the horizon.

I tried moving slower, rolling my hooves over the ground to prevent stirring the dust. It took some practise but I think I can do it. It's hard though that dust is very fine. Also I don't know if my hooves are immune to the necrotization effect. Only time and long travelling will tell.

Flight gives my legs rest, for the next few miles I try alternating flight and travel by foot and it helps. It's sustainable.

That's how I'm going to do this, flight and slow careful ground movement. No need being in a hurry. Slow and steady and hope whatever dust does settle on me has little or no effect on my body.

I decide to try flying at higher altitudes so I can glide farther with less fatigue. It's working. At least until I see something come towards me from over the horizon. I flew too high, and now it seems something has taken an interest in me.

%scene goal
I just need to approach this peacefully, I'm sure this entity has better things to do than pick a fight. This should be over quick and I can continue on my quest.

%scene development
I continued on my way until it came closer. A dragon it seems like but more serpent like, not the typical fantasy dragons. It seemed to be swimming through the air like it was water, and was extremely agile. It was truly massive and the agility it displays just seems to defy what one would expect of such a large creature.

I said, ``Hail spirit. I am Susan and I travel in peace. What might I do for thee oh noble spirit?''

It said, ``I have come to destroy you. I must in order that all that is may be saved. Prepare yourself.''

I said, ``How does that make sense? I said I travel in peace, you think I deceive?''

It said, ``Nay I trust in your word, your intentions are good. I have come to destroy you for it must be done.''

I said, ``Dude, you forget your meds this morning? Who wakes up and says to themselves what a lovely day I should destroy Susan today?''

It said, ``Don't concern yourself with why, I must destroy you, it simply must be done.''

I said, ``What the actual fuck? You need serious help dude. Somebody needs to put you in the spirit world psych ward because I'm pretty sure you gotta be talking to lamps---''

I felt a sledgehammer hit one wing and it threw me into a spiral. I hit the ground hard creating a huge cloud of dust. I stood up after a few minutes and dusted myself off thoroughly.

I don't know where it came from but I heard a booming voice say, ``I am the great Leviathan. You who are known as Susan will be destroyed by my hand.''

Great. You make friends everywhere you go Susan. Especially anyone with homicidal ideation. I threw my arms up in a profound shrug.

I said, ``OK buddy, come get a little.''

\parasep{}

%scene proper
It was rather quick as it came down and nearly swallowed me alive but I rolled to the side just in time only to have it's tail slap me hard and throw me thirty feet into the air. I was breathing so hard I felt like I was going to pass out but managed to pull myself together and fought hard to get my wings to move again. Oddly being slapped around like a hockey puck does wonders for invigorating tired muscles. 

Not even touching the ground after it's strafing run it pulled up and headed straight at me. I went into a dive and rolled in the air again just missing that huge maw, one razor sharp tooth catching me in my side then again the tail hit and threw me another 30 or 40 feet. It feels like it's holding back it's strength but not it's determination. Every attack is more than strong enough to tear me to pieces.

It said, ``You're quite fast, I'm impressed. Yet I'm faster as you will see.''

A snap of the tail and a crack, my shoulder is broken. The shock sent me hurling to the ground. I managed to snap out of shock and flap my wings once at the last minute slowing my descent but still hit hard.

I grit my teeth and punch the ground hard, pushing back my pain I take to the skies again. Being airborne is my only chance against this thing.

This time when it came at me I flew toward the ground, speedily moving out of the way of the giant maw. With lightning reflexes I pushed back up and strafed the creatures torso with my talons as it's momentum pushed it by. I finally got a good hit in, it faltered in the air. It fell into a dive but pulled back up with a fluid motion just before it hit the ground. It pushed toward me with it's talons ready to tear me up. The creature banked to the right and I did a flip that would make any pole jumper proud, right over it's leg. I sunk a talon into the leg as I came down the other side and spun raking it's leg as I planted my leg talons into it's torso. Not to make the same mistake twice it snapped itself around pushing it's maw at me hoping to catch me like a fly on pasteboard, talons sunk deep into it's torso. I was quick enough to use the leverage of those talons to throw myself fast and hard away from the creature as it's maw washed by missing me. Unfortunately it's tail came up hard on me and sent me into the sky like a home run in the big leagues. I felt something snap on my chest and a sudden overwhelming spike of pain. I was in a tailspin again hitting the ground with such tremendous forward motion I felt like a commercial jet making a crash landing in the Mojave. I was tumbling like a stone.

When my body came to rest I checked myself over I seemed to have broken about every bone in my body. Broken bones were protruding from my wings, one arm and one leg. I'm done for.

% scene disaster
Leviathan came in for a final attack, I didn't feel the hit, it was just lights out, game over.
















