I awake. I'm feeling very groggy. I hear a voice say, ``Ah. Good, you're awake. How are you feeling? ''

``Like roadkill. Where am I?'', I said.

``Mount Sinai hospital, I'm Dr. Steve and I've been assigned to your care.'', he said.

I looked around, a hospital bed lay next to me with the privacy curtain partially drawn. I can hear staff being paged in the hall and a nurse request button is clipped next to me. I looked and I'm wearing a hospital gown.

I said, ``OK. What happened? ''

He said, ``From how I understand it an Englishman called an emergency on an inbound flight and emergency services brought you in here in a stupor. We were told you were witness to a firefight and shortly after were advised of the death of someone close so it makes complete sense for you to need to be here. I prepared something to take the edge off the nurse will bring it in shortly. As it is I don’t see why you shouldn’t be out of here in a short time we just need to get through this crisis.’’

I said, ``Easy for you to say. You didn’t end up in an asylum all broken in the head.’’

He said, ``It’s not an asylum at all, you are still in the hospital as an inpatient. You can leave tomorrow if you wish but it would be against my recommendation. Let us do our work, you won’t do anybody any good if you leave just to crack again. Consider this a place to rest a while, a time out, or going on strike. You’ve been through a lot, most anybody would be here as a result.’’

Whether it was a week or two I can’t remember, the doctor was right it was too much and I popped my lid. The second night I grabbed a book from the book cart that rolled through the wing every night. I weaved some baskets and coloured some adult colouring book then the afternoon I read in the fireplace room. There was some excitement a couple times including one patient who needed over 20 security guards to subdue. She of course went to the bubble room for the night after some injections. The funny thing was she was a tiny little young woman who looked incredibly innocent. I guess you never know.

When I got out I borrowed a copy of the book and finished the read in central park. Dammit it had been so long since I actually sat down and read a book, that was therapeutic all in itself. After returning the book I returned to a red court human form from the fully human form so I have the benefit of seeing what’s coming and fighting or fleeing depending on circumstance. I grew up in New York and most people live and work without getting killed it’s not that bad but I have other vampires and perhaps other supernatural beings that could be keen on ending me.

I slipped into a small 24 hour cafe and had some coffee and a snack. I need to get in contact with the fellowship here to figure out what needs to be done next. I think the first thing would be to get myself into some type of media like a newspaper or set myself up somehow with the public that I can use my skills and get influence with the right people, or just simply with people period. I need to work with the fellowship though to make this work, the contingent in New York would know what is best to aim for since they’ve lived here a long time and have been here during the years I haven’t up to and including the present.

As I sat pondering I smelled something quite foul. Like a cadaver. A black court vampire is here. Other customers slowly started filtering out the door and the waitress flipped to sign on the door to closed while she tried to locate the source of the stink. An individual in a cloak and cowl slowly moved over to my table and sat across from me. Glancing outside I seen that the sun had set. It was definitely the right decision to change form.

He said, ``Greetings my queen, pray you do not take offence that I had failed to bow, I thought it prudent not to alarm the humans here any more than necessary.’’

I said, ``Umm, sure, no problem. Are you a friend of the one known as Damian?’’ He might not remember me but I remember him, what a piece of shit.

He said, ``Certainly not, the foul creature. He has been working against your word in promoting the old ways. I am of the empire, one of your servants.’’ He made a slight bow of his head then said, ``I have come to take you to your seat of power below this city of humans.’’

A dangerous proposition indeed, but what do I care now? What do I have left to go back to? Ah fuck it. Maggie has a good family now she doesn't need me. All I could do is screw up her life now, she deserves a normal life with a normal family. Oh I wish I could just lay down and sleep my life away; to not think about anything anymore; to not feel anything anymore; to just be numb for a while; to take a break from this torment. What is the point of existence if existence is pain? If only to escape from it and hide away somewhere the pain cannot find me.

Maybe this throne is a real world answer, maybe I can hide myself in this place that few If any know exists. Maybe here I can escape the pain.

Into the street I followed him, and down into the subway. We travelled until we reached an abandoned station. The lights went out then amid the confusion my companion pulled me out through the slifhtly opened door. The train continued and the lights came back on. This station is oddly ornate, and in all my youth living in New York I cant remember this station at all. Everything is dusty but there are tapestries of rich material. The columns are gold and silver as is the floor. As far as I can tell it is no veneer. The cathedral like ceiling is gold with a profuse adorment of precious jewels. i dont imagine even the most powerful human could never imagine to have ownership of anything so rich and beautiful.

``I never caught your name'', I said.

``I am known as seth my queen.'' He said.

``Why have I never remembered this place when I was young?'', I said.

``Our kind has always kept this place a very close secret. We have sufficient psychic capacity that the sentries here are able to cause humans and some others to simply dismiss this place as inconsequential and forget about it. Mind you unless being used that curtain hides it well.'', he said.

Just as he said there is a curtain that looks like a dirty and old line maintenance tarp. That would indeed work well there is always work being done on New Yorks underground tunnels.

``So what now?'', I asked.

``Now we wait for the royal train.'' He said.

``Yeah, ok. Im real tired can I rest? I have a hard time giving a fuck after recent events. Nothing personal.'' I said.

``Of course my queen. I have been informed. We will be waiting only a few minutes you may rest once you are aboard.'' He said.

``So how long will I be on this train?'', I asked.

``The travel will likely take 8 hours if there are no unexpected delays.'' He said

``8 Jesus we going to Buffalo?'' I said.

``Nay, we are not going across country it is way down we go.'' He said.

``8 hours down sounds like we're going straight to hell.'' He said.

``I must say some have insinuated no less, I dare say not. It is my home no matter how dangerous and it is the seat of your power, your throne. Forgive if I speak poorly my queen but I think you will heal more quickly resting in your own house.'', he said.

just as he said the train arrived in a few minutes. I could never have imagined anything so ornate as this train. It in no way resembled a subway train or any other for that matter. The outside was all stone intricately carved down to the most minute detail. Microscopic detail it would seem. Different stones merged together as if they were one and even the thinest rock structure has held as strong as if it were rolled steel. The outside had the appearance of having rolled through a blast furnace which was a rathet forboding sight to me.

Seth seen me looking at him and said, ``yes my queen it would be wise to remain In your true form especially one we arrive. Any other may serve you a quick death upon disembarking.''

I folded my wings behind me and the dissappeared into my form. His words fell on attentive ears. The inside of the train was no less beautiful than any other. Fine leather and precious metal. Extremely minute and intricate carving throughout. The train had about a dozen segments for sleeping and eating. It also had a meeting area, bar, and my personal room to rest and sleep. It had a tv. I missed tv. it was not ornate in here, a shower, bed, tv as I mentioned, and a stocked beer fridge. I grabbed a couple cold ones, threw on a sleeping shirt and relaxed. The kitchen brought in some pizza, corn chips and popcorn when I threw on some movies when the game was done. How they knew im not sure they brough things in right on cue as if they already knew me. If this is a sign Seth was right. This is pretty damned healing after all the shit I went through. I fell asleep during some action flick and had no dreams at all. Just as I would want. Any dream that would come to me now would be no less than a nightmare. How could it be anything but a nightmare when my waking hours are a nightmare?

It was like no time had passed. I blinked and 9 hours had passed. Seth knocked on my door to notify me 30 minutes until arrival. I've drooled all over myself. First thing I do is jump in the shower and get dressed. I leave the room and head to the lounge car. The first thing I see outside the window is that there is a natural light, a fire like glow, and sparks flowing gently and occasionally bursting out along the train. 

Then I see the tunnel suddenly open into a cavern that has an expanse far beyond the line of sight. Even for my sight. Rock and lava flows, and volcanic activity. Lightning streaks down and hits the tops of tall buildings which are made of solid stone. Solid stone skyscrapers en mass reach far into the height of the cavern.

I say, ``What is this?’’

He says, ``This is the seat of your power my queen, a city beneath New York that is no less the size of New York itself. In this city is your palace and your throne. I realize this is the first you know of this, and that it is hard to take in. We that are your people have sworn to keep it safe since long before any person can remember or any record can speak.’’

I take the pills I received from the hospital and hold them away from me. I drop them to the ground while holding my other had out and swear by all that is holy and true I will not partake in any more of the goddamned poison that would make me have such visions as this.

I say, ``Seth.’’

He said, ``Yes my queen.”

I say, ``I must drink.’’

He said, ``right away my queen.’’

He shortly comes out with a small minibar on wheels. He offers me what drinks there is available. I see a half gallon jug of 40 creek whiskey in the bottom tray and grab it. I try to pour a drink but my hands are shaking too much so I forsake the glass and take both hands to steady the bottle and kick some back like a barbarian. I put my back against the wall of the train and slide down until I’m sitting on the floor. Then take another swig of the whiskey.

Seth said, ``We are still a little less than an hour to reach your palace. We travel at great speed from the mouth of the tunnel across these plains of fire.’’

I said, ``Where are we really?’’

He said, ``To be somewhat more precise we are far below the New York underground and far deeper than the dangerous undercity of supernatural creatures. We sit where the mantle meets the core perhaps 10 miles down. We are as far down as could be imaginable. A place of fire; a place of burning brimstone; here is where lava flows and volcanic eruptions are constant; here as well is where lightning strikes like a heart beating with life; as the fires burn below, clouds of smoke cover the ceiling above and the ash endlessly propelled aloft falls like snow back to the fiery ground below. It is a beautiful place. The unique and rare gems and metals that are surrounding us are mundane here, yet these would be precious metals and gems of the surface world.’’

I said, ``Looks like the goddamned Hadrian era out there.’’

Gulp whiskey.

I laid my back against the wall, and slowly slid down with my eyes wide. I hit the floor and, gulped more whiskey.

Reflecting for a moment on what I saw I said, ``What are the pangolins out there? That cuteness is the one redeeming factor to that godforsaken landscape.’’

He said, ``Those pangolins as you say are our current development of an environmental suit to allow any creature access to the grounds in order to perform tasks. Those who use them have enhanced strength from the powered nature of the suits. They’re self-contained and self-powered.’’

I said, ``Oh. Well pangolins are cute anyway. I’ll just call them pangolins.’’

He said, ``As you wish my queen.’’

We then arrived at the door, so to speak. As it was explained to me the tracks don’t end but rather continue back out in a loop. So we paused at the end of the loop in an antichamber. Seth told me that all access to the environment takes place through an anti-chamber so the heat doesn’t flood the inner chambers. The mystical power imbued in this place allows for dramatic changes in the ambient environment indoors vs. the conditions outside as long as there remains a physical barrier between the two. This particular one is the size needed to liberally contain the train. Torches are lit upon exit and the ground I see is loose gravel of volcanic rock, and there is also a beautiful clean and flawless red carpet leading the way to a large wooden door. A sign above the door reads, ``Abandon hope, all ye who enter here.’’ in latin. I glance over at Seth.

He said, ``Yes I know, sounds like Dante. How was he to know the phrase was already taken? We didn’t exactly have a copyright office during the first half of eternity.’’

There is a crew of around half a dozen who all disembarked from the train. 3 lifted and dropped the door knocker 3 times. I noticed there is absolutely no echo in here, as if I was floating in space or something. I anchored my feet, grabbed the bottle with both hands and glugged the whiskey some more. Damned primevil shit. The door opened, two doors actually I only thought it was one. An overwhelming stench of decay hit me, the air was cold and damp. I heard water every once in a while but no more. There was a slight breeze but I couldn’t figure out where it was coming from. There were support columns ahead on either side of the carpet leading forward. I could see two torches very far ahead with a very large stone throne. The columns were the size of the typical low rise apartment building in circumference which goes to help me comprehend the immense dimensions of this place. I think that throne is a mile away. Literally. If I didn’t have my true form eyes I would never have seen it. That’s all my senses are telling meso far.

As we entered the chamber another vampire, a white one this time, took his place behind and to my right. Seth took his place behind and to my left. Seth said, ``I am the top ranking in your followers my queen. I am called the Master-at-arms. At your other side is Rodney, he is the one called “Counsel’’ in your ranks. We will explain more later. If my queen would be pleased I wish to bring you forthwith to your own chambers to compose yourself. Your’s has been a hard journey thusfar and I speak not of the meager train trip.’’

I nodded in agreement and we started forward. I was able to refrain from the firewater and yet by the time we got to the other side it looked like Saving Private Ryan in how my companions were holding me up to the point of dragging me.

Seth's eyes were blazing. He said, ``Why don't you doff this true human form and end this disgraceful drunken state?''

I said, ``It doesnt work that way. I'm sure I would sober up mighty fast yet it wouldn't matter. I want to be drunk right now Seth. I need to be numb. Even if just for a little while. I can carry on by will or perhaps by a little pill for a time. If that hurt doesn't stop, and the stress has no end don't you dare blame me for picking up the bottle. Things have to be real bad and I tell you and have no doubt when I say things are real bad for me now.''

Seth said to Rodney, ``Her carriage is waiting. I'll advise the driver she requests an expedited transport to her chambers. No stopping along the way. Then I guess we will need to bide our time until she is in a better state to take her city to herself again.''

I said nothing.

The hallways of this castle were no less the size of a two lane highway except it had the finest of carpet and the walls and ceiling were pure gold adorned with silver and other precious metal. The carriage was only gold plated but I have no idea of the wood I have never seen this type of wood before. Its wheels were customized for running on the carpet and looked rather like bicycle wheels.

With the occasional jingle of a bell the carriage
ran these massive hallways at great speed. Seth and Rodney kept the curtains closed but I could still see through the cracks and they didnt try to restrain me.

We arrived at a door that didn't appear like any other. By now I couldnt talk so Seth, Rodney and the driver carried me down. A couple human passersby looked curious so Seth made a very convincing act that made me looked like I was, if you pardon the word, alive. It seemed to work. Like weekend at burnies.

Seth said, ``It's generally known in the city that you've arrived but your highness I don't want it to be seen that we hurled a lifeless body into the royal chambers.''

The two remained getting snacks setting up the tv.

They asked me why I would stay in human form and suffer such mental distress to the point of entering a hospital and I said to them that to do anything else would be to hide from my pain.

Later Rodney suggested to me to go outside into the fields of fire as the heat may help me. Apparently the Queen had been known to enjoy the flames. I was going to argue but was just too depressed to bother. The heat hit me like a wall, and then wrapped around me in a hug. I walked out and found a large lava flow. I touched it and it seemed like a hot tub in my true form. So down I went into the flame. I could see Rodney through a window smiling and giving me a double thumbs up as if to inquire whether I’m pleased and I gave him a single thumbs up to confirm that all is good with me. Then I slowly sunk down into the lava.

I was there about a day. I signed some paperwork to take possession of things and reaffirm parliament to run the territory down here by my authority. I guess the governance is a monarchic democracy. I am so glad, I don’t want to have the sole responsibility of a place that is just as large if not larger than the area of New York City above me. Yeah I found out this territory or realm if you like to call it is huge.

I received the keys for an apartment that was arranged for me when I left central america. It is in the upper west side. I was also told of a small basement tavern called Yuri’s in Hell’s Kitchen that functions as the neutral territory within this city. There was one in chicago too, McAnally’s pub. Basically it means that those groups and persons that are a signatory certain accords will not act against any other group within the confines of the tavern. It’s a good way of getting different groups together who would not otherwise feel safe to talk and for various agreements to be signed.

\parasep{}

I entered the apartment. It is a very classic New York City building one west 71st st. An edwardian building. The apartment is dual zoned for residential and commercial. Although the aparment fits the definition having a large area immediately behind the door it’s size is rather tiny to be used for any combined commercial and residential purpose.

There is a bedroom and an office, or living room if it could be considered so. The door is the standard translucent glass window in the upper half of the door the rest being wood. A fireplace is set in the far end of the room. This place reminds me of Sherlock Homes and his 221b baker st.

The apartment has only the bedroom, and there is a shared washroom and shower for the floor. Not the best circumstance I would imagine, and rather unexpected for someone that is allegedly of high position in the vampiric hierarchy. Something to be asked later, personally I thing this will work fine and it is very close to the universities just north of this location. I’m sure I’m going to need a place to research in the time to come.The greatest threat to our existence are the outsiders and I know next to nothing about them besides the deathstone ammunition I used in and around central america.

I need to setup the apartment for my needs as well as for the work I plan to do to make a living here. I don’t want to try to take from the city far underground that has been willed to me, in fact I don’t want to have anything to do with that city until I learn more about it. I can’t believe such a place has existed all these years and nobody has noticed.

A few days later I have things set up, a few black court were send to get things set up faster. What I ended up with the large area as an office. The bedroom although really small is my personal space. The bed I got just fit in the bedroom with no space to spare. The glass panel door remains. The genuine wood floor was sanded and resealed. I have wall to wall bookshelving in the office, as well as a large heavy oak desk and wood and leather chair. Chairs near my desk and a couch further back is there now, as well as ashtrays and small tables. I have a mini bar behind my chair. My diplomas and honorary titles are high behind my desk. There is a can of miswak on my table and a clay tobacco pipe. Assorted cigars are at the mini bar particularly for guests. As a matter of fact most of all that’s here are for clients, I just don’t know what I’m going to be doing or for whom right now. I have a computer at the right of my desk. I ran cables to the roof and established some antennas so I can readily listen and even transmit things on the RF spectrum. I copied and placed a picture of my human daughter Maggie on my desk. Floral print wallpaper sits nearly hidden behind the bookshelves, an artifact from when I moved in. There didn’t seem to be any sense in doing anything with it. There are doors below the mini bar that contains some lab equipment. There was a small ad hoc kitchen area in the corner of the large room. It seemed to be there as an after thought. I can see where it would have been a later installation as the building has a single washroom with showers and sauna on each floor as well as a room for a kitchen.

Having turned the large room into an office it looks wonderful, a very academic look. I’ll see how i goes. I head over to the Times building and meet Freddy. Wearing tight and revealing clothes when he starts talking he had the heaviest gay lisp I’ve ever heard and his gestures as he talks sung gayness like a jukebox full of show tunes. I love this guy already. He reminds me so much of my thralls from central america. Of course of George in particular.

He said, ``Oh thank you for coming dear. There is this job floating around in the Times about corruption in the corrections system, in particular a prison.’’

I said, ``Sounds good. I assume that at some point it settled on some reporters desk otherwise I don’t see how it didn’t just die.’’

He said, ``The first reporter to notice the stink in that prison died not long after he started working the case. Patrick was the next one to try but he had to let it go because of death threats. Nobody had the will to persue it after that it’s too hot.’’

I said, ``Which is where I come in, because of my experience in central america.’’

He said, ``Quite so. We need a top notch reporter and seeing your work you most certainly are. We also need a soldier. To build this story you need to survive.’’

I said, ``My standard per diem fee applies then with a 2 week minimum, subject to change based on hazards and complexity. Any changes to the standard fee will be forwarded to you in advance for approval. Please do not mention my name in any interactions you may have with people. Do not attempt to contact me for any reason I will contact you.’’

He said, ``Got it. I guess we’ll share keys and I’ll get on with having my day off.’’

We shared GnuPG keys so I can communicate too him reasonably safely and I was off to see Patrick.

I said, ``Hi I'm Susan.''

He said, ``Patrick. So you're going to try to crack Sing Sing?''

I said, ``Seems that way.''

He said, ``Good luck with that. I was the last one to try to crack this but I ended up just spinning my wheels.''

I said, ``So why don't you get me up to speed.''

He said, ``Sure. Here's the deal. You know what prison can be like, but at the same time depending on what day you get there there might be none or there might be 2 or 3 guys getting busy with each other. Completely in the open. Like roaches what you see in the open is a thousand times worse where it's hidden.''

I said, ``eww, is that normal there?''

He said, ``hell no, sure as shit not in front of the guards. Those bastards gotta either have som3 re big hairy gonads or something is d4iving them to it.''

I said, ``I get the picture. Did you find anything out?''

He said, ``Well it s3emed clear to me that some drug compqny is testing their newest formula on these clowns but I could never find a clear link. Right now there are three generic companies supplying the prison with it's prescription meds. There are numerous other sources for it's other drugs of need.''

I said, ``Right, I hear ya. So no smoking gun.''

He said, ``meds tested in the lab were what they said, a search of the cells turned up nothing. some contraband but it didn't test out incorrectly.''

I said, ``Have you thought of drugs without any residual blood toxicology?''

He said, ``Definately. The prisoners receive regular blood testing and even running it through forensics got nothing. That's the only way but how is it getting to them?''

I said, ``Exactly. Anything environmental turn up?''

He said, ``Cells were tested, 2ater supply, food, halls and yard. Everything really nothing turned up. mold, virii, bacteria, chemical nothing.''

I said, ``Where were you left spinning your wheels?''

He said, ``Finding the source of the drugs, how was it being trafficked, I focused on the drug angle it was the only one I had.''

I said, ``Is that what the previous guy or guys focused on too or did they cover other bases?''

He said, ``I think everybody went the same route but Jason was looking at the coming and going of people and personel at the end before he was pulled off.''

I said, ``Was he on the story a long time?''

He said, ``Longer than the rest of us. He told me he figured if he can't track the drugs, and it is a problem with people, then he should track the people.''

I said, ``I like that, it makes entirely too much sense. I think I'm going to follow Jason's idea when I get there and just skip what seems like a dead end. I'll be talking with the warden tomorrow.''

He said, ``Sounds good hope I could help.''

I said, ``You definately helped thanks a lot man, I can hopefully skip past most of the dead ends.''

Interesting. That is definately some rather extreme behaviour. I would think drugs too like a newer and better viagra testing phase or something. No weird drugs were found anywhere. I like the people angle, I think I'm going to go for that. When I talk to the warden I think I'll see if I can truck as an inmate. I'll need to be careful not to get heavy handed though I need to blend in ans not look like some superhuman. Or worse some kind of rite 9f passage and end up fighting the whole yard. There's no way I could hide my nature then.

I get back to my place. It's late fall now and the building hasn't fired the boilers that feed the hot water registers yet. I pull down some wood from the lumber room and atart up a fire. I kick back in my lounge chair and toss out the old miswak from the ashtray and cut a fresh one from the package. I don't smoke but I kinda need something to chew on sometimes to think. After a ahort while the dire got going well. The snap and pop is rather nice as sure as the heat on a cool evening. The temperature dropped fast over the last day. It was quite warm until after the rain past.

What possible advantage could anyone have in this? The drug end of it was a dead end, and it nevee fails if there is trouble afoot it is either for the love of money, power or lust. Very little else motivates save maybe vengeance. Vengeance makes little sense unless it wqs against the 2arden and there certainly are more effextive ways to mews with him. I think in chasing the drug angle 2e have nearly exhausted the money angle. As for lust well that would be the issue in itself, as a motivation I have yet to see it. For vengeance though I should check to see if only one segment of the inmate population is effexted. It would definately be an embarrasment to a rival gang to have this brought on them. So there is that. The po2er factor, unless like I thought it 2as rival gangs and an attempt at shaming the other I would say there is no power grasp in the population. There could be blackmail against the 2arden maybe, or q higher political maneuvering to gain advantage over one or more people thqt govern corr3ctions. Holding back that key evidence that would allow us journalists to print a story. The warden has not been threatened to silence that much I can see as he is helping me get placed inside. hmm. Also I need to examine administration at the prison to see if there are any inconsistencies. Jason was focused on people that would be the best place to start, to see if I can find any inconsistencies. I should take a look at the movements of 8nmates as well but I don't think I will spend a great time with that. All the work on tracking illicit srugs would have unearthed unusual activities of inmates I would think.

I got another chunk from the lumber room and fed the fire, then slipped off into meditation for the rest of the night, sitting in front of the fire in nightshirt and knitted shawl. lying restfully in my lounge chair. Having a tea party with Maggie in her little dream world.

Damned commute was over an hour and a half to Sing Sing. I'm going to need to bring work to do, or at least books to read, making this pilgrimage to and from every day. I might lock up a bicycle at the train station to turn a twenty minute walk into a five minute bike ride though. That would help. I presented my ID and weapon permit, leaving my glock at the guard station. Another guard escorted me to the wardens office. I introduced myself.

``Hello, I'm Susan from the times.''

``Ah good, I hope you can finally come to a conclusion to what in the hell is going on in my prison. Goddamned embarrassing. You wouldn't believe the wise cracks I get about the worlds biggest bathhouse and crap. Anyway that's my trouble not yours what would you like to do to start?''

``Well it's been made pretty clear what's been going on and where we've already looked, may I start just working in the qdministration office? If possible checking out the different roles and historical paperwork over the next couple weeks.''

``Um. Yeah. Nobodies done that yet. Try not to fall asleep.''

``I do not sleep that I am aware of, but thank you. I will assume you will show me fresh coffee?''

``Oh yes, we have a commercial coffeemaker. It's going all day long.''

``Heh, I'll bet.''

So he introduced me to the office staff as a new hire in need of job shadowing before moving to another local prison. The staff looked about as boring and plain as their job. Friendly enough though. I had a quick runthrough of the different positions  but the jumble of information just fell out of my head, I'll get to learning it over the next couple weeks. I couldn't use vampire vision to check their auras with them looking right at me, the change of my eyes would scare the hell out of them. Again plenty of time over the next couple of weeks.
Back home again, I'm taking a break from the evening work routine. Since I don't sleep I read at 24hour coffee pubs although I still need to eat a solid meal at night to stay firm and avoid needing to eat human prey. Talking about prey I've also been enjoying cruising bars and nightclubs. I haven't gotten more than a nice conversation yet. The odd one I've stayed with for the night but I can't go all the way. I'm afraid I might eat him. Eventually I'll lose it completely and either eat somebody, fuck somebody, or both. I hope I can recover some semblance of my original human sexuality, but I have little hope. I presume I may end up with a snuggle buddy like an asexual. If I was on a good old fashioned fuck-a-thon it really wouldn't matter but of the men I've met, at least the ones that approached me, they just aren't genuine or are really shallow. I think some of them are going to pull out a mirror just to look at themselves. So after kicking aside the players and aforementioned chaff, I did end up with some regular friends that may develop into something someday so at least there's that. I need something soon though, my pussy is starting to eat my leg.

Speaking of going out, after the first week of monumental boredom I went with the crew for the Friday night afterwork drinks. There's a little pub not too far away where we ordered some pitchers. I heard from them memories of times past and people they once worked with. Then came the frustrations of work. I really didn't get much from them but as they got more drunk I was able to use my vampire sight. I don't get drunk on alcohol by the way. It just comes out just as alcoholicn as it went in. Weird. Anyway what I found is that these people are scoundrels, the whole lot of them. They are shallow and petty, ready to take any bribe and kiss any ass. They are so crooked the couldn't lie in bed straight. Lying, cheating, stealing and all with a perfect friendly demeanor that hides a thousand crimes. These people are exactly where this shit is coming from. Now I need to find out who or how many of these snakes have made a deal and for what.

The night degenerated into petty arguments and rumours so I left team slimy and saddled up to the bar. A nice looking fellow named Chuck bought me a drink. He was a writer who authored some works in current affairs, so we chatted a long time essentially talking shop. It went well into the night and broke up at a coffee shop. The guy was still shallow but I enjoyed our time. We exchanged E-Mail addresses as he wanted to keep in touch. I'm not sure whether to be angry with him or just disappointed in general that my hope of a romantic encounter turned into an exercise in business networking.

That weekend I kicked it up with my phone rolling through about a million messages from players in an online dating site. Looked like every guy in manhattan loved me except the same generic message came up many times and the same guys came up multiple times. Blanket bombing. Nice guys are buried in ten tons of horseshit. With the Tinder literally every guy likes me. Blanket bombing players again. Nice guys mailboxes are probably so empty there is the sound of a single cricket and I'll be damned if I know how to get to them. Some of the players are idiots, made me laugh, the line was, ``I put the std in stud and all i need is u.'' Fuck.

So me, Eury and friends saddled up at my apartment for a game of french tarot. I used esoteric cards because they're so cool and it was a great afternoon. Except maybe when Eury said to me, ``Love the modern mother hubbard theme Susan'' when he got here. The only thing I could come back with at the time was, ``Oh shut up.'' In good humor though it worked out just fine. Later that night I went out again and the bars seemed to be filled with people that came together and left together. No singles. I really fucking hate that, I wish there were signs outside the establishment that literally said, ``singles bar.'' Sunday I did the church thing, where in the back of my mind even as poor a match as it would be I might find a good guy. Churches are the best place to find good guys I think if you can sift through the sea of grey hair and family men. I cruised through a library and a bookstore. More than one bookstore. Partly to get ideas to solve the mystery of my current assignment and partly to find men. I seem to have very quickly picked up another full time job in finding some man. I think I've heard it said a girl should establish herself first before looking for fresh meat, and I am solidly established so maybe that's why my interests are leaning this way. It my lifes next big challenge for personal success, not to sound shallow or anything just a psychological theory. On an emotional level I lost my hukan sexuality at Chich\'{e}n Itz\'{a} and it was imprisoned in an infected body around a decade earlier at Bianca's ball. I hope she's burning in hell for that. If not it seems to me Eury would know who to talk to in order to arrange it. Yes friends humour does help. It's still a horribly deep wound, and memories like Bianca especially burn deep. When I was in the fellowship I had a purpose and a mission. I was a hero of the people against the monsters who would devour them. Oh Harry I wish there was something I could have done, I would have taken your ring and married you in a second if I didn't pose a danger to you. It was the most painful thing I've ever had to do. To decline your ring and to leave for war. Even as much purpose as I had there I wanted so much for you to be with me, but I knew you couldn't, and I thought of you every single day. Every single day. Burn forever you fucking witch you ruined both our lives and I lost years of my humanity I will never get back. I'm only now catching up on building the happy life I could have had long ago. Thank God I consumed your species, and now the whole red court is gone. I pledge that I will never allow there to be another like you. I swear to it by my life.

All my infected life and since I was turned Bianca has been that representation to me of vampirism looking down in arrogance and patience. That voice that tells me it's only a matter of time and you will be exactly like us. 

Especially if my vampiric instinct comes out Bianca's voice echos as if through time telling me I am or have become just like them. She laughs and tells me, ``Child, how did you think it was not going to be so? You cannot resist, you are to be our sister, give up this futile struggle and let death come to your feeble human spirit. Savour the sweet taste of your spiritual death. Complete your journey and be the true full red court vampire I know you are to be.''

This hatred I have for vampires in my human soul I think, as horrible as it is for me, has made Bianca like a conscience to me. Oh I wish I could forget Bianca and what she did to me but perhaps that arrogant, ridiculing voice is something I desperately need when I am living with a mind and body of an immeasurably powerful vampire. Without it I might just risk the loss of my humanity in the psychological sense.

Back to work on Monday. I try to observe the employees in various ways but I'm not seeing much. A lot of ass kissing and trying to one up their coworkers is all. I think maybe that's all I'll get for now. The warden gives me leave to check out the prison proper and warns me I must be crazy. I go with two guards and when we enter the cell block as I expected the prisoners were yelling and whistling pretty good. When my fist brought down two feet of a 6 foot concrete wall there was quiet. I yell back, ``who wants some of this?'' All the inmates return to the rear of their cells saying ``Not worth it'' ``Not me'' ``No way'' ``The hell with you''. 

The guards said, ``How did you do that?'' 

I said to them, ``Someone I knew once, his dad was an illusionist. You know like stage magician?''

``He must have been real fucking good.''

``Damn straight.''

``Were you looking for anything in particular?''

``I don't think I'll know until I find it.''

``This big brute has been effected for quite a while. It might be a good place to start.''

Big brute is right. The guards had to yell at him to stand back, as soon as they came in he pushed right into them, one reached for his nightstick. I took that son of a bitch by the throat and had him high on the wall with just a touch of vampiric speed. I had him  there by one hand. Since this dude was being an ass I didn't give it a second thought and pulled over my third eyelid and started my sight. I did a red court thing for good measure all with the guards getting their senses behind me I ruffled my skin mask. See I don't really have skin as a vampire it is just a layer on top. A mask basically. I can't say for what the red court could or could not do but I can move it around like you could move around your tongue against your cheek. For me though it looks a little like a nest of flesh eating grubs squirming around under my skin. It is quite visually appealing, truly sexy. So what I found besides this guy being a scumbucket is that I seen residue of vampirism on him. This shit just got real interesting.

``Get her off me! Get her off me! She's a fucking alien man she'll eat my fucking brains get her off!''

I toss him on the bed, ``Buddy get off the cheap drugs and stay there. Don't fucking move.''

The guards recovered themselves, ``Where did you learn to do that miss?''

``I fought in a South American war for many years.''

``No shit? Maybe we'll hire you to protect us in here, I ain't never seen nothing like that from a girl.''

``Hey thanks. Well I think I may have found something. Let me search around I wont know what it is until I find it.''

I search around, using my sight when the guards weren't looking. I feel life energy signatures and sniff around. I haven't found anything strange though.

``Hey boys, this guy get it on with anybody in here? Do you know where it happened in here if he did?''

``Last week he was giving it to collins here over the sink.''

I sniff the area and I smell dispersed life force, quite a bit of it in fact, at that location.

``A month ago I seen him with O'Grady bent over the can here.''

I sniff, trying to set aside the other smell of the toilet. My vampiric senses picked up the life force signature not as strong as by the sink. To varying degrees I noted about a dozen points of abnormal static life force signatures. This dude was getting some business. I would like to shakedown this guy but I don't have the questions for him to answer yet.

``Ok who's next?''

``Well the lastest party animal is Jackson over there on the second level. He started a week ago and his latest shag was yesterday.''

``No kidding? So the just seem to take a pill or something and start racing? Do the ever quit?''

``We've had half a dozen quit. Dead of a heart attack.''

``Christ, were they older?''

``Most were young as spring kittens, which is why we've been trying to find what kind of drug they're bringing in here.''

``Man. Well ok you seen this latest one start a week ago. Do you remember anything else from a week ago, anything or any person coming to or from his cell?''

``No, same as when other cops and reporters came, nothing.''

``Well lets go, I'll try to gumshoe it.''

We arrive at the cell. This dude is more restrained. He's heard what went on outside and doesn't want any part of it. I sniff, same disturbances as before but only 3 distinctly rather than the shephards pie of disturbances from the guy below.

``He is this stuff like the kind enjoyed by both or not?''

``Don't say anyone I said it but I wish me and my wife had the joy these boneheads do when they're fucking in here.''

Wow, I'm assuming the guards relations are chilly. The way he said it indicates that it's rather over the top in pleasure. That's actually even more indication of something vampiric. It might be a phage, a fae entity that feeds on emotion. With only three disturbances I sniffed a little deeper. The oldest signature seems to have some other energy around it. I think Phil might be able to help me with that later. I found a little wooden talisman under the bed near to that original signature. I use my senses on it but I get nothing. I'll take that to examine later. Good search.

``Say has there been anything normal that started around the same time as these incidents?''

``Well thats quite the question. There has been a clinical trial for some vitamin supplements. We changed our medical supply contractor, food supplier has changed. Using different cleaning chemical supplier. Lady we are pretty much getting everything from somewhere else. Anything to try and resolve this problem.''

``Fascinating. Well good enough for now I better go finish some research on this.''

``Well have a good one.''

That was that. I'm going to put in extra time on research now that I got something to look into. I hate all this man chasing anyway I need a vacation from what is supposed to so much fun but isn't. I can't do too much without Phil but I can at least work through mine and Phils library to find this talisman. Then I'm going to meditate for a time to go play with Maggie.

what i found out was that the little talisman had symbols referring to the winter court and my knowledge of the ancient craft indicates it would be used as a spirit vessel. I'll have to verify with Phil on that but I do believe some is carrying faery spirits around and dollars to donuts it is some kind of phage due to the fluctuations of Life energies.

So, perhaps the motive lies in the change of contracts? There is a whole hell of a lot of money changing hands in this than could have been seen by the original investigators. I should be able to check documentation at the prison office to see whose hand is on what. Someone has to push this stuff through and it needs to go through that office. That administrative team are the Devil's own and if there is something foul going on in that prison I like them for it. There needs to be something supernatural or a practiced wizard involved to in order to know to capture and release phages with an intent.

I guess if for  nothing else having supernatural senses is a great advantage in journalism and I appreciate being able to scare the bejesus out of the bad guys too.

The next day I'm back at the prison. Staying in the office today now that I know what to look for. I found the cabinet where the contractor documents are kept. Shit it's gonna take a month of Sundays to get through that cabinet of papers. Well one day at a time. Issues started happening about 2 years ago so I grabbed records going back to around that time. One year at a time. Supply requests, bills and receipts, even the most ridiculous items were kept in the folders and I was staying up every night to pour through it all. A change in a generic drug distributor to a company named goodtime pharmaceuticals. I was inspired to find out more about that one. The company specializes in the distribution of sexual and mood drugs for pharmatherapy as well as aphrodesiacs mostly of the herbal variety, and pharmaceuticals related to transgender needs. Otherwise they are a general needs distributor and even so I don't understand why the happy hell the New York state correctional authority would choose a company named goodtime pharmaceuticals as it's medical use drugs contractor. That went off in my head like an air raid siren. The sanitary contracting supply company it Red Toad sanitary supply. Nothing jumped out as abnormal. I checked the website and looked at the promotional material. Based in San Francisco there were testimonials that offered a clue as to their client base at least. Three panties to the wind dance club, the Shiny Black Rubber garment manufacturing company, brothel house distribution of California, and you get the point. As a matter of fact the changes in contractors were pretty consistent in being linked to the sex industry which to me means the source of this phenomenon is originating with whoever has a common interest in these companies. Some kind of sex industry mogul seems to make the most sense and it links well to the nature of what is happening here.

I placed a hardware key-logger in-line with the wardens keyboard. I think the warden would have probably given up his password but I preferred to leave him with reasonable deniability since he has gone over and above in helping me with this story. I waited until after he punched out and grabbed some information on other institutions and printed it. This phenomenon is starting to branch out a little bit into other locations but as of yet the contractors in the other institutions haven't changed.

OK so it looks like the next stop is San Francisco. I gave Joe an update on the story so far and the Times got me the tickets to take a flight out there.

After a few hours of meditation and dreamworld play with Maggie. I have nothing to link these companies together yet so I need to do that. First thing is all of these locations have a physical address but not all are in the city proper so I found ownership and mortgage information on the locations some on-line and some I had to the actual land records office of the county they were in. No slam dunk here the ownerships were sometimes different. That doesn't mean the company or individuals listed are the actual companies in residence at the locations. Granted some are in personal names like Mandeep Patel but one stood out pretty clearly. A leasing company called Osreal Land Holdings LLC. So the easiest place to start seems to be to find that company and sweet talk them into spilling something useful. I found the headquarters in Los Angeles proper. Land records were to no avail, it owns it's own land. Evaluating the board of directors was interesting though, they all have links into the porn industry. Fairly heavy links. To three separate companies.

The porn companies seem to be distinct, I can't link them together to any common people yet. That's not a dead end though even without a smoking gun the story so far is enough to bring up questions about integrity in the correctional system or possibly questions of fraud within this particular company. I don't need to draw perfect lines as long as I can dismiss coincidence and make people think. Nonetheless I want to find the smoking gun and I'm feeling like I'm close.

I took a few days to track the comings and goings of the board of directors, see who they are meeting and where they do lunch. They all live in exclusive parts of town, and I used camerav on my phone to snap some pictures of some of these meetings for later. I relaxed some distance from them as they had casual lunches and off-site meetings just to listen, and get some names. I found most of these people fairly quickly, they are coordinating the supply, funding and operation of all these other organizations. At least one of the names on the land records was mentioned even though I couldn't find any record of the persons existence. I think the goods are all here.

As I was making notes I found the physical locations of many of the landowners listed in the land records, only the individuals in question seemed to have more than one name as I confronted them with their land records name on the street having allegedly met at a business function. Of course they responded as their alter ego and why shouldn't they? I asked them how their company was doing, intentionally forgetting the name, but they knew the name of their company everytime. This is getting more and more interesting all the time.

After about a week in a larger meeting at a local Starbucks there came an individual to the table that made the whole board rise and bow in a customary Japanese fashion. I think I just found the kingpin here! Everyone settled into their seats and I heard one name that made me turn away from the table save I should giggle right at them. Raith. They addressed him as mister Raith. This is a white court enterprise, oh most excellent!

OK, so what's left. Motive appears to be financial gain, the corrections contracts although I'm sure pale in comparison to the income through the porn industry are still decent enough and represent a very steady income. One thing that is nagging at me though is the fact that the money gain really doesn't fit, it isn't enough of a benefit to warrant all the time and effort to establish this enterprise. The means does not make sense either, I still don't know what is really going on at the prison. I do know a hell of a lot more than the other reporters found out so far though. I'll need to try to use what I know to find the true means and motive behind this mystery, the very fact that the Raith's are involved lends itself well to the talisman I found in that prisoners cell. The Raith family, being white court vampires, would have the connections and the knowledge to assemble a scheme involving the supernatural like that.

I picked myself up and settled my bill pretty much right away, again being vampires they are much more aware of their surroundings and to the fact that I am entirely too interested in their conversation. I can learn more later, I made a very big leap forward in this story. I fired up tails on my laptop and sent to Joe the update via GPG E-Mail including photos and identities, sometimes multiple identities per person, of those involved that I seen so far. Joe is liking what I am telling him so far the implications could be far reaching. Now I need to think about where to go next in this.

What do I need? The true motive. I need a solid link to implicate the Raith's in this, and I need to identify the nature of the phenomenon at the prison, hard facts as to what is really happening there. Maybe it's time to start preparing for an infiltration, I'll need to gather intel on the location in general and identify what I really need to obtain from this place. I need to check to see if there is a possibility for an electronic approach as well. I have some skill but if this location is setup too impressively my means of obtaining information electronically may be limited. I need to try though because such information is a journalistic bazooka.

I head to the building the next day for some preliminary recon. It isn't in a retail location like the last place, and is surrounded by small industry and a Wendy's. I love Frostys and I'm not ashamed to say it. So no sitting at a coffeeshop in a mall and observing the location. It isn't busy though, there is a security guard in the front who does little more than take mental note of who comes and goes. Like a scarecrow behind a desk to keep out the vagrants. I easily entered into the location and found the bottom floor to be composed of a small inhouse cafe and variety store and different departments setup as different suites. The hallway is huge and people are filtering back and forth constantly between departments. My quick passage in and out of the location went unnoticed although if I had to come back I'll need to get a stack of file folders to juggle with a bagel and a coffee as that is what I'm seeing the most of here. There is a small hallway leading to the back to supply the cafe and access to the garbage and recycling in the back. Note to self the back door there is one way only. The parking lot in the back is a pretty decent size. There are stairs and elevators to the second floor of this two story building. The hallways on the second floor are a little more of a labyrinth. The offices of all the senior staff are here as well as the secretarial pool. I think I can safely plan multiple incursions here, based on what I've heard from the employees nobody seems to know anybody very well and nobody cares. The impression is strong enough I really don't need the sight to know. I'll come in here first to identify some key people if I can but mostly to identify other weaknesses of electronic and social structure. I'll take a look at the inside of the different departments and see basically what I can accomplish on my next turn in. I'm going to avoid the second floor for now it is much less chaotic making it a lot more dangerous for me to infiltrate.

So the day near closing I head to the back of the building and flip over the garbage bins. They are those huge plate steel bins with the plastic flip doors on the top. They do weigh hundreds of pounds if not a ton or more but I'm a strong girl and eat my sprouts every day so easy peasy. I gathered what I needed from the ground of the trash and recycling and flipped the bins back to their proper place for the sanitation truck to deal with in the morning. So I got a pile of unclassified documents to read through and use during my incursion as well as company pens and swag. A nice real leather company foundation briefcase was disposed of due to a broken clasp, so I'll fix that. I got some names and itineraries, that little trick gained me quite a lot actually. Even the IT team through a bunch of old scratch notes to the recycling rather than the shredder. I'm sure not on purpose, not like I haven't seen security incompetence before or anything. So now I have an incomplete network map and some passwords as well as physical locations of network equipment. Not bad. It has the credentials for the company top level DNS server. I fall on the ground laughing, anyone ever met the man in the middle?

The next day I filter through the different departments, they are all laid out the same. A small departmental mail desk at the front passing paperwork and packages in and out, entering all the actions taken into a workstation, shooting the shit and drinking coffee. In behind are permanently assigned cubicles and a couple offices on one side for the assistant manager and manager of the department. Two meeting rooms are on the other side of the room currently unoccupied. There are half a dozen stand up workstations for brief use by the employees. There is a login but I have a few employee logins from the paperwork I snatched. There is an actual IT department that is just as busy as the rest of the office. From what I gather the existing IT staff has built the in house system with sufficient complexity and lack of automation as to assure their job security. I setup a postfix server at my own virtual hosted machine and took a moment at the stand up kiosk here to login and change the DNS MX record to point there. Now all company E-Mail is being sent to my own server, recorded, and relayed back to the company E-Mail server for normal delivery. That right there folks is called man in the middle. I'm going to go check what I got in a few days to see how badly I nailed these guys.

I made use of those good old social engineering skills while I was there and it worked out very well indeed. I obtained a clandestine recorded record of some of these conversations they were so sweet. The employees know very well the Raith family run this enterprise. Apparently it was actually spearheaded by Madeline Raith but later adopted by the family through her father. I got the names of some other companies involved and the hint that there has been a new project underway for the last couple years to increase the market penetration of this group of companies products. The employees on the floor do not know much more than it's a government initiative and uses the appropriation of exclusive contracts in New York State. I asked how are we getting those contracts or is it the old fashioned song and dance of effective sales technique. Apparently the director in charge of the logistics department is operating the project and the nuts and bolts of it are run offsite and noone knows anything else about it. I checked in the logistics department but the staff didn't know any more than the others and there wasn't much more to be found. I walked my useless papers back and forth between departments all day long and snapped some quick photos of the odd documents that I took into the can and then placed back into the various departments they came from. I headed out of what seemed like the New York stock exchange at closing time and went back to my hotel to process the material I had obtained. It took me the better part of the week to organize the documents and learn how everything fit together. There were still pieces missing but I knew the road I needed to take to finish the puzzle. After a quick trip back at the end of the week to correct the MX record on that companies DNS server I logged into my cloud server and pulled down the email I had saved from the company. There was a risk of getting my IP address traced but within the white court I would put a couple notches on my respect for executing an excellent intrigue. As far as the mortal world goes the cloud server belongs to a ghost, registered under the name of a dead woman named Susan Rodriguez and paid through a bank account of the same name via cash deposit. A dead end to any real world investigation, unless the investigators knew enough to dredge the Times employee records to find me.

As I expected, critically classified E-Mail was being exchanged without encryption the same as most companies do it. It was an absolute goldmine of incriminating correspondence. All roads lead to Rome of course and the E-Mail interchange showed headers that tracked back to the Chicago area. Somewhere I really really don't want to go. I'm going to have to though, to identify the location of the Raith office and finish the story by getting photographic records identifying them and linking them definitively to the operation.

First things first, I need to go to the lab. According to the E-Mails they are using magnetic manipulation of brain wave patterns to attempt to illicit a permanent increase in sexual desire that will lead to the Raith group of companies reaping increased profits upon success of the venture. I think it's a clever ruse, they are up to something that involves the nevernever and likely phage in some way.

I check out the location and find it is in a heavy industry location and is a sizeable property. Neighbouring buildings have the same design and are completely open warehouses sending and receiving shipments via big rig. Observing the outside I seen a touch pad security lock and loitering near the gate I observed the numerical combination that was used to lock up. Odds are the same combination is used to open up and the next morning proved the point. That evening I used the combination to disable the alarm and passed through the door in mist form. With my vampiric sight the pitch black warehouse looked like twilight, and within 20 minutes I located the lights and flipped them on. This was magical not scientific, I have no fucking clue what in the hell is going on here. I take some camerav snaps of the equipment in an equal share of the magical and the mundane, the first for Phil to look at and tell me what's going on and the second for use with the Times article to show evidence of experimentation and confirm the scientific aspect of the operation alleged in the E-Mails I obtained. In the wee hours having scoured the location and finding what I could I passed through the door again and set the alarm. Then escaped into the night to organize the documentation I found and got it sent to Joe who at this point is losing his shit with excitement.

I postponed the trip to Chicago so I could get back to New York and identify what the Raiths are doing in California.

``What is all this Phil? What's the real motive here I know they're up to something but I can't put my finger on exactly what.''

``Fucking genius that's what Susan. There's one dangerous motherfucker that has a serious mind to change the balance of power in the vampire world.''

``Phil. Spill it.''

``A lot of the magical theory is similar to the rite of ascension you underwent, it looks like whoever it was learned something, which means whoever it is knows what happened at Chich\'{e}n Itz\'{a}.''

``Great. A big nasty who knows I got the juju.''

``Or at least knows that you came out a human vampiric crossbreed. This work is an attempt to allow the white vampires to spawn themselves in a manner similar to the red and black courts. We were correct for the most part the talisman is a spirit cage, they are obtaining compatible phage from the nevernever and caging them in talismans. Once a human touches the talisman with their skin the phage is transferred to them and is awakened in them in their first sexual act. Similar to the coming of age of white court vampires. The talisman concept is similar to a group of fallen angels I know called the denarians. The difference being once the talisman has transferred the phage to the host it can be discarded or reused but is of no further use to the victim.''

``The white court is gaining an interest in conquest.''

``They're looking to grow their numbers fast, for purposes known only to them.''

``As far as I'm concerned it's conquest. Whether the Raith are intending to utterly conquer their own court or are looking at world domination it's still conquest. Why else would someone build an army?''

``Something else to be considered. It's generally accepted by you and me that the Red Court enlisted the aid of a very powerful wizard to write the spell that bid you to rise back in power and majesty, not to flatter you or anything. They did it to gain favor with the court, it would seem, and likely gain favor from you. I don't know why they haven't approached you about it yet. I think there were other hands in the pie that day in Chich\'{e}n Itz\'{a}, people this wizard would rather not cross. I think he is trying again with the white court to make them indebted to him in exchange for victory over their enemies.''

``It sounds probable. I can't know until I can confirm it though. I'll head over to the Times for a debriefing of the mundane side of this. Then I need to head to Chicago to visit the address for the Raith enterprise mentioned in the E-Mail to put a bow on the package and complete the story.''

``Godspeed Susan.''

Time goes fast and in a couple days I'm off to Chicago. I called Father Forthill ahead of time to see if I could stay with him and catch up for the few days I was going to be there. He said it was OK but be careful to keep it under wraps about being there. I told him if someone does see me I'll go mist form faster than he can say pop, they'll think I was nothing but a memory. That would be fine by him. So I arrived with a litigation briefcase, you know the kind, a briefcase with wheels. I pour over the documents I have to determine a plan of action. The location is downtown in one of those office towers, unit 508. Lorriatt Enterprises. All I really want to do is get some verifiable evidence that the office location exists, and then if I can get some camerav verifiable media snaps of the location, the name on the door, maybe some paperwork at the location. I thought about it and rather than that I think I will actually get a video recording of the place showing the people there and other nice things. I craft together a fake pocket protector and clip it near my shirt collar so my well endowed rack doesn't force the camera to take a video of the ceiling. I finally build a harness that works well with a powersuit I pick up downtown and keeps the cell phone camera pretty level. I practise with it to get a sense of it's frame rate and the optimal position to hold paperwork to get a reasonable facsimile in the recording. I sent a secure email to Joe to detail the plan I'm considering executing and so far he likes it. They might try to make the Chicago office vanish like the wind and this should nail them to the wall. Preparation takes a whole week and I think the carpenters were at the parish four score and ten by the time the week was up. That is while I hid in the guest bedroom in the manse of course. Well, to be honest I did peek outside the window to see Maggie. She was flying on angel wings most of the time  when I seen her in front of the church. It's the supernatural hearing thing I caught every word. She said she is an angel princess flying on angel wings with mommie over New York city and all it's twinkling lights. My face went red, aw shucks. I love you too Maggie.

The day came to go to the Lorriatt Enterprises office. I timed it so that I arrived at about noon. I entered under the guise of an FBI investigator. I had the fake ID with my stuff from the Arcane that was sent to me a year ago after I had risen. As for the warrant I knew a guy in town that rolls immigration papers for illegal immigrants from across the border. It wasn't much of a problem for him to roll me up a warrant. I got pretty much all the significant paperwork on video. It was just a matter of flip flip flip. I had my litigation briefcase with me so I filed a fair amount that was stamped or sealed. Through the resources of the Times I had documents, especially those signed or sealed, tested at a forensic facility and then returned to the  Lorriatt office. The office manager took a moment with me and I explained we are investigating reports of organized crime locating an office front in the building but advised him that his office is in the clear. He breathed a sigh of relief, and shook my hand as he left. Well, job done.

Back at the manse I get myself all packed up and give father Forthill a hug before I leave. Father opens the door and bang there's Harry! Aw shit! Poof! I'm mist, and I float away on a breeze.

Harry said, ``Hells bells father did you just see Susan? Was someone just there!''
``No son, no-ones here I'm afraid. Do come in.''
``Give me a minute father, I think I just dropped something. I'll be in shortly.''
``Take your time son, it's a beautiful day today.''

I looked as he put his head in his hands for a couple minutes. When he looked up his eyes were red and filled with tears. As I floated away I heard him say, ``Pull yourself together Harry, she's gone, let her go.''\\

If I had eyes at that moment, I would have wept too.\\

I considered the way things are now, again, so that I understood well why I haven't gone to him to explain that I've returned with my spirit still intact. First thing he probably wouldn't believe me, or if he did he would never believe I was anything but a full red court vampire. Second, I have my own life now and I'm very happy. I'm where I want to be in my career, and have a chance to make a difference in the world both as a journalist and as a leader of the vampire courts. I can't re-enter a relationship with him all the way out here and he has his own place in the world right here and I don't think he would ever move. Third Maggie has an excellent home, more than I could ever give her, close to her daddy and her mommie plays with her every night in her dreams. She has both her parents in her life insomuch as it is possible. Lastly, although I know there are more reasons Harry lives his life on the edge, he walks on the edge of a sword and if he leans too far one way or the other he is sure to be killed. It would destroy me and Maggie both and I'm unwilling to go through that although I would be there for Maggie without hesitation. As father Forthill told me stay safe Susan, if the worst happens and Harry is gone at least Maggie will have one parent left in this world.

I fly back to New York city and played with Maggie in her dream world. Well I'm halfway there, just need to write up the story so I'm going to be commuting to the office for a while to get the story written up. It took me a week and a half working full days to get it all right. I passed it to Joe who worked it over and it was in the paper the next day.

You could hear the shit rolling all the way to the governors office. FBI investigations dug up even more than I did writing the story. Mass corruption in the Sing Sing administrative pool triggered a mass firing and replacement of the existing staff, as well as placing New York state department of corrections under investigation for fraud in general. The negative publicity destroyed Lorriatt Enterprises and a significant part of the Raith power base with it. Executives went on trial for crimes against humanity, although there still didn't exist any causal link in the smoking gun sense there was massive evidence in documentation and email transactions that destroyed them.

I just executed an earth shaking power move that crippled house Raith and cemented a high degree of respect for me from the entire white court. The white king himself along with his daughter Lara declared their intention to parley and we met at Kenworth's pub to negotiate a private allegiance to the empire. So the matter won't be public, and the white king will remain the white king because he has access to the resources of the empire to protect the position of his house.

A small note, in the white court members of the empire are called imperialists and I plan on using that for colloquial reference to members of the empire internally just because I think it's rather cool, and a good definitive way for us to identify ourselves and each other.

Although the white court wasn't present when I returned to my house, at the news a scourge returned with a small gathering of prey picked from the murderers, rapists, predatory pedophiles and other wonderful fellows who were present in the city. There was a great feast in celebration of the great victory and acquisition of a white court house into our glorious empire. I abstained from the blood-letting and joined Phil on the balcony that sits off the 2nd floor (due to a floor collapse) and observed the celebrations sharing a glass of wine with each other.








 