%scene ... intentionally withholding goal statement for effect
\lettrine[lines=2,lraise=0]{T}he next afternoon Spook caught me on my way to finding another excuse from going on nursing duty in the medical tents. I dislike the way the patients seem to know exactly what I am and how it couldn't be more obvious to others that something is amiss if they threw themselves at my fangs they're so desperate to receive the venom. I have no idea how they know I got it, they just seem to smell the red court on me.

He said, ``Susan do you have some time this evening? I want to apologize for what I said earlier about your powers, I didn't mean for it to come out the way it did. It is what it is. I've been doing nothing but paperwork in the warlock's area today and I'm going to be doing my daily magical practise. I thought that perhaps we could get together and I might help you in understanding your abilities. You were scheduled for duty in the patient tents, I asked and they seemed relieved you could be somewhere else. Something about the patients aren't right when you're around. I'm not surprised.''

I said, ``Thank you. Thank you. Thank you, Spook. Oh thank you.''

We stopped for some bangers and mash at the mess tent and retired to his assigned tent. I think he's the only one of us that was assigned his own tent due to his being a warlock and thus his importance within the fellowship at this time in history.

He said, ``So what do you know so far about your new abilities?''

I said, ``Fuck all. When I woke up in \chichenitza* I was true form red court. That's still my most natural state if I'm tired or very hurt. Putting on a flesh mask and holding it is some effort, but not much really. That bird-like true form thing I've found I can turn into only when I'm being true to myself. I have to be right in my heart. It's about focusing on what and who I am rather than just wrapping myself up in something. Once I'm a bird though I can just stay that way I just need to refocus inside if I want to change back to a bird. Not really a bird but I don't know what else to say about that form. I feel it's my most powerful and exalted form I've seen yet. I have the infamous venom, and the infamous hunger. My eyes have strong hypnotic ability. I can see a lot more in people with my vampire eyes. When I went to get you I seemed to have transported myself by instinct. I don't know how I did it. I have mistform of course, good to pass walls or just plain disappear then reappear somewhere else nearby. I can move around on any surface even inverted like a spider. I can walk around during the day which many vampires can't. I'm not sure if it matters but I'm not bothered by cold but love the heat. I'm sure I'll find out more as time goes on.''

He said, ``So it seems you're a shapeshifter of sorts. That doesn't say much the reds were a bit like shapeshifters except that really they were just wrapping themselves up in a mask. The bird shape as you call it, that is real shapeshifting though which makes me think you have a greater depth in that area. Look Susan I want to explore that a little more tonight. What about the eyes Susan? Sometimes human, sometimes black and sometimes white regardless of your form. Can you explain that a little more?''

I said, ``Yeah sure. It's after dark now so it's a little easier to show you. Basically human eyes are human eyes. I can see farther and sharper than other people but not much more. Honestly as the days go by I'm learning new things about myself and new things are developing in me on their own time. The bird form I didn't know existed until it spontaneously happened and over time I learned to better control it. That's the way with all of this. It's just taking time.''

He said, ``From my experience with certain entities that seems to be the way. You might be able to do something one time then it just doesn't happen for you the next, like the long process of learning your instincts naturally rather than an animals faultless instinct to breathe.''

I said, ``That's about right yeah, I can't really depend on anything special I got except what I knew back as a half vampire. Well, and more and more the bird form seems to be reliable. Now about the eyes---''

I switch over to vampire vision, my black eyes.

I said, ``Now this is a busy set of eyes. The white eyes you seen are just nictitating membranes to protect these vampiric eyes from the daylight, and maybe other environmental hazards but I think mainly sunlight. That way I have abilities and senses I would normally in vampire form after dark. Pure white or pure black eyes are just different forms of creepy. When I'm walking around I just have the human eyes. In vampire vision the stimuli is huge I'm only now just scratching the surface. A whole new range of colour, if you can say colour, is available for me to see and I'm just going by instinct as to what I'm seeing. I'm using it as an enhancement of watching body language. I know what hungry looks like by watching people in the mess tent over time, just studying what I see.''

He said, ``Here I might be able to help with that. Do you have any special ability to detect deathstone by any chance?''

I said, ``No. No special sense of it. I wish I did.''

He said, ``I wish you did too.''

He walked over to a bookshelf, trailed his finger along the spines of each and withdrew one book carefully. It was a work composed by a still existing magickal tradition. The name on it was The Secret Doctrine of the Rosicrucians, Part XII, The Aura and Auric Colors.

He said, ``I've found it to be quite accurate for me, and many of my colleagues swear by this one. The ancient traditions have done a lot of good work. Every person or group has it's fallacies, each warlock needs to determine for themselves what works for them best and some people I know cannot use this tome. I would like to know which group you fall in perhaps I can help in this area. Remember Susan don't trust what you see out of hand, I know magic that will alter or obscure my aura to the aura of others and most warlocks possess the same abilities.''

I noted that little piece of information. We looked over the book together and I found that from what I can recall my experiences conformed to what was described in the book. Auric abilities are powerful I can see that now. It's a bit of a game to play though when I consider what Spook said about how auras can be altered. What I read does not completely encompass all the breadth and depth of what I see through vampiric eyes but this does solve some of the mystery involved. It gives me a foundation which I can learn with.

He said, ``Now for the shapeshifting. Let's take a walk it's quite dark out now.''

He grabbed some things and we headed out into the night by the light of a fuel lantern. It is a very black night. It's overcast, there is no sign of neither moon nor star. Rain is likely coming soon it is humid and still, a stillness like would come before a storm. He took us into an area of the camp that is unused during the night but far enough away from the camp borders that it isn't ever patrolled. I made note of the area, I think I could use this knowledge later.

He put down the lantern and turned to me. Taking some spell components from a small leather pouch, he whispered some words in enochian and the components were consumed.

He said, ``Could you extend and retract your talons Susan? I want to try and observe the underlying mechanism that causes the effect.''

His eyes glowed deep green. I did as he asked and a shadow of green smoke passed over and through my hand as I did so. He looked at my arm. He asked me what form I am in currently I said masked red court form. He told me to expect a sharp poke and he drove an ice pick through my forearm. No blood. The flesh appeared necrotic from the inside and I was black as a rubber tire behind the flesh. He removed the ice pick and the wound healed over as the ice pick was being extracted.

He said, ``That's a fast heal. Are you okay so far Susan?''

I said I was. He told me to expect a cutting sensation. He took a bowie knife, I took the bowie from him. After a sincere petition that left him with a black eye he gave me a local anesthetic. Just because I'm a fast healer doesn't mean I know no pain. Then he proceded to fillet my arm from shoulder to wrist. The flesh came off and became a tar like substance on the ground, and new flesh grew behind the blade as it was cutting.

He said, ``That's a goddamned fast heal Susan. How are you feeling?''

I said, ``Hungrier by the minute. I don't think I should do much more healing tonight Spook I'll eat somebody.''

He said, ``Understood. What about the hunger? What is your experience of it?''

I said, ``I'm not as hungry in the birdlike true form. As a matter of fact I just kind of exist in that form with a manageable abiding hunger that never goes away. If I'm too hungry then I'm too weak and vice versa I can't leave this red court form. For the time in which I'm in the bird form though when I return to a red court form I'm neither more nor less hungry that when I left it before except if there's a reason I should be, like I got hurt, which weakens me, eventually forcing me back to the red court form. I feel better being the bird and I'm better off that way I just can't walk around that way indefinitely I just don't fit in with polite society. I'd rather just be human again anyway. It's what I always wanted but never got.''

He said, ``Bite down on this leather, there's going to be another poke in the area I anaesthetized and it will hurt.''

I bit. He poked. I screamed into my other arm so as not to alarm anyone nearby because that hurt like a motherfucker. I looked as I seen a deathstone dagger snapping back into it's handle. My arm had a hole. It wasn't healing. I could see straight through my upper arm although the hole wasn't a big one. Icepick size maybe. I looked over at Spook.

I said, ``I'm going to shove that up your ass later. I take it this is a further experiment?''

He said, ``It is. If I help show you your shapeshifting ability might you forego on inserting deathstone into my anus?''

I said, ``Done. You show me that then I will owe you. What do you have in mind?''

He said, ``First shift to red court true form, I'll check the wound and you can do some exercises for me.''

I did. He nearly hurled on my talons. It is not a pleasing sight for anybody and especially not for a fellowship soldier. I felt like I was at the doctor's getting a physical. He put on some thick gloves and used a number of instruments to learn more about the slimy rubber composition that is my H. R. Giger alien born of a vampire bat form. He checked the wound which was still there from before. I changed to the bird form. The wound remained still as it would in any form. Deathstone needs to heal naturally. He analysed the action of my furling and unfurling of wings. It made him smile. Then I did extending and retracting talons on both hands and birdfeet. I curled my talons into hooves and the forming of the digitigrade stance which I learned some time ago just out of instinct. He pushed back against the curling of my talons and the reshaping of my legs during the transition, and the action of entering into a digitigrade stance made him smile again.

He said, ``Susan everything you're doing hints at shapeshifting. There is significantly more conscious thought in the actions of entering your digitigrade stance and the unfurling of your wings. Your wings appear of fixed size but it appears you can unfurl them to have any span you want. It is a supernatural capacity and it is true shapeshifting for every act you take in refurling your wings. In taking the digitigrade stance, the action is instinctual but the execution is a conscious effort. I see that the folding of your talons is conscious when I had you push back against me, and the same with the changing of your leg structure. You were making a conscious effort in the change, and pushed back against me in the ways I prescribed for you to do. You have full control in those 2 particular transformations and it is my presumption that if it is so then you do have the capacity of a true shapeshifter. Let's do another exercise to see how far we can take this thought.''

He took some more components from his pouch, and with a few more words of enochian his eyes went from green to leathery eye sockets with a thick brown smoke in place of eyeballs. He had me turn into mistform, and the smoke intermingled with my mistform in a way that seemed rather intimate. I wasn't very comfortable at first with the sensation but he explained he was making a deep connection with my psyche in order to guide my intuition and conscious action, helping me realize the actions through which shapeshifting takes place. Reaching that deeper level is what caused the sensation of intimacy, it is my psyche being protective of itself. I felt things I never felt before. Things I didn't know where there. It was like someone was walking me around inside myself with a lantern illuminating things I never knew were there. He helped me do things within myself and it didn't take me long before he said I was ready to start learning on my own. He concluded his spell and I returned to my birdform.

He said, ``Now focus on me, remember what I showed you in mistform. Focus on me, and be me.''

I did. I couldn't see myself but he smiled big. He said it's been a good night and beckoned me to return to his tent to wrap up. He asked me to focus on him again when we got back. Then take the internal actions I was taught to gain the sense of being him. I did that. He asked me to hold it and look in the mirror behind him. I did. I was him. He showed me that I can bleed as a human, to see that I am true human. Completely shapeshifted. I refocused my thought to become me again, and to project myself contingently, to see my human self at my true age. I did it, and I did it well. I have a couple wrinkles, I cut myself and I bleed, I'm human. I rolled back into a red court form with flesh mask and lost my older appearance but my wound healed. I'm hungry. I wasn't hungry when I was human but there was an effort sustaining the change.

He said, ``You've done amazing tonight Susan. For a long time you are going to find it rather draining maintaining a shapeshift for long. It means it will drive you to feed more often. It will get better with practise. I've worked with recessive populations of shapeshifters before and I've learned some things about it. Also you will be able to more easily shift into forms you are familiar with. Foremost your trueforms which seem to be the birdform and the red court forms. In my work with you it seems you resonate more with that birdform I think that's your genuine true form. The red court forms are a legacy from your vampiric ancestors. It's the difference between walking and crawling, it's preferable to walk around but if worse comes to shove if all you can do is crawl around then all the power to you, red court forms for the win. Like I was saying more familiar forms would then be true forms, your own human form you are familiar with or like you just did a form of yourself projected contingently to change age, hair colour, etc. Other humans wouldn't be too hard. Just don't try for rocks and twigs yet unless as I stated you have a preexisting understanding of what it is like to be a rock or a twig. You'll get better.''

I grabbed him hard for a long hug. A really long hug. This is such a huge self-discovery I'm almost in tears. I can be the real human me now and I know how to do it. I've waited a lifetime for the chance to be human again and now I can be.

He took some references on vampires and magical use off his bookshelf. He also grabbed a really old dusty reference on the d\ae monic. He helped me delve into some magic workings but after having read a few words and seeing the energy spark and snap around me we decided to take our show on the road again to the abandoned area of the camp. My magical ability isn't like a warlock, it's not human, and it's not fae. Spook said it was like magic was attempting to cast unto itself and created a feedback loop which had an infinite escalation pattern. Working with me we found I can use magic if rather than focus on it I go zen and acknowledge my awareness of my intentions and let it go. Keep ritual brief or use simple somatic or verbal components, a wave of the hand or an enochian word or sentance. The most important thing for me is distraction and not focus. We found during the course of our investigations that when I was working with him I created many magical effects without even having done anything, or intended anything. I fart magic. I have no magical training and know enough to be dangerous. To myself as much as others. I can cast the same spellwork and I may or may not ever get the same result. Testing for magical leakage as he called it further indicated I have a perfect efficiency, and unlike human casters will have no issues with technology whatsoever. What he taught me was enough to get by in the presence of magic and have some self-control in it's simple use without causing an implosion of all that is which is what he was greatly worried of.

He took the reference on the d\ae monic and formulated a test, a residual test for d\ae monic energy. He brewed up a beaker of liquid and took a drop of my blood, it was supposed to turn a colour depending on what type of d\ae monic energy was present. The d\ae monic isn't like demons that can possess, the influence of d\ae monic is very rare and often subtle but infinitely powerful. As Spook said before every wizard and warlock he knows avoids working with the d\ae monic for the very reason that it is far too dangerous. Like trying to lasso a speeding locomotive. The beaker imploded on itself and fell as dust on the ground. Both Spook and I fell backwards on the ground from both surprise and the shockwave. He examined what was left.

He said, ``I've never heard of anything like that. I won't be able to complete the test until I can find a way to resolve that problem. According to the colour of the dust, pitch black, I think it might be the presence of pure black magic. The d\ae mon who is the personification of black magic is unknown to any my colleagues. We have seen instances where such an influence has been seen but it is a mystery what name we could place on it. When we have seen it, well one instance was in the mass presence of creatures of the night like vampires, in an unholy place, a holocaust cemetary, which was the active site of truly vile black magic. Just as a reference if that colour appeared in the liquid in the beaker I would have said definitively that it is what the powerful influence is on you. This colour with a deep blue hint is water, the influence of Leviathan. This colour with a little grey speckle is the influence of the death d\ae monic of which it is said there is more than one. Earth tone would be Belial, the earth energy. I guess what I'm trying to say is with slight differences this could mean just about anything and it's made even worse because of the fact you are a full blown vampire. You are exuding this energy already just by your very nature. That said few vampires we've tested had even tested positive for any direct influence of this type of d\ae monic energy. I've still never seen this test do that, implode into pieces.  Maybe I'll be able to research a better test later on to find something out.

``For what it's worth this is what I know about the d\ae monic. Their influence is actually inherent. The d\ae monic is the created universe. They each have their personalities though, being anthropomorphic personifications. The universe as understood by many of my colleagues at this point is multiversal. Each particular instance of a universe has all it's own parts, it's own nevernever, it's own gods even. What doesn't change is the white God who stands above all and in recent research the d\ae monic seem to exist in their own realm that intersects the whole multiverse which means true omnipotence is applicable to not only the one white God but also to d\ae mon.

``Coincidentally although I don't get it correct all the time, traditionally those who have dealt with the d\ae monic have had trouble keeping a separation in naming convention between the malevolent demon and the benign d\ae mon. It originally came from the Greek definition and carried down through the ages primarily through our hermetic research. Much of what we know of d\ae mon came from our hermetic scholars and their astral work. We have tried with keeping specific spellings, and by using d\ae mon as a singular entity. Like saying: summon a demon, raise a demon, raise demons, I am a demon, that is a demon all would refer to a malevolent being. Saying: summon d\ae mon, raise d\ae mon, we are d\ae mon or I am d\ae mon helps refer to the benign d\ae mon. Pronunciation of Daimon helps, which is greek for divine power which seems suitable. Still questionable though as we don't see d\ae mon as having a direct influence on us as much as an indirect influence through the gods or the mundane. Indeed it is the gods that we expect to actually tap into d\ae monic power to create influence in our world, like a god of water such as neptune would be no god of anything without water. Water in turn would have no influence on our world without neptune to create that influence. Imagine the surprise our ancestors had when they realized that water indeed had it's own voice, personality, and name. That name is Leviathan. Philosophically I've wondered if the demonification of the d\ae monic pardon the pun, was a way for the church to direct the flock away from the worldly things toward heaven according to the doctrines of faith. There is nothing more worldly than the d\ae monic afterall. I digress though, you said you had encounters with an entity that called itself Leviathan and named you as his sister? Pray tell me more of that now that we have some time.''

So I retold the story from when I went to rescue Spook. He hung on every word but admitted he didn't know much about what it meant. He took notes as I spoke and said he would consult with colleagues of his to see if he can get any more knowledge. There aren't any hermetic scholars around at the moment and he doesn't know how to contact any but the next time he sees one he will parlay with them.

When I got home I experimented more with my shapeshifting. I can shapeshift my clothes into my new forms which is something I was starting to realize back on the road to the camp. Anything I wear can be changed but like Spook said I have to be familiar with being what I change to. I'm familiar with being clothed. I'm familiar with being naked. If I hold a spoon I'll be damned if I could do anything with it as I'm not familiar with changing into or out of a spoon. Similarly I can't just be clothes. I've been naked and I've been clothed, but I've never just been a set of clothes. I've been capable of mistform for a long time but that doesn't mean I can be smoke as I've never before known what it's like to be smoke. 

I wandered off to spend time with my thralls as I need to recover the energy I've lost with all the shapechanging I've been doing tonight. I truly believe that one day, I will be the spoon.

\parasep

Later that night after speaking with Laura I gathered the paperwork together and headed back to the research area. I found Jane's tent and see her searching for some papers. I strode in burdened with inglorious purpose. I placed the documents on her desk and stood there facing her. She looked straight at me for a moment then walked from the corner of the tent where she was searching. She looked down at the papers then back to me. Her face reddening.

``What in the blue fuck is this about? What did you do just lift these off the table when I wasn't looking? Who sent you? Colonel Joachim? The general is going to hear about this don't fucking move bitch'', said Jane.

She started moving toward the door of the tent but didn't any more than turn around before I caught her by the waist. She said, ``Get off m---''

I took her fast and pulled her close. My vampire vision came out and she was hypnotized. I could see her aura and life's blood, she was very strong in spirit. She was self sacrificing and relentless. She is very much the hero I hoped she would prove to be. I brought her lips to mine for an intimate kiss. 

This isn't what a person might assume. Venom is quite effective if deposited on the skin but works best if transferred through mucus membranes. The mouth is the most generally accepted target. Other areas vary from slightly more awkward to the kind of place that unless you are really into that person it's, well it's just wrong.

It's what has been called, ``The Kiss'' in the red court. We are actually wired to take down our prey with a kiss, it's in our genes, it excites us.

The moment seemed like an hour, I could feel her succumb to the effect in my arms and it was pulling me to the kill. I gently pulled away from her. I really didn't want to. Dear God that felt so good.

I said, ``You were confused about something hun, where do you say I'm from?''

She said, ``The red court---''

She gasped and wiped her brow from arousal, then leaned gently on her desk to help her keep on her feet. My mouth is drooling with hunger.

She said, ``Why? How are you still here? What are you going to do? Do you want to destroy the only chance these suffering people have to live? You god-forsaken vindictive creatures your empire falls in tatters and you take it out on the sick and helpless. We are going to kill whatever of you are left I swear to God if I'm gone others will come. If you succeed in killing our sick you can be sure we will give you a very painful death.''

She sighed in excitement. I wiped drool from my chin.

I said, ``I suppose that would be what you would think. That's actually not what I had in mi---''

She brushed her fingers through her hair, then threw her head back and moaned. She looked at me submissively and gasped. She said, ``Then what? What could a red possibly want besides revenge? What are you scheming? You damned creatures are always scheming. We are going to find out and we will stop you. Kill me if you like I will never help you, before you enthrall me I will kill myself you can never have me.''

She grabbed a letter opener from the desk, I caught her hand and it dropped. She sighed. I looked at her like someone who hasn't eaten for a week sees a smoked ham.

She said, ``Just take me. I can't handle this any longer I need you to take me. Just take me now.'' I swooped in for a bit but tore myself away just in time.

She said, ``What's the deal bitch? My blood not red enough for you?''

I said, ``Shut up Jane, ok? Just shut up. I hit you too hard with the venom although just enough given you have such fight. We are getting out of here see? We have somewhere to go. Look at me and tell me if you understand. We have to be quiet and not arouse others interest. Tell me you understand you can be sure I will know if you lie.''

She said, ``Not before you answer me this. I deserve to at least know what your intent is in this.''

I said, ``You said you need venom for the cure. I intend to get you the venom you need to cure all these and any others in need. I'm the only one who can do this for you and unless you chanced to meet another red and didn't tell me I think I may be your golden goose so don't you dare fuck this up for yourself.''

Her eyes were the size of golf balls, by her aura she seemed to accept what I'm saying. She was swaying, holding onto the desk. The venom is dangerously close to paralysing her, she looked intoxicated.

I said, ``Do you have some booze?''

She said, ``I think I'm under enough influence right now why would you need booze?''

I said, ``If there's something here for God sake just get it.''

She went to the back of the tent and in a pile of papers just beside a file cabinet she grabbed a mickey of whiskey in a paper bag.

I said, ``Perfect, let's go.''

We left the tent with her slumped over my shoulder half-paralysed with venom. I sprinkled some fine single malt over us and took the bottle of whiskey for a walk in plain sight. We passed people by as they shook their head in understanding. Two people passing us said, ``Yup. Told you. She's snapped. Working too hard for too long and I even heard the general has shut her down and reassigned her. Yup, that's what Dave told me yesterday. Seen it coming from afar.''

So we stumbled and dragged ourselves to the back quarter of the encampment close to the embankment. The sentries in this area are placed further up the embankment and all that's here are supplies, having already passed the ammunition tents. We found one that looks like it hasn't been touched in months. Inside it's still dry and there is metal shelving holding mostly used clothing, both civilian and military. I found a pile of exercise mats in the corner and took some to put Jane down on.

She said, ``So what's the deal, you going to camp out in this filthy place for me to milk venom? I can do better for you than this shithole nobody knows what you are and I'm not going to tell anyone. You're helping me help thousands who can't help themselves.''

I said, ``I really can't do that. The general is going to search for me if I go missing. He may not keep me in the encampment and eventually ship me out which I know for a fact he is going to do soon, he has already given me orders. I'm a journalist and need to go north eventually to find help and support among those who have it. Besides whatever arrangement you can make is eventually going to be found out anyway and sure as shit the fellowship is going to kill any red they find, probably also those who conspire with them most notably you in this case. Your patients lose not only hope but their most outstanding doctor. Using me to harvest venom is a losing proposition.''

She looked at me, ``You deceived me, I believed you. Why did I believe you? Now you have me here, I'm such a fool. You intended to kill me here to hide the evidence and use the drunken stagger from earlier tonight to make it think it was something I did in my drunken state. Fine go ahead and kill me, give me more venom and make me like it more. Bitch.''

I said, ``Oh no, I told no word of a lie, I do intend you will get the venom you need. Believe every word I told you. Just not from me''

She said, ``You aren't making sense, if you won't give venom then who---''

I said, ``You.''

At that last word I leapt like a tiger. I was on top of her in a split second and drowned her in a deep kiss. Her eyes went as deep as the ocean as waves of venom flowed through her. 

She said, ``No, please, no.'' and gasped. 

She threw her head back from pleasure and she said, ``Yes, Please. Yes''

I dove into her neck and fresh beautiful blood poured into me, my whole body quivered in a new way in response to my intent. Her body became cold and her eyes dead as glass. I shifted to my own true form, the bird form, and held her in my arms. She is quite dead. Inside my blood meal is stirring. I feel myself beginning to heave. My body is incubating my seed into my bloodmeal. The excitement is building in me as the moment comes. I lock my lips with hers and deliver our life back to her. I see her eyes open pure black. I wrapped my wings around her and held her tight. My seed is consuming her etheric body and looking down on her aura I can see that part of her die and the vampire take it's place. On the completion of the infection she releases a hiss for the first time. My first baby girl as a vampire. What will she be like? She didn't regain consciousness for an hour while I rocked her, or at least functioning. She laid there still, her eyes large and black and unblinking. Honestly, I thought my firstborn turned out a bit wrong until she spoke.

She said, ``Hungry. Want food.''

I said, ``I don't think you need food dear. I'll be here until you gain your senses and can decide that for yourself.''

She sniffed the air and looked around like an animal, ``Smells good, out there, there.'' and she pointed to the main area of the encampment.

I said, ``I know dear. It smells good.''

I sang a lullaby to try to take her mind off her hunger. After a while she said, ``Where am I?''

I said, ``Jane? Can you hear me?''

She said, ``Who, who are you? Where am I?''

I said, ``Jane my name is Susan, we are in a supplies tent at the back of the encampment.''

She said, ``Why? What am I doing out here? What's wrong with my eyes things look funny.''

I said, ``Stay with me a while. I'll look after you just relax Jane while things start to come together.''

She said, ``I feel a hunger, I've felt this before not so long ago. Something's wrong. Something's terribly wrong.''

I said, ``It's all wrong Jane, there ain't nothing right here.''

She said, ``That's damn straight. I'll take you up on it, I'll rest here a while.''

\parasep

She said, ``Bloodlust? Oh Christ I remember, you fucking whore goddammit you fucking turned me you fuck---''

She looked up at me, she said, ``Oh.''

I said, ``Yeah, oh.'' as I gave my wings a shake and tucked them behind.

She said, ``What team am I playing for now? What's the color?''

I told her of the events so far from \chichenitza* until now.

She said, ``Sounds like we used to be the red court.''

I said, ``Don't even say that. We have some red court genes.''

%scene - disaster
She said, ``I like that better. Still have the half turned stage as well, you left me half-turned.''

I said, ``I left it your choice what path you wanted to take from here. I feel it's your right to choose.''

She said, ``You're right, and you took that away when you didn't explain what you had in mind. I don't want to be back in the position of infected. No fellowship member would.''

I said, ``If I did you wouldn't have gone through with it, I know that.''

She said, ``You're right. We might have still found venom at some old encampment. Now it doesn't matter what's done is done. I understand your reasons. I want you to stay away from me. When you leave this place don't come back I don't want to see or hear from you again.''

At that she left. I hope this was the right choice; that I should turn her; that it was her who should be turned first; That she should have been turned at all. May God have mercy on us all if I have chosen wrongly.

